### 2017-11-26 draft.tex
Add files via upload

\documentclass[11pt]{amsart}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{showlabels}
\usepackage{amsthm}

\usepackage[english]{babel}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{faktor}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{tikz,tikz-cd}
\usepackage[all]{xy}
\usepackage{hyperref}

\newcommand{\M}[4]{\overline{\mathcal M}_{#1,#2}(#3,#4)}
\newcommand{\PP}{\mathbb P}
\newcommand{\OO}{\mathcal O}
\renewcommand{\to}{\rightarrow}
\newcommand{\A}{\mathcal A}
\newcommand{\B}{\mathcal B}
\newcommand{\X}{\mathcal X}
\newcommand{\XP}{\mathcal{XP}}
\renewcommand{\L}{\mathcal L}
\newcommand{\hL}{\hat{\mathcal L}}
\newcommand{\C}{\mathfrak C}
\newcommand{\cC}{\mathcal C}
\newcommand{\Z}{\mathcal Z}
\newcommand{\MM}{\mathfrak M}
\newcommand{\oM}{\overline{\mathcal M}}
\newcommand{\R}{\operatorname{R}}

\newcommand{\bq}{\begin{equation}}
\newcommand{\eq}{\end{equation}}
\newcommand{\ba}{\begin{aligned}}
\newcommand{\ea}{\end{aligned}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bsm}{\left(\begin{smallmatrix}}
\newcommand{\esm}{\end{smallmatrix}\right)}                   
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\barr}{\begin{displaymath}\begin{array}{cccc}}
\newcommand{\earr}{\end{array}\end{displaymath}}
\newcommand{\barrl}{\begin{displaymath}\begin{array}{lcl}}
\newcommand{\earrl}{\end{array}\end{displaymath}}
\newcommand{\barl}{\begin{displaymath}\begin{array}{l}}
\newcommand{\earl}{\end{array}\end{displaymath}}
\newcommand{\bxym}{ \begin{displaymath}\xymatrix }
\newcommand{\exym}{\end{displaymath}}
\newcommand{\bcd}{\begin{center}\begin{tikzcd}}
\newcommand{\ecd}{\end{tikzcd}\end{center}}

\newcommand{\tr}{{\rm tr}}
\newcommand{\Isom}{\text{Isom}}
\newcommand{\Spec}{\operatorname{Spec}}
\newcommand{\Pic}{\operatorname{Pic}}
\newcommand{\pr}{\operatorname{pr}}
\newcommand{\id}{{\rm id}}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{teo*}{Theorem}
\newtheorem{ipotesi}{ipotesi}
\newtheorem*{nota}{Nota}
\newtheorem{claim}{Claim}
\newtheorem{question}[thm]{Question}

\theoremstyle{definition}
\newtheorem{example}[thm]{Example}
\newtheorem{ex}[thm]{Example}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{com}[thm]{Comment}
\newtheorem{num}{Number}
\newtheorem*{sketch}{Sketch}
\newtheorem*{rem}{Remark}

\newcommand{\todo}[1]{\vspace{5mm}\par \noindent
\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}

\def\ti{-\allowhyphens}
\newcommand{\thismonth}{\ifcase\month % case 0 --- impossible!
  \or January\or February\or March\or April\or May\or June%
  \or July\or August\or September\or October\or November%
  \or December\fi}
\newcommand{\thismonthyear}{{\thismonth} {\number\year}}
\newcommand{\thisdaymonthyear}{{\number\day} {\thismonth} {\number\year}}

\title{Reduced GW invariants from cuspidal curves}
\author{L.Battistella, F.Carocci, C.Manolache}
\date{\today}
\begin{document}

\begin{abstract}
abstract
\end{abstract}

\maketitle

The moduli stack of stable maps to projective space is a fundamental object in Gromov-Witten theory, since any moduli space of maps to a (smooth) projective variety is cut inside that of the ambient projective space by a set of induced equations. Yet its structure in higher genus is still largely mysterious.

Recall that, in genus zero, $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension $\operatorname{vdim}=r-3+d(r+1)+n$ (we see that it is unobstructed from the fact that $H^1(\PP^1,f^*T_{\PP^r})=0$ for any map $f\colon\PP^1\to\PP^r$). Furthermore, for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$, the sheaf $\pi_*f^*E$ (where $\pi$ is the structure map of the universal curve and $f$ the universal stable map) is actually a vector bundle on $\M{0}{n}{\PP^r}{d}$.
\bcd
\mathcal C_{0,n}(\PP^r,d)\ar[r,"f"]\ar[d,"\pi"] & \PP^r\times \M{0}{n}{\PP^r}{d} \\
\M{0}{n}{\PP^r}{d} &
\ecd

It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that, if $i\colon X\to \PP^r$ is a complete intersection of degree $(l_1,\ldots,l_k)$ (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic) and we denote by $j$ the corresponding inclusion
$$\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}\hookrightarrow\M{0}{n}{\PP^r}{d}$$
then the following equality, expected by the interpretation of Chern classes as zero loci, holds:
$$j_*[\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}]^{\operatorname{vir}}=c_{\operatorname{top}}(E)\cap[\M{0}{n}{\PP^r}{d}].$$
This so-called ``hyperplane property'' allows us to compute GW invariants of complete intersections as twisted invariants on projective space.
The situation in higher genera is much more intricated: the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional; the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle. One of the reason for this (in fact the only reason in genus one) is that there are maps from reducible curves with a genus $g$ core that is contracted and some rational tails that carry all the degree; if $f\colon C\to \PP^r$ is such a map, then $H^1(C,f^*\mathcal O_{\PP^r}(1))\neq 0$, as can be easily deduced from the normalisation sequence.
\section{Genus one stable maps to $\PP^r$ - Equations, components and alternate compactifications}

\subsection{Local equations and components}

The geometry of the genus one moduli space of Kontsevich' stable maps to projective space $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre} and is by now well understood. Assume $d>0$. Let $E$ be a smooth genus one curve with a non-constant morphism $f\colon E\to \PP^r$; then $H^1(E,f^*T_{\PP^r})=0$ by Riemann-Roch, hence we may define the \emph{main component} of $\M{1}{n}{\PP^r}{d}$ as the closure of the locus of maps the source of which is a smooth genus one curve. It is irreducible of the expected dimension $\operatorname{vdim}=d(r+1)+n$. On the other hand, for every positive integer $k$ and partitions $\lambda$ of $d$ into $k$ (positive) parts and $\mu$ of $n$ into $k$ (positive) parts, consider the boundary component $D_{\lambda,\mu}(\PP^r,d)$ that is the closure of the locus where (i) the source curve is obtained by gluing a smooth elliptic curve with $k$ many $\PP^1$'s (as rational tails), (ii) the map contracts the core elliptic curve to a point, and (iii) the rational tail $R_i$ has degree $\lambda_i$ and $\mu_i$ many marked points. In fact $D_{\lambda,\mu}(\PP^r,d)$ is the image of the gluing morphism from the fiber product
$$\M{1}{k}{\PP^r}{0}\times_{\PP^r}\prod_{i=1}^k\M{0}{\mu_i+1}{\PP^r}{\lambda_i}.$$

\begin{prop}\label{prop:components}
\emph{(1)} The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{(\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\circ=\operatorname{main}\}$, i.e.
$$\M{1}{n}{\PP^r}{d}=\M{1}{n}{\PP^r}{d}^\circ\cup\bigcup_{\lambda,\mu}D_{\lambda,\mu}(\PP^r,d).$$

\emph{(2)} Let $(E {}_{p_1,\ldots,p_k}\sqcup_{q_1,\ldots,q_k}\bigsqcup_{i=1}^k R_i,f)$ be a degenerate stable map with $k$ rational tails; then it lies in the boundary of the main component if and only if $\operatorname{d}\!f(T_{q_i}R_i)$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
\end{prop}

In order to understand how the Gromov-Witten invariants differ from the naive expectation of counting smooth embedded genus $g$ curves in the given homology class, one needs to have a good understanding of the virtual fundamental class and of its splitting on the various components. 
This has led to the study of explicit local equation for the moduli space of stable maps in a smooth (over $\mathfrak M_{1,n}$) ambient space \cite{HL}, which we shall now briefly explain. Recall that a map from a scheme $C$ to projective $r$-space is the same as the datum of a line bundle $L$ on $C$ together with $r+1$ global sections in $H^0(C,L)$ that generate the line bundle at every point of $C$. Then it seems natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1,n}$. The problem is that this cone is not smooth, due to the jumps in fiber dimension at the boundary.
%(besides there is a small issue due to the $\mathbb G_m$ automorphism group of objects of $\mathfrak{P}_{1,n}$, which can be avoided by dishomogenising).

Let $[f\colon C\to \PP^r]$ be a point of $\M{1}{n}{\PP^r}{d}$; we may fix homogeneous coordinates on $\PP^r$ in a way that $D_0:=f^*\{X_0=0\}$ is a $d$-uple of smooth points on $C$ (i.e. \'{e}tale on the base) (this property will hold in a neighbourhood of $[f]$). This gives a map from (an \'{e}tale chart of) $\M{1}{n}{\PP^r}{d}$ to (an \'{e}tale chart of) the moduli space of pre-stable curves with a degree $d$ divisor $\mathfrak M_{1,n}^{\operatorname{div}=d}$, that we may assume to be landing in the locus where the divisor is composed by $d$ smooth distinct points (notice this locus is smooth over $\mathfrak M_{1,n}$ by the deformation theory of smooth subschemes). A morphism to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ global sections of $\mathcal O_C(D)$: the morphism can be written as $[1:u_1:\ldots:u_r]$, where $1$ is the image of the constant global section along the given map $\mathcal O_C\to\mathcal O_C(D)$ (i.e. we have taken dishomogenised local coordinates on $\PP^r$).

Furthermore, \'{e}tale locally on $\M{1}{n}{\PP^r}{d}$, we may pick extra sections $\mathcal A$ and $\mathcal B$ of $\mathcal C_{1,n}(\PP^r,d)$ such that (i) they pass through the core elliptic curve, and (ii) they are disjoint smooth points away from $\mathcal D_0$. Then $\pi_*\mathcal L(\mathcal A)$ \emph{is} a vector bundle on $\mathfrak P_{1,n}$ and $\pi_*\mathcal L$ is carved inside it by requiring that the restriction (residue) map $\pi_*\mathcal L(\mathcal A)\to\pi_*\mathcal L(\mathcal A)_{|\mathcal A}$ is zero.

\begin{prop}
\emph{(1)} \'{E}tale locally, there is a locally closed imbedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V_1:=\operatorname{Spec}(\pi_*\mathcal L(\A)^{\oplus r})$ over $\mathfrak M_{1,n}^{\operatorname{div}=d}$. It is obtained by imposing the nondegeneracy and stability conditions \emph{(open)} on the vanishing locus of the restriction of the universal section of $\pi_*\mathcal L(\A)^{\oplus r}$ to $\A$ \emph{(closed)}.

\emph{(2)} Let $\mathcal V$ be an (affine local) \'{e}tale chart around a smooth point of $\mathfrak M_{1,n}^{\operatorname{div}=d}$. Then $\pi_*\mathcal L(\A)\cong \pi_*\mathcal L(\A-\B)\oplus \pi_*\mathcal \mathcal L(\A)_{|\B}$ (trivially, $\mathcal O_{\mathcal V}^{\oplus d+1}\cong\mathcal O_{\mathcal V}^{\oplus d}\oplus\mathcal O_{\mathcal V}$) and the restriction-to-$\A$ map is zero on the second factor. Call $\varphi\colon \pi_*\mathcal L(\A-\B)\to\pi_*\mathcal L(\A)_{|\A}$ the induced  restriction to $\A$.

\emph{(3)} If we choose a suitable basis of $\pi_*\mathcal L(\A-\B)$, the restriction-to-$\A$ map can be written in a very explicit form: let $D=\sum_{i=1}^d\delta_i$, then $\pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B)$ is a sub-line bundle of $\pi_*\mathcal L(\A-\B)$ and $\varphi=\oplus\varphi_i\colon\oplus_{i=1}^d \pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B)\to \pi_*\mathcal L(\A)_{|\A}.$ Furthermore $\varphi_i\colon\mathcal O_\mathcal V\to\mathcal O_\mathcal V$ is given (up to invertibles) by multiplication by $\prod_{q\in[\A,\delta_i]}\zeta_q$, where $\zeta_q$ is the smoothening variable on $\mathfrak M_1$ corresponding to the node $q$, and $q\in[a,\delta_i]$ stands for all the nodes separating $\A$ (i.e. the core elliptic curve) from the point $\delta_i$.
\end{prop}

Given these explicit equations and by carefully examining the proof of \cite[Prop. 4.13]{HL}, we can look back at the problem of determining the boundary of the main component of the space of stable maps. The following characterisation of smoothability was already known to (and partly proven in) \cite[Lem. 5.9]{Vre}.

\begin{prop}\label{smoothability_with_eqn}
Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree). The following are equivalent:
\begin{enumerate}
\item $[f]$ is smoothable;
\item $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$;
\end{enumerate}
\end{prop}
\begin{proof}
 Let us start with the easiest degenerate situation: a contracted elliptic curve joined with a rational tail of degree $d$ at a single node $q$. Equations for the moduli space of maps around such a point look like $\zeta_q\sum_{i=1}^d w_i^j=0$, for $j=1,\ldots,r$, the $w_i$'s being coordinates for $\pi_*\mathcal O_{\mathfrak C}(D+\A-\B)$ in the basis given by $\pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B),\ i=1,\ldots,d$. Our point corresponds to a smoothable map if and only if the equations admit a solution with $\zeta_q\neq 0$, hence it must be $\sum_{i=1}^d w_i^j=0$ for every $j$. Taking a coordinate $z$ on the rational tail around the node $q$ (i.e. $\{z=0\}$ corresponds to the node), we see that the $i$-th vector in the chosen basis corresponds to a polynomial vanishing at the node and at every other point $\delta_j,\ j\neq i$; hence that can be written as $e_i(z)=z\prod_{j\neq i}\frac{(z-\delta_j)}{-\delta_j}$ (we chose a convenient normalisation). So the map corresponding to the point of coordinates $(w_i^j)_{i=1,\ldots,d;j=1,\ldots,r}$ can be represented as $[1:\sum_{i=1}^d w_i^1e_i(z):\ldots,\sum_{i=1}^d w_i^re_i(z)]$ on the rational tail; differentiating we see that the tangent vector at the node is sent to $(\sum_{i=1}^d w_i^1,\ldots,\sum_{i=1}^d w_i^r)$ (in affine coordinates), hence smoothability is equivalent to the image of the tangent vector being zero.

 More generally, we may assume the dual graph is terminally weighted. Let us say there are $m$ positive-weight rational tails and denote by $D(k),\ k=1,\ldots,m,$ the set of indices $j$ s.t. $\delta_j$ belongs to the $k$-th rational tail, by $E(k)$ the set of nodes separating the core genus one curve from the $k$-th rational tail. The equations have then the following form
 $$\sum_{k=1}^m(\prod_{q\in E(k)}\zeta_q)(\sum_{i\in D(k)}w_i^j)=0,\ j=1,\ldots,r$$
 which can be assembled in matrix form
 $$W\cdot\underline\zeta:=(\sum_{i\in D(k)}w_i^j)_{j,k}\cdot(\prod_{q\in E(k)}\zeta_q)_k=0.$$
 We see that smoothability is equivalent to linear dependence of the rows of the above matrix $W$. On the other hand, on every positive-weight rational tail $R_k$, we can choose a suitable coordinate $z_k$ around the node and write the map as $[1:p_k^1(z_k):\ldots:p_k^r(z_k)]$, where $p_k^j(z_k)=\sum_{i\in D(k)}w_i^je_i^k(z_k)$ and $e_i^k(z_k)=z_k\prod_{h\in D(k)\setminus\{i\}}\frac{(z_k-\delta_h)}{-\delta_h}$. The elliptic curve is contracted to the point $[1:0:\ldots:0]$ and the tangent vector to $R_k$ at the node is mapped to the $k$-th row of $W$ (in affine coordinates around that point). Again we see that the map is smoothable if and only if the image of the tangent vectors to the rational tails at the nodes are linearly dependent in $T_{f(E)}\PP^r$.
 \begin{comment}{
 Let us now address the equivalence of (1) and (3). Assume that we have a smoothing of a degenerate map $f_0\colon C_0\to\PP^r$
 \bcd
 \mathcal C\ar[d,"\pi"]\ar[r,"f"] & \PP^r\times S \\
 S &
 \ecd
 We may assume that $S$ is a DVR scheme. The line bundle $\mathcal L=f^*\mathcal O_{\PP^r}(1)\otimes\omega^{log}_{\mathcal C/S}$ is $S$-semiample: trivial on a subcurve of $C_0$ of arithmetic genus one, and ample everywhere else. Let's note that $\mathcal L$ is of  the form $\mathcal L=\omega_{\mathcal C/S}(E+\Sigma)$, where $E$ is the contracted genus 1 curve and $\Sigma$ is a Cartier divisor supported away from $E$. It follows from Smyth's contraction lemma \cite[Lemma 2.13]{SMY2} that $\mathcal L$ can be used to produce a smoothing family $\mathcal C'$ of a genus 1 Gorenstein singularity. The relative $\mathcal O(1)$ of the Proj construction defines a compatible morphism to $\PP^r$
 \bcd
 \mathcal C\ar[rr,"f"]\ar[dr]\ar[dd,"\pi"] & & \PP^r\times S\\
 & \mathcal C'=\underline{\operatorname{Proj}}_S(\sum_{n\geq 0}H^0(\mathcal C,\mathcal L^n)) \ar[ld,"\pi'"]\ar[ru,dashed,"f'"] & \\
 S & & 
 \ecd
Expressed in terms of $(2)$, we are saying that having dependent tangent vectors corresponds to the fact that the sections of $\mathcal L$ which define the morphism to $\PP^r$ descend to section on the Goreinstein singularity.
 Viceversa, assume $f_0$ factors through a Gorenstein singularity of genus one such that $f_0'\colon C_0'\to\PP^r$ is nondegenerate (i.e. it does not contract all the branches of the singularity). We can pick compatible smoothings of $C_0$ and $C_0'$:  
 \bcd
 \mathcal C\ar[rr,"\phi"]\ar[dr,"\pi" below=.1cm] & & \mathcal C'\ar[dl,"\pi'"]\\
 & S &
 \ecd
 The line bundle $L_0'=(f_0')^*\mathcal O_{\PP^r}(1)$ can be extended to a line bundle $\mathcal L'$ on $\mathcal C'$ because the Picard scheme for curves is unobstructed (and general theory of algebraisation of coherent sheaves on projective varieties); furthermore, the sections $u^0_0,\ldots,u^r_0$ can be extended to $\mathcal C'$ because $H^1(C_0',L_0')=0$ by Serre duality, the fact that $L_0'$ has positive degree on at least one of the branches of the singularity, and the fact that the dualising sheaf is trivial. Composing the resulting map $\mathcal C'\to \PP^r\times S$ with $\phi$ proves the desired smoothability of the original map.}
 \end{comment}
 \end{proof}

\subsection{Viscardi's compactifications}
For any homology class $\beta\in H_2(X,\mathbb Z)$, let $\mathcal M_{1,n}(X,\beta)$ be the stack of maps $f\colon C\to X$ from a smooth genus one curve with $n$ marked points, satisfying  $f_{*}\left [C\right ]=\beta$. The $m$-stable maps give compactifications of such a moduli space.
  \begin{dfn} Let $C$ be a reduced, connected, proper curve of arithmetic genus one, and let $p_1,\dots,p_n\in C$ be smooth, distinct points. A map $f\colon C\to X$ is said to be \emph{$m$-stable} if the following conditions hold:
\begin{enumerate}
 \item $C$ has only nodes and elliptic $l$-fold points, $l\leq m$, as singularities.
 \item For any connected subcurve $E\subset C$ of arithmetic genus one on which $f$ is constant, 
 \[|\left\{E\cap \overline{C\setminus E}\right\}\cup\left\{p_i : p_i \in E\right\}| > m.\]
 \item $f$ has no non-trivial infinitesimal automorphisms.
 \end{enumerate}
\end{dfn}
Recall that a $k$-rational $p\in C$ is called an \emph{elliptic $m$-fold point} if 
\[
\hat{\mathcal{O}}_{C,p}\cong
\begin{cases}
k[[x,y]]/(y^2-x^3) & \textit{if } m=1\\
k[[x,y]]/(x(x-y^2))& \textit{if } m=2\\
k[[x,y]]/ I_m & \textit{if } m\geq 3
\end{cases}
\] 
where $I_m=(x_hx_i-x_hx_j : i,j,h\in\left\{1,\dots,m-1\right\})$ and $i,j,h$ are distinct.

The definition of a family of $m$-stable maps is then the natural one and Viscardi's main result \cite[Thm. 3.6]{VISC} is that the associated moduli functor gives a compactification of $\mathcal M_{1,n}(X,\beta)$ (alternative to Kontsevich' moduli space).
\begin{thm}
The moduli functor of $m$-stable maps in a fixed homology class $\overline{\mathcal{M}}^m_{1,n}(X,\beta)$ is represented by a proper DM stack of finite type.
\end{thm}
\begin{remark}\label{remark:sprouting}
It seems to us that the algorithm presented by Viscardi to prove properness of the moduli space oversees a case. The problem is that, given a map $f\colon C\to\PP^r$ with $f$ constant on a genus one connected sub-curve $E\subseteq C$, it is not always true that $f$ descends to a map $f'\colon C'\to\PP^r$, where $C'$ is the singularity obtained from $C$ by contracting $E$. Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero. A counterexample is the following.

Consider the stable map $[f]$ in $\overline{\mathcal M}_{1,0}(\PP^3,4)$ from an elliptic bridge $R_1\sqcup_{q_1}E\sqcup_{q_2} R_2$ to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e. its image is the non-Gorenstein singularity $C:=\mathbb C[x,y,z]/(x,y)\cap (z,y^2-x^3)$. 
Notice that $\operatorname{d}\!f(T_{q_2}R_2)=0$, so there is a non-trivial linear relation
\[0\cdot\operatorname{d}\!f(T_{q_1}R_1+1\cdot\operatorname{d}\!f(T_{q_2}R_2)=0\] and the map is smoothable; however, it is impossible to make the first coefficient non-zero and the map \emph{does not factorise} through an elliptic $m$-fold singularity. Indeed, the only chance would be to factorise through a birational map $f'\colon C'\to C$ from a tacnodal singularity $C'$. This is impossible since $C$ and $C'$ have the same $\delta$ invariant and so $f'$ would actually be an isomorphism. 
Observe that Viscardi suggests that the map should extend to the contraction, in a way that the image should still be $C$, since there is only one indeterminacy point (the singularity). We suggest that in this case the correct procedure would be to sprout $(R_1,q_1)$, but then there is actually no factorisation.

\begin{center}
\includegraphics[width=10cm,height=5cm]{cusp_line_transv.png}
\end{center}

However, the argument can easily be fixed. Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $S$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}. 
As described in \cite[Step~1, Theorem~3.6]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_S\to\PP^r_{S}$, for which we may suppose that $C_0$ is nodal and $f:=F_0$ is stable.

If $f$ is not constant on the minimal genus one sub-curve \cite{SMY1}, then it is also $m$-stable and there is nothing to say. Otherwise, let $E\subset C$ be the maximal connected genus one sub-curve where $f$ is constant and let $R_1\sqcup\dots\sqcup R_m=\overline{C/E}$.
 By Proposition~\ref{prop:components}(2) we know there is a non-trivial linear relation among the $\operatorname{d}\!f(T_{q_i}R_i)$'s.
 %In other words, the first derivatives of the sections $s_0,\dots,s_r$ defining $f$, satisfy a non trivial linear relation around $q_1,\dots,q_m =E\cup\bar{C/E}$.
 There are two possible situations:
 \begin{enumerate}
 \item $\operatorname{d}\!f(T_{q_i}R_i)\neq 0$ for every $i=1,\ldots,m$. Possibly after relabelling, this non-trivial relation looks like
 \[\alpha_1\operatorname{d}\!f(T_{q_{1}}R_{1})+\ldots +\alpha_j \operatorname{d}\!f(T_{q_{j}}R_{j})=0\]
  with all the coefficients being non-zero. Then, we may blow-up $\mathcal{C}$ in $q_{j+1},\ldots, q_m$. The induced map $\tilde{F_0}$ is constant on the exceptional divisors $E_{j+1},\ldots, E_m$, so we can complete the above linear relation to 
 \[\alpha_1\operatorname{d}\!\tilde f(T_{q_{1}}\tilde R_{1})+\ldots +\alpha_j \operatorname{d}\!\tilde f(T_{q_{j}}\tilde R_{j})+\beta_{j+1}\operatorname{d}\!\tilde f(T_{q_{j+1}}E_{j+1})+\ldots+\beta_m\operatorname{d}\!\tilde f(T_{q_{m}}E_m)=0\]
  with any choice of non-zero coefficients $\beta$. Now this \emph{sprouting} \cite[Section 2.3]{SMY2} ensures that the sections descend to the corresponding elliptic $m$-fold singularity. At this point, go to Step~2 of Viscardi's algorithm and follow it.
\item  
$\operatorname{d}\!f(T_{q_i}R_i)=0$ for some $i$, say for $i\in\left\{1,\dots,j\right\}$. 
 Then blow-up $\mathcal{C}$ at $q_{j+1},\ldots, q_m$. Observe that all $\operatorname{d}\!\tilde f(T_{q_i}R_i),\ i=1,\ldots,j$ and $\operatorname{d}\!\tilde f(T_{q_i}E_i),\ i=j+1,\ldots,m$ vanish, hence they satisfy any linear relation with non-zero coefficients, and they factorise through the corresponding singularity. The map has positive degree on the first $i=1,\ldots,j$ branches.
 \end{enumerate}
\end{remark}

The irreducible components of Viscardi's moduli space $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ are well understood too \cite[Thm.~5.9]{VISC}; indeed they have a similar description to the ones of Kontsevich' space. The main advantage of the $m$-stable compactification is that the number of components drops as $m$ increases.
 \begin{cor}\cite[Cor.~5.10]{VISC}
 For $m\geq\operatorname{min}(r,d)+n$, $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ is irreducible.
 \end{cor}

 Moreover, inspired by Viscardi's alternate compactification, we express a sufficient condition for smoothability in yet another way.
 \begin{prop}
Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree). 
 If $f$ factorises through a \emph{non-degenerate} (i.e. having positive degree along at least one of the branches of the singularity) map $f'\colon C'\to\PP^r$ from an elliptic $k$-fold singularity, with $k\leq m$, then  $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$.
 \end{prop}
 \begin{proof}
 Let $\xymatrix{C\ar[r]^{\pi} &C'\ar[r]^{f'} &\PP^r}$ be the factorization of $f$. Then $E'=\operatorname{Exc}(\pi)\subseteq E$ and 
  $\overline{C\setminus E'}=(S_1,q'_1)\sqcup\dots\sqcup (S_k,q'_k)\to (C',p)$ 
  is the normalization of the elliptic $k$-fold point. By hypothesis, $f=f'\circ\pi$ and $f$ is non-constant on $R_1,\dots R_m.$ Being $f'$ non-degenerate implies that there exists a subset
  $\left\{S_1,\ldots S_j\right\}\subseteq\left\{S_1,\ldots S_k\right\}$ 
  such that \[(S_1,q'_1)\cong (R_{i_1}, q_{i_1}),\ldots, (S_j,q'_j)\cong (R_{i_j}, q_{i_j}),\;\;\left\{i_1,\dots,i_j\right\}\subseteq \left\{1,\dots,m\right\}.\] 
By Smyth's characterisation of elliptic $k$-fold singularities, \cite[Lem.~2.2]{SMY1}, we obtain a non trivial linear relation 
  \begin{equation*}
  \label{eq:dep}\alpha_1\operatorname{d}\!\pi(T_{q_{i_1}}R_{i_1})+\ldots+\alpha_j \operatorname{d}\!\pi(T_{q_{i_j}}R_{i_j})+\alpha_{j+1}\operatorname{d}\!\pi(T_{q_{j+1}}S_{j+1})+\ldots+\alpha_k \operatorname{d}\!\pi(T_{q_k}S_k)=0
  \end{equation*}
  since all the coefficients are non-zero, $j\neq0$, and the second half of the formula can be ignored, we've got what we wanted.
  \end{proof}
\begin{rem}\label{remark:cuspunionline} 
The viceversa is not true, as Remark \ref{remark:sprouting} shows.
\end{rem}

In order to achieve the original goal of Gromov-Witten theory, i.e. the enumeration of smooth curves of genus $g$ in a target variety, mathematicians have been trying either to eliminate the unwanted components of Kontsevich's space (e.g. degenerate contributions from lower genus curves and multiple covers of lower degree curves) by defining alternate compactifications, or to concentrate the attention on the main component (i.e. find a suitable fundamental class supported on it). In genus one, Vakil and Zinger managed to do so by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}). The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc. and taking the fiber product
\bcd
\widetilde{\mathcal M}_{1,n}(\PP^r,d)\ar[r]\ar[d] & \M{1}{n}{\PP^r}{d}\ar[d] \\
\widetilde {\mathfrak M}_{1,n}^{\operatorname{wt}=d} \ar[r] & \mathfrak M_{1,n}^{\operatorname{wt}=d}
\ecd
the strict transform of the main component becomes smooth and meets the rest of the components in normal crossing fashion (the \'{e}tale local model being the union of two linear subspaces of different dimensions in affine space). Furthermore, the sheaves $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ contain a vector subbundle of rank $dl$ supported on the strict transform of the main component. This paved the way to the definition of reduced invariants.
\begin{dfn}
Let $X$ be a complete intersection of degree $(l_1,\ldots,l_k)$ in $\PP^r$. The genus one \emph{reduced} Gromov-Witten invariants of $X$ are defined by integration on $$[\widetilde{\mathcal M}_{1,n}(\PP^r,d)^\circ]\cap c_{\operatorname{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i))^\circ).$$
\end{dfn}

It is a matter of fact that the virtual dimension of the moduli space of maps to a three-fold $X$ is independent of the genus. In this context it was plausible to test the better enumerative properties of reduced invariants; in fact, Li-Zinger \cite{LZ} in the symplectic category and, later on, Chang-Li \cite{CL} in the algebraic one, proved a comparison formula for the quintic three-fold $X_5\subseteq\PP^4$ (or, more generally, for a complete intersection three-fold $X$ of degree $(l_1,\ldots,l_k)$ in $\PP^r$ with $\sum l_i\leq r+1$) of the form
$$GW_1(X)=\widetilde{GW}_1(X)+c\cdot GW_0(X).$$
We notice that the genus zero contribution to this formula comes from the boundary component with a single rational tail of degree $d$, while elliptic bridges and degenerate contributions with more rational tails do not matter to the genus one Gromov-Witten count. This suggests that removing the component with elliptic tails would provide a more direct and efficient definition of reduced invariants. We plan to do so by comparing the ordinary space of stable maps with Viscardi's space of 1-stable maps.

\section{Cuspidal curves and maps}

In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal. We will see how in this case we can give a comparison with the GW-invariant and explain why the same technique does not work for higher $m$.
The first thing we do is the following:
we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves. We show that there is a birational morphism from a correspondingly decorated moduli space of prestable nodal curves. Taking the fiber product with Viscardi's moduli space of stable cuspidal maps, we show that the resulting space includes in the usual Kontsevich's moduli space, precisely avoiding the component with elliptic tails $D_{\{d\},\{n\}}(X,d)$.

Why should such a morphism on decorated prestable curves exist? 
Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node. In the first case we can associate to this the locally constant family of cusps obtained by forgetting the elliptic tail and contracting a length-two infinitesimal neighborhood of the node in the rational component; in the second case, we claim that the line bundle $\mathcal O_\mathcal C(3q)$ gives a morphism to a smoothing of the cuspidal $\PP^1$. This heuristics (i.e. being able to substitute an elliptic tail with a cusp over points or DVR schemes) motivates us to believe we can define a morphism from suitably defined moduli spaces of nodal genus one curves to cuspidal curves (cfr. \cite[Lemma 4.2]{SMY2}). In fact we shall extend \cite[Corollary 4.5]{SMY2} to an appropriate setup of moduli stacks of weighted prestable curves. Assume $d>0$ throughout the following.

\begin{dfn}
Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ be the stack of \emph{prestable} (projective, nodal and reduced), connected, arithmetic genus one, $n$-marked curves that are \emph{stably weighted} with total weight $d$, i.e. for every geometric point there is an integer-valued function on the set of irreducible components of the corresponding curve, such that it is compatible with specialisation maps and the sum of the integers is $d$; furthermore we require that all integers are nonnegative and every $p_a=0$ weight-0 component has at least three special points (every $p_a=1$ weight-0 component has at least one special point).
\end{dfn}
Remark that there is an \'{e}tale, non-separated morphism $\mathfrak M_{1,n}^{\operatorname{wt}}\to\mathfrak M_{1,n}$ and the weight stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factorises through $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.

\begin{dfn}
Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective, reduced, connected, arithmetic genus one, $n$-marked curves that are stably weighted with total weight $d$, i.e. as above with (stricter) stability condition: every $p_a=0$ weight-0 component has at least three special points (every $p_a=1$ weight-0 component has at least \emph{two} special point) \emph{and} every weight-0 cusp has at least two further special points.
\end{dfn}

Note that the only type of nodal curves that we are getting rid of is the one with an elliptic tail of weight zero.

\begin{thm}
There exists a morphism $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ which extends the identity on the smooth locus.
\end{thm} 
Since it is hard to define such a map on an arbitrary base, we proceed as follows. Let $\mathcal C$ and $\mathcal C'$ be the universal curves over $\mathfrak{M}:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ and $\mathfrak{M}':=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ respectively. Abusing notation slightly, we will still write $\mathcal C$ and $\mathcal C'$ for their pullbacks to the product $\mathfrak{M}\times\mathfrak{M}'$ along the two projections. The proof of the theorem follows from two Lemmas:

\begin{lem}\label{lemma:def_X}
 There is a locally closed substack $\mathcal X\subseteq\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ representing morphisms $C\to C'$ that contract weight-zero elliptic tails to cusps and are weight-preserving isomorphisms everywhere else. 
\end{lem}

\begin{lem}\label{lamma:projection_iso}
 The first projection $\pr_1\colon \operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')\to\mathfrak M$ restricted to $\mathcal X$ is an isomorphism with $\mathfrak M$.
\end{lem}

\begin{proof}\ref{lemma:def_X}
Recall that $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ is an algebraic stack; in fact the map to $\mathfrak{M}\times\mathfrak{M}'$ is representable by Grothendieck's theory of the Hilbert scheme for projective morphisms. We now proceed to construct $\mathcal X$ as a locally closed substack in the space of morphisms.

\begin{description}[labelindent=0cm,leftmargin=\parindent]

\item[Step 1] Consider
 \[\pi\colon\mathfrak{P}=\mathfrak{Pic}^{tot deg=d,st}_{1,n}\to\mathfrak{M},\ \pi'\colon\mathfrak{P}'=\mathfrak{Pic}^{tot deg=d,st}_{1,n}(1)\to\mathfrak{M}'\]
  the Picard stacks on $\mathfrak{M}$ and $\mathfrak{M'}$ with universal line bundles $\mathfrak{L}$ and $\mathfrak{L'}$, where $\pi$ and $\pi'$ are defined by taking the multi-degree of line bundles. We can now look at the algebraic stack $\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$ with universal morphism
 $\Phi$ and natural projection $\Pi$ to $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$. We claim that there exists a locally closed substack $\mathcal{Y'}\subseteq \operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$ representing those morphisms that \emph{preserve the line bundles}. Indeed, given a chart 
 \begin{equation}\label{equation:Spoints} 
 S\to\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C'),
  \end{equation} 
   the locus of $s\in S$ where $\Phi_s^*\mathfrak{L}'_s\cong\mathfrak{L}_s$ is nothing else than the locus $T$ where the two sections $\mathfrak{L}_S$ and $\Phi_S^*\mathfrak{L}'_S$ of $\mathfrak{P}(S)\to\mathfrak{M}(S)$ induced by \ref{equation:Spoints} coincide. In other words, we are looking for the fiber product 
  \[\xymatrix{T\ar[r]\ar[d]&\mathfrak{P}\ar[d]^{\Delta}\\
  S\ar[r]&\mathfrak{P}\times_{\mathfrak{M}}\mathfrak{P}}\]
Being $\mathfrak{P}\to\mathfrak{M}$ representable by schemes, it follows that $U\to S$ is a locally closed immersion.

\item[Step 2] 
Furthermore, there is a closed substack $\mathcal Y\subseteq \mathcal Y'$ representing \emph{surjective morphisms that preserve the markings}.

Given a chart $S\to\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$, the locus of $s\in S$ where $\Phi_s$ is marking-preserving is the equaliser of the two sections
\bcd
S \ar[r,shift left, "\times\sigma_i'" above]\ar[r,shift right,"\times\Phi\circ\sigma_i" below] & \mathcal C_S'\times_S\ldots\times_S \mathcal C_S'
\ecd
This defines a closed subscheme of $S$, since $\mathcal C_S'\to S$ is separated.

As regards surjectivity, since $\Phi$ is proper, and by upper semicontinuity of the dimension of the fiber \cite[\href{http://stacks.math.columbia.edu/tag/0D4I}{Tag 0D4I}]{stacks-project}, the locus in $\mathcal C_S'$ where the fiber of $\Phi$ is empty is open. The complement of its image in $S$ is the locus we were after.

\item[Step 3] Let $\mathcal{X}'$ be the image of $\mathcal Y$ under $\Pi$. This is a constructible substack of $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ by Chevalley's theorem \cite[\href{http://stacks.math.columbia.edu/tag/054K}{Tag 054K}]{stacks-project}. Recall that, to show that a constructioble set is open (respectively closed), it is enough to check that it contains all the generisations of its points (respectively all the specialisations) \cite[\href{http://stacks.math.columbia.edu/tag/0903}{Tag 0903}]{stacks-project}. Finally, under Noetherian assumptions, two points related by specialisation/generisation are contained in the image of a DVR scheme \cite[\href{http://stacks.math.columbia.edu/tag/054F}{Tag 054F}]{stacks-project}.

It is clear that being surjective and marking-preserving are closed conditions, as above. The requirement that $\phi$ can be covered by a line bundle-preserving map can be translated into the following combinatorial conditions:

\begin{enumerate}
\item\emph{$\phi$ contracts only weight zero components.} We show that this is open. Assume that $S$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $S\to\mathcal X'$ such that $\phi_0\colon\mathcal C_0\to \mathcal C_0'$ does not contract any positive weight component. Suppose, by contradiction, that there exists an irreducible component $W\subseteq C_{\eta}$ of positive weight $d_W$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e. $\left\{c\in \mathcal{C}_{S} | \dim_c\phi^{-1}(\phi(c))=1\right\}$, is closed by semicontinuity of fiber dimension and contains all the components $D_i\subseteq C_0$ to which $D$ specialises; at least one of them must have positive weight, since the sum of their weights is $d_W$, which is a contradiction.

\item\emph{$\phi$ has degree 1 on every non contracted component}, or, equivalently, there is an $S$-dense open in $\mathcal C'_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
This is an open and closed condition; we show it is open. Let $S$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property. We may assume that $S$ is the local ring at $0$ of a smooth projective curve $\bar S$ \cite[Thm. I.6.9]{HAR} and that $S\to\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ extends to $\bar S$ (by the valuative criterion of properness). \marginpar{FIX ME: properness seems to fail, but we don't need to extend to $\bar S$ to use Fulton's intersection theory} Let us now write $\phi_{\bar S,*}[\mathcal C_{\bar S}]=\sum n_i[\mathcal C'_{\bar S,i}]$; by Gysin pull-back to $0$ and \cite[Prop. 10.1(a)]{FUL}, we see that all the $n_i$'s are 1, apart from some that involve components of $\mathcal C'_{\bar S}$ away from $0$. Discarding these, we find an open neighborhood of $0$ such that the restriction of the morphism to every closed point in the base is birational in our sense, i.e. we find a $\bar S$-dense (around $0$) open in $\mathcal C'_{\bar S}$ on which $\phi$ gives an isomorphism, hence $\phi_\eta$ also satisfies the property.

\item\emph{$\phi$ is weight-preserving.} This is again an open condition: assume that $\phi_0$ is weight-preserving; the existence of $\phi_S$ implies that the maps $\tilde \phi_0$ and $\tilde\phi_\eta$ (induced at the level of weighted dual graphs) are compatible with the specialisation maps. Since the weight of a component of the generic fiber is determined by those of the components to which it specialises, this proves that $\phi_\eta$ must be weight-preserving as well.
\end{enumerate}

\item[Step 4] We have seen that, if $\phi$ contracts a component $E$ of the fiber, it must have zero weight. Then it has to be elliptic by the stability condition. Since the target has only nodes and cusps as singularities, it must be $|\overline{C\setminus E}\cap E|\leq 2$, i.e. $E$ is either an elliptic tail or an elliptic bridge. There are basically two possibilities:
(a) the elliptic tail gets contracted to a cusp, or $\phi$ is an isomorphism everywhere; (b) the elliptic tail/bridge gets contracted to a smooth point or node, then a non-separating node or a cusp must be created somewhere else in order to preserve the genus. 
We want to get rid of case (b), so we define the open substack $\mathcal X\subseteq \mathcal X'$ as follows.
Given $\mathcal{C}_S\to\mathcal C_S'\in\mathcal X'(S)$, let $U'\subseteq \mathcal C'$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U')}\colon\phi_S^{-1}(U')\to U'$ is an isomorphism and $Z'$ its closed complement in $\mathcal C_S'$. 
Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055D}{Tag 055D}, \href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(Z')}\colon \phi^{-1}(Z')\to S$ are geometrically connected.
\end{description} 
 \end{proof}

 \begin{proof}\ref{lamma:projection_iso}
 This result will follow from an application of Zariski's Main Theorem for algebraic spaces.
First of all, we claim that the projection is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points; hence we are just saying that
$\operatorname{Aut}(\phi)\subseteq\operatorname{Aut}(C).$ 
 This follows from the fact that, if $\phi\in\mathcal X$, then it is dominant and of degree one.
Secondly, $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion
\bcd
\eta=\Spec(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
S=\Spec(R)\ar[r] & \mathfrak M
\ecd
Let $\pi \colon \mathcal C_S\to S$ be the family of nodal curves on $S$; there are three cases to consider:
\begin{enumerate}
\item the central fiber contains no elliptic tail, then so does $\mathcal C_\eta$, hence $\phi_\eta$ 
\marginpar{\begin{color}{red} It's right but confusing! Write it better!!!\end{color}}is an isomorphism and admits a unique extension to an isomorphism $\phi\colon \mathcal C_S\cong \mathcal C_S'.$

\end{enumerate}
If instead $\mathcal C_0$ has got an elliptic tail, then we have two possibilities:
\begin{enumerate}
\setcounter{enumi}{1}
\item $\mathcal C_{\eta}$ still has an elliptic tail, i.e. the node separating the weight zero, genus one curve from the rest of $\mathcal C_S$ is not smoothened. Then $\mathcal C_S$ is the push-out of a family of rational curves $\mathcal R_S$ and a family of genus one curves $\mathcal Z_S$.
%The map $S\to\partial \mathfrak M_{1,n}$ lifts to the normalisation of the boundary, i.e. $\mathfrak M_{0,n_0+1}\times\mathfrak M_{1,n_1+1}$, which gives two families of pointed curves on $S$; there is a map from the push-out to $\mathcal C_S$ by the universal property, and it is proper bijective and flat (crit\`{e}re de platitude par fibres \cite[\href{http://stacks.math.columbia.edu/tag/039A}{Tag 039A}]{stacks-project}).
\bcd
S\ar[d]\ar[r] & \mathcal R_S \ar[d] \\
\mathcal Z_S\ar[r] & \mathcal C_S
\ecd
\marginpar{\begin{color}{red} Before writing the push down diagram we might need to change base. Write down the double push-out diagram\end{color}}
Locally around the node, $\phi_{\eta}$ is the contraction of the elliptic curve to the cusp, and, on the adjacent rational component, it is the normalisation of the cusp; by the universal property of push-outs, it can be uniquely extended to the same map on the central fiber (far from this node, $\phi_\eta$ is an isomorphism).
\item If $\mathcal C_S$ smoothens the elliptic tail, then the map is given on the generic fiber by a $\pi$-ample line bundle $\mathcal L_{\eta}$. Then the extension to the central fiber is determined by the unique extension $\mathcal L_0$ of $\mathcal L_{\eta}$ which is trivial on the minimal subcurve $Z\subseteq \mathcal C_0$ of arithmetic genus 1 and, possibly after twisting, is ample elsewhere. 
\end{enumerate}
Finally, observe that the map is bijective by construction and $\mathfrak M$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \mathfrak M$ is an isomorphism by an application of Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
 \end{proof}
\subsection*{Why only cusps?} 
\subsection*{Alternative constructions}
\begin{itemize}
\item adapt the ideas of \cite{HassettHyeon}: check out section 3 of this paper;
\item check \cite[\S 3]{RSPW}.
\end{itemize}
 \section{Comparison with $p$-fields and splitting}
\subsection{Notation}
Let $\Z$ be defined by the pullback diagram:
\bcd
\mathcal Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
\mathcal X\ar[r] & \mathfrak M_1^{(1)}
\ecd

Objects of $\Z$ over $S$ consist of diagrams
\bcd
\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 \\
& S & & &
\ecd
where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisation (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams
\bcd
\cC\ar[r,"\phi"]\ar[d,"\psi"] &  \hat\cC\ar[r,"f"]\ar[d,"\hat\psi"] & \PP^4 \ar[d,"\id_\PP"]\\
\cC'\ar[r,"\phi'"] &  \hat\cC'\ar[r,"f'"] & \PP^4

\ecd
where $\psi$ and $\hat\psi$ are isomorphisms; note once again that $\hat \psi$ is determined by $\psi$, due to the required commutativity with the dominant ``birational'' morphism $\phi$.

Forgetting $\hat \cC$ and keeping $f\circ\phi\colon \cC\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d)$, which we claim is a \emph{closed embedding}: in fact, from the above description of arrows in $\Z$, it is representable (i.e. faithful) and a proper (check the valuative criterion: use the fact that $\X\to\MM_1$ is proper, and the map to $\PP$ descends to the $1$-stabilisation because we are only contracting weight $0$ elliptic tails; compare with \cite[Theorem 4.3]{RSPW}) monomorphism (i.e. full). So we may add the commutative diagram to the left:
\bcd
\oM_1(\PP^4,d)\ar[d] & \mathcal Z \ar[l,swap,hook,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
\MM_1 & \mathcal X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{(1)}
\ecd

\begin{lem}
There is a closed embedding $i\colon\Z\hookrightarrow\oM_1(\PP^4,d)$. In particular $\Z$ is a proper DM stack.
\end{lem}

Furthermore we inherit a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree. Notice that the above lemma signifies that each and every component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$. The point is that given any stable map there is at most one factorisation through the weighted $1$-stabilisation of the curve: objects of $\oM_1(\PP^4,d)\setminus D^1$ are $1$-stable already; objects of $D^1\cap \oM_1(\PP^4,d)^\text{main}$ do factor thanks to Vakil's criterion and objects of $D^1\cap D^k$ ($k\geq 2$) do factor through a map which is constant on the cusp.\marginpar{insert figure of a typical element of $D^1\cap D^2$.} On the other hand, objects of $D^{1,\circ}=D^1\setminus(\oM_1(\PP^4,d)^\text{main}\cup\bigcup_{k\geq 2}D^k)$ do not admit any factorisation, so that $\Z$ has no corresponding component.

\textcolor{red}{Introduce a Hu-Li type blow-up of $\MM_1^{(1)}$.}

We can push this reasoning further to the level of $p$-fields:
\bcd
\oM_1(\PP^4,d)^p\ar[d] & \mathcal Z^p \ar[l,swap,hook,"j"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
\oM_1(\PP^4,d)\ar[d] & \mathcal Z \ar[l,swap,hook,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
\MM_1 & \mathcal X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{(1)}
\ecd
where this time an object of $\Z^p$ over $S$ is given by
\bcd
\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 & \text{and} & \xi\in\Gamma(\hat\cC,f^*\OO_\PP(-5)\otimes\omega_{\hat\cC/S}) \\
& S & & & & &
\ecd
(I think to satisfy the stack condition $\xi$ should be really thought of as a section of $\hat\pi_*(f^*\OO_\PP(-5)\otimes\omega_{\hat\cC/S})$.)

For the existence of $j$ we are claiming that, pulling back along $\phi$, $\xi$ induces a section of $\pi_*((f\circ\phi)^*\OO_\PP(-5)\otimes\omega_{\cC/S})$. We may work on an atlas for $\Z^p$, which we shall (maybe abusing notation slightly) denote by $S$, as the base scheme in the above diagram; let us also denote by $\hat{\mathcal L}=f^*\OO(1)$ and $\L=\phi^*\hL$.

First we claim that the adjunction map $\OO_{\hat\cC}\to\phi_*\OO_\cC$ is an isomorphism: it is injective by dominance of $\phi$; to check the cokernel is trivial it is enough to do so after restricting to each and every irreducible component of $\Z^p$. Then $\hat\cC$ is normal\marginpar{NO, $\hat\cC_{|D^k}$ has multiple components} (so is the base\footnote{on VZ here}; R1 follows from the fact that singularities are isolated in the fiber, S2 \footnote{OK when fibers are Cartier i.e. over a DVR; actually take a look at Thm 23.9 in Matsumura's Commutative Ring Theory, fibers are CM in the situation at hand } follows from reducedness of the fibers) and we conclude by Zariski's main theorem (geometric fibers of $\phi$ are either points or elliptic curves, in either case connected).

The equality $\phi^*\omega_{\hat\cC/S}=\omega_{\cC/S}(\mathcal E)$, where $\mathcal E$ is the locus spanned by elliptic tails, can be checked on $\X$ and then pulled back. Notice that $\mathcal E$ is a Cartier divisor; $\phi$ is generically an isomorphism, so $\phi^*\omega_{\hat\cC/S}$ and $\omega_{\cC/S}$ may differ only on the locus where $\phi$ is not an isomorphism. The statement may now be proved by an intersection-theoretic argument by reducing to smoothings over the spectrum of a DVR, see\cite[Lemma 2.13]{SMY1}.

It is clear now that $\omega_{\cC/S}\otimes\L^{\otimes -5}\hookrightarrow \phi^*(\omega_{\hat\cC/S}\otimes\hL^{\otimes-5})$. Pushing down along $\pi=\hat\pi\circ\phi$, we get a map $\pi_*(\omega_{\cC/S}\otimes\L^{\otimes -5})\hookrightarrow \hat\pi_*(\omega_{\hat\cC/S}\otimes\hL^{\otimes-5})$ (using the projection formula and $\phi_*\OO_\cC=\OO_{\hat\cC}$). These are both $0$ on $\Z^{\text{main},\circ}=\Z^\text{main}\setminus(\bigcup_{k\geq2} D^k\Z)$; on the other hand they are both line bundles on $D^k\Z$... \marginpar{Fix me}

\begin{lem}
There is a close embedding $j\colon \Z^p\hookrightarrow \oM_1(\PP^4,d)^p$.
\end{lem}

Notice that the $p$-field is forced to vanish on $\Z^{\text{main},\circ}$, so $(\Z^p)^{\text{main},\circ}\simeq\Z^{\text{main},\circ}$ is the zero-section of the cone $\Z^p\to\Z$ (even though $\oM_1(\PP^4,d)^p\to \oM_1(\PP^4,d)$ is non-trivial on $\oM_1(\PP^4,d)^\text{main}\cap D^1$).

Finally it will be useful to introduce
\bcd
\XP\ar[r]\ar[d]\ar[dr,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)}\ar[d] \\
\X\ar[r] & \MM_1^{(1)}
\ecd
so that objects of $\XP(S)$ are
\bcd
\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[dl,"\hat\pi"] & \text{and} & \hL\in\Pic_{\hat \cC/S}(S) \\
& S & & &
\ecd
Notice that the map $\XP\to\mathfrak{Pic}$ that associates to an object as above $(\cC\to S,\phi^*\hL)$ is highly non-trivial on the locus of elliptic tails/cusps, since
\begin{itemize}
\item line bundles of the same degree on the cusp are identified (there is a $\mathbb G_a$ wealth of them), and
\item only line bundles that restrict to effective line bundles on the elliptic tail are in the image of this morphism.
\end{itemize}

\subsection{Splitting the cone}
We may notice that $(\Z^p)^{\text{main},\circ}\to\XP$ is smooth onto its image, which is an open substack; furthermore on this open the relative tangent is represented by $\hat\pi_*\hL^{\oplus 5}$, and $\R^1\hat\pi_*\hL^{\oplus 5}=\hat\pi_*(\hat\omega\otimes\hL^{\otimes -5})=0$. Let $E^\bullet=\R^\bullet\hat\pi_*(\hL^{\oplus 5}\oplus \hat\omega\otimes\hL^{\otimes -5})$ denote the dual perfect obstruction theory of $\Z^p\to \XP$. Then the intrinsic normal cone of $\Z^p\to \XP$ splits into:
\begin{itemize}
\item the closure of the zero section of $h^1/h^0(E^\bullet)_{|\text{main},\circ}$, which we shall name $\mathfrak C^{\text{main}}$;
\item other components supported on the boundary, which we should accordingly name $\mathfrak C^k$ ($k\geq 2$).
\end{itemize}
\bibliographystyle{alpha}
\bibliography{cusp}

\end{document}

### 2017-12-03 draft.tex
Saturday work with Fra: fixing our description of the map

@@
 \renewcommand{\to}{\rightarrow}
+\newcommand{\pr}{\rm{pr}}
 \newcommand{\A}{\mathcal A}
@@
 \newcommand{\Pic}{\operatorname{Pic}}
-\newcommand{\pr}{\operatorname{pr}}
 \newcommand{\id}{{\rm id}}
@@
 \end{thm} 
-Since it is hard to define such a map on an arbitrary base, we proceed as follows.
+We approach the proof in two different manners: first we adopt the strategy of constructing the graph of such morphism and prove that projection on the source is an isomorphism; second we construct the $1$-stabilisation at the level of curves with divisors with an argument \'{a} la Hassett \cite{HassettHyeon}, then argue that it descends to a morphism between moduli spaces of weighted curves.
+
+\subsection{First approach: the graph}
+
 Let $\mathcal C$ and $\mathcal C'$ be the universal curves over $\mathfrak{M}:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ and $\mathfrak{M}':=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ respectively.
-Abusing notation slightly, we will still write $\mathcal C$ and $\mathcal C'$ for their pullbacks to the product $\mathfrak{M}\times\mathfrak{M}'$ along the two projections.
+Abusing notation, we will still write $\mathcal C$ and $\mathcal C'$ for their pullbacks to the product $\mathfrak{M}\times\mathfrak{M}'$ along the two projections.
 The proof of the theorem follows from two Lemmas:
@@
 \begin{proof}\ref{lemma:def_X}
-Recall that $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ is an algebraic stack; in fact the map to $\mathfrak{M}\times\mathfrak{M}'$ is representable by Grothendieck's theory of the Hilbert scheme for projective morphisms.
+Recall that $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ is an algebraic stack; in fact the map to $\mathfrak{M}\times\mathfrak{M}'$ is representable (by algebraic spaces) \cite{OlssonHOM}.
 We now proceed to construct $\mathcal X$ as a locally closed substack in the space of morphisms.
@@
  \[\pi\colon\mathfrak{P}=\mathfrak{Pic}^{tot deg=d,st}_{1,n}\to\mathfrak{M},\ \pi'\colon\mathfrak{P}'=\mathfrak{Pic}^{tot deg=d,st}_{1,n}(1)\to\mathfrak{M}'\]
-  the Picard stacks on $\mathfrak{M}$ and $\mathfrak{M'}$ with universal line bundles $\mathfrak{L}$ and $\mathfrak{L'}$, where $\pi$ and $\pi'$ are defined by taking the multi-degree of line bundles.
+  the Picard stacks of $\cC\to\mathfrak{M}$ and $\cC'\to\mathfrak{M'}$ with universal line bundles $\mathfrak{L}$ and $\mathfrak{L'}$, where $\pi$ and $\pi'$ are defined by taking the multi-degree of line bundles.
 We can now look at the algebraic stack $\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$ with universal morphism
@@
 Indeed, given a chart
- \begin{equation}\label{equation:Spoints} 
+ \begin{equation*}%\label{equation:Spoints} 
  S\to\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C'),
-  \end{equation} 
-   the locus of $s\in S$ where $\Phi_s^*\mathfrak{L}'_s\cong\mathfrak{L}_s$ is nothing else than the locus $T$ where the two sections $\mathfrak{L}_S$ and $\Phi_S^*\mathfrak{L}'_S$ of $\mathfrak{P}(S)\to\mathfrak{M}(S)$ induced by \ref{equation:Spoints} coincide.
-In other words, we are looking for the fiber product
+  \end{equation*} 
+   the locus of $s\in S$ where $\Phi_s^*\mathfrak{L}'_s\cong\mathfrak{L}_s$ is nothing else than the locus $T$ where the two sections $\mathfrak{L}_S$ and $\Phi_S^*\mathfrak{L}'_S$ of $\mathfrak{P}(S)\to\mathfrak{M}(S)$ coincide.
+In other words, we are looking at the fiber product
   \[\xymatrix{T\ar[r]\ar[d]&\mathfrak{P}\ar[d]^{\Delta}\\
   S\ar[r]&\mathfrak{P}\times_{\mathfrak{M}}\mathfrak{P}}\]
-Being $\mathfrak{P}\to\mathfrak{M}$ representable by schemes, it follows that $U\to S$ is a locally closed immersion.
+Being $\mathfrak{P}\to\mathfrak{M}$ representable by locally separated algebraic spaces \cite[Theorem~8.3.1]{neron}, $\Delta$ is a quasi-compact locally closed immersion \cite[\href{http://stacks.math.columbia.edu/tag/04YU}{Tag 04YU}]{stacks-project}, so in particular $T\subseteq S$ is locally closed.
 
 \item[Step 2] 
-Furthermore, there is a closed substack $\mathcal Y\subseteq \mathcal Y'$ representing \emph{surjective morphisms that preserve the markings}.
+Furthermore there is a closed substack $\mathcal Y\subseteq \mathcal Y'$ representing \emph{surjective morphisms that preserve the markings}.
 
@@
 
-As regards surjectivity, since $\Phi$ is proper, and by upper semicontinuity of the dimension of the fiber \cite[\href{http://stacks.math.columbia.edu/tag/0D4I}{Tag 0D4I}]{stacks-project}, the locus in $\mathcal C_S'$ where the fiber of $\Phi$ is empty is open.
-The complement of its image in $S$ is the locus we were after.
+As regards surjectivity, since $\Phi$ is proper and the dimension of the fiber is upper semicontinuous \cite[\href{http://stacks.math.columbia.edu/tag/0D4I}{Tag 0D4I}]{stacks-project}, the locus in $\mathcal C_S'$ where the fiber of $\Phi$ is empty is open.
+Its image in $S$ is open by flatness of $\cC'\to S$ \cite[\href{http://stacks.math.columbia.edu/tag/01UA}{Tag 01UA}]{stacks-project}, and the complement of it is the locus we need.
 
 \item[Step 3] Let $\mathcal{X}'$ be the image of $\mathcal Y$ under $\Pi$.
-This is a constructible substack of $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ by Chevalley's theorem \cite[\href{http://stacks.math.columbia.edu/tag/054K}{Tag 054K}]{stacks-project}.
-Recall that, to show that a constructioble set is open (respectively closed), it is enough to check that it contains all the generisations of its points (respectively all the specialisations) \cite[\href{http://stacks.math.columbia.edu/tag/0903}{Tag 0903}]{stacks-project}.
+This is a constructible substack of $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ by Chevalley's theorem \cite[Theorem 5.9.4]{LMB}.
+Recall that to show that a constructible set is open (respectively closed) it is enough to check that it contains all the generisations of its points (respectively all the specialisations) \cite[\href{http://stacks.math.columbia.edu/tag/0DQN}{Tag 0DQN}\href{http://stacks.math.columbia.edu/tag/0903}{Tag 0903}]{stacks-project}.
 Finally, under Noetherian assumptions, two points related by specialisation/generisation are contained in the image of a DVR scheme \cite[\href{http://stacks.math.columbia.edu/tag/054F}{Tag 054F}]{stacks-project}.
@@
 Assume that $S$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $S\to\mathcal X'$ such that $\phi_0\colon\mathcal C_0\to \mathcal C_0'$ does not contract any positive weight component.
-Suppose, by contradiction, that there exists an irreducible component $W\subseteq C_{\eta}$ of positive weight $d_W$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e.
-$\left\{c\in \mathcal{C}_{S} | \dim_c\phi^{-1}(\phi(c))=1\right\}$, is closed by semicontinuity of fiber dimension and contains all the components $D_i\subseteq C_0$ to which $D$ specialises; at least one of them must have positive weight, since the sum of their weights is $d_W$, which is a contradiction.
+Suppose there exists an irreducible component $D_\eta\subseteq C_{\eta}$ of positive weight $d_W$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e.
+$\left\{c\in \mathcal{C}_{S} | \dim_c\phi^{-1}(\phi(c))\geq 1\right\}$, is closed by semicontinuity of fiber dimension, hence it contains all the components $D_i\subseteq C_0$ to which $D_\eta$ specialises.
+At least one of them has positive weight, since the sum of their weights is $d_W$, which is a contradiction.
 
-\item\emph{$\phi$ has degree 1 on every non contracted component}, or, equivalently, there is an $S$-dense open in $\mathcal C'_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
-This is an open and closed condition; we show it is open.
-Let $S$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property.
-We may assume that $S$ is the local ring at $0$ of a smooth projective curve $\bar S$ \cite[Thm.
-I.6.9]{HAR} and that $S\to\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ extends to $\bar S$ (by the valuative criterion of properness).
-\marginpar{FIX ME: properness seems to fail, but we don't need to extend to $\bar S$ to use Fulton's intersection theory} Let us now write $\phi_{\bar S,*}[\mathcal C_{\bar S}]=\sum n_i[\mathcal C'_{\bar S,i}]$; by Gysin pull-back to $0$ and \cite[Prop.
-10.1(a)]{FUL}, we see that all the $n_i$'s are 1, apart from some that involve components of $\mathcal C'_{\bar S}$ away from $0$.
-Discarding these, we find an open neighborhood of $0$ such that the restriction of the morphism to every closed point in the base is birational in our sense, i.e.
-we find a $\bar S$-dense (around $0$) open in $\mathcal C'_{\bar S}$ on which $\phi$ gives an isomorphism, hence $\phi_\eta$ also satisfies the property.
+\item\emph{$\phi$ has degree 1 on every non contracted component} or, equivalently, there is an $S$-dense open in $\mathcal C'_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
+This is an open and closed condition; we show it is open. Let $S$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property. Since $\phi_S$ is proper, we may consider 
+\[\phi_{S,*}[\mathcal C_{S}]=\sum n_i[\mathcal C'_{S,i}]\in A_2(\cC'_S)\].
+Applying Gysin pull-back to $0$ (which is a regular closed point of the base) \cite[Prop.
+10.1(a)]{FUL}, we see that all the $n_i$'s are 1 for those $\cC'_i$'s such that $0^![\cC'_i]\neq 0$.
+On the other hand there is no irreducible component of $\cC'$ supported on $\cC'_\eta$.
 
-\item\emph{$\phi$ is weight-preserving.} This is again an open condition: assume that $\phi_0$ is weight-preserving; the existence of $\phi_S$ implies that the maps $\tilde \phi_0$ and $\tilde\phi_\eta$ (induced at the level of weighted dual graphs) are compatible with the specialisation maps.
-Since the weight of a component of the generic fiber is determined by those of the components to which it specialises, this proves that $\phi_\eta$ must be weight-preserving as well.
+\item\emph{$\phi$ is weight-preserving.} This is again an open condition, as we can see from the weighted dual graphs.
+Let $\tilde \phi$ be the map induced at the level of weighted dual graphs $\Gamma(\cC)\to\Gamma(\cC')$.
+It is compatible with the specialisation maps:
+\bcd
+\Gamma(\cC_0)\ar[r,"\tilde\phi_0"]\ar[d,"\rm{sp}"] & \Gamma(\cC'_0)\ar[d,"\rm{sp}"] \\
+\Gamma(\cC_{\eta})\ar[r,"\tilde\phi_\eta"]& \Gamma(\cC'_\eta)
+\ecd
+Since the weight of a component of the generic fiber is determined by those of the components to which it specialises
+\[ \deg(v)=\sum_{w\in\rm{sp}^{-1}(v)}\deg(w)
+\]
+$\tilde{\phi}_\eta$ has to be weight-preserving as well.
 \end{enumerate}
 
-\item[Step 4] We have seen that, if $\phi$ contracts a component $E$ of the fiber, it must have zero weight.
-Then it has to be elliptic by the stability condition.
-Since the target has only nodes and cusps as singularities, it must be $|\overline{C\setminus E}\cap E|\leq 2$, i.e.
+\item[Step 4] We have seen that, if $\phi$ contracts a connected subcurve $E$ of the fiber, it must have zero weight.
+Since the target only has nodes and cusps as singularities, and the markings are required to be smooth points, we observe that $E$ must be of arithmetic genus one by weighted stability and $|\overline{C\setminus E}\cap E|\leq 2$, i.e.
 $E$ is either an elliptic tail or an elliptic bridge.
 There are basically two possibilities:
-(a) the elliptic tail gets contracted to a cusp, or $\phi$ is an isomorphism everywhere; (b) the elliptic tail/bridge gets contracted to a smooth point or node, then a non-separating node or a cusp must be created somewhere else in order to preserve the genus.
-We want to get rid of case (b), so we define the open substack $\mathcal X\subseteq \mathcal X'$ as follows.
+\begin{enumerate}
+\item $\phi$ contracts an elliptic tail to a cusp and is an isomorphism everywhere else, or there is no elliptic tail to start with and $\phi$ is an isomorphism;
+\item the elliptic tail/bridge is contracted to a smooth point/node, then a non-separating node or a cusp must be created somewhere else in order to preserve the arithmetic genus.
+\end{enumerate} 
+We want to avoid the second scenario, so we define the open substack $\mathcal X\subseteq \mathcal X'$ as follows.
 Given $\mathcal{C}_S\to\mathcal C_S'\in\mathcal X'(S)$, let $U'\subseteq \mathcal C'$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U')}\colon\phi_S^{-1}(U')\to U'$ is an isomorphism and $Z'$ its closed complement in $\mathcal C_S'$.
-Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055D}{Tag 055D}, \href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(Z')}\colon \phi^{-1}(Z')\to S$ are geometrically connected.
+Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(Z')}\colon \phi^{-1}(Z')\to S$ are geometrically connected.
 \end{description} 
@@
  This result will follow from an application of Zariski's Main Theorem for algebraic spaces.
-First of all, we claim that the projection is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points; hence we are just saying that
-$\operatorname{Aut}(\phi)\subseteq\operatorname{Aut}(C).$ 
- This follows from the fact that, if $\phi\in\mathcal X$, then it is dominant and of degree one.
-Secondly, $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion
+First we claim that the projection is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points.
+Hence we need to say that, given $\phi\colon C\to C'$ a $k$-point of $\X$, we have
+$\operatorname{Aut}(\phi)\subseteq\operatorname{Aut}(C)$. Recall that automorphisms of $\phi$ are commutative diagrams:
+\bcd C\ar[r,"\phi"]\ar[d,"\psi"] & C'\ar[d,"\psi'"] \\ C\ar[r,"\phi"] & C' \ecd
+ Now $\psi'$ is determined by $\psi$ due to our description of $\phi$.
+
+Secondly $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion
 \bcd
-\eta=\Spec(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
-S=\Spec(R)\ar[r] & \mathfrak M
+\eta'=\Spec(K')\ar[r]\ar[d] & \eta=\Spec(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
+S'=\Spec(R')\ar[r]\ar[urr,dashed,"\exists?", left] & S=\Spec(R)\ar[r] & \mathfrak M
 \ecd
@@
 \begin{enumerate}
-\item the central fiber contains no elliptic tail, then so does $\mathcal C_\eta$, hence $\phi_\eta$ 
-\marginpar{\begin{color}{red} It's right but confusing! Write it better!!!\end{color}}is an isomorphism and admits a unique extension to an isomorphism $\phi\colon \mathcal C_S\cong \mathcal C_S'.$
+\item the central fiber contains no elliptic tail, then the same is true for $\mathcal C_\eta$, hence $\phi_\eta$ is an isomorphism. We can extend $\phi_\eta$ as follows:
+\bcd
+\cC_\eta\arrow{r}{\sim}[swap]{\phi_\eta}\ar[d,hook,"\iota"] & \cC'_\eta\ar[d,hook,"\iota\circ\phi_\eta^{-1}"] \\
+\cC_S\ar[r,"\id_\cC"] & \cC_S=:\cC'_S
+\ecd
+Another extension $\phi'\colon \mathcal C_S\cong \mathcal C_S'$ would be isomorphic to the previous one via:
+\bcd
+\cC_S\ar[r,"\phi'"]\ar[d,"\id"] &\cC_S'\ar[d,"(\phi')^{-1}"] \\
+\cC_S\ar[r,"\id"] & \cC_S
+\ecd
 
@@
 \setcounter{enumi}{1}
-\item $\mathcal C_{\eta}$ still has an elliptic tail, i.e.
-the node separating the weight zero, genus one curve from the rest of $\mathcal C_S$ is not smoothened.
-Then $\mathcal C_S$ is the push-out of a family of rational curves $\mathcal R_S$ and a family of genus one curves $\mathcal Z_S$.
+\item $\mathcal C_{\eta}$ has an elliptic tail as well; that is the image of $S\to\MM$ is contained in the boundary, so we can find a lift
+\bcd
+ & \MM_{1,1}\times\MM_{0,1+n}^\text{wt}\ar[d] & \\
+ S\ar[r]\ar[ur,dashed] & \mathfrak D_{\{1,\emptyset\},\{0,n\}}\ar[r,hook] &\MM.
+\ecd
+ Then $\mathcal C_S$ is the push-out of a family of rational curves $\mathcal R_S$ and a family of genus one curves $\mathcal Z_S$:
 %The map $S\to\partial \mathfrak M_{1,n}$ lifts to the normalisation of the boundary, i.e.
 $\mathfrak M_{0,n_0+1}\times\mathfrak M_{1,n_1+1}$, which gives two families of pointed curves on $S$; there is a map from the push-out to $\mathcal C_S$ by the universal property, and it is proper bijective and flat (crit\`{e}re de platitude par fibres \cite[\href{http://stacks.math.columbia.edu/tag/039A}{Tag 039A}]{stacks-project}).
-\bcd
+\begin{equation}\label{eq:pushout}
+\begin{tikzcd}
 S\ar[d]\ar[r] & \mathcal R_S \ar[d] \\
 \mathcal Z_S\ar[r] & \mathcal C_S
+\end{tikzcd}
+\end{equation}
+Recall that the cuspidal curve $\cC'_K$ can be characterised as the push-out of the following diagram:
+\bcd
+2K\ar[r]\ar[d] & \mathcal R_K\ar[d] \\
+K\ar[r] & \mathcal C'_K.
 \ecd
-\marginpar{\begin{color}{red} Before writing the push down diagram we might need to change base. Write down the double push-out diagram\end{color}}
-Locally around the node, $\phi_{\eta}$ is the contraction of the elliptic curve to the cusp, and, on the adjacent rational component, it is the normalisation of the cusp; by the universal property of push-outs, it can be uniquely extended to the same map on the central fiber (far from this node, $\phi_\eta$ is an isomorphism).
-\item If $\mathcal C_S$ smoothens the elliptic tail, then the map is given on the generic fiber by a $\pi$-ample line bundle $\mathcal L_{\eta}$.
-Then the extension to the central fiber is determined by the unique extension $\mathcal L_0$ of $\mathcal L_{\eta}$ which is trivial on the minimal subcurve $Z\subseteq \mathcal C_0$ of arithmetic genus 1 and, possibly after twisting, is ample elsewhere.
+Since the smooth section $S\to\mathcal R_S$ defines a Cartier divisor, it makes sense to take its double and we can thus define $\cC'_S$ by means of the similar diagram:
+\bcd
+2S\ar[r]\ar[d] & \mathcal R_S\ar[d] \\
+S\ar[r] & \mathcal C'_S
+\ecd
+The morphism $\phi_S\colon\cC_S\to\cC'_S$ extending $\phi_\eta$ is then defined by exploiting the description of $\cC_S$ as a push-out \eqref{eq:pushout}, and the morphisms $\id\colon\mathcal R_S\to \mathcal R_S$ and $\pr_{\mathcal Z_S}\colon\mathcal Z_S\to S$.
+\item If $\mathcal C_S$ smoothens the elliptic tail, then $\phi_\eta$ is an isomorphism.
+We may assume that $S$ is the spectrum of a complete DVR with algebraically closed residue field \cite[Theorem 7.10]{LMB}.
+Then we may pick one smooth section for each rational component of $\cC_0$ and extend them to sections of $\cC_S\to S$ by Grothendieck's existence theorem; let us denote by $\Sigma$ the Cartier divisor that is the sum of all such sections.
+Let $Z$ be the elliptic tail in the central fiber; then we claim that $\omega_{\cC_S/S}(Z)\otimes\mathcal O_{\cC_S}(\Sigma)$ is $\pi_S$ semi-ample, ample on the generic fiber, and gives the contraction of the elliptic tail to the cusp in the central fiber.
+We shall not prove the claim here, since this is the core of the second approach.
 \end{enumerate}
-Finally, observe that the map is bijective by construction and $\mathfrak M$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \mathfrak M$ is an isomorphism by an application of Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
+Finally, observe that the map is bijective by construction and $\mathfrak M$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \mathfrak M$ is an isomorphism by Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
  \end{proof}
@@
 \item adapt the ideas of \cite{HassettHyeon}: check out section 3 of this paper;
-\item check \cite[\S 3]{RSPW}.
+\item check \cite[\S 4]{RSPW}.
 \end{itemize}

### 2017-12-04 draft.tex
started writing p-fields

@@
 
+\usepackage{calrsfs}
+\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
+
 \newcommand{\M}[4]{\overline{\mathcal M}_{#1,#2}(#3,#4)}
+\newcommand{\Mone}[3]{\overline{\mathcal M}^{(1)}_{#1}(#2,#3)}
 \newcommand{\PP}{\mathbb P}
@@
 \newcommand{\pr}{\rm{pr}}
+\newcommand{\Aaff}{\mathbb A}
 \newcommand{\A}{\mathcal A}
@@
 \newcommand{\MM}{\mathfrak M}
+\newcommand{\pP}{\mathfrak P}
+\newcommand{\hP}{\hat{\mathfrak P}}
 \newcommand{\oM}{\overline{\mathcal M}}
 \newcommand{\R}{\operatorname{R}}
+\newcommand{\Gm}{\mathbb{G}_{\rm{m}}}
+\newcommand{\w}{\mathbf{w}}
+\newcommand{\PtoM}{\rho}
 
@@
 \newcommand{\Spec}{\operatorname{Spec}}
+\newcommand{\Proj}{\operatorname{Proj}}
 \newcommand{\Pic}{\operatorname{Pic}}
+\newcommand{\Hom}{\operatorname{Hom}}
 \newcommand{\id}{{\rm id}}
@@
 \begin{prop}
-\emph{(1)} \'{E}tale locally, there is a locally closed imbedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V_1:=\operatorname{Spec}(\pi_*\mathcal L(\A)^{\oplus r})$ over $\mathfrak M_{1,n}^{\operatorname{div}=d}$.
+\emph{(1)} \'{E}tale locally, there is a locally closed embedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V_1:=\Spec(\pi_*\mathcal L(\A)^{\oplus r})$ over $\mathfrak M_{1,n}^{\operatorname{div}=d}$.
 It is obtained by imposing the nondegeneracy and stability conditions \emph{(open)} on the vanishing locus of the restriction of the universal section of $\pi_*\mathcal L(\A)^{\oplus r}$ to $\A$ \emph{(closed)}.
@@
  \end{proof}
+
+\subsection{Second approach: constructing the contraction}
+The idea of this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
+
+Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that $\omega_\pi\otimes \mathcal L^{\otimes 3}$ is $\pi$-ample.
+We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
+More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields}), where the section is not $0$ on any irreducible component of the curve.
+Alternatively one can think of the moduli functor of a line bundle with a section up to scalar as the hom-stack $\Hom_{\MM_1}(\C,[\Aaff^1/\Gm])$, again requiring the section not to be $0$ and the total degree of the line bundle to be $d$.
+
+We shall first construct the contraction over $\MM^{\rm{div}}$ and then show that it descends to $\MM^{\rm{wt}}$.
+
+Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{wt}_1$, which we shall freely pullback and keep denoting by $E$.
+We write $\mathcal M:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$, where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+
+\begin{prop}
+ The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal M$:
+ \bcd
+ (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ & \MM_1^{\rm{div}} &
+ \ecd
+\end{prop}
+\begin{prop}
+The $1$-stabilisation with divisors descends to the level of weighted curves:
+\bcd
+\MM_1^{\rm{div}}\ar[r]\ar[d] & \MM_1^{(1),\rm{div}}\ar[d] \\
+\MM_1^{\rm{wt}}\ar[r] & \MM_1^{(1),\rm{wt}}
+\ecd
+\end{prop}
+
 \subsection*{Why only cusps?} 
@@
 \end{itemize}
+
+\section{From $p$-fields to the quintic three-fold}
+We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cusp invariants of the quintic three-fold up to a sign.
+This is a word-by-word repetition of the arguments in \cite{CLpfields}, once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
+Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}.
+
+Let us first establish some notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is a smooth quintic three-fold.
+In this section we shall denote by $\rm{M}:=\oM_1^{(1)}(\PP^4,d)$, by $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ the universal $1$-stable curve and map over it, by $\L_{\rm M}=f_{\rm M}^*\OO_{\PP^4}(1)$ and by $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}$.
+Furthermore we shall write $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\MM_1^{(1)}}$.
+
+\begin{lem}
+ $\hP$ is a smooth Artin stack of dimension $0$. Furthermore there is a compatible triple of dual perfect obstruction theories:
+ \bcd
+ \lambda^*\mathbb T_{\hP/\MM_1^{(1)}}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\MM_1^{(1)}} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus \mathcal L_{\rm M}^{\oplus 5})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \ecd
+ implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus \mathcal L_{\rm M}^{\oplus 5})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
+\end{lem}
+\begin{proof}
+ The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\MM_1^{(1)}$ is unobstructed of relative dimension $0$ and $\MM_1^{(1)}$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations can be found inside $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+
+ The fact that $\mathbb T_{\rm M/\MM_1^{(1)}}\to \mathbb E_{\rm M/\MM_1^{(1)}}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is \cite[Proposition 6.3]{BF}.
+
+ The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
+The middle column comes from identifying the space of stable maps as an open substack of the cone of sections of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
+The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
+
+ The last claim follows from functoriality of virtual pullback \cite{Manolache-pullback}.
+\end{proof}
+
+We proceed to define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
+
+\begin{dfn}
+ The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p$ parametrises $1$-stable maps
+ \bcd
+ \hat\cC_S\ar[r,"f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
+ S &
+ \ecd
+ with a $p$-field $\hat\psi\in H^0(\hat\cC_S,f_{S}^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_{S}})$.
+\end{dfn}
+Due to the fact that $\R^1\hat\pi_*\mathcal F$ behaves well under base change, while $\hat\pi_*\mathcal F$ may not, the correct way to formalise this is via relative Serre duality: \[\Mone{1}{\PP^4}{d}^p=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M})):=\Spec_{\rm M}(\R^1\hat\pi_{\rm M,*}(\L_{\rm M}^{\otimes 5}))\]
+We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
+\bcd
+& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
+\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
+\pazocal P \ar[r,"\PtoM"] & \rm M
+\ecd
+
+\begin{lem}
+ There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}))\] for the triangle:
+ \bcd
+ \pazocal P\ar[rr,"\PtoM"]\ar[dr] & & \rm M\ar[dl] \\
+ & \hP &
+ \ecd
+\end{lem}
+See \cite[Proposition 3.1]{CLpfields}.
+Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
+In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the existence of a cosection of the obstruction bundle whose degeneracy locus is the afore-mentioned substack, and the machinery of cosection localised virtual classes \cite{KLcosection}.
+Recall their Theorem 1.1:
+
+\begin{teo*}[Localization by cosection]\label{thm:KLlocalisation}
+Let $\pazocal M$ be a Deligne-Mumford stack endowed with a perfect
+obstruction theory. Suppose the obstruction sheaf $\rm{Ob}_\pazocal M$ admits a
+surjective homomorphism $\sigma:\rm{Ob}_\pazocal M|_U  \to \OO_U$
+over an open $U\subseteq \pazocal M$.
+Let $\pazocal{M}(\sigma)=\pazocal{M}\setminus U$.
+Then $(\pazocal{M},\sigma)$ has a localized virtual cycle
+$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).
+$$
+This cycle enjoys the usual properties of the virtual cycles; it relates to
+the usual virtual cycle $[\pazocal{M}]^{\rm{virt}}$ via 
+$[\pazocal{M}]^{\rm{virt}} = \iota_*[\pazocal{M}]^{\rm{virt}}_{\rm{loc}} \in A_*  \pazocal{M}$, where
+$\iota: \pazocal{M}(\sigma)\to \pazocal{M}$ is the inclusion.
+\end{teo*}
+
+In \cite[\S\S3.2-3.4]{CLpfields} the following facts are proved. Based on Serre duality, there is a morphism
+\[ h_1\colon\rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
+By differentiating it and pulling it back along the universal evaluation
+\bcd
+& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\ar[d] \\
+\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
+\pazocal P \ar[r] & \rm \hP
+\ecd
+we obtain a cosection of the relative obstruction sheaf
+\[\begin{split}
+ \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
+ \sigma_{1|(u,\psi)}(z,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)z_i
+\end{split}\]
+The degeneracy locus of such cosection is $\Mone{1}{X}{d}$ (again based on Serre duality) and $\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
+
+We are left with proving the following:
+\begin{prop}
+ \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}=:GW_1^{\rm{cusp}}(X,d)\]
+\end{prop}
+This is achieved in \cite[\S4]{CLpfields} by a family version of the previous construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
+
+\begin{lem}
+ The deformation to the normal cone $V$ is cut inside $\rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t$ with basis coordinates $[x_0:\ldots:x_4]$ and fiber coordinate $y$ by the equation $\w(x)-ty=0$.
+\end{lem}
+See \cite[Lemma 4.1]{CLpfields}. This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\pazocal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
+
+\bcd
+& \pazocal Z'\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & V\ar[d] \\
+& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
+\hat \cC_{\pazocal V}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal V}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
+\pazocal V:=\Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
+\ecd
+
 \section{Comparison with $p$-fields and splitting}

### 2017-12-04 draft.tex
second approach to the contraction

--- 2017-12-03 draft.tex
@@
 \newcommand{\MM}{\mathfrak M}
+\newcommand{\pP}{\mathfrak P}
 \newcommand{\oM}{\overline{\mathcal M}}
 \newcommand{\R}{\operatorname{R}}
+\newcommand{\Gm}{\mathbb{G}_{\rm{m}}}
 
@@
  \end{proof}
+
+\subsection*{Second approach: constructing the contraction}
+The idea of this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
+
+Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that $\omega_\pi\otimes \mathcal L^{\otimes 3}$ is $\pi$-ample.
+We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
+More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields}), where the section is not $0$ on any irreducible component of the curve.
+Alternatively one can think of the moduli functor of a line bundle with a section up to scalar as the hom-stack $\Hom_{\MM_1}(\C,[\Aaff^1/\Gm])$, again requiring the section not to be $0$ and the total degree of the line bundle to be $d$.
+
+We shall first construct the contraction over $\MM^{\rm{div}}$ and then show that it descends to $\MM^{\rm{wt}}$.
+
+Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{wt}_1$, which we shall freely pullback and keep denoting by $E$.
+We write $\mathcal M:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$, where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+
+\begin{prop}\label{1-stabilization-div}
+ The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal M$:
+ \bcd
+ (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ & \MM_1^{\rm{div}} &
+ \ecd
+\end{prop}
+We prove a proposition through a series of Lemma s. The first one is a technical statement telling us that we can reduce to verify semi-ampleness and local freeness on families over DVR.
+\begin{lem}{Reduction to DVR}\label{DVR}
+Let $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$ and let $f\colon T\to\MM_1^{\rm{div}}$ such that $0\in \mathfrak{D}^1$ and $\eta\in \MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then
+\[f^*\pi_*\mathcal M\cong \pi_*f^*\mathcal M.\]
+We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
+\end{lem}
+\begin{proof}
+The argument is taken from \cite[Lemmma~3.7.2.2]{RSPW}.
+Let $K^{\bullet}$ the complex of locally free sheaves on $S$ which satisfy cohomology and base change, i.e. such that for any $T\xrightarrow{f} S$  we get
+$H^i(f^*K^{\bullet})=\R^i\pi_*f^*\mathcal M.$ The construction of $K^{\bullet}$ is standard, (see e.g.
+\cite[Proposition~12.2]{HAR} and since the cohomology is concentrated in degree 0,1, we can assume $K^{\bullet}=K_0\to K_1.$ Let $f$ be the map defined in the statement of the Lemma.
+Then we have the following exact sequences:
+\begin{equation}\label{eq:exact1}
+0\to \pi_*\mathcal M\to K^0\to K^1\to \R^1\pi_*\mathcal M\to 0,
+\end{equation}
+\begin{equation}\label{eq:exact2}
+0\to \pi_*f^*\mathcal M\to f^*K^0\to f^*K^1\to \R^1\pi_*f^*\mathcal M\to 0.
+\end{equation}
+The derived pull-back $Lf^*$ of the complex~\eqref{eq:exact1} is zero since the complex is exact.
+Writing down explicitly the spectral sequence which compute the derived pull-back, we find that its convergence to zero implies that:
+\begin{align*}
+\operatorname{coker}(f^*\pi_*\mathcal M\to\pi_*f^*\mathcal M)&\cong \rm{L}_1f^*\R^1\pi_*\mathcal M\\
+\operatorname{ker}(f^*\pi_*\mathcal M\to\pi_*f^*\mathcal M)&\cong \rm{L}_2f^*\R^1\pi_*\mathcal M.
+\end{align*} 
+Now, notice that $\R^1\pi_*\mathcal M$ is a line bundle supported on the Cartier divisor $\mathfrak{D}^1;$ it is clearly zero on the smooth locus and one can easily check that is rank is constant and equal to one on the divisor.
+To prove that $\rm{L}_if^*\R^1\pi_*\mathcal M=0$ for $i=1,2$ it is enough to work locally on $S$, where we have a free resolution for  of the form $\R^1\pi_*\mathcal M$ of the form:
+\[0\rightarrow \OO_S\xrightarrow{g}\OO_S\rightarrow \R^1\pi_*\mathcal M\rightarrow 0\] 
+and thus pulling back along $f$
+\[0\rightarrow  \rm{L}_1f^*\R^1\pi_*\mathcal M \OO_T\xrightarrow{f^*g}\OO_T\rightarrow f^*\R^1\pi_*\mathcal M\rightarrow 0.\] 
+It immediately follows that $ \rm{L}_2f^*\R^1\pi_*\mathcal M=0.$ Finally notice that since the image of $f$ is not contained in the boundary divisor $f^*g\neq 0$ and thus injective of sheaves as $T$ is a DVR.
+We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.
+\end{proof}
+\begin{lem}\label{lemma:semiample}
+The line bundle $\mathcal M$ is $\pi$ semi-ample, i.e. the natural map
+\[\pi^*\pi_*\mathcal M^{\otimes n}\to \mathcal M^{\otimes n}\]
+is surjective.
+\end{lem}
+\begin{proof}
+Outside the locus of elliptic tails $\mathcal M$ is $\pi$- ample and thus in particular $\pi$-semi ample.
+To check that it is still $\pi$-semi ample also for any $x\in C$ when $C$ has an elliptic tail, thanks to the above Lemma we can reduce to check this condition when $C$ is the central fiber of a one parameter smoothing of the elliptic tail.
+But then this has been proved by Smyth~\cite[Lemma~2.12]{SMY1}.
+\end{proof}
+
+\begin{lem}
+$\pi_*\mathcal M$ is locally free of rank $d$ on $\MM_1^{\rm{div}}.$
+\end{lem}
+\begin{proof}\cite[Proposition~3.7.2.1]{RSPW}
+We have essentially to check that $\pi_*\mathcal M$ has constant rank.
+On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ this follows simply from the fact that $\R^1\pi_*\mathcal M=0$ and the rank is determined by Riemann-Roch.
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can always find a DVR $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypothesis of Lemma~\ref{DVR} and thus we can check the rank looking at $\pi_*f^*\mathcal M$ over the DVR  $T.$ But notice that $\pi_*f^*\mathcal M$ is torsion free over $T$, which conclude the proof.
+\end{proof}
+
+\begin{proof}\ref{1-stabilization-div}
+Let $S\to \MM_1^{\rm{div}}$ be a smooth atlas, then we have:
+ \bcd
+ (C,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat C=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ & S &
+ \ecd
+where: $\phi$ is proper and birational  since $\mathcal M$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal M$ is locally free.
+
+Consider the caresian diagram 
+\bcd
+C'\ar[r,"f_C"]\ar[d,"\pi'"] & C\ar[d,"\pi"] \\
+S'\ar[r,"f"] & S.
+\ecd
+To show that the above construction is compatible with base change it is enough to show that for any base change holds what we proved in Lemma~\ref{DVR}:
+\begin{equation}\label{eq:generalbasechange}
+f^*\pi_*\mathcal M\cong \pi'_*f^*\mathcal M.
+\end{equation}
+Since $\pi$ is flat we do have an isomorphism if we consider everything derived:
+\begin{equation}\label{eq:derivedbasechange}
+\rm{L}f^*\R\pi_*\mathcal M\cong \R\pi'_*\rm{L}f^*\mathcal M.
+\end{equation}
+First notice that the $H^0$ on the LHS of \eqref{eq:derivedbasechange} is exactly the LHS of \ref{eq:generalbasechange}.
+
+\end{proof}
+
+\begin{prop}
+The $1$-stabilisation with divisors descends to the level of weighted curves:
+\bcd
+\MM_1^{\rm{div}}\ar[r]\ar[d] & \MM_1^{(1),\rm{div}}\ar[d] \\
+\MM_1^{\rm{wt}}\ar[r] & \MM_1^{(1),\rm{wt}}
+\ecd
+\end{prop}
+
 \subsection*{Why only cusps?} 

### 2017-12-05 draft.tex
finished and polished resume of p-fields paper

--- 2017-12-04 draft.tex
@@
 \newcommand{\hP}{\hat{\mathfrak P}}
+\newcommand{\hM}{\hat{\mathfrak M}}
 \newcommand{\oM}{\overline{\mathcal M}}
@@
 \section{From $p$-fields to the quintic three-fold}
-We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cusp invariants of the quintic three-fold up to a sign.
+We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
 This is a word-by-word repetition of the arguments in \cite{CLpfields}, once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
-Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}.
+Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it should otherwise be skipped.
 
-Let us first establish some notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is a smooth quintic three-fold.
+First we introduce the notion of the \emph{cone of sections} of a smooth object $\pazocal Z$ over a family of curves $\cC$: let $B$ be any base (algebraic stack) and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
+curves; let $\mathcal L$ be a line bundle on $\cC$.
+Then there is an algebraic stack over $B$ representing sections of $\mathcal L$, and it can be defined as $C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L)$; this is because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
+More generally, the cone of section $\mathfrak S$ of $\pazocal Z$ is defined by the universal diagram:
+\bcd
+& \pazocal Z\ar[d] \\
+\cC_{\mathfrak S}\ar[r]\ar[ur,bend left,"\mathfrak e"]\ar[d,"\pi_{\mathfrak S}"] & \cC\ar[d,"\pi"] \\
+\mathfrak S \ar[r] & B
+\ecd
+The previous case can be recovered by setting $\pazocal Z=\rm{Vb}(\mathcal L)$. The morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
+\[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\pazocal Z/\cC}\]
+Notice that in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$.
+The construction for a general smooth $\pazocal Z$ is way more flexible.
+The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex, but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
+
+Let us now establish some further notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold under consideration.
 In this section we shall denote by $\rm{M}:=\oM_1^{(1)}(\PP^4,d)$, by $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ the universal $1$-stable curve and map over it, by $\L_{\rm M}=f_{\rm M}^*\OO_{\PP^4}(1)$ and by $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}$.
-Furthermore we shall write $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\MM_1^{(1)}}$.
+Furthermore we shall write $\hM$ for $\MM_1^{(1)}$ and $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$.
 
@@
  \bcd
- \lambda^*\mathbb T_{\hP/\MM_1^{(1)}}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\MM_1^{(1)}} \ar[r,"{[}1{]}"]\ar[d] & {} \\
- \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus \mathcal L_{\rm M}^{\oplus 5})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
  \ecd
- implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus \mathcal L_{\rm M}^{\oplus 5})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
+ implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
 \end{lem}
 \begin{proof}
- The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\MM_1^{(1)}$ is unobstructed of relative dimension $0$ and $\MM_1^{(1)}$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations can be found inside $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+ The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
 
- The fact that $\mathbb T_{\rm M/\MM_1^{(1)}}\to \mathbb E_{\rm M/\MM_1^{(1)}}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is \cite[Proposition 6.3]{BF}.
+ The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
 
  The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
-The middle column comes from identifying the space of stable maps as an open substack of the cone of sections of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
+The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
 The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
@@
 \begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p$ parametrises $1$-stable maps
+ The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))$ parametrises $1$-stable maps
  \bcd
@@
 \end{dfn}
-Due to the fact that $\R^1\hat\pi_*\mathcal F$ behaves well under base change, while $\hat\pi_*\mathcal F$ may not, the correct way to formalise this is via relative Serre duality: \[\Mone{1}{\PP^4}{d}^p=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M})):=\Spec_{\rm M}(\R^1\hat\pi_{\rm M,*}(\L_{\rm M}^{\otimes 5}))\]
-We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
-\bcd
-& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
-\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
-\pazocal P \ar[r,"\PtoM"] & \rm M
-\ecd
+
+We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. %This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
+%\bcd
+%& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
+%\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
+%\pazocal P \ar[r,"\PtoM"] & \rm M
+%\ecd
 
@@
 
-In \cite[\S\S3.2-3.4]{CLpfields} the following facts are proved. Based on Serre duality, there is a morphism
+We are now going to construct the cosection as in \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by tensoring of line bundles:
 \[ h_1\colon\rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
@@
 \bcd
-& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\ar[d] \\
+& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal P_{\hP})\ar[d] \\
 \hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
@@
 \ecd
-we obtain a cosection of the relative obstruction sheaf
+(here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
 \[\begin{split}
  \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
- \sigma_{1|(u,\psi)}(z,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)z_i
+ \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
 \end{split}\]
-The degeneracy locus of such cosection is $\Mone{1}{X}{d}$ (again based on Serre duality) and $\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
+The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
+$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
 
-We are left with proving the following:
-\begin{prop}
- \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}=:GW_1^{\rm{cusp}}(X,d)\]
-\end{prop}
-This is achieved in \cite[\S4]{CLpfields} by a family version of the previous construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
+We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle, and we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
+\begin{thm}
+ \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}\]%=:GW_1^{\rm{cusp}}(X,d)\]
+\end{thm}
+This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
 
@@
  The deformation to the normal cone $V$ is cut inside $\rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t$ with basis coordinates $[x_0:\ldots:x_4]$ and fiber coordinate $y$ by the equation $\w(x)-ty=0$.
+If $C(V)$ denotes the affine cone over $V$, then its tangent bundle is determined by the following exact sequences:
+ \begin{equation*}
+  \begin{split}
+   0\to T_{C(V)/\Aaff^1_t}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}}\OO_{C(V)}\to 0 \\
+   0\to T_{C(V)}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}-y\mathring{t}}\OO_{C(V)}\to 0
+  \end{split}
+ \end{equation*}
 \end{lem}
@@
 & \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
-\hat \cC_{\pazocal V}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal V}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
-\pazocal V:=\Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
+\hat \cC_{\oM_1^{(1)}(V)}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat{\pi}_{\oM_1^{(1)}(V)}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
+\Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
 \ecd
+
+Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\pazocal Z:=\pazocal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
+The general theory explained above provides an obstruction theory for $\pazocal V\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
+
+\begin{lem}
+ A dual perfect obstruction theory is given by \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
+ The restriction of $\phi_{\pazocal V/\hP\times\Aaff^1_t}$ to a fiber
+ \[
+ \pazocal V_t=\left\{\begin{array}{lr} \pazocal P & t\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & t=0 \end{array}\right.
+\] gives the standard obstruction theory of $\pazocal V_t\to\hP$.
+\end{lem}
+
+We would like to conclude that the restriction of the virtual cycle to the fibers is the standard virtual cycle on the fiber.
+The techniques of functoriality in intersection theory teach us that we should look for a triple of compatible obstruction theories for the triangle:
+\bcd
+\pazocal V_t\ar[rr,hook,"\iota_t"]\ar[dr] & & \pazocal V \ar[dl] \\
+& \hP &
+\ecd
+The cone of sections interpretation provides us with an obstruction theory relative to $\pazocal V\to \hP$ given by:
+\[
+ \mathbb E'_{\pazocal V/\hP}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal K\oplus\mathcal P_{\pazocal V})
+\]
+where $\mathcal K$ is determined by the following exact sequence on $V$:
+\[
+ 0\to\mathcal K\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\oplus\OO_{\PP^4}\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}-y\mathring{t}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0
+\]
+Of course $h^0(\mathbb E'_{\pazocal V/\hP})\simeq\mathbb T_{\pazocal V/\hP}$, but the previous lemma hints at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\pazocal V/\hP})$ contains one factor $\R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}$ too many, so that restricting to the fibers we would find a different obstruction theory with respect to the standard one.
+A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber (i.e.
+applying $\iota_t^!$) we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
+
+This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to $\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP}$, where the latter fits into an exact triangle:
+\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]} \]
+
+A further complication comes from the fact that we need to work with cosection localised cycles.
+A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
+\[
+ \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{(\pr_2,\pr_3)}\rm{Vb}(\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{\cdot}\rm{Vb}(\omega_{\hat\pi_{\hP}})
+\]
+The cosection takes then the following form:
+\[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
+It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is $\Mone{1}{X}{d}\times\Aaff^1_t$.
+
+Recall that the sections $(x,y)$ are required to satisfy $\w(x)-ty=0$.
+So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\pazocal P$ when $t\neq 0$.
+It is proved in \cite[Theorem 5.2]{KLcosection} that the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
+\[
+ \iota_{t\neq0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\pazocal P]^{\rm{vir}}_{\rm{\sigma}}\in A_0(\pazocal Q),\quad \iota_{0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}\in A_0(\pazocal Q)
+\]
+where we have denoted by $\pazocal Q:=\Mone{1}{X}{d}$.
+
+We are left with proving that $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $[\Mone{1}{X}{d}]^{\rm{vir}}$.
+We shall introduce more shorthand notation: $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$.
+Chang and Li notice that there is a perfect obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})$ compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
+Then \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\pazocal N/\pazocal Q}$ is supported inside
+\[
+ h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{|D(\sigma_0')}
+\]
+so that they may combine the techniques of virtual pullback \cite{Manolache-pullback} and localisation by cosection \cite{KLcosection} to define:
+\[
+ v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0'))
+\]
+Finally they notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as $[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]$ along the fibers, and this is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
+
+Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves.
 

### 2017-12-05 draft.tex
finished second approach, needs reviewing

--- 2017-12-04 draft.tex
@@
 
-Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that $\omega_\pi\otimes \mathcal L^{\otimes 3}$ is $\pi$-ample.
+Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that 
+\[\omega_\pi\otimes \mathcal L^{\otimes 3}\]
+ is $\pi$-ample.
 We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
@@
 Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{wt}_1$, which we shall freely pullback and keep denoting by $E$.
-We write $\mathcal M:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$, where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+We write
+\begin{equation}\label{eq:linebundlecontraction}
+\mathcal N:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D),
+\end{equation} where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so if the contraction morphism is well defined it will contract this locus.
 
 \begin{prop}\label{1-stabilization-div}
- The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal M$:
+ The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal N$:
  \bcd
@@
 \end{prop}
-We prove a proposition through a series of Lemma s. The first one is a technical statement telling us that we can reduce to verify semi-ampleness and local freeness on families over DVR.
-\begin{lem}{Reduction to DVR}\label{DVR}
-Let $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$ and let $f\colon T\to\MM_1^{\rm{div}}$ such that $0\in \mathfrak{D}^1$ and $\eta\in \MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then
+
+We shall prove this proposition through a series of lemmas.
+The first one is a technical tool drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base change to generically chosen curves inside $\MM_1^{\rm{div}}$.
+In the following it will allow us to check that $\mathcal N$ is semi-ample and that $\pi_*\mathcal N$ is locally free assuming that $\cC\to T$ is a smoothing over the spectrum of a discrete valuation ring.
+
+\begin{lem}[pullback with a boundary]\label{DVR}
+Let $\pi\colon\cC\to S$ be a proper family of l.c.i.
+curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\Delta\subseteq S$.
+Then for every $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\Delta$ and $f(\eta)\in S\setminus\Delta$ we have
 \[f^*\pi_*\mathcal M\cong \pi_*f^*\mathcal M.\]
-We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
+%We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
 \end{lem}
 \begin{proof}
-The argument is taken from \cite[Lemmma~3.7.2.2]{RSPW}.
+The argument can be found in \cite[Lemmma~3.7.2.2]{RSPW}.
+
 Let $K^{\bullet}$ the complex of locally free sheaves on $S$ which satisfy cohomology and base change, i.e. such that for any $T\xrightarrow{f} S$  we get
@@
 where: $\phi$ is proper and birational  since $\mathcal M$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal M$ is locally free. 
+To verify that this define a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{C}$ has reduced fibers and only nodes and cusps as singularities.
 
-Consider the caresian diagram 
+Since these properties only concern the fiber of $\hat{\pi}$ so we can verify them after base change to a DVR $T$ and we can choose it as in Lemma~\ref{DVR} so that the construction commutes with base change.
+
+But then this is just the statement of Smyth's contraction Lemma~\cite[Lemma~2.13]{SMY1} if we assume $C_T$ smooth and, otherwise, one can argue following \cite[Proposition~3.7.3.1]{RSPW}:
+being $C_T$ a smoothing of a nodal curve over a DVR it is normal by Serre's criterion of normality (($R_1$), ($S_2$)).
+Moreover $C_0\setminus E\to\hat{C}_0$ is birational, which implies $\hat{C}_0$ is reduced as well.
+Finally, the fact that $\hat{C}_0$ can only acquire a cusp as singularity simply follows from the classification of genus 1 uni-branch singularities \cite[Appendix~A]{SMY1}
+
+Finally, to conclude that this define a morphism 
+\[\MM_1^{\rm{div}}\to \MM_1^{\rm{div}}(1)\]
+it is enough to verify that
+ $\rm{pr}_1(\phi)\cong\rm{pr}_2(\phi)$ where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\to S$ and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
+ The first condition follows from the fact that $\rm{pr}^*_i\phi$ are the morphism defined by 
+ $\rm{pr}_i^*\pi_{s,*}\mathcal{M}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal M.$ Thus it is enough to show that 
+ \[\rm{pr}_1^*\mathcal M\cong \rm{pr}_2^*\mathcal M.\]
+  But $\mathcal M$ is actually pulled back from $\MM_1^{\rm{div}}$ and thus the wanted isomorphism just follows from the commutativity of the following diagram
+
  \bcd
-C'\ar[r,"f_C"]\ar[d,"\pi'"] & C\ar[d,"\pi"] \\
-S'\ar[r,"f"] & S.
+S\times_{\MM_1^{\rm{div}}} S\ar[r,"\rm{pr_1}"]\ar[d, "\rm{pr_2}"] & S\ar[d] \\
+S\ar[r] & \MM_1^{\rm{div}}
 \ecd
-To show that the above construction is compatible with base change it is enough to show that for any base change holds what we proved in Lemma~\ref{DVR}:
-\begin{equation}\label{eq:generalbasechange}
-f^*\pi_*\mathcal M\cong \pi'_*f^*\mathcal M.
-\end{equation}
-Since $\pi$ is flat we do have an isomorphism if we consider everything derived:
-\begin{equation}\label{eq:derivedbasechange}
-\rm{L}f^*\R\pi_*\mathcal M\cong \R\pi'_*\rm{L}f^*\mathcal M.
-\end{equation}
-First notice that the $H^0$ on the LHS of \eqref{eq:derivedbasechange} is exactly the LHS of \ref{eq:generalbasechange}.
 
+The  cocycle condition is similarly straightforward to verify. 
 \end{proof}
@@
 \end{prop}
+\begin{proof}
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can always choose sections $s_i$s such that the associated Cartier divisor $D$ satisfies that $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ is trivial on elliptic tails and ample else-where.
+Then if $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to take an {\'e}tale cover we can assume there are sections  $s_i$ s of $\mathcal C_S\xrightarrow{\pi_S} S$ defining a lifting $S\to \MM_1^{\rm{div}}$ and thus trough the above construction a morphism $S\to  \MM_1^{(1),\rm{wt}}.$
+
+Now to show this define a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{(1),\rm{wt}}$ we need once again to verify that, in the notation of the above Proposition,  $\rm{pr}_1(\phi)\cong\rm{pr}_2(\phi)$  and the cocycle condition is satisfied.
+
+In other words, we need to check that for two different lifting $S\xrightarrow{s_i,\;s'_i}\MM_1^{\rm{div}}$, 
+\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(D_1))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(D_2))^{\otimes n}\right)=\hat{\mathcal C}_2.
+\]
+By construction, we have a birational map 
+ \bcd
+&\mathcal C \ar[dl,"\phi_1"]\ar[dr,"\phi_2"]  \\
+ \hat{\mathcal C}_1\ar[rr,dashed, "\psi"] & &\hat{\mathcal C}_2.
+ \ecd
+
+We want to show that it extends to a regular morphism. 
+First of all, notice that $ \hat{\mathcal C}_i$ are normal.
+Indeed, since $S$ is smooth and the singularities of the fibers are in co-dimension 1, both $ \hat{\mathcal C}_i$ are regular in codimension 1.
+Moreover, since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy the ($S_2$) condition of Serre, also the total spaces do\cite[Thorem~23.9]{MAT}.
+In particular, this implies  that
+\[\phi_{i,*}\OO_{\mathcal C}\cong \OO_{\hat{\mathcal C}_i} \]
+ Moreover notice that by construction $\operatorname{Ex}(\phi_1)\cong \operatorname{Ex}(\phi_2),$ so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then a standard argument \cite{debarre}
+shows that $\phi_2$ factorise through $\phi_1$ and vice versa. This prove the existence of the isomorphism $\psi.$ Notice that this is in fact unique as it is the one making the diagram commutative.
+
+Likewise we can show the cocycle condition and thus the proof is completed.
+\end{proof}
 
 \subsection*{Why only cusps?}
-\subsection*{Alternative constructions}
-\begin{itemize}
-\item adapt the ideas of \cite{HassettHyeon}: check out section 3 of this paper;
-\item check \cite[\S 4]{RSPW}.
-\end{itemize}
+
  \section{Comparison with $p$-fields and splitting}

### 2017-12-06 draft.tex
reviewed

--- 2017-12-04 draft.tex
@@
 
-Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{wt}_1$, which we shall freely pullback and keep denoting by $E$.
-We write $\mathcal M:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$, where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $E$.
+We shall also denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$ (and its various pullbacks), which is a Cartier divisor as well.
+
+We write 
+\begin{equation}\label{eq:linebundlecontraction}
+\mathcal N:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D),
+\end{equation} where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so if the contraction morphism is well defined it will contract this locus.
 
 \begin{prop}\label{1-stabilization-div}
- The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal M$:
+ The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal N$:
  \bcd
- (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
  & \MM_1^{\rm{div}} &
@@
 \end{prop}
-We prove a proposition through a series of Lemma s. The first one is a technical statement telling us that we can reduce to verify semi-ampleness and local freeness on families over DVR.
-\begin{lem}{Reduction to DVR}\label{DVR}
-Let $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$ and let $f\colon T\to\MM_1^{\rm{div}}$ such that $0\in \mathfrak{D}^1$ and $\eta\in \MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then
-\[f^*\pi_*\mathcal M\cong \pi_*f^*\mathcal M.\]
-We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
+
+We shall prove this proposition through a series of lemmas.
+The first one is a technical tool drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base change to generically chosen curves inside $\MM_1^{\rm{div}}$.
+In the following it will allow us to check that $\mathcal N$ is semi-ample and that $\pi_*\mathcal N$ is locally free assuming that $\cC\to T$ is a smoothing over the spectrum of a discrete valuation ring.
+
+\begin{lem}[pullback with a boundary]\label{DVR}
+Let $\pi\colon\cC\to S$ be a proper family of curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\mathfrak D\subseteq S$.
+Then for every $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
+\[f^*\pi_*\mathcal N\cong \pi_*f^*\mathcal N.\]
+%We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
 \end{lem}
 \begin{proof}
-The argument is taken from \cite[Lemmma~3.7.2.2]{RSPW}.
+The argument can be found in \cite[Lemmma~3.7.2.2]{RSPW}.
+\begin{color}{gray}{
 Let $K^{\bullet}$ the complex of locally free sheaves on $S$ which satisfy cohomology and base change, i.e. such that for any $T\xrightarrow{f} S$  we get
@@
 \end{align*} 
-Now, notice that $\R^1\pi_*\mathcal M$ is a line bundle supported on the Cartier divisor $\mathfrak{D}^1;$ it is clearly zero on the smooth locus and one can easily check that is rank is constant and equal to one on the divisor.
 To prove that $\rm{L}_if^*\R^1\pi_*\mathcal M=0$ for $i=1,2$ it is enough to work locally on $S$, where we have a free resolution for  of the form $\R^1\pi_*\mathcal M$ of the form:
@@
 and thus pulling back along $f$
-\[0\rightarrow  \rm{L}_1f^*\R^1\pi_*\mathcal M \OO_T\xrightarrow{f^*g}\OO_T\rightarrow f^*\R^1\pi_*\mathcal M\rightarrow 0.\] 
+\[0\rightarrow  \rm{L}_1f^*\R^1\pi_*\mathcal M \to \OO_T\xrightarrow{f^*g}\OO_T\rightarrow f^*\R^1\pi_*\mathcal M\rightarrow 0.\] 
 It immediately follows that $ \rm{L}_2f^*\R^1\pi_*\mathcal M=0.$ Finally notice that since the image of $f$ is not contained in the boundary divisor $f^*g\neq 0$ and thus injective of sheaves as $T$ is a DVR.
-We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.
+We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.}\end{color}
 \end{proof}
+Now recall that $\mathcal N$ is trivial on elliptic tails and of positive degree everywhere else.
+The rank of $\R^1\pi_*\mathcal N$ can be checked on the fibers \cite[Theorem III.12.11]{HAR}, so we see that it is $0$ outside $\mathfrak D^1$ and $1$ on it.
+
 \begin{lem}\label{lemma:semiample}
-The line bundle $\mathcal M$ is $\pi$ semi-ample, i.e. the natural map
-\[\pi^*\pi_*\mathcal M^{\otimes n}\to \mathcal M^{\otimes n}\]
+The line bundle $\mathcal N$ is $\pi$ semi-ample, i.e. the natural map
+\[\pi^*\pi_*\mathcal N^{\otimes n}\to \mathcal N^{\otimes n}\]
 is surjective.
@@
 \begin{proof}
-Outside the locus of elliptic tails $\mathcal M$ is $\pi$- ample and thus in particular $\pi$-semi ample.
-To check that it is still $\pi$-semi ample also for any $x\in C$ when $C$ has an elliptic tail, thanks to the above Lemma we can reduce to check this condition when $C$ is the central fiber of a one parameter smoothing of the elliptic tail.
-But then this has been proved by Smyth~\cite[Lemma~2.12]{SMY1}.
+Outside the locus of elliptic tails $\mathcal N$ is $\pi$-ample.
+We are left to check on points belonging to an elliptic tail; thanks to the above Lemma we can reduce to the case that $C$ is the central fiber of a one-parameter smoothing of the elliptic tail.
+This has been proved by Smyth~\cite[Lemma~2.12]{SMY1}.
 \end{proof}
@@
 \begin{lem}
-$\pi_*\mathcal M$ is locally free of rank $d$ on $\MM_1^{\rm{div}}.$
+$\pi_*\mathcal N$ is locally free on $\MM_1^{\rm{div}}.$
 \end{lem}
 \begin{proof}\cite[Proposition~3.7.2.1]{RSPW}
-We have essentially to check that $\pi_*\mathcal M$ has constant rank.
-On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ this follows simply from the fact that $\R^1\pi_*\mathcal M=0$ and the rank is determined by Riemann-Roch.
-Given a point $x$ on the boundary $\mathfrak{D}^1$, we can always find a DVR $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypothesis of Lemma~\ref{DVR} and thus we can check the rank looking at $\pi_*f^*\mathcal M$ over the DVR  $T.$ But notice that $\pi_*f^*\mathcal M$ is torsion free over $T$, which conclude the proof.
+We have to check that $\pi_*\mathcal N$ has constant rank.
+On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ we see that $\R^1\pi_*\mathcal N=0$, so $\pi_*\mathcal N$ satisfies Cohomology and Base Change and its rank is determined by Riemann-Roch.
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can always find a DVR $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank looking at $\pi_*f^*\mathcal N$ over the DVR scheme $T.$ But now $f^*\mathcal N$ is flat over $T$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free over $T$.
 \end{proof}
@@
  \bcd
- (C,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat C=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ (C,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat C=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
  & S &
  \ecd
-where: $\phi$ is proper and birational  since $\mathcal M$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal M$ is locally free.
+where $\phi$ is proper and birational morphism since $\mathcal N$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal N$ is locally free. 
+To verify that this define a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{C}$ has reduced fibers and only nodes and cusps as singularities.
 
-Consider the caresian diagram 
+Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $T$ chosen as in Lemma~\ref{DVR} so that the construction commutes with base change.
+Furthermore we can pick $f\colon T\to \MM_1$ so that the total space $\cC_T$ is regular, so we are in the hypotheses of Smyth's contraction Lemma~\cite[Lemma~2.13]{SMY1}
+
+Finally to conclude that this defines a morphism 
+\[\MM_1^{\rm{div}}\to \MM_1^{\rm{div}}(1)\]
+it is enough to verify that there is an isomorphism
+ $\rm{pr}_1^*\hat\cC\cong\rm{pr}_2^*\hat\cC$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
+
+ This follows from the fact that $\pr_i^*\hat\cC$ are obtained from applying the Proj construction to 
+ $\rm{pr}_i^*\pi_{S,*}\mathcal{N}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal N$, by flatness of $S'\to S$. Thus it is enough to show that 
+ \[\rm{pr}_1^*\mathcal N\cong \rm{pr}_2^*\mathcal N.\]
+  But $\mathcal N$ is the pullback of a line bundle on $\MM_1^{\rm{div}}$, thus the desired isomorphism follows from the commutativity of the following diagram
+
  \bcd
-C'\ar[r,"f_C"]\ar[d,"\pi'"] & C\ar[d,"\pi"] \\
-S'\ar[r,"f"] & S.
+S\times_{\MM_1^{\rm{div}}} S\ar[r,"\rm{pr_1}"]\ar[d, "\rm{pr_2}"] & S\ar[d] \\
+S\ar[r] & \MM_1^{\rm{div}}
 \ecd
-To show that the above construction is compatible with base change it is enough to show that for any base change holds what we proved in Lemma~\ref{DVR}:
-\begin{equation}\label{eq:generalbasechange}
-f^*\pi_*\mathcal M\cong \pi'_*f^*\mathcal M.
-\end{equation}
-Since $\pi$ is flat we do have an isomorphism if we consider everything derived:
-\begin{equation}\label{eq:derivedbasechange}
-\rm{L}f^*\R\pi_*\mathcal M\cong \R\pi'_*\rm{L}f^*\mathcal M.
-\end{equation}
-First notice that the $H^0$ on the LHS of \eqref{eq:derivedbasechange} is exactly the LHS of \ref{eq:generalbasechange}.
 
+The cocycle condition is derived similarly. 
 \end{proof}
@@
 \end{prop}
+\begin{proof}
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose sections $s_i$ such that their sum as a relative Cartier divisor $D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
+If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to taking an {\'e}tale cover we can assume there are sections $s_i$ of $\cC_S\xrightarrow{\pi_S} S$ that define a lifting $S\to \MM_1^{\rm{div}}$ and thus through the above construction a morphism $\xi\colon S\to  \MM_1^{(1),\rm{wt}}.$
+
+In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{(1),\rm{wt}}$ we need to verify that  $\rm{pr}_1(\xi)\cong\rm{pr}_2(\xi)$ and the cocycle condition is satisfied, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
+
+This boils down to checking that for two different choices of a lifting $S\xrightarrow{s_i,\;s'_i}\MM_1^{\rm{div}}$ we have a unique isomorphism 
+\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D'))^{\otimes n}\right)=\hat{\mathcal C}_2.
+\]
+By construction we have a birational map 
+ \bcd
+&\mathcal C \ar[dl,"\phi_1"]\ar[dr,"\phi_2"]  \\
+ \hat{\mathcal C}_1\ar[rr,dashed, "\psi"] & &\hat{\mathcal C}_2.
+ \ecd
+
+We want to show that it extends to a regular morphism. 
+First of all notice that $ \hat{\mathcal C}_i$ is normal, $i=1,2$.
+Indeed, since $S$ is smooth and the singularities of the fibers are in co-dimension 1, $ \hat{\mathcal C}_i$ is regular in codimension 1.
+Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy the ($S_2$) condition of Serre, also the total space does \cite[Thorem~23.9]{MAT}.
+Then, since the fibers are geometrically connected, Zariski's connectedness theorem implies that
+\[\phi_{i,*}\OO_{\mathcal C}\cong \OO_{\hat{\mathcal C}_i} \]
+ Moreover notice that by construction $\operatorname{Ex}(\phi_1)\cong \operatorname{Ex}(\phi_2),$ so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then a standard argument \cite[Lemma 1.15]{debarre}
+shows that $\phi_2$ factors through $\phi_1$ and vice versa. This proves the regularity of $\psi$ and its inverse. Notice that $\psi$ is unique as it is the only extension of $\phi_2\circ\phi_1^{-1}$.
+\end{proof}
 
 \subsection*{Why only cusps?}
-\subsection*{Alternative constructions}
-\begin{itemize}
-\item adapt the ideas of \cite{HassettHyeon}: check out section 3 of this paper;
-\item check \cite[\S 4]{RSPW}.
-\end{itemize}
+
  \section{Comparison with $p$-fields and splitting}
@@
 \end{itemize}
+
 \bibliographystyle{alpha}

### 2017-12-06 draft.tex

--- 2017-12-05 draft.tex
@@
 \subsection{Second approach: constructing the contraction}
+
 The idea of this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
 
-Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that $\omega_\pi\otimes \mathcal L^{\otimes 3}$ is $\pi$-ample.
+Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that 
+\[\omega_\pi\otimes \mathcal L^{\otimes 3}\]
+ is $\pi$-ample.
 We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
@@
 
-Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{wt}_1$, which we shall freely pullback and keep denoting by $E$.
-We write $\mathcal M:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$, where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $E$.
+We shall also denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$ (and its various pullbacks), which is a Cartier divisor as well.
 
-\begin{prop}
- The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal M$:
+We write 
+\begin{equation}\label{eq:linebundlecontraction}
+\mathcal N:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D),
+\end{equation} where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
+Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so if the contraction morphism is well defined it will contract this locus.
+
+\begin{prop}\label{1-stabilization-div}
+ The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal N$:
  \bcd
- (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal M^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
  & \MM_1^{\rm{div}} &
@@
 \end{prop}
+
+We shall prove this proposition through a series of lemmas.
+The first one is a technical tool drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base change to generically chosen curves inside $\MM_1^{\rm{div}}$.
+In the following it will allow us to check that $\mathcal N$ is semi-ample and that $\pi_*\mathcal N$ is locally free assuming that $\cC\to T$ is a smoothing over the spectrum of a discrete valuation ring.
+
+\begin{lem}[pullback with a boundary]\label{DVR}
+Let $\pi\colon\cC\to S$ be a proper family of curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\mathfrak D\subseteq S$.
+Then for every $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
+\[f^*\pi_*\mathcal N\cong \pi_*f^*\mathcal N.\]
+%We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
+\end{lem}
+\begin{proof}
+The argument can be found in \cite[Lemmma~3.7.2.2]{RSPW}.
+\begin{color}{gray}{
+Let $K^{\bullet}$ the complex of locally free sheaves on $S$ which satisfy cohomology and base change, i.e. such that for any $T\xrightarrow{f} S$  we get
+$H^i(f^*K^{\bullet})=\R^i\pi_*f^*\mathcal M.$ The construction of $K^{\bullet}$ is standard, (see e.g.
+\cite[Proposition~12.2]{HAR} and since the cohomology is concentrated in degree 0,1, we can assume $K^{\bullet}=K_0\to K_1.$ Let $f$ be the map defined in the statement of the Lemma.
+Then we have the following exact sequences:
+\begin{equation}\label{eq:exact1}
+0\to \pi_*\mathcal M\to K^0\to K^1\to \R^1\pi_*\mathcal M\to 0,
+\end{equation}
+\begin{equation}\label{eq:exact2}
+0\to \pi_*f^*\mathcal M\to f^*K^0\to f^*K^1\to \R^1\pi_*f^*\mathcal M\to 0.
+\end{equation}
+The derived pull-back $Lf^*$ of the complex~\eqref{eq:exact1} is zero since the complex is exact.
+Writing down explicitly the spectral sequence which compute the derived pull-back, we find that its convergence to zero implies that:
+\begin{align*}
+\operatorname{coker}(f^*\pi_*\mathcal M\to\pi_*f^*\mathcal M)&\cong \rm{L}_1f^*\R^1\pi_*\mathcal M\\
+\operatorname{ker}(f^*\pi_*\mathcal M\to\pi_*f^*\mathcal M)&\cong \rm{L}_2f^*\R^1\pi_*\mathcal M.
+\end{align*} 
+To prove that $\rm{L}_if^*\R^1\pi_*\mathcal M=0$ for $i=1,2$ it is enough to work locally on $S$, where we have a free resolution for  of the form $\R^1\pi_*\mathcal M$ of the form:
+\[0\rightarrow \OO_S\xrightarrow{g}\OO_S\rightarrow \R^1\pi_*\mathcal M\rightarrow 0\] 
+and thus pulling back along $f$
+\[0\rightarrow  \rm{L}_1f^*\R^1\pi_*\mathcal M \to \OO_T\xrightarrow{f^*g}\OO_T\rightarrow f^*\R^1\pi_*\mathcal M\rightarrow 0.\] 
+It immediately follows that $ \rm{L}_2f^*\R^1\pi_*\mathcal M=0.$ Finally notice that since the image of $f$ is not contained in the boundary divisor $f^*g\neq 0$ and thus injective of sheaves as $T$ is a DVR.
+We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.}\end{color}
+\end{proof}
+Now recall that $\mathcal N$ is trivial on elliptic tails and of positive degree everywhere else.
+The rank of $\R^1\pi_*\mathcal N$ can be checked on the fibers \cite[Theorem III.12.11]{HAR}, so we see that it is $0$ outside $\mathfrak D^1$ and $1$ on it.
+
+\begin{lem}\label{lemma:semiample}
+The line bundle $\mathcal N$ is $\pi$ semi-ample, i.e. the natural map
+\[\pi^*\pi_*\mathcal N^{\otimes n}\to \mathcal N^{\otimes n}\]
+is surjective.
+\end{lem}
+\begin{proof}
+Outside the locus of elliptic tails $\mathcal N$ is $\pi$-ample.
+We are left to check on points belonging to an elliptic tail; thanks to the above Lemma we can reduce to the case that $C$ is the central fiber of a one-parameter smoothing of the elliptic tail.
+This has been proved by Smyth~\cite[Lemma~2.12]{SMY1}.
+\end{proof}
+
+\begin{lem}
+$\pi_*\mathcal N$ is locally free on $\MM_1^{\rm{div}}.$
+\end{lem}
+\begin{proof}\cite[Proposition~3.7.2.1]{RSPW}
+We have to check that $\pi_*\mathcal N$ has constant rank.
+On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ we see that $\R^1\pi_*\mathcal N=0$, so $\pi_*\mathcal N$ satisfies Cohomology and Base Change and its rank is determined by Riemann-Roch.
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can always find a DVR $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank looking at $\pi_*f^*\mathcal N$ over the DVR scheme $T.$ But now $f^*\mathcal N$ is flat over $T$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free over $T$.
+\end{proof}
+
+\begin{proof}\ref{1-stabilization-div}
+Let $S\to \MM_1^{\rm{div}}$ be a smooth atlas, then we have:
+ \bcd
+ (C,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat C=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ & S &
+ \ecd
+where $\phi$ is proper and birational morphism since $\mathcal N$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal N$ is locally free. 
+To verify that this define a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{C}$ has reduced fibers and only nodes and cusps as singularities.
+
+Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $T$ chosen as in Lemma~\ref{DVR} so that the construction commutes with base change.
+Furthermore we can pick $f\colon T\to \MM_1$ so that the total space $\cC_T$ is regular, so we are in the hypotheses of Smyth's contraction Lemma~\cite[Lemma~2.13]{SMY1}
+
+Finally to conclude that this defines a morphism 
+\[\MM_1^{\rm{div}}\to \MM_1^{\rm{div}}(1)\]
+it is enough to verify that there is an isomorphism
+ $\rm{pr}_1^*\hat\cC\cong\rm{pr}_2^*\hat\cC$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
+
+ This follows from the fact that $\pr_i^*\hat\cC$ are obtained from applying the Proj construction to 
+ $\rm{pr}_i^*\pi_{S,*}\mathcal{N}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal N$, by flatness of $S'\to S$. Thus it is enough to show that 
+ \[\rm{pr}_1^*\mathcal N\cong \rm{pr}_2^*\mathcal N.\]
+  But $\mathcal N$ is the pullback of a line bundle on $\MM_1^{\rm{div}}$, thus the desired isomorphism follows from the commutativity of the following diagram
+
+ \bcd
+S\times_{\MM_1^{\rm{div}}} S\ar[r,"\rm{pr_1}"]\ar[d, "\rm{pr_2}"] & S\ar[d] \\
+S\ar[r] & \MM_1^{\rm{div}}
+\ecd
+
+The cocycle condition is derived similarly. 
+\end{proof}
+
 \begin{prop}
@@
 \end{prop}
+\begin{proof}
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose sections $s_i$ such that their sum as a relative Cartier divisor $D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
+If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to taking an {\'e}tale cover we can assume there are sections $s_i$ of $\cC_S\xrightarrow{\pi_S} S$ that define a lifting $S\to \MM_1^{\rm{div}}$ and thus through the above construction a morphism $\xi\colon S\to  \MM_1^{(1),\rm{wt}}.$
 
-\subsection*{Why only cusps?} 
-\subsection*{Alternative constructions}
-\begin{itemize}
-\item adapt the ideas of \cite{HassettHyeon}: check out section 3 of this paper;
-\item check \cite[\S 4]{RSPW}.
-\end{itemize}
+In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{(1),\rm{wt}}$ we need to verify that  $\rm{pr}_1(\xi)\cong\rm{pr}_2(\xi)$ and the cocycle condition is satisfied, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
+
+This boils down to checking that for two different choices of a lifting $S\xrightarrow{s_i,\;s'_i}\MM_1^{\rm{div}}$ we have a unique isomorphism 
+\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D'))^{\otimes n}\right)=\hat{\mathcal C}_2.
+\]
+By construction we have a birational map 
+ \bcd
+&\mathcal C \ar[dl,"\phi_1"]\ar[dr,"\phi_2"]  \\
+ \hat{\mathcal C}_1\ar[rr,dashed, "\psi"] & &\hat{\mathcal C}_2.
+ \ecd
+
+We want to show that it extends to a regular morphism. 
+First of all notice that $ \hat{\mathcal C}_i$ is normal, $i=1,2$.
+Indeed, since $S$ is smooth and the singularities of the fibers are in co-dimension 1, $ \hat{\mathcal C}_i$ is regular in codimension 1.
+Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy the ($S_2$) condition of Serre, also the total space does \cite[Thorem~23.9]{MAT}.
+Then, since the fibers are geometrically connected, Zariski's connectedness theorem implies that
+\[\phi_{i,*}\OO_{\mathcal C}\cong \OO_{\hat{\mathcal C}_i} \]
+ Moreover notice that by construction $\operatorname{Ex}(\phi_1)\cong \operatorname{Ex}(\phi_2),$ so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then a standard argument \cite[Lemma 1.15]{debarre}
+shows that $\phi_2$ factors through $\phi_1$ and vice versa. This proves the regularity of $\psi$ and its inverse. Notice that $\psi$ is unique as it is the only extension of $\phi_2\circ\phi_1^{-1}$.
+\end{proof}
 

### 2017-12-07 draft.tex
equations and splitting

@@
 \newcommand{\B}{\mathcal B}
-\newcommand{\X}{\mathcal X}
-\newcommand{\XP}{\mathcal{XP}}
+\newcommand{\X}{\pazocal X}
+\newcommand{\XP}{\pazocal{X\!P}}
+\newcommand{\tXP}{\tilde{\pazocal{X\!P}}}
 \renewcommand{\L}{\mathcal L}
@@
 \newcommand{\cC}{\mathcal C}
-\newcommand{\Z}{\mathcal Z}
+\newcommand{\Z}{\pazocal Z}
+\newcommand{\Zp}{\pazocal Z^p}
+\newcommand{\tZ}{\widetilde{\pazocal Z}}
+\newcommand{\tZp}{\widetilde{\pazocal Z}^p}
 \newcommand{\MM}{\mathfrak M}
@@
 \newcommand{\hM}{\hat{\mathfrak M}}
-\newcommand{\oM}{\overline{\mathcal M}}
+\newcommand{\oM}{\overline{\pazocal M}}
+\newcommand{\tM}{\widetilde{\pazocal M}}
 \newcommand{\R}{\operatorname{R}}
@@
 \newcommand{\PtoM}{\rho}
+\newcommand{\vir}[1]{[#1]^{\rm{vir}}}
+\newcommand{\virloc}[1]{[#1]^{\rm{vir}}_{\rm{loc}}}
 
@@
 
-\section{Comparison with $p$-fields and splitting}
+\section{Local equations and desingularisation}
 \subsection{Notation}
@@
 \mathcal Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\mathcal X\ar[r] & \mathfrak M_1^{(1)}
+\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
 \ecd
@@
 \ecd
-where $\psi$ and $\hat\psi$ are isomorphisms; note once again that $\hat \psi$ is determined by $\psi$, due to the required commutativity with the dominant ``birational'' morphism $\phi$.
-
-Forgetting $\hat \cC$ and keeping $f\circ\phi\colon \cC\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d)$, which we claim is a \emph{closed embedding}: in fact, from the above description of arrows in $\Z$, it is representable (i.e.
-faithful) and a proper (check the valuative criterion: use the fact that $\X\to\MM_1$ is proper, and the map to $\PP$ descends to the $1$-stabilisation because we are only contracting weight $0$ elliptic tails; compare with \cite[Theorem 4.3]{RSPW}) monomorphism (i.e.
-full).
+where $\psi$ and $\hat\psi$ are isomorphisms.  Recall that $\hat \psi$ is determined by $\psi$. %due to the required commutativity with the dominant ``birational'' morphism $\phi$.
+
+Forgetting $\hat \cC$ and keeping $f\circ\phi\colon \cC\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d).$
+
+\begin{lem}
+The morphism $i\colon\Z\hookrightarrow\oM_1(\PP^4,d)$ is a closed immersion. In particular $\Z$ is a proper DM stack.
+\end{lem}
+\begin{proof}
+From the above description of arrows in $\Z$, $i$ is  representable (i.e. faithful)  and a monomorphism (i.e. full).
+
+We can check properness using the valuative criterion. We argue as in \cite[Theorem 4.3]{RSPW}. Let $T$ be a DVR scheme with generic point $\eta;$ consider a diagram:
+\bcd
+\cC_{\eta}\ar[r]\ar[d,"\phi_{\eta}"]  & \cC_T\ar[d,"\phi_T"]\ar[r,"f"] &\PP^4\\
+\hat{\cC}_{\eta}\ar[r,"j"]\ar[urr] & \hat{\cC_T}\ar[ur,dashed ,"g"] &
+ \ecd 
+Notice that there is an open dense substack of $\Z$ where $\phi$ is an isomorphism.
+Indeed the generic point of either the main component or any boundary component is already $1$-stable.
+Thus we can assume that $\phi_{\eta}$ in the above diagram is an isomorphism.
+
+Observe that $f$ is constant on the fibers of $\phi$ so it factors topologically through $\hat{\cC}.$
+We can conclude as in \cite{RSPW} or show that $\phi_*\OO_{\cC_T}\cong\OO_{\hat{\cC}_T}$ and appeal to \cite[Lemma~1.15]{debarre}. To do that, consider the exact sequence:
+\[0\to \OO_{\hat{\cC}_T}\to\phi_*\OO_{\cC_T}\to \phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T}\to 0\]
+Since $\phi$ is an isomorphism away from the cuspidal point, the cokernel is supported in dimension $0$.
+However $\chi (\OO_{\hat{\cC}_T})=\chi(\phi_*\OO_{\cC_T})$ as we can check on $\eta$ since the Euler characteristic is constant in flat families.
+So   $\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T}=0.$
+\end{proof}
+
 So we may add the commutative diagram to the left:
@@
 \oM_1(\PP^4,d)\ar[d] & \mathcal Z \ar[l,swap,hook,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\MM_1 & \mathcal X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{(1)}
-\ecd
-
-\begin{lem}
-There is a closed embedding $i\colon\Z\hookrightarrow\oM_1(\PP^4,d)$. In particular $\Z$ is a proper DM stack.
-\end{lem}
-
-Furthermore we inherit a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
+\MM^{\rm{wt}}_1 & \mathcal \MM^{\rm{wt}}_1\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{\rm{wt},(1)}
+\ecd
+
+From the inclusion we inherit a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
+
 Notice that the above lemma signifies that each and every component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$.
@@
 
-\textcolor{red}{Introduce a Hu-Li type blow-up of $\MM_1^{(1)}$.}
-
-We can push this reasoning further to the level of $p$-fields:
-\bcd
-\oM_1(\PP^4,d)^p\ar[d] & \mathcal Z^p \ar[l,swap,hook,"j"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
-\oM_1(\PP^4,d)\ar[d] & \mathcal Z \ar[l,swap,hook,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\MM_1 & \mathcal X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{(1)}
-\ecd
+We introduce some more notation: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
+\bcd
+\mathcal Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
+\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)} \ar[d] \\
+\X\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
+\ecd
+
+We are going to use the obstruction theory $\R^\bullet\hat{\pi}_*(\mathcal L^{\oplus 5}\oplus\mathcal P)$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1^{(1)}$ to induce a virtual class on $\Z^p$ which we would like to compare with ordinary $p$-fields.
+
+Remark that $\XP$ parametrises
+\bcd
+\cC\ar[rr,"\phi"]\ar[dr] & & \hat\cC\ar[ld] \\
+& S &
+\ecd
+with a line bundle $\hat{\mathcal L}$ on $\hat{\cC}$.
+Notice that by pulling back $\hat{\mathcal L}$ via $\phi$ we obtain a line bundle on $\cC$, hence a morphism $\XP\to \mathfrak{Pic}_1$.
+This is generically an isomorphism, but has $1$-dimensional fibers over the locus of elliptic tails, due to the fact that $\Pic(\hat C)\to\Pic(C)$ has kernel $\mathbb G_{\rm a}$ when $\hat C$ has a cusp.
+
+Similarly $\Z^p$ parametrises
+\bcd
+\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[ld,"\hat\pi"] \ar[r,"f"] & \PP^4\\
+& S & &
+\ecd
+with a $p$-field $\psi\in H^0(\hat\cC,f^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi}$.
+\begin{remark}
+why we cannot include $\Z^p$ into $p$-fields
+\end{remark}
+
+As anticipated, we may endow $\Z^p$ with a virtual class by ``localised virtual pullback'': indeed $\XP$ is a smooth Artin stack, and:
+\[
+\mathfrak C_{\Z^p/\XP} \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1^{(1)}}} \subseteq \alpha^* h^1/h^0(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1^{(1)}}})_\sigma
+\]
+
+\begin{lem}
+localised virtual pullback commutes with pushforward
+\end{lem}
+\marginpar{check \cite{KLcosection}}
+
+\begin{cor}
+$\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
+\end{cor}
+\subsection{Equations for $\Z^p$ relative to $\XP$}
+We are going to need a description of the normal cone $\mathfrak C_{\Z^p/\XP}$ in order to perform a splitting.
+
+Since $\Z^p$ simply is a line bundle over the boundary of $\Z$, we may instead find equations for the latter.
+
+Recall that $\Z$ can be embedded as an open inside $C(\hat{\pi}_*\mathcal L^{\oplus 5})$ over $\XP$.
+We are going to find an embedding of $C(\hat{\pi}_*\mathcal L^{\oplus 5})$ in a smooth ambient space over $\XP$, that will be a vector bundle obtained by suitably twisting $\mathcal L$.
+
+Following \cite{HL}, we work locally on $\Z$: start with a point $\xi=[(C\xrightarrow{\phi}\hat C\xrightarrow{f}\PP^4]\in\Z$ and choose coordinates on $\PP^4$ such that $f^{-1}\{x_0=0\}$ is a simple smooth divisor $D=\sum_{i=1}^d\delta_i$ on $\hat C$.
+This continues to be true on a neighbourhood $U$.
+
+ Locally the morphism $\Z\to\XP$ can be written as $\xi\mapsto[C\to\hat C,\OO_{\hat C}(D)]$, which admits a local lifting $U\to\MM_1^{(1),\rm{div}}$ and in fact hits the smooth locus of the latter.
+
+  Notice though that the projection $\MM_1^{(1),\rm{div}}\to \XP$ (or to $\Pic_1^{(1)}$ for what it is worth) is \emph{not} smooth.
+In fact, when the line bundle is trivial on the minimal elliptic subcurve $E$, it may be deformed to a degree $0$, non-effective line bundle on such a subcurve, so that sections of $\OO_{\hat C}(D)$ which are constant and non-zero on $E$ are obstructed.
+
+There is a way around this: in a neighbourhood $V\subseteq \XP$ of $[C\to\hat C,\OO_{\hat C}(D)]$ we can write the universal line bundle $\mathcal L_V$ as $\OO_{\hat\cC_V}(\pazocal D + p-p_0)$.
+Indeed we can pick a local section $p_0$ through the minimal genus $1$ subcurve, so that $\mathcal L_V(p_0)$ becomes effective.
+We should then think of $p$ as a local coordinate on $\XP$ relative to $\X$.
+
+Locally on $V$ we can pick another smooth section $\A$ of the minimal genus $1$ subcurve not intersecting $p_0$, neither the support of $\pazocal D+p$.
+
+\begin{lem}
+$C(\hat\pi_*\mathcal L)$ is the kernel of the vector bundle map:
+\[ \hat\pi_*\OO_{\hat\cC}(\A+\pazocal D+p-p_0)\xrightarrow{\varphi}\hat\pi_*\OO_{\A}(\A)\]
+Up to shrinking $V$ we may write:
+\[\hat\pi_*\OO_{\hat\cC}(\A+\pazocal D+p-p_0)\cong\bigoplus_{i=1}^d\hat\pi_*\OO_{\hat\cC}(\A+\pazocal \delta_i+p-p_0)\oplus\hat\pi_*\OO_{\hat\cC}(\A+p-p_0)\]
+\end{lem}
+Compare with \cite[Lemma 4.10]{HL}.
+Denote by \[\varphi_i\colon\hat\pi_*\OO_{\hat\cC}(\A+\pazocal \delta_i+p-p_0)\to\hat\pi_*\OO_{\A}(\A)\] (and similarly $\varphi_p$) the composite of the inclusion with $\varphi$.
+
+Let us introduce some more notation: around a point $[\hat C]\in\MM_1^{(1),\rm{wt}}$, for every node $q$ of $\hat C$ there is a coordinate $\zeta_q$ whose vanishing locus is the divisor where such a node is \emph{not} smoothed.
+These functions can be pulled back to $V$.
+Denote by \[\zeta_{[\delta_i,a]}=\prod\zeta_q\]
+where the product runs over all the nodes separating $\delta_i$ from the minimal genus $1$ curve.
+
+\begin{lem}
+We may find an explicit local expression for $\varphi_i$ and $\varphi_p$ after trivialising the relevant line bundles:
+\[\varphi_i=\zeta_{[\delta_i,a]}, \quad \varphi_p=(p-p_0)\]
+\end{lem}
+Compare with \cite[Proposition 4.13]{HL}.
+\begin{remark}
+The vanishing locus of $(p-p_0)$ on the boundary means that the line bundle restricts to the trivial one on the minimal genus $1$ subcurve. The meaning of it is not clear outside the boundary.
+\end{remark}
+
+\begin{lem}\label{lem:equations}
+A local chart $U$ for $\Z$ can be embedded as an open inside:
+\[ (F_0=\ldots=F_4=0)\subseteq \rm{Vb}(\hat{\pi}_*\mathcal L^{\oplus 5}) \]
+where
+\[ F_j=\sum_{i=1}^d \zeta_{[\delta_i,a]}w_i^j+(p-p_0)w_{d+1}^j \]
+and $w_i^j$ are coordinates on the fiber of the $j$-th copy of $\rm{Vb}(\hat{\pi}_*\mathcal L)$ over $\XP$.
+\end{lem}
+Compare with \cite[Theorems 2.17-19]{HL}.
+
+\subsection{Hu-Li blow-up and desingularisation}
+We perform a modular blow-up of $\MM_1^{1,\rm{wt}}$: we successively blow up $\hat\Theta_k, \;k\geq 2$  defined as the closure of the loci where the minimal elliptic subcurve $E$ has weight $0$ and $\lvert\overline{C\setminus E}\cap E\rvert=k.$
+
+Notice that after the $k$-th blow-up, the strict transform of $\Theta_{k+1}$ is smooth, so the final result  $\widetilde{\MM}_1^{1,\rm{wt}}$ is smooth as well.
+
+\begin{remark}
+The fiber product 
+\[\widetilde{\MM}_1^{1,\rm{wt}}\times_{\MM_1^{1,\rm{wt}}}\MM_1^{\rm{wt}}\]
+recovers the Hu-Li blow-up $\widetilde{\MM}_1^{\rm{wt}}.$ The key observation is that $\Theta_1$ is already a Cartier divisor and the pullback of $\hat\Theta_k$ is precisely $\Theta_k$.
+\marginpar{you can use the universal property of the blow up to show there are maps in both directions. Check the statement about the $\Theta_k$}
+\end{remark}
+
+\begin{remark}\label{rmk:eqn}
+After blowing up, the equations in \ref{lem:equations} are simplified and assume the following form:
+\[\tilde\zeta\tilde w+(p-p_0)w_{d+1}=0\]
+where $\tilde\zeta$ is one of the newly created boundary divisors $\widetilde{\Theta_k}$ from $\widetilde{\MM}_1^{\rm{wt}}$ (i.e.
+one of the exceptional divisors produced by the blow-up process), and $\tilde w$ is a suitably defined coordinate on the fiber of $\rm{Vb}(\hat{\pi}_*\mathcal L)\times_{\XP}\widetilde{\XP}$.
+\end{remark}
+
+Summing up, we get:
+\bcd
+   &  \widetilde{\Z}^p \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \tM_1^{(1)}(\PP^4,d)^p \ar[d] \\
+\tM_1(\PP^4,d)\ar[d] & \widetilde{\Z} \ar[l,hook,swap,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \tM_1^{(1)}(\PP^4,d) \ar[d] \\
+\widetilde{\mathfrak{Pic}}_1\ar[d] &\widetilde{\XP}\ar[l]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \widetilde{\mathfrak{Pic}}_1 ^{(1)}\ar[d]\\
+\widetilde{\MM}^{\rm{wt}}_1 & \widetilde{\X}\ar[l,swap,"\sim"]\ar[r] & \widetilde{\MM}_1^{(1),\rm{wt}}
+\ecd
+
+\begin{comment}
 where this time an object of $\Z^p$ over $S$ is given by
@@
 \end{itemize}
-
-\subsection{Splitting the cone}
+\end{comment}
+We conclude this brief section remarking that the blow up procedure does not affect the invariants:
+\begin{lem}
+We have the identity:
+\[\deg\virloc{\tZp}=\deg\virloc{\Zp}\]
+\end{lem}
+Compare with \cite[Proposition~2.5]{CL}.
+\section{Splitting the cone and proof of the Main Theorem}
+We are finally in a position to study the cone $\mathfrak{C}_{\tZp/\tXP}.$ This is essentially going to be a word-by-word repetition of the arguments in \cite{CLpfields}.
+\begin{lem}\label{lem:open_cones}
+Let $\tilde{\rho}\colon \tZp\to\tXP$ be the natural map and $\mathbb {E}_{\tZp/\tXP}=\R\hat\pi_*(\mathcal L^{\oplus 5}\oplus\mathcal P)$  the relative perfect obstruction theory for $\tilde{\rho},$ then $\mathfrak{C}_{\tZp/\tXP}$ has the following properties:
+\begin{enumerate}
+\item Its restriction to  $\tZ^{p,\circ}= \tZ^{p,\rm{main}}\setminus \bigcup_{k\geq 2}D^k \tZp$ can be described as the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}$
+\item Its restriction to $\tZ^{p,gst,\circ}=\tZp - \tZ^{p,\rm{main}}$  is a rank $2$ subbundle stack of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,gst,\circ}}$
+\end{enumerate}
+\end{lem}
+\begin{proof} Compare with \cite[Lemma 4.3]{CLpfields}
+\begin{enumerate}
+\item Observe that $\tZ^{p,\circ}\cong \tZ^{\circ}$ because here $H^0(\hat C, L^{\otimes -5}\otimes \omega_{\hat C})=0$.
+Moreover $\tZ^{\circ}$ is unobstructed on its image, which is an open of $\tXP$, because $\R^1\hat{\pi}_*\mathcal L=0$.
+So the normal cone is $[\tZ^{p,\circ}/\hat{\pi}_*\mathcal L^{\oplus 5}]$, which is the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}=[0\oplus \R^1\hat{\pi}_*\mathcal P/\hat{\pi}_*\mathcal L^{\oplus 5}\oplus 0]$.
+\item We know that $\tZ^{p,gst,\circ}$ is a line bundle over $\tZ^{gst,\circ}$.
+From the equations \ref{rmk:eqn} we see that the latter is smooth over its image $\pazocal W$ in $\tXP$, which is the codimension $2$ locus where the minimal genus $1$ subcurve has weight $0$ and the line bundle is trivial on it.
+Recall that every smooth morphism $A\to B$ factors as $A\xrightarrow{\acute{e}t} B\times \Aaff^n\xrightarrow{\pr_1} B$.
+So we have
+\bcd
+\tZ^{p,gst,\circ} \ar[r,"\acute{e}t"] & \pazocal W\times\Aaff^{5d+5}\ar[r,hook]\ar[d,"q"] & \tXP\times \Aaff^{5d+5}\ar[d] \\
+& \pazocal W \ar[r,hook] & \tXP
+\ecd
+where the bottom horizontal arrow is a codimension $2$ regular embedding. Thus 
+\[\mathfrak{C}_{\tZp/\tXP}\rvert_{\tZ^{gst,\circ}}\cong \left[ q^* C_{\pazocal W/\tXP}/ \hat{\pi}_*\mathcal L^{\oplus 5}\right]\]
+is a rank 2 subbundle stack of  $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,gst,\circ}}.$
+\end{enumerate}
+\end{proof}
+
+ Notice that the image of $\tZ^{\circ}$ in $\tM_1(\PP^4)$ contains $\tM_1(\PP^4)^{main}\cap \tilde{D}^1.$
+
+Recall the definition of the \emph{closure of the zero section of a vector bundle stack}: let $B$ be an integral algebraic stack and let $[F_0\xrightarrow{d} F_1]$ be a complex of locally free sheaves on $B$.
+The zero section is $0_{\mathbf F}\colon [F_0/F_0]\to\mathbf F=[F_1/F_0]$ (notice that it is not in general a closed embedding); the closure of the zero section is then defined as:
+\[ \overline{0}_{\mathbf F}=[\operatorname{cl}(dF_0)/F_0] \]
+$\overline{0}_{\mathbf F}$ is an integral stack.
+
+\begin{ex}
+When $h^0(F_\bullet)=0$, the closure of the zero section looks like $B$ with some stacky structure on the vanishing locus of $d$.
+Consider for example $B=\PP^1$ and $F_\bullet=[\OO_{\PP^1}\xrightarrow{x}\OO_{\PP^1}(1)]$.
+Then the action of $e\in F_0$ on $F_1$ is by $f\mapsto f+xe$.
+Clearly $\operatorname{cl}(dF_0)$ is the whole line bundle $F_1$; the $F_0$-action is transitive on the fibers over $\{x\neq 0\}$ and trivial on the $\{x=0\}$-fiber.
+Hence $\overline{0}_{\mathbf F}$ is isomorphic to $\PP^1\setminus\{x=0\}$ with a stacky point $B\mathbb G_{\rm a}$ replacing $\{x=0\}$.
+\end{ex}
+
+We may now split the cone $\mathfrak{C}_{\tZp/\tXP}$ in the following manner: we denote by $\mathfrak C^{\rm{main}}$ the closure of the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{main}}}$, which is an irreducible cone supported on the main component; all the rest is supported on the boundary components, possibly on their intersection with the main one, and we are going to pack all the components supported on $D^k\tZp$ together and label them $\mathfrak C^k$ accordingly, so in the end we get a splitting:
+\[
+ \mathfrak{C}_{\tZp/\tXP}=\mathfrak C^{\rm{main}}+\sum_{k\geq 2} \mathfrak C^k
+\]
+We are going to show that:
+\begin{enumerate}
+ \item the contribution of $\mathfrak C^{\rm{main}}$ is exactly the reduced invariants of $X$;
+ \item the other cones $\mathfrak C^k,\ k\geq 2$ are enumeratively meaningless.
+\end{enumerate}
+
+In order to prove the first we proceed as in \cite[\S5]{CLpfields}: notice that the obstruction theory $\mathbb E$ splits as $\mathbb E_1\oplus\mathbb E_2$ where $\mathbb E_1=\R\hat\pi_*(\mathcal L^{\oplus 5})$ and $\mathbb E_2=\R\hat\pi_*(\mathcal P)$.
+When we restrict ourselves to $\tZ^{p,\rm{main}}$ we see that $\mathbb E_1$ is the closure of its own zero section; it follows that:
+\[
+ \mathfrak C^{\rm{main}}=\overline{0}_{\mathbb E\rvert_{\tZ^{p,\rm{main}}}}=\mathbb E_1\rvert_{\tZ^{p,\rm{main}}}\oplus \overline{0}_{\mathbb E_2\rvert_{\tZ^{p,\rm{main}}}}
+\]
+Then by excess intersection:
+\[
+ 0^!_{\mathbb E}[\mathfrak C^{\rm{main}}]=0_{\mathbb E_2}^![\overline{0}_{\mathbb E_2\rvert_{\tZ^{p,\rm{main}}}}]
+\]
+
+At this point we recall the following \cite[Lemma 5.3]{CLpfields}:
+\begin{lem}
+Let $\mathbb E=[E_0\to E_1]$ be a complex of locally free sheaves on an integral Deligne-Mumford stack $B$ such that
+$H^1(\mathbb E)$ is a torsion sheaf on $B$ and the image sheaf of $E_0\to E_1$ is locally free.
+Let $U\subseteq B$ be the complement of the support of $H^1(\mathbb E)$, and let $\mathbf{B}\subseteq h^1/h^0(\mathbb E^\vee[-1])$
+be the closure of the zero section  of the vector bundle $h^1/h^0(\mathbb E^\vee[-1]|_U)= H^0(\mathbb E|_U)^\vee$. Then
+$$0^![\mathbf{B}]=e(H^0(\mathbb E)^\vee)\in A_*(B).
+$$
+\end{lem}
+
+We apply this with $\mathbb E=\R\hat{\pi}_*\mathcal L^{\otimes 5}$. Notice that it satisfies the hypotheses by virtue of the equations in Remark \ref{rmk:eqn}.
+
+\begin{lem}
+ If we let $i$ be the inclusion of $\tZ$ in $\tM_1(\PP^4,d)$, then:
+ \[
+  i_*(c_{\text{top}}(\hat{\pi}_*\hat{\mathcal L}^{\otimes 5})\cap[\tZ^{p,\rm{main}}])=c_{\text{top}}({\pi}_*\mathcal L^{\otimes 5})\cap[\tM_1(\PP^4,d)^{p,\rm{main}}]
+ \]
+
+\end{lem}
+
+\begin{itemize}
+\item split the cone
+\item recall lemma 5.3
+\item compare the main component with reduced invariants
+\item deal with the other bits
+\end{itemize}
+
+\begin{comment}{
 We may notice that $(\Z^p)^{\text{main},\circ}\to\XP$ is smooth onto its image, which is an open substack; furthermore on this open the relative tangent is represented by $\hat\pi_*\hL^{\oplus 5}$, and $\R^1\hat\pi_*\hL^{\oplus 5}=\hat\pi_*(\hat\omega\otimes\hL^{\otimes -5})=0$.
@@
 \item other components supported on the boundary, which we should accordingly name $\mathfrak C^k$ ($k\geq 2$).
-\end{itemize}
+\end{itemize}}
+\end{comment}
 \bibliographystyle{alpha}

### 2017-12-08 draft.tex
avoiding the vector bundle stack

@@
 \newcommand{\XP}{\pazocal{X\!P}}
-\newcommand{\tXP}{\tilde{\pazocal{X\!P}}}
+\newcommand{\tXP}{\widetilde{\pazocal{X\!P}}}
 \renewcommand{\L}{\mathcal L}
@@
 (here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
-\[\begin{split}
+\begin{equation*}\label{eqn:cosection}
+ \begin{split}
  \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
  \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
-\end{split}\]
+\end{split}
+\end{equation*}
+
 The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
@@
 Clearly $\operatorname{cl}(dF_0)$ is the whole line bundle $F_1$; the $F_0$-action is transitive on the fibers over $\{x\neq 0\}$ and trivial on the $\{x=0\}$-fiber.
-Hence $\overline{0}_{\mathbf F}$ is isomorphic to $\PP^1\setminus\{x=0\}$ with a stacky point $B\mathbb G_{\rm a}$ replacing $\{x=0\}$.
+Hence $\overline{0}_{\mathbf F}$ is isomorphic to $\PP^1\setminus\{x=0\}$ with a gerbe $[\Aaff^1/\mathbb G_{\rm a}]$ replacing the point $\{x=0\}$.
 \end{ex}
 
-We may now split the cone $\mathfrak{C}_{\tZp/\tXP}$ in the following manner: we denote by $\mathfrak C^{\rm{main}}$ the closure of the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{main}}}$, which is an irreducible cone supported on the main component; all the rest is supported on the boundary components, possibly on their intersection with the main one, and we are going to pack all the components supported on $D^k\tZp$ together and label them $\mathfrak C^k$ accordingly, so in the end we get a splitting:
+We may now split the cone $\mathfrak{C}_{\tZp/\tXP}$ in the following manner: we denote by $\mathfrak C^{\rm{main}}$ the closure of the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{main}}}$, which is an irreducible cone supported on the main component; all the rest is supported on the boundary components, possibly on their intersection with the main one, and we are going to pack all the components supported on $D^k\tZp$ together and label them $\mathfrak C^k$ accordingly, so in the end we obtain a splitting:
 \[
@@
  \item the contribution of $\mathfrak C^{\rm{main}}$ is exactly the reduced invariants of $X$;
- \item the other cones $\mathfrak C^k,\ k\geq 2$ are enumeratively meaningless.
+ \item the other cones $\mathfrak C^k,\ k\geq 2,$ are enumeratively meaningless.
 \end{enumerate}
@@
 
-We apply this with $\mathbb E=\R\hat{\pi}_*\mathcal L^{\otimes 5}$. Notice that it satisfies the hypotheses by virtue of the equations in Remark \ref{rmk:eqn}.
+We apply this lemma to $\mathbb E=\R\hat{\pi}_*\mathcal L^{\otimes 5}$.
+Notice that it satisfies the hypotheses by virtue of the equations in Remark \ref{rmk:eqn}: indeed the question may be addressed locally; looking at the resolution of $\mathbb E$:
+\[
+ \hat\pi_*\mathcal L^{\otimes 5}(\A)\to \hat\pi_*\mathcal L^{\otimes 5}(\A)\rvert_{\A}
+\]
+we deduce from the equation that the image sheaf of this map is $\pi_*\mathcal L^{\otimes 5}(\A)\rvert_{\A}\otimes\OO_{\tZ^{p,\rm{main}}}(-\Delta)$, where $\Delta$ denotes the boundary of the main component $\Delta=\tZ^{p,\rm{main}}\cap\left(\bigcup_{k\geq 2}D^k\tZp\right)$.
+Then $\hat\pi_*\mathcal L^{\otimes 5}$ is a vector bundle.
 
@@
  \[
-  i_*(c_{\text{top}}(\hat{\pi}_*\hat{\mathcal L}^{\otimes 5})\cap[\tZ^{p,\rm{main}}])=c_{\text{top}}({\pi}_*\mathcal L^{\otimes 5})\cap[\tM_1(\PP^4,d)^{p,\rm{main}}]
- \]
-
-\end{lem}
-
-\begin{itemize}
-\item split the cone
-\item recall lemma 5.3
-\item compare the main component with reduced invariants
-\item deal with the other bits
-\end{itemize}
+  i_*(c_{\rm{top}}(\hat{\pi}_*\hat{\mathcal L}^{\otimes 5})\cap[\tZ^{p,\rm{main}}])=c_{\rm{top}}({\pi}_*\mathcal L^{\otimes 5})\cap[\tM_1(\PP^4,d)^{p,\rm{main}}]
+ \]
+\end{lem}
+\begin{proof}
+ Obviously $i_*[\tZ^{p,\rm{main}}]=[\tM_1(\PP^4,d)^{p,\rm{main}}]$. On the other hand notice that on $\tZ^{p,\rm{main}}$ we have:
+ \[
+  \pi_*\mathcal L=\hat{\pi}_*\phi_*\phi^*\hat{\mathcal L}=\hat{\pi}_*\hat{\mathcal L}
+ \]
+by projection formula and since $\phi_*\OO_{\cC_{\tZ^{p,\rm{main}}}}=\OO_{\hat\cC_{\tZ^{p,\rm{main}}}}$. The result follows then from the projection formula for Chern classes.
+\end{proof}
+
+We are left with showing that the rest of the $\mathfrak C^k$'s do not contribute to the invariants.
+This is essentially a dimensional computation.
+The arguments of \cite[\SS6-8]{CLpfields} may be directly applied; we shall outline them for the benefit of the reader.
+We introduce the notation $\tZ^{p,\rm{gst}}:=\bigcup_{k\geq 2} D^k\tZp$ for the union of the boundary components, and $\mathfrak C^{\rm{gst}}=\bigcup_{k\geq 2}\mathfrak C^k$.
+
+\subsection*{Step I: reduction to the case of a cone inside a vector bundle and homogeneity}
+This section deals with removing the technicalities of working with a cone stack inside a vector bundle stack.
+
+The key point is that $\mathbb E\rvert_{\tZ^{p,\rm{gst}}}$ has locally free $h^0$ \emph{and} $h^1$, as can be seen from the equations.
+Then, when we pick a resolution by locally free sheaves $\mathbb E=[F_0\xrightarrow{d} F_1]$, the image sheaf $d(F_0)$, which is the kernel of $F_1\to h^1(\mathbb E\rvert_{\tZ^{p,\rm{gst}}})$, is really a sub-vector bundle of $F_1$.
+Then the projections:
+\[
+ \beta\colon F_1\to h^1/h^0(\mathbb E) \quad \text{and} \quad \beta'\colon F_1\to \tilde{V}:=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\mathcal P)
+\]
+are both flat.
+The cone stack $\mathfrak C^{\rm{gst}}$ can be descended to a cone $C^{\rm{gst}}$ by means of taking the quotient of $\beta^{-1}\mathfrak C^{\rm{gst}}$ by the free action of $d(F_0)$; $C^{\rm{gst}}$ should then be thought of as the coarse moduli of $\mathfrak C^{\rm{gst}}$.
+Recall that the cosection $\sigma$ is induced by a cosection $\sigma_1$ of $\tilde V$ (see Eq.
+\eqref{eqn:cosection}).
+It follows from the commutativity of localised Gysin pullback with flat pullback that:
+\[
+ 0^!_{h^1/h^0(\mathbb E),\sigma}(\mathfrak C^{\rm{gst}})= 0^!_{\tilde V,\sigma_1}(C^{\rm{gst}})
+\]
+See \cite[Proposition 6.3]{CLpfields}.
+
+They then introduce the notion of \emph{homogeneity} for substacks of $\tilde V$: write $\tilde V=\tilde V_1\oplus\tilde V_2$ with $\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})$ and $\tilde V_2=\R^1\hat{\pi}_*(\mathcal P)$, and $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ the projection.
+Since $\tZ^{p,\rm{gst}}$ is the total space of a line bundle over $\tZ^{\rm{gst}}$, it comes with a natural $\Gm$-action on the fibers of $\gamma$, and since $\tilde V_i=\gamma^*V_i$ for the corresponding vector bundles $V_i$ on $\tZ^{\rm{gst}}$, the total space of $\tilde V_i$ can be endowed with a $\Gm$-action that makes the projection to $\tZ^{p,\rm{gst}}$ equivariant.
+A closed substack of $\tilde V$ is $0$-homogeneous if it is the pullback of a closed substack of $V$ along $\gamma$.
+In facts the $\tilde V_i$'s can be endowed with different $\Gm$ actions that make the projection to $\tZ^{p,\rm{gst}}$ equivariant by twisting with two characters of $\Gm$, one for each $\tilde V_i$; this defines the concept of $(l_1,l_2)$-homogeneous substacks of $\tilde V$.
+Here is how we are going to use the homogeneity:
+
+\begin{lem}
+ Let $\tilde C\subseteq \tilde V$ be an $(l_1,l_2)$-homogeneous sub\emph{cone} of $\tilde V$; then the cone $\tilde C\cap(0\oplus\tilde V_2)$ is pulled back from a cone in $V_2$.
+\end{lem}
+\begin{proof}
+ Locally we may pick coordinates $t$ on the fibers of $\gamma$, $x_1,\ldots,x_5$ on the fibers of $\tilde V_1$, and $y_1,\ldots,y_{5d+5}$ on the fibers of $\tilde V_2$, such that the ideal of $\tilde C$ is generated by homogeneous polynomials $p_j$ in $t^{-l_1}x_i$ and $t^{-l_2}y_i$.
+The ideal of $\tilde C\cap(0\oplus\tilde V_2)$ is then given by $\langle x_1,\ldots, x_5,p_j(0,t^{-l_2}y)\rangle_j$, where $p_j(0,t^{-l_2}y)$ results from setting $x_i=0$ in $p_j$; notice now that $\tilde C$ being a cone, it is invariant by scalar multiplication on the fibers of $\tilde V$, so we may as well say that $\tilde C\cap(0\oplus\tilde V_2)$ is cut by the ideal $\langle x_1,\ldots, x_5,p_j(0,y)\rangle_j$.
+This makes it clear that $\tilde C\cap(0\oplus\tilde V_2)$ is pulled back from $(0\oplus V_2)$ on $\tZ^{\rm{gst}}$.
+\end{proof}
+
+Finally Chang and Li point out that the coarse moduli cone $C^{\rm{gst}}$ is $(0,1)$-homogeneous \cite[Proposition 6.7]{CLpfields}: recalling the interpretation of $\Mone{1}{\PP^4}{d}^p$ as an open inside the cone of sections of $\mathcal V=\rm{Vb}(\mathcal L^{\oplus 5}\oplus \mathcal P)$ over $\hat\cC_{\mathfrak{Pic}_1^{(1)}}$, the desired $\Gm$-action on the fibers of $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ is induced by endowing $\rm{Vb}(\mathcal L^{\oplus 5}\oplus \mathcal P)$ with the $\Gm$-action that is trivial on the fibers of every copy of $\rm{Vb}(\mathcal L)$, and has character $1$ on those of $\rm{Vb}(\mathcal P)$, with an underlying trivial action on $\mathfrak{Pic}_1^{(1)}$.
+This influences the obstruction theory  $\R^\bullet\hat\pi_*\left(\mathfrak e^* T_{\mathcal V/\hat\cC_{\mathfrak{Pic}_1^{(1)}}}\right)$ of $\Mone{1}{\PP^4}{d}^p$ in the obvious way, and consequently $\mathbb E$ on $\tZp$.
 

### 2017-12-08 draft.tex
missing only the last step of the proof

@@
 (here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
-\begin{equation*}\label{eqn:cosection}
+\begin{equation}\label{eqn:cosection}
  \begin{split}
@@
 \end{split}
-\end{equation*}
+\end{equation}
 
@@
 \eqref{eqn:cosection}).
-It follows from the commutativity of localised Gysin pullback with flat pullback that:
+\marginpar{rewrite what they are}It follows from the commutativity of localised Gysin pullback with flat pullback that:
 \[
@@
 
-They then introduce the notion of \emph{homogeneity} for substacks of $\tilde V$: write $\tilde V=\tilde V_1\oplus\tilde V_2$ with $\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})$ and $\tilde V_2=\R^1\hat{\pi}_*(\mathcal P)$, and $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ the projection.
-Since $\tZ^{p,\rm{gst}}$ is the total space of a line bundle over $\tZ^{\rm{gst}}$, it comes with a natural $\Gm$-action on the fibers of $\gamma$, and since $\tilde V_i=\gamma^*V_i$ for the corresponding vector bundles $V_i$ on $\tZ^{\rm{gst}}$, the total space of $\tilde V_i$ can be endowed with a $\Gm$-action that makes the projection to $\tZ^{p,\rm{gst}}$ equivariant.
+They then introduce the notion of \emph{homogeneity} for substacks of $\tilde V$: write 
+\[\tilde V=\tilde V_1\oplus\tilde V_2\;\;\text{ with} \;\;\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})\;\; \text{and}\;\; \tilde V_2=\R^1\hat{\pi}_*(\mathcal P),\]
+ and $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ the projection.
+Since $\tZ^{p,\rm{gst}}$ is the total space of a line bundle over $\tZ^{\rm{gst}}$, it comes with a natural $\Gm$-action on the fibers of $\gamma$.
+Moreover, since
+ \[\tilde V_i=\gamma^*V_i\]
+ \marginpar{say few words, that is not the definition of $\tilde V_i$ but a property (Lemma 6.1)}
+ for the corresponding vector bundles $V_i$ on $\tZ^{\rm{gst}}$, the total space of $\tilde V_i$ can be endowed with a $\Gm$-action that makes the projection to $\tZ^{p,\rm{gst}}$ equivariant.
 A closed substack of $\tilde V$ is $0$-homogeneous if it is the pullback of a closed substack of $V$ along $\gamma$.
@@
 \end{comment}
+\subsection*{Step II: from cosection localized to standard Gysin map}
+Recall that when we are working on a proper DM stack $\pazocal M$ endowed with a perfect obstruction theory and admitting a cosection $\sigma$, then the cosection localized Gysin map can be reduced to the ordinary Gysin map, i.e.
+\[\iota_*\circ 0^{!}_{E,\sigma}=0_E^{!}\circ \tilde{\iota}\;\;\;\text{where}\;\;\iota\colon D(\sigma)\hookrightarrow\pazocal M,\;\;\tilde{\iota}\colon E(\sigma)\hookrightarrow E\]
+and $E$ is the vector bundle containing the cone.
+
+Then to compute $0^!_{\tilde V,\sigma_1}(C^{\rm{gst}})$ we plan to compactify $\tZ^{p,\rm{gst}},$ extend the cone, the vector bundle and the section over it and then make use of the fact we just recalled.
+
+Since $\tZ^{p,\rm{gst}}\cong\operatorname{Tot}_{\tZ^{\rm{gst}}}\left(\R^1\hat{\pi}_*\mathcal P\right)$ we compactify considering
+\[\overline{\gamma}\colon \overline{\tZ^{p,\rm{gst}}}:=\PP\left(\R^1\hat{\pi}_*\mathcal P\oplus \OO_{\tZ^{\rm{gst}}}\right)\to \tZ^{\rm{gst}}\]
+and extend $\tilde{V}_1,\tilde{V}_2$ via:
+\[\tilde{V}^{\rm{cpt}}_1=\overline{\gamma}V_1(-D_{\infty}),\qquad \tilde{V}^{\rm{cpt}}_2=\overline{\gamma}V_2.\]
+Finally, let us extend the cosection as well. From the cosection $\sigma$ defined by \ref{eqn:cosection} we clearly get a cosection on $\Z^p$ by pull-back and again a 
+\[\widetilde{\sigma}\colon \pazocal Ob_{\tZp}\to\OO_{\tZp} \]
+ on the blow-up. Let us denote by $\widetilde{\sigma}_{\rm{gst}}$ its restriction to $\tZ^{\rm{gst}}.$
+ Writing down what $\widetilde{\sigma}_{\rm{gst}}$ looks like on points\cite[Lemma~6.2]{CL}, we see that it extend to a homomorphism of vector bundles:
+ \[\overline{\sigma}\colon\tilde{V}^{\rm{cpt}}=\tilde{V}^{\rm{cpt}}_1\oplus \tilde{V}^{\rm{cpt}}_2\to \overline{\tZ^{p,\rm{gst}}}.\]
+ \begin{prop}
+ Let $\iota_{!}\colon Z_*(\tilde{V}(\widetilde{\sigma}_{\rm{gst}}))\to Z_*(\tilde{V}^{\rm{cpt}})$ be defined by 
+ $\iota_{!}[C]=[\overline{C}].$ And $i\colon D(\widetilde{\sigma}_{\rm{gst}})\to \tilde{Z}_{\rm{gst}}$ the inclusion. Then
+ \[\overline{\gamma}_*\circ 0^{!}_{\tilde{V}^{\rm{cpt}}}\circ\iota_{!}=i\circ 0^{!}_{\widetilde{\sigma}_{\rm{gst}},\rm{loc}}\colon  Z_*(\tilde{V}(\widetilde{\sigma}_{\rm{gst}}))\to A_*(\tilde{Z}_{\rm{gst}}).\]
+ \end{prop}
+ This follows essentially from the property of cosection localized cycles recalled at the beginning of the section; see \cite[Proposition~6.4]{CL} for full details.
+ \subsection*{Step III: reduction of the support of the cone}
+We now explain a key technical lemma which will enable us to show that $C^{\rm{gst}}$ pushes forward to zero under a suitably defined morphism.
+It is basically reducing the support of $C^{\rm{gst}}\cap 0\oplus\tilde V_2$ to a manageable substack of $\tilde V_2$, that is the union of the zero-section (i.e.
+$\tZp$) and a sub-line bundle of $\tilde V_2$ supported on $\tilde \Delta=\tZ^{p,\rm{main}}\cap\tZ^{p,\rm{gst}}$.
+Even better, using the homogeneity we can show that such a line bundle comes from $\Delta=\tZ^{\rm{main}}\cap\tZ^{\rm{gst}}$.
+This is \cite[Proposition 7.1]{CLpfields}.
+\begin{lem}
+ There is a sub-line bundle $F$ of $V_2\rvert_\Delta$ such that:
+ \[
+  C^{\rm{gst}}\cap 0\oplus\tilde V_2\subseteq 0_{\tilde V_2}\cup \tilde F:= \tZ^{p,\rm{gst}}\cup \gamma^* F
+ \]
+\end{lem}
+First they use the fact that there is a triple of compatible obstruction theories for the triangle:
+\bcd
+\tZp \ar[rr]\ar[dr,"\gamma"] & & \tZ \ar[dl] \\
+& \XP &
+\ecd
+such that their restrictions to $\tZ^{p,\rm{gst}}$ have locally free $h^0$ and $h^1$. To the effect that by taking $h^1$ of the dual obstruction theories we obtain a commutative diagram:
+\bcd
+h^1(\mathbb L_{\tZp/\tZ}^\vee\rvert_{\tZ^{p,\rm{gst}}}) \ar[r]\ar[d] & h^1(\mathbb L_{\tZp/\XP}^\vee\rvert_{\tZ^{p,\rm{gst}}})\ar[r]\ar[d] &h^1(\gamma^*\mathbb L_{\tZ/\XP}^\vee\rvert_{\tZ^{p,\rm{gst}}})\ar[d] \\
+\tilde V_2\ar[r,"i_2"] & \tilde V_1\oplus\tilde V_2 \ar[r,"\pr_1"] & \tilde V_1
+\ecd
+The vertical arrows are injective by the definition of an obstruction theory, and the bottom triangle is exact.
+Notice that $0\oplus\tilde V_2$ is precisely the kernel of $\pr_1$.
+It follows that, in order to understand the support of $C^{\rm{gst}}\cap 0\oplus\tilde V_2$, it is enough to study that of $N$, where $N$ is the coarse moduli cone of $\mathfrak C_{\tZp/\tZ}$, living in the upper left corner of the above diagram.
+
+This is an easier task, since we know that $\tZp/\tZ$ is a line bundle on $\tZ^{\rm{gst}}$ and an isomorphism on $\tZ^{\rm{main},\circ}$.
+Hence we can always find a local chart $S\to \tZ$ such that the following diagram holds:
+\bcd
+\tZp\ar[d] & T\ar[l]\ar[ld,phantom,"\Box"]\ar[d]\ar[r,hook,"V(\zeta t)"] & S\times\Aaff^1_t\ar[ld] \\
+\tZ & S\ar[l,"\acute{e}t"] &
+\ecd
+where $\zeta$ is a local equation for the boundary.
+Then $\tau^{\geq-1}\mathbb L_{\tZp/\tZ}\rvert_T=[I/I^2\xrightarrow{\delta}\Omega_{\Aaff^1_S/S}]$; $I$ is generated by $\zeta t$, whose image under $\delta$ is $\zeta \rm{d}t$, which restricts to $0$ on $\tZ^{p,\rm{gst}}\times_{\tZp}T=\{\zeta=0\}$.
+So the action is trivial, and in fact the restriction of the coarse moduli cone is precisely $\Spec_{T^{\rm{gst}}}\operatorname{Sym}^{\bullet} I/I^2$, which is a line bundle supported on $\tilde \Delta\times_{\tZp}T$ and trivial otherwise.
+By gluing different charts we get the line bundle $\tilde F$ on $\tilde \Delta$.
+
+The last part of the statement, namely that $\tilde F$ descends to a line bundle $F$ on $\Delta$ is proved by homogeneity: the normal cone of $\tZp/\tZ$ is homogeneous with respect to the $\Gm$-action with character $1$ on the fibers of $\tilde V_2\to \tZ^{p,\rm{gst}}$, but being a cone it is $0$-homogeneous as well (see the above discussion of homogeneity), so it is $\gamma^*F$ for some line bundle $F$ on $\Delta\subseteq \tZ$.
+
+\subsection*{Step IV: pushing forward to zero} Recall from the previous sections that we need to show that the degree of the following class is $0$:
+\[
+ 0_{\overline{V}}^![\overline C^{\rm{gst}}]=0_{\overline V_2}^!(0_{\overline{V_1}}^![\overline C^{\rm{gst}}])=0_{\overline V_2}^!([N_{\overline C^{\rm{gst}}\cap (0\oplus \overline V_2)}\overline C^{\rm{gst}}])
+\]
+\bcd
+? \ar[r]\ar[d] & X\ar[d] & \\
+\overline C^{\rm{gst}}\cap (0\oplus \overline V_2) \ar[r]\ar[d] & V_2\ar[r]\ar[d] & X\ar[d] \\
+\overline C^{\rm{gst}} \ar[r] & \overline V\ar[r] & \overline V_1
+\ecd
+We know from the previous section that the last cycle can be split into two parts, one (call it $N_1$) supported on a sub-line bundle of $\overline V_2$ on $\tilde\Delta$, the other one (call it $N_2$) suypported on the zero section of $\overline V_2$.
+
+\begin{lem}
+ Both $N_1$ and $N_2$ are $5d+1$-dimensional cycles, and $\deg(0_{\overline V_2}^![N_i])=0$ for $i=1,2$.
+\end{lem}
+\begin{proof}
+ Compare with \cite[Lemma 8.1]{CLpfields}.
+The dimension of $\tZ^{\rm{gst}}$ is $5d+3$, being locally a $5(d+1)$ vector bundle over a dimension $-2$ stack; so $\tZ^{p,\rm{gst}}$, which is a line bundle on the former, has dimension $5d+4$.
+The coarse moduli cone has then dimension $5d+6$, as can be argued from \ref{lem:open_cones}.
+$\overline V_1\rvert_{\tZ^{p,\rm{gst}}}$ has rank $5$, so $0_{\overline{V_1}}^![\overline C^{\rm{gst}}]$ is a cycle of dimension $5d+1$.
+\end{proof}
+
 \bibliographystyle{alpha}

### 2017-12-11 draft.tex
Introduction and section 1

@@
 
-\newcommand{\M}[4]{\overline{\mathcal M}_{#1,#2}(#3,#4)}
-\newcommand{\Mone}[3]{\overline{\mathcal M}^{(1)}_{#1}(#2,#3)}
+\newcommand{\M}[4]{\overline{\pazocal M}_{#1,#2}(#3,#4)}
+\newcommand{\Mone}[3]{\overline{\pazocal M}^{(1)}_{#1}(#2,#3)}
 \newcommand{\PP}{\mathbb P}
@@
 
-The moduli stack of stable maps to projective space is a fundamental object in Gromov-Witten theory, since any moduli space of maps to a (smooth) projective variety is cut inside that of the ambient projective space by a set of induced equations.
+\section*{Introduction}
+
+The moduli stack of stable maps to projective space is a fundamental object in Gromov-Witten theory, since any moduli space of maps to a projective variety is cut inside the former by a number of equations induced by those of $X\subseteq \PP^r$.
 Yet its structure in higher genus is still largely mysterious.
 
-Recall that, in genus zero, $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension $\operatorname{vdim}=r-3+d(r+1)+n$ (we see that it is unobstructed from the fact that $H^1(\PP^1,f^*T_{\PP^r})=0$ for any map $f\colon\PP^1\to\PP^r$).
-Furthermore, for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$, the sheaf $\pi_*f^*E$ (where $\pi$ is the structure map of the universal curve and $f$ the universal stable map) is actually a vector bundle on $\M{0}{n}{\PP^r}{d}$.
+Recall that in genus zero $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension.
+Furthermore for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$ the sheaf $\pi_*f^*E$ is a vector bundle on $\M{0}{n}{\PP^r}{d}$.
 \bcd
@@
 
-It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that, if $i\colon X\to \PP^r$ is a complete intersection of degree $(l_1,\ldots,l_k)$ (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic) and we denote by $j$ the corresponding inclusion
-$$\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}\hookrightarrow\M{0}{n}{\PP^r}{d}$$
-then the following equality, expected by the interpretation of Chern classes as zero loci, holds:
+It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that, if $i\colon X\hookrightarrow \PP^r$ is a complete intersection of degree $(l_1,\ldots,l_k)$ and we denote by $j$ the corresponding inclusion of moduli spaces of maps,
+%$$\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}\hookrightarrow\M{0}{n}{\PP^r}{d}$$
+then the following equality holds:%, which is expected from the interpretation of Chern classes as zero loci of sections (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic):
 $$j_*[\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}]^{\operatorname{vir}}=c_{\operatorname{top}}(E)\cap[\M{0}{n}{\PP^r}{d}].$$
-This so-called ``hyperplane property'' allows us to compute GW invariants of complete intersections as twisted invariants on projective space.
-The situation in higher genera is much more intricated: the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional; the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle.
-One of the reason for this (in fact the only reason in genus one) is that there are maps from reducible curves with a genus $g$ core that is contracted and some rational tails that carry all the degree; if $f\colon C\to \PP^r$ is such a map, then $H^1(C,f^*\mathcal O_{\PP^r}(1))\neq 0$, as can be easily deduced from the normalisation sequence.
+This so-called ``hyperplane property'' allows us to compute GW invariants of complete intersections as twisted invariants of projective space, which enables us to perform computations by localisation.
+
+The situation in higher genera is much more intricate: the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional, and the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle.
+The enumerative meaning of the invariants is affected by the appearance of unexpected components, representing degenerate contributions from curves of lower genera.
+
+The situation in genus $1$ is better understood: the geometry of the moduli space of genus one stable maps to projective space $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre}.
+Contrary to higher genus, the closure of the locus of maps the source of which is a smooth elliptic curve is an irreducible component of $\M{1}{n}{\PP^r}{d}$, which is usually called the \emph{main component}.
+%One of the reasons for this (in fact the only reason in genus one) is that there are maps from reducible curves with a genus $g$ core that is contracted and some rational tails that carry all the degree; if $f\colon C\to \PP^r$ is such a map, then $H^1(C,f^*\mathcal O_{\PP^r}(1))\neq 0$, as can be easily seen from the normalisation sequence.
+
+In an attempt to extract the enumerative information hidden within Kontsevich's moduli space, Vakil and Zinger managed to desingularise the main component by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}).
+The end result $\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}$ is a stack on which $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ is a vector bundle, which allows them to define a notion of \emph{reduced invariants} for complete intersections in $\PP^r$, based on the hyperplane property:  %The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc.
+and taking the fiber product
+%\bcd
+%\widetilde{\mathcal M}_{1,n}(\PP^r,d)\ar[r]\ar[d] & \M{1}{n}{\PP^r}{d}\ar[d] \\
+%\widetilde {\mathfrak M}_{1,n}^{\operatorname{wt}=d} \ar[r] & \mathfrak M_{1,n}^{\operatorname{wt}=d}
+%\ecd
+%the strict transform of the main component becomes smooth and meets the rest of the components in normal crossing fashion (the \'{e}tale local model being the union of two linear subspaces of different dimensions in affine space).
+Furthermore, the sheaves $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ contain a vector subbundle of rank $dl$ supported on the strict transform of the main component.
+This paved the way to the definition of reduced invariants.
+\begin{dfn}
+Let $X$ be a complete intersection of degree $(l_1,\ldots,l_k)$ in $\PP^r$.
+The genus one reduced Gromov-Witten invariants of $X$ are defined by integrating against: $$[\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}]\cap c_{\rm{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i))).$$
+\end{dfn}
+
+Recently there has been a different attempt to discard some of the unwanted components.
+Viscardi \cite{VISC} has introduced a series of \emph{alternate compactifications} of the moduli space of maps from elliptic curves, based on Smyth's work on the birational geometry of $\oM_{1,n}$.
+In Viscardi's space $\oM_{1,n}^{(m)}(X,\beta)$ maps that contract an elliptic curve with at most $m$ rational tails are destabilised, and replaced by maps from $l$-elliptic fold singularities with $l\leq m$.
+
+The main result of this paper is that reduced invariants of the quintic three-fold can be recovered from Viscardi's alternate compactification.
+
+\begin{thm}
+Let $X$ be a generic smooth quintic three-fold. Then:
+\[
+N_1^{\rm{red}}(X,d)=N_1^{\rm{cusp}}(X,d)
+\]
+where:
+\[N_1^{\rm{red}}(X,d):=\deg \left([\widetilde{\pazocal M}_{1}(\PP^4,d)^{\rm{main}}]\cap c_{\rm{top}}(\tilde\pi_*\tilde f^*(\mathcal O_{\PP^4}(5)))\right)\]
+and
+\[N_1^{\rm{cusp}}(X,d):=\deg [\Mone{1}{X}{d}]^{\rm{vir}}.
+\]
+\end{thm}
+
+The insight for this fact comes from the following formula, the proof of which was first given by J. Li and A. Zinger \cite{LZ} in the symplectic category:
+
+$$N_1(X,d)=N_1^{\rm{red}}(X,d)+\frac{1}{12}N_0(X,d).$$
+Noticing that the genus $0$ contribution to this formula only comes from the boundary component with a single rational tail of degree $d$ suggests that removing such component would provide a more direct approach to reduced invariants.
+This is precisely what Viscardi's space of 1-stable maps does.
+
+\textcolor{red}{Li-Zinger's formula was later proved in the algebro-geometric setting by H.-W.
+Chang and J.
+Li in \cite{CL}.
+This was only the final of a series of papers where they developed the theory of stable maps with $p$-fields and applied it together with the techniques of cosection-localised virtual classes \cite{KLcosection}.
+$p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$; indeed Chang and Li managed to include the unwanted part of the obstruction theory in the moduli space, and by these means endow a well-understood space (very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.}
+\textcolor{blue}{To prove Li-Zinger formula in the algebro-geometric setting, one would like to understand how the virtual class of  $\oM_1(X,d)$ splits on the various component of the moduli space, but this seems to be unaccesible.
+To overcome this difficulty, Chang Li developed the theory of stable maps with $p$- fields.}
+
+The proof of our main theorem follows from adapting the techniques of Chang and Li to Viscardi's moduli spaces. We show the following:
+\begin{prop}
+There exists a well-defined $1$-stabilisation morphism at the level of weighted pre-stable curves:
+\[
+\MM_{1,n}^{\rm{wt}}\to \MM_{1,n}^{(1),\rm{wt}}
+\]
+\end{prop}
+The fiber product
+\[
+\MM_{1,n}^{\rm{wt}}\times_{\MM_{1,n}^{(1),\rm{wt}}}\Mone{1}{\PP^4}{d}^p
+\]
+is endowed with a virtual class counting $1$-stable maps to the quintic three-fold (the arguments in \cite{CLpfields} carry over almost unchanged).
+On the other hand we find a way to compare the main contribution of this space with Vakil-Zinger reduced invariants.
+A dimensional computation shows that this is the only enumeratively meaningful component.
+
+\subsection*{Outline of the paper}
+maybe table of notations
 \section{Genus one stable maps to $\PP^r$ - Equations, components and alternate compactifications}
@@
 \subsection{Local equations and components}
-
-The geometry of the genus one moduli space of Kontsevich' stable maps to projective space $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre} and is by now well understood.
-Assume $d>0$.
-Let $E$ be a smooth genus one curve with a non-constant morphism $f\colon E\to \PP^r$; then $H^1(E,f^*T_{\PP^r})=0$ by Riemann-Roch, hence we may define the \emph{main component} of $\M{1}{n}{\PP^r}{d}$ as the closure of the locus of maps the source of which is a smooth genus one curve.
-It is irreducible of the expected dimension $\operatorname{vdim}=d(r+1)+n$.
-On the other hand, for every positive integer $k$ and partitions $\lambda$ of $d$ into $k$ (positive) parts and $\mu$ of $n$ into $k$ (positive) parts, consider the boundary component $D_{\lambda,\mu}(\PP^r,d)$ that is the closure of the locus where (i) the source curve is obtained by gluing a smooth elliptic curve with $k$ many $\PP^1$'s (as rational tails), (ii) the map contracts the core elliptic curve to a point, and (iii) the rational tail $R_i$ has degree $\lambda_i$ and $\mu_i$ many marked points.
-In fact $D_{\lambda,\mu}(\PP^r,d)$ is the image of the gluing morphism from the fiber product
+We start by recalling a description of the global geometry of $\M{1}{n}{\PP^r}{d}$.
+Besides the main component, which we have defined in the Introduction, for every positive integer $k$ and partitions $\lambda\vdash d$ into $k$ parts and $\mu\vdash n$ into $k$ parts such that no $(\lambda_i,\mu_i)_{i=1}^k$ is either $(0,1)$ or $(0,2)$, there is a \emph{boundary} irreducible component $D_{\lambda,\mu}(\PP^r,d)$ defined to be the closure of the locus where:
+\begin{description}
+\item[i] the source curve is obtained by gluing a smooth elliptic curve with $k$ many $\PP^1$'s as rational tails,
+\item[ii] the map contracts the core elliptic curve to a point, and
+\item[iii] the rational tail $R_i$ has degree $\lambda_i$ and $\mu_i$-many marked points.
+\end{description}
+Indeed $D_{\lambda,\mu}(\PP^r,d)$ is the image of the gluing morphism from the fiber product:
 $$\M{1}{k}{\PP^r}{0}\times_{\PP^r}\prod_{i=1}^k\M{0}{\mu_i+1}{\PP^r}{\lambda_i}.$$
 
+The minimal arithmetic genus $1$ subcurve is called the \emph{core}. We then have:
 \begin{prop}\label{prop:components}
-\emph{(1)} The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{(\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\circ=\operatorname{main}\}$, i.e.
-$$\M{1}{n}{\PP^r}{d}=\M{1}{n}{\PP^r}{d}^\circ\cup\bigcup_{\lambda,\mu}D_{\lambda,\mu}(\PP^r,d).$$
-
-\emph{(2)} Let $(E {}_{p_1,\ldots,p_k}\sqcup_{q_1,\ldots,q_k}\bigsqcup_{i=1}^k R_i,f)$ be a degenerate stable map with $k$ rational tails; then it lies in the boundary of the main component if and only if $\operatorname{d}\!f(T_{q_i}R_i)$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
+\emph{(1)} The ones that we have described above are all the irreducible components of $\M{1}{n}{\PP^r}{d}$, %The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{\text{stable}\ (\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\rm{main}\}$,
+i.e.
+$$\M{1}{n}{\PP^r}{d}=\M{1}{n}{\PP^r}{d}^{\rm{main}}\cup\bigcup_{\lambda,\mu}D_{\lambda,\mu}(\PP^r,d).$$
+
+\emph{(2)} A map $[f]$ lies in the boundary of the main component  if and only if:
+\begin{itemize}
+\item either $f$ is non-constant on an irreducible component of the core,
+\item or if $(E\ {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^k R_i,f)$ is a stable map with $k$ rational tails, where $E$ is the maximal contracted genus one subcurve, then $\{\operatorname{d}\!f(T_{q_i}R_i)\}_{i=1}^k$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
+\end{itemize}
 \end{prop}
 
-In order to understand how the Gromov-Witten invariants differ from the naive expectation of counting smooth embedded genus $g$ curves in the given homology class, one needs to have a good understanding of the virtual fundamental class and of its splitting on the various components.
-This has led to the study of explicit local equation for the moduli space of stable maps in a smooth (over $\mathfrak M_{1,n}$) ambient space \cite{HL}, which we shall now briefly explain.
-Recall that a map from a scheme $C$ to projective $r$-space is the same as the datum of a line bundle $L$ on $C$ together with $r+1$ global sections in $H^0(C,L)$ that generate the line bundle at every point of $C$.
-Then it seems natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1,n}$.
-The problem is that this cone is not smooth, due to the jumps in fiber dimension at the boundary.
+This is due to R. Vakil and A. Zinger in \cite{Vre,VZpreview}. We shall later discuss a different proof of this fact based on local equations for the moduli space.
+
+%In order to understand how the Gromov-Witten invariants differ from the naive expectation of counting smooth embedded genus $1$ curves in the given homology class, one needs a good understanding of the virtual fundamental class and of its splitting on the various components.
+%This has led to the study of explicit local equation for the moduli space of stable maps in a smooth (relative to a moduli space of decorated curves) ambient space \cite{HL}, which we shall now briefly explain.
+We now review Hu-Li's procedure \cite{HL} to find local equations of $\M{1}{n}{\PP^r}{d}$ in a smooth ambient space.
+These are useful in describing the structure of the intrinsic normal cone and its splitting.
+
+Recall that a map $C\to\PP^r$ is given by a line bundle $L$ on $C$ together with $r+1$ sections in $H^0(C,L)$ that generate the line bundle.
+It is therefore natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1,n}=\mathfrak{Pic}(\cC_{1,n}\to\MM_{1,n})$.
+Hu and Li actually work on a local chart of the algebraic stack $\mathfrak M_{1,n}^{\rm{div}}$, parametrising families of pre-stable curves with a relative Cartier divisor of degree $d$. 
+ %The problem is that this cone is not smooth, due to the jumps in the dimension of the fiber at the boundary of the moduli space.
 %(besides there is a small issue due to the $\mathbb G_m$ automorphism group of objects of $\mathfrak{P}_{1,n}$, which can be avoided by dishomogenising).
 
-Let $[f\colon C\to \PP^r]$ be a point of $\M{1}{n}{\PP^r}{d}$; we may fix homogeneous coordinates on $\PP^r$ in a way that $D_0:=f^*\{X_0=0\}$ is a $d$-uple of smooth points on $C$ (i.e.
-\'{e}tale on the base) (this property will hold in a neighbourhood of $[f]$).
-This gives a map from (an \'{e}tale chart of) $\M{1}{n}{\PP^r}{d}$ to (an \'{e}tale chart of) the moduli space of pre-stable curves with a degree $d$ divisor $\mathfrak M_{1,n}^{\operatorname{div}=d}$, that we may assume to be landing in the locus where the divisor is composed by $d$ smooth distinct points (notice this locus is smooth over $\mathfrak M_{1,n}$ by the deformation theory of smooth subschemes).
-A morphism to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ global sections of $\mathcal O_C(D)$: the morphism can be written as $[1:u_1:\ldots:u_r]$, where $1$ is the image of the constant global section along the given map $\mathcal O_C\to\mathcal O_C(D)$ (i.e.
-we have taken dishomogenised local coordinates on $\PP^r$).
-
-Furthermore, \'{e}tale locally on $\M{1}{n}{\PP^r}{d}$, we may pick extra sections $\mathcal A$ and $\mathcal B$ of $\mathcal C_{1,n}(\PP^r,d)$ such that (i) they pass through the core elliptic curve, and (ii) they are disjoint smooth points away from $\mathcal D_0$.
-Then $\pi_*\mathcal L(\mathcal A)$ \emph{is} a vector bundle on $\mathfrak P_{1,n}$ and $\pi_*\mathcal L$ is carved inside it by requiring that the restriction (residue) map $\pi_*\mathcal L(\mathcal A)\to\pi_*\mathcal L(\mathcal A)_{|\mathcal A}$ is zero.
-
-\begin{prop}
-\emph{(1)} \'{E}tale locally, there is a locally closed embedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V_1:=\Spec(\pi_*\mathcal L(\A)^{\oplus r})$ over $\mathfrak M_{1,n}^{\operatorname{div}=d}$.
-It is obtained by imposing the nondegeneracy and stability conditions \emph{(open)} on the vanishing locus of the restriction of the universal section of $\pi_*\mathcal L(\A)^{\oplus r}$ to $\A$ \emph{(closed)}.
-
-\emph{(2)} Let $\mathcal V$ be an (affine local) \'{e}tale chart around a smooth point of $\mathfrak M_{1,n}^{\operatorname{div}=d}$.
-Then $\pi_*\mathcal L(\A)\cong \pi_*\mathcal L(\A-\B)\oplus \pi_*\mathcal \mathcal L(\A)_{|\B}$ (trivially, $\mathcal O_{\mathcal V}^{\oplus d+1}\cong\mathcal O_{\mathcal V}^{\oplus d}\oplus\mathcal O_{\mathcal V}$) and the restriction-to-$\A$ map is zero on the second factor.
-Call $\varphi\colon \pi_*\mathcal L(\A-\B)\to\pi_*\mathcal L(\A)_{|\A}$ the induced  restriction to $\A$.
-
-\emph{(3)} If we choose a suitable basis of $\pi_*\mathcal L(\A-\B)$, the restriction-to-$\A$ map can be written in a very explicit form: let $D=\sum_{i=1}^d\delta_i$, then $\pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B)$ is a sub-line bundle of $\pi_*\mathcal L(\A-\B)$ and $\varphi=\oplus\varphi_i\colon\oplus_{i=1}^d \pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B)\to \pi_*\mathcal L(\A)_{|\A}.$ Furthermore $\varphi_i\colon\mathcal O_\mathcal V\to\mathcal O_\mathcal V$ is given (up to invertibles) by multiplication by $\prod_{q\in[\A,\delta_i]}\zeta_q$, where $\zeta_q$ is the smoothening variable on $\mathfrak M_1$ corresponding to the node $q$, and $q\in[a,\delta_i]$ stands for all the nodes separating $\A$ (i.e.
-the core elliptic curve) from the point $\delta_i$.
+Let $[f\colon C\to \PP^r]$ be a point of $\M{1}{n}{\PP^r}{d}$: we may fix homogeneous coordinates on $\PP^r$ in such a way that $D_0=f^{-1}\{x_0=0\}$ is a simple smooth divisor on $C$ (i.e.
+a $d$-uple of smooth points); this property will then hold in a neighbourhood of $[f]$.
+This gives a map from an \'{e}tale chart $\pazocal U$ of $\M{1}{n}{\PP^r}{d}$ to an \'{e}tale chart $\pazocal V$ of $\mathfrak M_{1,n}^{\rm{div}}$, that we may assume to land in the locus where the divisor is made of $d$ distinct smooth points.
+Notice that this locus is smooth over $\mathfrak M_{1,n}$ by the deformation theory of smooth subschemes.
+A morphism to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ sections of $\mathcal O_C(D)$: the morphism can be written as $[1:u_1:\ldots:u_r]$, where $1$ means the given section of $\mathcal O_C\to\mathcal O_C(D)$.
+
+%is the image of the constant global section along the given map $\mathcal O_C\to\mathcal O_C(D)$ (i.e. we have taken dishomogenised local coordinates on $\PP^r$).
+
+Furthermore, \'{e}tale locally on $\M{1}{n}{\PP^r}{d}$, we may pick extra sections $\mathcal A$ and $\mathcal B$ of $\mathcal C_{1,n}(\PP^r,d)$ such that 
+\begin{enumerate}
+\item they pass through the core elliptic curve;
+\item they are distinct smooth points disjoint from the support of $\pazocal D_0$. 
+\end{enumerate}
+On  $\pazocal V$ we have that  $\pi_*\OO_{\cC}(\pazocal D+\mathcal A)$ is a vector bundle and $\pi_*\OO_{\cC}(\pazocal D)$ is carved inside it by requiring that the restriction map $\pi_*\OO_{\cC}(\pazocal D+\mathcal A)\to\pi_*\OO_{\cC}(\pazocal D+\mathcal A)\rvert_{\mathcal A}$ is zero.
+
+\begin{prop}\label{prop:smoothability}
+\emph{(1)} \'{E}tale locally on $\M{1}{n}{\PP^r}{d}$, there is a locally closed embedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V:=\Spec(\pi_*\OO_{\cC}(\pazocal D+\A)^{\oplus r})$ over $\pazocal V$:
+\bcd
+\M{1}{n}{\PP^r}{d} & \pazocal U\ar[l,"\acute{e}t"]\ar[r,hook]\ar[d] & V\ar[dl] \\
+\MM_{1,n}^{\rm{div}} & \pazocal V\ar[l,"\acute{e}t"] &
+\ecd
+Notice that $V$ is smooth.
+%It is obtained by imposing the nondegeneracy and stability conditions \emph{(open)} on the vanishing locus of the restriction of the universal section of $\pi_*\mathcal L(\A)^{\oplus r}$ to $\A$ \emph{(closed)}.
+
+\emph{(2)} Assume furthermore that $\pazocal V$ is affine; then on $\pazocal V$ we have 
+\[\pi_*\OO_{\cC}(\pazocal D+\A)\cong \pi_*\OO_{\cC}(\pazocal D+\A-\B)\oplus \pi_*\OO_{\cC}(\pazocal D+\A)_{|\B}\] %(trivially, $\mathcal O_{\mathcal V}^{\oplus d+1}\cong\mathcal O_{\mathcal V}^{\oplus d}\oplus\mathcal O_{\mathcal V}$)
+and the restriction-to-$\A$ map is zero on the second factor.
+
+\emph{(3)} Call $\varphi\colon \pi_*\OO_{\cC}(\pazocal D+\A-\B)\to\pi_*\OO_{\cC}(\pazocal D+\A)_{|\A}$ the map induced by restricting to $\A$.
+
+ If we choose a suitable basis of $\pi_*\OO_{\cC}(\pazocal D+\A-\B)$, $\varphi$ can be written in a very explicit form: let $D=\sum_{i=1}^d\delta_i$, then  
+ \[\varphi=\oplus\varphi_i\colon\oplus_{i=1}^d \pi_*\mathcal O_{\cC}(\delta_i+\A-\B)\to \pi_*\OO_{\cC}(\pazocal D+\A)_{|\A}.\] 
+  Furthermore, after choosing trivializations for the line bundles above,  $\varphi_i\colon\mathcal O_\pazocal V\to\mathcal O_\pazocal V$ is given by multiplication by \[\prod_{q\in[\A,\delta_i]}\zeta_q,\]
+   where $\zeta_q$ is the smoothing variable on $\mathfrak M_1$ corresponding to the node $q$, and $[\A,\delta_i]$ are all the nodes separating $\A$ (i.e. the core) from the point $\delta_i$.
 \end{prop}
-
-Given these explicit equations and by carefully examining the proof of \cite[Prop.
+We refer the reader to \cite[Lemma~4.10, Proposition~4.13]{HL} for full details; we are going to review the key ideas in \S\ref{sec:equations}, where we adapt the theory to $\Mone{1}{\PP^r}{d}$.
+We include here a proof of Proposition~\ref{prop:smoothability}-(2) based on the local equations.
+
+%Given these explicit equations and by carefully examining the proof of \cite[Prop.
 4.13]{HL}, we can look back at the problem of determining the boundary of the main component of the space of stable maps.
@@
 
-\begin{prop}\label{smoothability_with_eqn}
-Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree).
+%\begin{prop}\label{smoothability_with_eqn}
+%Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree).
 The following are equivalent:
-\begin{enumerate}
-\item $[f]$ is smoothable;
-\item $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$;
-\end{enumerate}
-\end{prop}
+%\begin{enumerate}
+%\item $[f]$ is smoothable;
+%\item $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$;
+%\end{enumerate}
+%\end{prop}
+
 \begin{proof}
- Let us start with the easiest degenerate situation: a contracted elliptic curve joined with a rational tail of degree $d$ at a single node $q$.
-Equations for the moduli space of maps around such a point look like $\zeta_q\sum_{i=1}^d w_i^j=0$, for $j=1,\ldots,r$, the $w_i$'s being coordinates for $\pi_*\mathcal O_{\mathfrak C}(D+\A-\B)$ in the basis given by $\pi_*\mathcal O_{\mathfrak C}(\delta_i+\A-\B),\ i=1,\ldots,d$.
+ Let us start with the easiest degenerate situation: a contracted elliptic curve attached to a $\PP^1$ of degree $d$ at a single node $q$.
+Equations for the moduli space of maps around such a point look like
+ \[\zeta_q\sum_{i=1}^d w_i^j=0,\;\;\;\text{for} \;\;\;j=1,\ldots,r\]
+ where the $w_i$ are coordinates on the fibers of $\pi_*\mathcal O_{\cC}(D+\A-\B)$ in the basis given by $\pi_*\mathcal O_{\cC}(\delta_i+\A-\B),\ i=1,\ldots,d$.
+
   Our point corresponds to a smoothable map if and only if the equations admit a solution with $\zeta_q\neq 0$, hence it must be $\sum_{i=1}^d w_i^j=0$ for every $j$.
-Taking a coordinate $z$ on the rational tail around the node $q$ (i.e.
-$\{z=0\}$ corresponds to the node), we see that the $i$-th vector in the chosen basis corresponds to a polynomial vanishing at the node and at every other point $\delta_j,\ j\neq i$; hence that can be written as $e_i(z)=z\prod_{j\neq i}\frac{(z-\delta_j)}{-\delta_j}$ (we chose a convenient normalisation).
-So the map corresponding to the point of coordinates $(w_i^j)_{i=1,\ldots,d;j=1,\ldots,r}$ can be represented as $[1:\sum_{i=1}^d w_i^1e_i(z):\ldots,\sum_{i=1}^d w_i^re_i(z)]$ on the rational tail; differentiating we see that the tangent vector at the node is sent to $(\sum_{i=1}^d w_i^1,\ldots,\sum_{i=1}^d w_i^r)$ (in affine coordinates), hence smoothability is equivalent to the image of the tangent vector being zero.
-
- More generally, we may assume the dual graph is terminally weighted.
-Let us say there are $m$ positive-weight rational tails and denote by $D(k),\ k=1,\ldots,m,$ the set of indices $j$ s.t.
-$\delta_j$ belongs to the $k$-th rational tail, by $E(k)$ the set of nodes separating the core genus one curve from the $k$-th rational tail.
-The equations have then the following form
- $$\sum_{k=1}^m(\prod_{q\in E(k)}\zeta_q)(\sum_{i\in D(k)}w_i^j)=0,\ j=1,\ldots,r$$
+Taking a coordinate $z$ on  $\PP^1$ centred at the node $q$, we see that the $i$-th basis vector corresponds to a polynomial vanishing at $q$ and at $\delta_j,\;\forall j\neq i$.
+This can be written as
+  \[e_i(z)=z\prod_{j\neq i}\frac{(z-\delta_j)}{-\delta_j},\] 
+  where we have chosen a convenient normalisation.
+So the restriction to the rational tail of the map corresponding to the point of coordinates $(w_i^j)_{i=1,\ldots,d}^{j=1,\ldots,r}$ can be written as
+  \[[1:\sum_{i=1}^d w_i^1e_i(z):\ldots,\sum_{i=1}^d w_i^re_i(z)].\] 
+  Differentiating with respect to $z$ we see that the image of the tangent vector at $q$ is given in affine coordinates around $f(E)$ by:
+  \[(\sum_{i=1}^d w_i^1,\ldots,\sum_{i=1}^d w_i^r).\] 
+  Hence smoothability is equivalent to the image of the tangent vector being zero.
+
+ More generally we may assume that the dual graph is terminally weighted \cite[\S 3.1]{HL}.
+Assume there are $k$ positive-weighted rational tails and denote by $D(h),\ h=1,\ldots,k,$ the set of indices $i$ s.t.
+$\delta_i$ belongs to the $h$-th rational tail, by $E(h)$ the set of nodes separating the core from the $h$-th rational tail.
+The equations take then the following form
+ $$\sum_{h=1}^k(\prod_{q\in E(h)}\zeta_q)(\sum_{i\in D(h)}w_i^j)=0,\ j=1,\ldots,r$$
  which can be assembled in matrix form
- $$W\cdot\underline\zeta:=(\sum_{i\in D(k)}w_i^j)_{j,k}\cdot(\prod_{q\in E(k)}\zeta_q)_k=0.$$
- We see that smoothability is equivalent to linear dependence of the rows of the above matrix $W$.
-On the other hand, on every positive-weight rational tail $R_k$, we can choose a suitable coordinate $z_k$ around the node and write the map as $[1:p_k^1(z_k):\ldots:p_k^r(z_k)]$, where $p_k^j(z_k)=\sum_{i\in D(k)}w_i^je_i^k(z_k)$ and $e_i^k(z_k)=z_k\prod_{h\in D(k)\setminus\{i\}}\frac{(z_k-\delta_h)}{-\delta_h}$.
-The elliptic curve is contracted to the point $[1:0:\ldots:0]$ and the tangent vector to $R_k$ at the node is mapped to the $k$-th row of $W$ (in affine coordinates around that point).
+ $$W\cdot\underline\zeta:=(\sum_{i\in D(h)}w_i^j)_{j,h}\cdot(\prod_{q\in E(h)}\zeta_q)_h=0.$$
+ We see that smoothability is equivalent to the linear dependence of the rows of the above matrix $W$.
+On the other hand, on every positive-weighted rational tail $R_h$, we can choose a suitable coordinate $z_h$ around the node $q_h$ and write the map as $$[1:p_h^1(z_h):\ldots:p_h^r(z_h)],$$ where: \[p_h^j(z_h)=\sum_{i\in D(h)}w_i^je_i^h(z_h) \quad \text{and} \quad e_i^h(z_h)=z_h\prod_{l\in D(h)\setminus\{i\}}\frac{(z_h-\delta_l)}{-\delta_l}.\] The elliptic curve is contracted to the point $[1:0:\ldots:0]$ and the tangent vector to $R_h$ at $q_h$ is mapped to the $h$-th row of $W$ (in affine coordinates around $f(E)$).
 Again we see that the map is smoothable if and only if the image of the tangent vectors to the rational tails at the nodes are linearly dependent in $T_{f(E)}\PP^r$.
@@
 \subsection{Viscardi's compactifications}
-For any homology class $\beta\in H_2(X,\mathbb Z)$, let $\mathcal M_{1,n}(X,\beta)$ be the stack of maps $f\colon C\to X$ from a smooth genus one curve with $n$ marked points, satisfying  $f_{*}\left [C\right ]=\beta$.
-The $m$-stable maps give compactifications of such a moduli space.
+For any homology class $\beta\in H_2(X,\mathbb Z)$, let $\pazocal M_{1,n}(X,\beta)$ be the stack of maps $f\colon C\to X$ from a \emph{smooth} elliptic curve with $n$ marked points, satisfying  $f_{*}\left [C\right ]=\beta$.
+The moduli spaces of $m$-stable maps give alternate compactifications of $\pazocal M_{1,n}(X,\beta)$.
   \begin{dfn} Let $C$ be a reduced, connected, proper curve of arithmetic genus one, and let $p_1,\dots,p_n\in C$ be smooth, distinct points.
@@
 
-The definition of a family of $m$-stable maps is then the natural one and Viscardi's main result \cite[Thm.
-3.6]{VISC} is that the associated moduli functor gives a compactification of $\mathcal M_{1,n}(X,\beta)$ (alternative to Kontsevich' moduli space).
+ Viscardi's main result \cite[Thm. 3.6]{VISC} is:
+% that the associated moduli functor gives a compactification of $\mathcal M_{1,n}(X,\beta)$ (alternative to Kontsevich' moduli space).
 \begin{thm}
-The moduli functor of $m$-stable maps in a fixed homology class $\overline{\mathcal{M}}^m_{1,n}(X,\beta)$ is represented by a proper DM stack of finite type.
+The moduli functor of $m$-stable maps in a fixed homology class $\overline{\pazocal{M}}^{(m)}_{1,n}(X,\beta)$ is represented by a proper DM stack of finite type.
 \end{thm}
 \begin{remark}\label{remark:sprouting}
-It seems to us that the algorithm presented by Viscardi to prove properness of the moduli space oversees a case.
-The problem is that, given a map $f\colon C\to\PP^r$ with $f$ constant on a genus one connected sub-curve $E\subseteq C$, it is not always true that $f$ descends to a map $f'\colon C'\to\PP^r$, where $C'$ is the singularity obtained from $C$ by contracting $E$.
-Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
+We think that the algorithm presented by Viscardi to prove properness of the moduli space oversees a case.
+The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ constant on a genus one connected sub-curve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $f'\colon \cC'_T\to\PP^r_T$, where $\cC'_0$ has a genus $1$ Gorenstein singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
 A counterexample is the following.
@@
 Consider the stable map $[f]$ in $\overline{\mathcal M}_{1,0}(\PP^3,4)$ from an elliptic bridge $R_1\sqcup_{q_1}E\sqcup_{q_2} R_2$ to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e.
-its image is the non-Gorenstein singularity $C:=\mathbb C[x,y,z]/(x,y)\cap (z,y^2-x^3)$.
+its image is the non-Gorenstein singularity: \[D:=\Spec\left(\mathbb C[x,y,z]/(x,y)\right)\cup \Spec\left(\mathbb C[x,y,z]/(z,y^2-x^3)\right).\]
 Notice that $\operatorname{d}\!f(T_{q_2}R_2)=0$, so there is a non-trivial linear relation
-\[0\cdot\operatorname{d}\!f(T_{q_1}R_1+1\cdot\operatorname{d}\!f(T_{q_2}R_2)=0\] and the map is smoothable; however, it is impossible to make the first coefficient non-zero and the map \emph{does not factorise} through an elliptic $m$-fold singularity.
-Indeed, the only chance would be to factorise through a birational map $f'\colon C'\to C$ from a tacnodal singularity $C'$.
-This is impossible since $C$ and $C'$ have the same $\delta$ invariant and so $f'$ would actually be an isomorphism.
-Observe that Viscardi suggests that the map should extend to the contraction, in a way that the image should still be $C$, since there is only one indeterminacy point (the singularity).
-We suggest that in this case the correct procedure would be to sprout $(R_1,q_1)$, but then there is actually no factorisation.
-
+\[0\cdot\operatorname{d}\!f(T_{q_1}R_1)+1\cdot\operatorname{d}\!f(T_{q_2}R_2)=0\] and the map is smoothable.
+Viscardi claims that the map factors through the family $\cC'_T$, obtained by contracting $E$ to a tacnode.
+Notice that the image of $f'$ would still need to be $D$, since there is at most one indeterminacy point of $\cC'\dashrightarrow\PP^r_T$ at the singularity.
+However our $f$ \emph{does not factorise} through the tacnode.
+Indeed we would have a birational morphism between two singular curves with the same $\delta$ invariant and common normalisation, so $f'\colon C'\to D$ would need to be an isomorphism, which is a contradiction.
+ We suggest that in this case the correct procedure would be to sprout $(R_1,q_1).$
 \begin{center}
@@
 
-However, the argument can easily be fixed.
-Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $S$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}.
-As described in \cite[Step~1, Theorem~3.6]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_S\to\PP^r_{S}$, for which we may suppose that $C_0$ is nodal and $f:=F_0$ is stable.
-
-If $f$ is not constant on the minimal genus one sub-curve \cite{SMY1}, then it is also $m$-stable and there is nothing to say.
-Otherwise, let $E\subset C$ be the maximal connected genus one sub-curve where $f$ is constant and let $R_1\sqcup\dots\sqcup R_m=\overline{C/E}$.
- By Proposition~\ref{prop:components}(2) we know there is a non-trivial linear relation among the $\operatorname{d}\!f(T_{q_i}R_i)$'s.
+However Viscardi's argument can be fixed.
+Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $T$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}.
+As described in \cite[Theorem~3.6, Step~1]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_T\to\PP^r_{T}$, for which we may suppose that $C_0$ is nodal and $f:=F_0$ is stable.
+
+If $f$ is not constant on the minimal genus $1$ subcurve \cite{SMY1}, then it is already $m$-stable and there is nothing to say.
+Otherwise let $E\subset C$ be the maximal connected genus $1$ subcurve where $f$ is constant and let $R_1\sqcup\dots\sqcup R_m=\overline{C/E}$.
+
+ By Proposition~\ref{prop:components}~(2) we know there is a non-trivial linear relation among the $\operatorname{d}\!f(T_{q_i}R_i)$'s.
  %In other words, the first derivatives of the sections $s_0,\dots,s_r$ defining $f$, satisfy a non trivial linear relation around $q_1,\dots,q_m =E\cup\bar{C/E}$.
- There are two possible situations:
- \begin{enumerate}
- \item $\operatorname{d}\!f(T_{q_i}R_i)\neq 0$ for every $i=1,\ldots,m$. Possibly after relabelling, this non-trivial relation looks like
- \[\alpha_1\operatorname{d}\!f(T_{q_{1}}R_{1})+\ldots +\alpha_j \operatorname{d}\!f(T_{q_{j}}R_{j})=0\]
-  with all the coefficients being non-zero.
-Then, we may blow-up $\mathcal{C}$ in $q_{j+1},\ldots, q_m$.
-The induced map $\tilde{F_0}$ is constant on the exceptional divisors $E_{j+1},\ldots, E_m$, so we can complete the above linear relation to
+ Consider a maximal one with all non-zero coefficients.  Possibly after relabelling this relation looks like
+ \begin{equation*}\label{eq:linrelation}
+ \alpha_1\operatorname{d}\!f(T_{q_{1}}R_{1})+\ldots +\alpha_j \operatorname{d}\!f(T_{q_{j}}R_{j})=0
+ \end{equation*}
+ In this case we blow-up $\mathcal{C}$ in $q_{j+1},\ldots, q_m$.
+The induced map $\tilde{F_0}$ is constant on the exceptional divisors $G_{j+1},\ldots, G_m$ and we can complete the above linear relation to
  \[\alpha_1\operatorname{d}\!\tilde f(T_{q_{1}}\tilde R_{1})+\ldots +\alpha_j \operatorname{d}\!\tilde f(T_{q_{j}}\tilde R_{j})+\beta_{j+1}\operatorname{d}\!\tilde f(T_{q_{j+1}}E_{j+1})+\ldots+\beta_m\operatorname{d}\!\tilde f(T_{q_{m}}E_m)=0\]
@@
 Now this \emph{sprouting} \cite[Section 2.3]{SMY2} ensures that the sections descend to the corresponding elliptic $m$-fold singularity.
-At this point, go to Step~2 of Viscardi's algorithm and follow it.
-\item  
-$\operatorname{d}\!f(T_{q_i}R_i)=0$ for some $i$, say for $i\in\left\{1,\dots,j\right\}$. 
- Then blow-up $\mathcal{C}$ at $q_{j+1},\ldots, q_m$.
+At this point proceed with Step~2 of Viscardi's algorithm.
+
+%$\operatorname{d}\!f(T_{q_i}R_i)=0$ for some $i$, say for $i\in\left\{1,\dots,j\right\}$. 
+% Then blow-up $\mathcal{C}$ at $q_{j+1},\ldots, q_m$.
 Observe that all $\operatorname{d}\!\tilde f(T_{q_i}R_i),\ i=1,\ldots,j$ and $\operatorname{d}\!\tilde f(T_{q_i}E_i),\ i=j+1,\ldots,m$ vanish, hence they satisfy any linear relation with non-zero coefficients, and they factorise through the corresponding singularity.
 The map has positive degree on the first $i=1,\ldots,j$ branches.
- \end{enumerate}
+
 \end{remark}
 
-The irreducible components of Viscardi's moduli space $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ are well understood too \cite[Thm.~5.9]{VISC}; indeed they have a similar description to the ones of Kontsevich' space.
+The irreducible components of Viscardi's moduli space $\overline{\pazocal{M}}^{(m)}_{1,n}(\PP^r,d)$ are well understood too \cite[Thm.~5.9]{VISC}; indeed they have a similar description to the ones of Kontsevich's space.
 The main advantage of the $m$-stable compactification is that the number of components drops as $m$ increases.
- \begin{cor}\cite[Cor.~5.10]{VISC}
- For $m\geq\operatorname{min}(r,d)+n$, $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ is irreducible.
- \end{cor}
-
+
+In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will be interested in the next sections does not have the boundary divisor $D_{d,n}(\PP^r,d).$
+% \begin{cor}\cite[Cor.~5.10]{VISC}
+% For $m\geq\operatorname{min}(r,d)+n$, $\overline{\mathcal{M}}^m_{1,n}(\PP^r,\beta)$ is irreducible.
+ %\end{cor}
+
+\begin{comment}
  Moreover, inspired by Viscardi's alternate compactification, we express a sufficient condition for smoothability in yet another way.
@@
 find a suitable fundamental class supported on it).
-In genus one, Vakil and Zinger managed to do so by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}).
-The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc.
-and taking the fiber product
-\bcd
-\widetilde{\mathcal M}_{1,n}(\PP^r,d)\ar[r]\ar[d] & \M{1}{n}{\PP^r}{d}\ar[d] \\
-\widetilde {\mathfrak M}_{1,n}^{\operatorname{wt}=d} \ar[r] & \mathfrak M_{1,n}^{\operatorname{wt}=d}
-\ecd
-the strict transform of the main component becomes smooth and meets the rest of the components in normal crossing fashion (the \'{e}tale local model being the union of two linear subspaces of different dimensions in affine space).
-Furthermore, the sheaves $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ contain a vector subbundle of rank $dl$ supported on the strict transform of the main component.
-This paved the way to the definition of reduced invariants.
-\begin{dfn}
-Let $X$ be a complete intersection of degree $(l_1,\ldots,l_k)$ in $\PP^r$.
-The genus one \emph{reduced} Gromov-Witten invariants of $X$ are defined by integration on $$[\widetilde{\mathcal M}_{1,n}(\PP^r,d)^\circ]\cap c_{\operatorname{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i))^\circ).$$
-\end{dfn}
 
@@
 We plan to do so by comparing the ordinary space of stable maps with Viscardi's space of 1-stable maps.
-
+\end{comment}
 \section{Cuspidal curves and maps}
@@
 
-\section{Local equations and desingularisation}
+\section{Local equations and desingularisation}\label{sec:equations}
 \subsection{Notation}

### 2017-12-13 draft.tex
added genus one CM singularities

@@
 
-In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will be interested in the next sections does not have the boundary divisor $D_{d,n}(\PP^r,d).$
+In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will consider in the next sections does not have the boundary divisor $D_{(d),(n)}(\PP^r,d).$
 % \begin{cor}\cite[Cor.~5.10]{VISC}
@@
  %\end{cor}
+ \subsection{A different characterization of smoothability}
+ Inspired by Viscardi's alternate compactification, we give yet another characterisation of smoothable maps in genus $1.$
+ \begin{dfn}
+ Let $C$ a reduced curve and $p\in C$ a singular point, we define the genus of the singularity in $p$ to be the quantity: $g(p)=\delta(p)-b(p)+1.$  We are using the following notation: $\delta(p)=\dim_k\OO_{\overline C}/\OO_C,$ $\overline{C}$ being the normalization of $C$; $b(p)$ is the number of branches at $p.$
+ \end{dfn}
+ \begin{prop}\label{prop:smoothability2}
+ Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a $n$-marked genus $1$ curve $(E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus $1$ subcurve, and $R_i$ are rational tails.
+
+  Then $f$ is smoothable if and only if it factors through a Cohen-Macaulay genus $1$ singularity with positive degree on at least one of its branches.
+\end{prop}
+
+\begin{lem}(Classification of CM genus $1$ singularities)
+The  Cohen-Macaulay genus $1$ singularities with $m$ branches are all and only obtained by gluing a genus $0$ singularity with $k$ branches with a Smyth's $m-k$-elliptic fold.
+Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
+\end{lem}
+\begin{proof}
+The proof follows the technique already used by Smyth \cite[Appendix~A]{SMY1} to classify the Goreinstein genus $1$ singularities.
+The question of classifying singularities in local analytic, so as in \cite[Appendix~A]{SMY1} we use the following notation:
+$R$ denote the analytic local ring of the singularity; 
+$\widetilde{R}=k[[t_1]\oplus\dots\oplus k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ is the maximal ideal in $R$  and $\mathfrak{m}_{\widetilde{R}}$ the maximal ideal in $\widetilde{R}.$
+
+Let us recall that to describe $R$ as a polynomial ring, it is enough to find a basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=(e_1,\dots e_s)$ where the $e_i$ are some regular functions in $\widetilde{R}.$ Indeed, once given such a basis, $R$ can be recognized as $k[x_1,\dots x_s]/I$ where $I$ is the kernel of the ring homomorphism
+\begin{align}\label{eq:singularity}
+k[[x_1,\dots x_s]]&\rightarrow R\subset k[[t_1]\oplus\dots\oplus k[[t_m]]\\
+\;\;x_i\;\; &\rightarrow \;\; e_i.\;\;
+\end{align}
+It has been observed by Smyth \cite[Proposition~A.3]{SMY1} that $R$ being the local ring of a genus $1$ singularity implies:
+\[\mathfrak{m}^2_{\widetilde{R}}\subset R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is codimension $1$},\]
+which allows him to say that, after Gauss elimination, we have $e_1,\dots e_{m-1}$ generators of $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$ of the following form
+\begin{align*}
+e_1=& (t_1 \,0\dots\,0\, a_1 t_m)\\
+e_2=&( 0\,t_2\,0\dots\, a_2 t_m)\\
+&\dots\\
+e_{m-1}=&(0\dots\,t_{m-1}\, a_{m-1}t_m ).
+\end{align*}
+with $a_{1},\dots, a_{m-1}\,\in \k.$ At this point Smyth restricts his attention on Gorenstein singularities and he shows that under the Gorenstein assumption and when $m\geq 3$: we can choose all the $a_i$ to be $1$; $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we are  done.
+Otherwise we have:
+
+\noindent{For $m\geq 3$} three possibilities:
+\begin{enumerate}
+\item At least two of the $a_i$ are non zero.
+\item Only one of the $a_i$ is non zero
+\item All the $a_i$ are zero
+\end{enumerate}
+\noindent{For $m=23$} two possibilities
+\item $a_1$ is non zero, then we have the tacnode;
+\item  $a_1$ is zero
+\noindent{For $m= 1$} As in Smyth's we prove that in this  case $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$ which means the singularity is a cusp. 
+\end{proof}
+\begin{lem}
+All of the Cohen-Macaulay genus ~$1$ singularities are smoothable.
+\end{lem}
+\begin{proof}
+We prove this statement by exhibiting an explicit smoothing for this singularities.
+Start considering two families $\cC^0\to T$ and $\cC^1\to T$ respectively of smooth rational curves and smooth elliptic curves, with $T$ a DVR scheme, e.g. consider two trivial families.
+
+ Then blow up respectively $k$ smooth points $p_1,\dots p_k$ and  $m-k$ smooth points $q_{k+1},\dots q_{m-k}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0.$
+
+On  $\widetilde{\cC}^0\xrightarrow{\pi_0} \cC^0\to T$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} \cC^1\to T$ there exist $\pi_0$, respectively $\pi_1$ semi-ample line bundles which are trivial on the proper transform of the central fibers and very ample every where else.
+If we started with the trivial families we can take \begin{align*}
+\mathcal L_0&=\pi_0^*\OO_{\cC^0}(p_1\times T+\dots+ p_k\times T)(-F_1-\dots -F_k),\\
+ \mathcal L_1&=\pi_1^*\OO_{\cC^1}(q_{k+1}\times T+\dots+ q_{m-k}\times T)(-F_{k+1}-\dots -F_{m-k})
+\end{align*}
+where we denoted by $F_j$ the exceptional divisors of both the blow ups.
+We can then contract respectively  $\;\pi_0^*(\cC^0)_0(-F_1-\dots -F_k)\;$ and $\;\pi_1^*(\cC^1)_0(-F_{k+1}-\dots -F_{m-k}).$
+
+The contracted families   $\;\hat{\cC}^0\to T\;$ and $\;\hat{\cC}^1\to T\;$ have still generic smooth fibers of genus $0$ and $1$ respectively and, by construction: $(\hat{\cC}^0)_0$ has a genus $0$ singularities with $k$ branches and $(\hat{\cC}^)_0$ has an $m-k$ elliptic curves\cite[Lemma~2.12]{SMY1}.
+
+Choose $\sigma_0$ and $\sigma_1$ two sections of $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ passing through the singular points in the central fibers and let $\hat{\cC}\to T$ the family of curves obtained identifying $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$, endowed with their reduced structures.
+Then $\hat{\cC}$ has nodal generic fiber and one of our genus 1 singularities as central fibers.
+
+Choose now a simultaneous smoothing of the generic fiber, e.g.
+if the families were trivial this is clearly possible; a generic direction of the two parameter family obtained this way is a smoothing of our singularity.
+\end{proof}
+
+\begin{proof}\ref{prop:smoothability2}
+ The argument to prove that if $f$ is smoothable then it has to factors through a genus $1$ singularity is exactly the same used by Vakil to show that the tangent vectors have to be linearly dependent in the image and thus we do not repeat it but we refer the reader to \cite{Vre}.
+
+Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $a genus $1$ singularity.
+Let $\hat{\cC}$ be a smoothing of $\hat{C}$ and $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on the smoothing, which exists because deforming line bundles on curves is unobstructed.
+Then all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
+Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0.$
+
+Since all the curve we are considering are Cohen-Maculay, they have a dualising pure sheaf $\omega_{\hat{C}}.$
+
+  \end{proof}
+
+\begin{remark}
+It is not hard to adapt Vakil's argument \cite{Vre} to show that factoring through a genus $1$ singularity is equivalent to the tangent vectors being linearly dependent in the image.
+\end{remark}
+\begin{remark}
+The ideas above are similar to those employed in \cite[Theorem 4.5.1]{RSPW} to show that $\pazocal{VZ}_{1,n}(\PP^r,d)$ is smooth, where the latter is defined by requiring the factorisation property for the map through a Smyth's singularity after sprouting.
+\end{remark}
 
@@
   \end{proof}
+
   \begin{rem}\label{remark:cuspunionline} 
@@
 \end{comment}
-\section{Cuspidal curves and maps}
-
-In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal.
+
+\section{From $p$-fields to the quintic three-fold}
+We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
+This is a word-by-word repetition of the arguments in \cite{CLpfields}, once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
+Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it should otherwise be skipped.
+
+First we introduce the notion of the \emph{cone of sections} of a smooth object $\pazocal Z$ over a family of curves $\cC$: let $B$ be any base (algebraic stack) and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
+curves; let $\mathcal L$ be a line bundle on $\cC$.
+Then there is an algebraic stack over $B$ representing sections of $\mathcal L$, and it can be defined as $C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L)$; this is because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
+More generally, the cone of section $\mathfrak S$ of $\pazocal Z$ is defined by the universal diagram:
+\bcd
+& \pazocal Z\ar[d] \\
+\cC_{\mathfrak S}\ar[r]\ar[ur,bend left,"\mathfrak e"]\ar[d,"\pi_{\mathfrak S}"] & \cC\ar[d,"\pi"] \\
+\mathfrak S \ar[r] & B
+\ecd
+The previous case can be recovered by setting $\pazocal Z=\rm{Vb}(\mathcal L)$. The morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
+\[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\pazocal Z/\cC}\]
+Notice that in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$.
+The construction for a general smooth $\pazocal Z$ is way more flexible.
+The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex, but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
+
+Let us now establish some further notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold under consideration.
+In this section we shall denote by $\rm{M}:=\oM_1^{(1)}(\PP^4,d)$, by $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ the universal $1$-stable curve and map over it, by $\L_{\rm M}=f_{\rm M}^*\OO_{\PP^4}(1)$ and by $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}$.
+Furthermore we shall write $\hM$ for $\MM_1^{(1)}$ and $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$.
+
+\begin{lem}
+ $\hP$ is a smooth Artin stack of dimension $0$. Furthermore there is a compatible triple of dual perfect obstruction theories:
+ \bcd
+ \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \ecd
+ implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
+\end{lem}
+\begin{proof}
+ The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+
+ The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
+
+ The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
+The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
+The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
+
+ The last claim follows from functoriality of virtual pullback \cite{Manolache-pullback}.
+\end{proof}
+
+We proceed to define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
+
+\begin{dfn}
+ The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))$ parametrises $1$-stable maps
+ \bcd
+ \hat\cC_S\ar[r,"f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
+ S &
+ \ecd
+ with a $p$-field $\hat\psi\in H^0(\hat\cC_S,f_{S}^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_{S}})$.
+\end{dfn}
+
+We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. %This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
+%\bcd
+%& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
+%\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
+%\pazocal P \ar[r,"\PtoM"] & \rm M
+%\ecd
+
+\begin{lem}
+ There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}))\] for the triangle:
+ \bcd
+ \pazocal P\ar[rr,"\PtoM"]\ar[dr] & & \rm M\ar[dl] \\
+ & \hP &
+ \ecd
+\end{lem}
+See \cite[Proposition 3.1]{CLpfields}.
+Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
+In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the existence of a cosection of the obstruction bundle whose degeneracy locus is the afore-mentioned substack, and the machinery of cosection localised virtual classes \cite{KLcosection}.
+Recall their Theorem 1.1:
+
+\begin{teo*}[Localization by cosection]\label{thm:KLlocalisation}
+Let $\pazocal M$ be a Deligne-Mumford stack endowed with a perfect
+obstruction theory. Suppose the obstruction sheaf $\rm{Ob}_\pazocal M$ admits a
+surjective homomorphism $\sigma:\rm{Ob}_\pazocal M|_U  \to \OO_U$
+over an open $U\subseteq \pazocal M$.
+Let $\pazocal{M}(\sigma)=\pazocal{M}\setminus U$.
+Then $(\pazocal{M},\sigma)$ has a localized virtual cycle
+$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).
+$$
+This cycle enjoys the usual properties of the virtual cycles; it relates to
+the usual virtual cycle $[\pazocal{M}]^{\rm{virt}}$ via 
+$[\pazocal{M}]^{\rm{virt}} = \iota_*[\pazocal{M}]^{\rm{virt}}_{\rm{loc}} \in A_*  \pazocal{M}$, where
+$\iota: \pazocal{M}(\sigma)\to \pazocal{M}$ is the inclusion.
+\end{teo*}
+
+We are now going to construct the cosection as in \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by tensoring of line bundles:
+\[ h_1\colon\rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
+By differentiating it and pulling it back along the universal evaluation
+\bcd
+& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal P_{\hP})\ar[d] \\
+\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
+\pazocal P \ar[r] & \rm \hP
+\ecd
+(here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
+\begin{equation}\label{eqn:cosection}
+ \begin{split}
+ \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
+ \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
+\end{split}
+\end{equation}
+
+The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
+$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
+
+We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle, and we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
+\begin{thm}
+ \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}\]%=:GW_1^{\rm{cusp}}(X,d)\]
+\end{thm}
+This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
+
+\begin{lem}
+ The deformation to the normal cone $V$ is cut inside $\rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t$ with basis coordinates $[x_0:\ldots:x_4]$ and fiber coordinate $y$ by the equation $\w(x)-ty=0$.
+If $C(V)$ denotes the affine cone over $V$, then its tangent bundle is determined by the following exact sequences:
+ \begin{equation*}
+  \begin{split}
+   0\to T_{C(V)/\Aaff^1_t}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}}\OO_{C(V)}\to 0 \\
+   0\to T_{C(V)}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}-y\mathring{t}}\OO_{C(V)}\to 0
+  \end{split}
+ \end{equation*}
+\end{lem}
+See \cite[Lemma 4.1]{CLpfields}. This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\pazocal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
+
+\bcd
+& \pazocal Z'\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & V\ar[d] \\
+& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
+\hat \cC_{\oM_1^{(1)}(V)}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat{\pi}_{\oM_1^{(1)}(V)}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
+\Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
+\ecd
+
+Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\pazocal Z:=\pazocal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
+The general theory explained above provides an obstruction theory for $\pazocal V\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
+
+\begin{lem}
+ A dual perfect obstruction theory is given by \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
+ The restriction of $\phi_{\pazocal V/\hP\times\Aaff^1_t}$ to a fiber
+ \[
+ \pazocal V_t=\left\{\begin{array}{lr} \pazocal P & t\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & t=0 \end{array}\right.
+\] gives the standard obstruction theory of $\pazocal V_t\to\hP$.
+\end{lem}
+
+We would like to conclude that the restriction of the virtual cycle to the fibers is the standard virtual cycle on the fiber.
+The techniques of functoriality in intersection theory teach us that we should look for a triple of compatible obstruction theories for the triangle:
+\bcd
+\pazocal V_t\ar[rr,hook,"\iota_t"]\ar[dr] & & \pazocal V \ar[dl] \\
+& \hP &
+\ecd
+The cone of sections interpretation provides us with an obstruction theory relative to $\pazocal V\to \hP$ given by:
+\[
+ \mathbb E'_{\pazocal V/\hP}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal K\oplus\mathcal P_{\pazocal V})
+\]
+where $\mathcal K$ is determined by the following exact sequence on $V$:
+\[
+ 0\to\mathcal K\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\oplus\OO_{\PP^4}\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}-y\mathring{t}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0
+\]
+Of course $h^0(\mathbb E'_{\pazocal V/\hP})\simeq\mathbb T_{\pazocal V/\hP}$, but the previous lemma hints at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\pazocal V/\hP})$ contains one factor $\R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}$ too many, so that restricting to the fibers we would find a different obstruction theory with respect to the standard one.
+A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber (i.e.
+applying $\iota_t^!$) we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
+
+This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to $\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP}$, where the latter fits into an exact triangle:
+\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]} \]
+
+A further complication comes from the fact that we need to work with cosection localised cycles.
+A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
+\[
+ \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{(\pr_2,\pr_3)}\rm{Vb}(\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{\cdot}\rm{Vb}(\omega_{\hat\pi_{\hP}})
+\]
+The cosection takes then the following form:
+\[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
+It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is $\Mone{1}{X}{d}\times\Aaff^1_t$.
+
+Recall that the sections $(x,y)$ are required to satisfy $\w(x)-ty=0$.
+So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\pazocal P$ when $t\neq 0$.
+It is proved in \cite[Theorem 5.2]{KLcosection} that the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
+\[
+ \iota_{t\neq0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\pazocal P]^{\rm{vir}}_{\rm{\sigma}}\in A_0(\pazocal Q),\quad \iota_{0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}\in A_0(\pazocal Q)
+\]
+where we have denoted by $\pazocal Q:=\Mone{1}{X}{d}$.
+
+We are left with proving that $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $[\Mone{1}{X}{d}]^{\rm{vir}}$.
+We shall introduce more shorthand notation: $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$.
+Chang and Li notice that there is a perfect obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})$ compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
+Then \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\pazocal N/\pazocal Q}$ is supported inside
+\[
+ h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{|D(\sigma_0')}
+\]
+so that they may combine the techniques of virtual pullback \cite{Manolache-pullback} and localisation by cosection \cite{KLcosection} to define:
+\[
+ v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0'))
+\]
+Finally they notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as $[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]$ along the fibers, and this is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
+
+Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves.
+
+\section{The comparison morphism}
+
+%In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal.
 We will see how in this case we can give a comparison with the GW-invariant and explain why the same technique does not work for higher $m$.
-The first thing we do is the following:
-we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves.
+%The first thing we do is the following:
+%we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves.
 We show that there is a birational morphism from a correspondingly decorated moduli space of prestable nodal curves.
@@
 
-Why should such a morphism on decorated prestable curves exist? 
-Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node.
+%Why should such a morphism on decorated prestable curves exist? 
+%Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node.
 In the first case we can associate to this the locally constant family of cusps obtained by forgetting the elliptic tail and contracting a length-two infinitesimal neighborhood of the node in the rational component; in the second case, we claim that the line bundle $\mathcal O_\mathcal C(3q)$ gives a morphism to a smoothing of the cuspidal $\PP^1$.
@@
 Assume $d>0$ throughout the following.
+In this section: we show in two different ways that there exists a morphism at the level of weighted prestable curves $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1);$ introduce the spaces
+\[\Z:= \mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M_{1,n}(\PP^4,d)(1),\qquad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M^p_{1,n}(\PP^4,d)(1) \]
+ and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$
 
@@
 
-\section{From $p$-fields to the quintic three-fold}
-We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
-This is a word-by-word repetition of the arguments in \cite{CLpfields}, once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
-Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it should otherwise be skipped.
-
-First we introduce the notion of the \emph{cone of sections} of a smooth object $\pazocal Z$ over a family of curves $\cC$: let $B$ be any base (algebraic stack) and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
-curves; let $\mathcal L$ be a line bundle on $\cC$.
-Then there is an algebraic stack over $B$ representing sections of $\mathcal L$, and it can be defined as $C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L)$; this is because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
-More generally, the cone of section $\mathfrak S$ of $\pazocal Z$ is defined by the universal diagram:
-\bcd
-& \pazocal Z\ar[d] \\
-\cC_{\mathfrak S}\ar[r]\ar[ur,bend left,"\mathfrak e"]\ar[d,"\pi_{\mathfrak S}"] & \cC\ar[d,"\pi"] \\
-\mathfrak S \ar[r] & B
-\ecd
-The previous case can be recovered by setting $\pazocal Z=\rm{Vb}(\mathcal L)$. The morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
-\[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\pazocal Z/\cC}\]
-Notice that in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$.
-The construction for a general smooth $\pazocal Z$ is way more flexible.
-The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex, but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
-
-Let us now establish some further notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold under consideration.
-In this section we shall denote by $\rm{M}:=\oM_1^{(1)}(\PP^4,d)$, by $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ the universal $1$-stable curve and map over it, by $\L_{\rm M}=f_{\rm M}^*\OO_{\PP^4}(1)$ and by $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}$.
-Furthermore we shall write $\hM$ for $\MM_1^{(1)}$ and $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$.
-
-\begin{lem}
- $\hP$ is a smooth Artin stack of dimension $0$. Furthermore there is a compatible triple of dual perfect obstruction theories:
- \bcd
- \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
- \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
- \ecd
- implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
-\end{lem}
-\begin{proof}
- The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
-
- The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
-
- The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
-The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
-The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
-
- The last claim follows from functoriality of virtual pullback \cite{Manolache-pullback}.
-\end{proof}
-
-We proceed to define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
-
-\begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))$ parametrises $1$-stable maps
- \bcd
- \hat\cC_S\ar[r,"f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
- S &
- \ecd
- with a $p$-field $\hat\psi\in H^0(\hat\cC_S,f_{S}^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_{S}})$.
-\end{dfn}
-
-We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. %This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
-%\bcd
-%& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
-%\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
-%\pazocal P \ar[r,"\PtoM"] & \rm M
-%\ecd
-
-\begin{lem}
- There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}))\] for the triangle:
- \bcd
- \pazocal P\ar[rr,"\PtoM"]\ar[dr] & & \rm M\ar[dl] \\
- & \hP &
- \ecd
-\end{lem}
-See \cite[Proposition 3.1]{CLpfields}.
-Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
-In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the existence of a cosection of the obstruction bundle whose degeneracy locus is the afore-mentioned substack, and the machinery of cosection localised virtual classes \cite{KLcosection}.
-Recall their Theorem 1.1:
-
-\begin{teo*}[Localization by cosection]\label{thm:KLlocalisation}
-Let $\pazocal M$ be a Deligne-Mumford stack endowed with a perfect
-obstruction theory. Suppose the obstruction sheaf $\rm{Ob}_\pazocal M$ admits a
-surjective homomorphism $\sigma:\rm{Ob}_\pazocal M|_U  \to \OO_U$
-over an open $U\subseteq \pazocal M$.
-Let $\pazocal{M}(\sigma)=\pazocal{M}\setminus U$.
-Then $(\pazocal{M},\sigma)$ has a localized virtual cycle
-$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).
-$$
-This cycle enjoys the usual properties of the virtual cycles; it relates to
-the usual virtual cycle $[\pazocal{M}]^{\rm{virt}}$ via 
-$[\pazocal{M}]^{\rm{virt}} = \iota_*[\pazocal{M}]^{\rm{virt}}_{\rm{loc}} \in A_*  \pazocal{M}$, where
-$\iota: \pazocal{M}(\sigma)\to \pazocal{M}$ is the inclusion.
-\end{teo*}
-
-We are now going to construct the cosection as in \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by tensoring of line bundles:
-\[ h_1\colon\rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
-By differentiating it and pulling it back along the universal evaluation
-\bcd
-& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal P_{\hP})\ar[d] \\
-\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
-\pazocal P \ar[r] & \rm \hP
-\ecd
-(here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
-\begin{equation}\label{eqn:cosection}
- \begin{split}
- \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
- \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
-\end{split}
-\end{equation}
-
-The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
-$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
-
-We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle, and we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
-\begin{thm}
- \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}\]%=:GW_1^{\rm{cusp}}(X,d)\]
-\end{thm}
-This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
-
-\begin{lem}
- The deformation to the normal cone $V$ is cut inside $\rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t$ with basis coordinates $[x_0:\ldots:x_4]$ and fiber coordinate $y$ by the equation $\w(x)-ty=0$.
-If $C(V)$ denotes the affine cone over $V$, then its tangent bundle is determined by the following exact sequences:
- \begin{equation*}
-  \begin{split}
-   0\to T_{C(V)/\Aaff^1_t}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}}\OO_{C(V)}\to 0 \\
-   0\to T_{C(V)}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}-y\mathring{t}}\OO_{C(V)}\to 0
-  \end{split}
- \end{equation*}
-\end{lem}
-See \cite[Lemma 4.1]{CLpfields}. This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\pazocal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
-
-\bcd
-& \pazocal Z'\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & V\ar[d] \\
-& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
-\hat \cC_{\oM_1^{(1)}(V)}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat{\pi}_{\oM_1^{(1)}(V)}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
-\Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
-\ecd
-
-Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\pazocal Z:=\pazocal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
-The general theory explained above provides an obstruction theory for $\pazocal V\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
-
-\begin{lem}
- A dual perfect obstruction theory is given by \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
- The restriction of $\phi_{\pazocal V/\hP\times\Aaff^1_t}$ to a fiber
- \[
- \pazocal V_t=\left\{\begin{array}{lr} \pazocal P & t\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & t=0 \end{array}\right.
-\] gives the standard obstruction theory of $\pazocal V_t\to\hP$.
-\end{lem}
-
-We would like to conclude that the restriction of the virtual cycle to the fibers is the standard virtual cycle on the fiber.
-The techniques of functoriality in intersection theory teach us that we should look for a triple of compatible obstruction theories for the triangle:
-\bcd
-\pazocal V_t\ar[rr,hook,"\iota_t"]\ar[dr] & & \pazocal V \ar[dl] \\
-& \hP &
-\ecd
-The cone of sections interpretation provides us with an obstruction theory relative to $\pazocal V\to \hP$ given by:
-\[
- \mathbb E'_{\pazocal V/\hP}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal K\oplus\mathcal P_{\pazocal V})
-\]
-where $\mathcal K$ is determined by the following exact sequence on $V$:
-\[
- 0\to\mathcal K\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\oplus\OO_{\PP^4}\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}-y\mathring{t}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0
-\]
-Of course $h^0(\mathbb E'_{\pazocal V/\hP})\simeq\mathbb T_{\pazocal V/\hP}$, but the previous lemma hints at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\pazocal V/\hP})$ contains one factor $\R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}$ too many, so that restricting to the fibers we would find a different obstruction theory with respect to the standard one.
-A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber (i.e.
-applying $\iota_t^!$) we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
-
-This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to $\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP}$, where the latter fits into an exact triangle:
-\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]} \]
-
-A further complication comes from the fact that we need to work with cosection localised cycles.
-A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
-\[
- \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{(\pr_2,\pr_3)}\rm{Vb}(\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{\cdot}\rm{Vb}(\omega_{\hat\pi_{\hP}})
-\]
-The cosection takes then the following form:
-\[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
-It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is $\Mone{1}{X}{d}\times\Aaff^1_t$.
-
-Recall that the sections $(x,y)$ are required to satisfy $\w(x)-ty=0$.
-So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\pazocal P$ when $t\neq 0$.
-It is proved in \cite[Theorem 5.2]{KLcosection} that the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
-\[
- \iota_{t\neq0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\pazocal P]^{\rm{vir}}_{\rm{\sigma}}\in A_0(\pazocal Q),\quad \iota_{0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}\in A_0(\pazocal Q)
-\]
-where we have denoted by $\pazocal Q:=\Mone{1}{X}{d}$.
-
-We are left with proving that $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $[\Mone{1}{X}{d}]^{\rm{vir}}$.
-We shall introduce more shorthand notation: $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$.
-Chang and Li notice that there is a perfect obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})$ compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
-Then \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\pazocal N/\pazocal Q}$ is supported inside
-\[
- h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{|D(\sigma_0')}
-\]
-so that they may combine the techniques of virtual pullback \cite{Manolache-pullback} and localisation by cosection \cite{KLcosection} to define:
-\[
- v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0'))
-\]
-Finally they notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as $[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]$ along the fibers, and this is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
-
-Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves.
-
-\section{Local equations and desingularisation}\label{sec:equations}
-\subsection{Notation}
+\subsection{Fiber products and induced obstruction theories}
 Let $\Z$ be defined by the pullback diagram:
@@
 
-We introduce some more notation: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
+We introduce some more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
 \bcd
@@
 \end{cor}
+
+\section{Local equations and desingularisation}\label{sec:equations}
 \subsection{Equations for $\Z^p$ relative to $\XP$}

### 2017-12-18 draft.tex
revising sec 3

@@
  %\end{cor}
+
  \subsection{A different characterization of smoothability}
@@
  \begin{dfn}
- Let $C$ a reduced curve and $p\in C$ a singular point, we define the genus of the singularity in $p$ to be the quantity: $g(p)=\delta(p)-b(p)+1.$  We are using the following notation: $\delta(p)=\dim_k\OO_{\overline C}/\OO_C,$ $\overline{C}$ being the normalization of $C$; $b(p)$ is the number of branches at $p.$
+ Let $C$ be a reduced curve over a field $k$ and $p\in C$ a singular point.
+We define the \emph{genus of the singularity} in $p$ to be the quantity: $$g(p)=\delta(p)-b(p)+1,$$ where $\delta(p)=\dim_k\OO_{\overline C}/\OO_C,$ $\overline{C}$ is the normalisation of $C$, and $b(p)$ is the number of branches at $p.$
  \end{dfn}
@@
 
-\begin{lem}(Classification of CM genus $1$ singularities)
+\begin{lem}\label{lem:classificationsing}(Classification of CM genus $1$ singularities)
 The Cohen-Macaulay genus $1$ singularities with $m$ branches are all and only obtained by gluing a genus $0$ singularity with $k$ branches with a Smyth's $m-k$-elliptic fold.
+We call such a singularity a \textbf{(k,m)-type} genus $1$ singularity.
 Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
@@
 \end{enumerate}
-\noindent{For $m=23$} two possibilities
+\noindent{For $m=2$} two possibilities
 \item $a_1$ is non zero, then we have the tacnode;
@@
 \begin{lem}
-All of the Cohen-Macaulay genus ~$1$ singularities are smoothable.
+Every Cohen-Macaulay genus $1$ singularity is smoothable.
 \end{lem}
 \begin{proof}
-We prove this statement by exhibiting an explicit smoothing for this singularities.
-Start considering two families $\cC^0\to T$ and $\cC^1\to T$ respectively of smooth rational curves and smooth elliptic curves, with $T$ a DVR scheme, e.g. consider two trivial families.
+We exhibit explicit smoothings for the above singularities.
+Start with two families $\cC^0\to T$ and $\cC^1\to T$ over a DVR scheme, respectively of smooth rational curves and smooth elliptic curves, with $T$ a DVR scheme, e.g. consider two trivial families.
 
@@
 
-Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $a genus $1$ singularity.
+Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $ a genus $1$ singularity.
+
 Let $\hat{\cC}$ be a smoothing of $\hat{C}$ and $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on the smoothing, which exists because deforming line bundles on curves is unobstructed.
-Then all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
+We are first going to show that we can extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ and then argue how to get a smoothing of $f$ from $\hat{F}.$
+
+For the first part, all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
 Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0.$
 
-Since all the curve we are considering are Cohen-Maculay, they have a dualising pure sheaf $\omega_{\hat{C}}.$
+Since all the curve we are considering are Cohen-Maculay, they have a dualising pure sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
+\[H^1(\hat{C},\hat{L})=(H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}}))^{\vee}.\]
+It is well know \cite[IV, \S~3]{serre} that  $\omega_{\hat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ locally satisfying:
+\[\omega\in \nu_* \omega_{\overline{C}}\otimes K(\overline{C})(U)\;\;\;\text{s.t.}\;\;\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*f\omega) =0\;\;\;\forall \,f\in\,\OO_C(U).\]
+Let $\hat{C}$ be a genus $1$ curve with only one singularity which is a genus $1$ singularity of $(k,m)$-type
+ Using the explicit local description of genus $1$ singularities that we worked out in Lemma~\ref{lem:classificationsing}, we see that 
+\[\omega_C\hookrightarrow \nu_*\omega_{\overline{C}}(p_1+\dots p_k+2 p_{k+1}\dots+2p_m)=\nu_*\left(\OO_{\PP^1}(-1)\oplus\dots\oplus\OO_{\PP^1}\oplus\dots \OO_{\PP^1}\right)\]
+and the kernel of the inclusion is supported on the singular point. We then have an inclusion
+\[H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}})\hookrightarrow H^0(\nu_*\left(\OO_{\PP^1}(-1)\oplus\dots\oplus\OO_{\PP^1}\oplus\dots \OO_{\PP^1}\right)\otimes\hat{L})^{-1})=0;\]
+where the last equality follows from the fact that $\hat{L}){-1}$ has degree less or equal to $0$ on every irreducible component of $\hat{C}.$
+
+We conclude showing how to smooth $f\colon C\to \PP^r$ given $\hat{F}\colon\hat{C}\to\PP^r.$
 
@@
 
-\section{From $p$-fields to the quintic three-fold}
+\section{From $p$-fields to the quintic three-fold}\label{section:p-fields}
+
 We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
@@
 \section{The comparison morphism}
-
 %In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal.
@@
 Assume $d>0$ throughout the following.
-In this section: we show in two different ways that there exists a morphism at the level of weighted prestable curves $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1);$ introduce the spaces
-\[\Z:= \mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M_{1,n}(\PP^4,d)(1),\qquad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M^p_{1,n}(\PP^4,d)(1) \]
- and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$
-
+In this section we shall:
+\begin{itemize}
+ \item argue in two different ways that there is a natural fashion to associate a weighted $1$-stable curve to a weighted-stable nodal curve of genus $1$, essentially by replacing elliptic tails of weight $0$ by cusps, which results in a morphism:
+ \[\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)\]
+extending the identity on the locus of smooth elliptic curves;
+ \item introduce the fiber product 
+ \[\Z:= \mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)\]
+ and show that it is a closed substack of $\oM_1(\PP^4,d)$, isomorphic to it outside the boundary divisor $D^1$;
+ \item introduce the fiber product \[\Zp:=\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)^p \]
+ and endow it with an obstruction theory and a cosection thereof, which are pulled back from  $\pazocal M^{(1)}_{1,n}(\PP^4,d)^p$; unfortunately we will not be able to compare them directly with $\oM_1(\PP^4,d)^p$;
+ \item explain along the way all the notation one needs in order to understand the previous sentences.
+\end{itemize}
+%in two different ways that there exists a morphism at the level of weighted prestable curves $\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1);$ introduce the spaces
+%\[\Z:= \mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M_{1,n}(\PP^4,d)(1),\qquad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M^p_{1,n}(\PP^4,d)(1) \]
+%and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$
+
+Let us start with some notation. In the following by \emph{special point} we mean the preimage of a node or a marking on the normalisation.
 \begin{dfn}
-Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ be the stack of \emph{prestable} (projective, nodal and reduced), connected, arithmetic genus one, $n$-marked curves that are \emph{stably weighted} with total weight $d$, i.e.
-for every geometric point there is an integer-valued function on the set of irreducible components of the corresponding curve, such that it is compatible with specialisation maps and the sum of the integers is $d$; furthermore we require that all integers are nonnegative and every $p_a=0$ weight-0 component has at least three special points (every $p_a=1$ weight-0 component has at least one special point).
+Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ be the stack of \emph{prestable} (nodal and reduced), projective, connected, arithmetic genus one, $n$-marked curves that are \emph{stably weighted} with total weight $d$, i.e.
+for every geometric point of $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ there is an integer-valued function on the set of irreducible components of the corresponding curve, such that it is compatible with specialisation maps and the sum of the integers is $d$; furthermore we require that it takes nonnegative values, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
 \end{dfn}
-Remark that there is an \'{e}tale, non-separated morphism $\mathfrak M_{1,n}^{\operatorname{wt}}\to\mathfrak M_{1,n}$ and the weight stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factorises through $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.
+Remark that there is an \'{e}tale, non-separated morphism $\mathfrak M_{1,n}^{\operatorname{wt}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.
 
@@
 Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective, reduced, connected, arithmetic genus one, $n$-marked curves that are stably weighted with total weight $d$, i.e.
-as above with (stricter) stability condition: every $p_a=0$ weight-0 component has at least three special points (every $p_a=1$ weight-0 component has at least \emph{two} special point) \emph{and} every weight-0 cusp has at least two further special points.
+the weight is nonnegative, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component  of weight $0$ has at least \emph{two} special points).
 \end{dfn}
 
-Note that the only type of nodal curves that we are getting rid of is the one with an elliptic tail of weight zero.
+Note that the only type of nodal curves that we are getting rid of are the ones with an elliptic tail of weight zero.
 
@@
 \end{thm} 
-We approach the proof in two different manners: first we adopt the strategy of constructing the graph of such morphism and prove that projection on the source is an isomorphism; second we construct the $1$-stabilisation at the level of curves with divisors with an argument \'{a} la Hassett \cite{HassettHyeon}, then argue that it descends to a morphism between moduli spaces of weighted curves.
+As anticipated we explain two different approaches to the proof:
+\begin{enumerate}
+ \item we adopt the strategy of constructing the graph of such a morphism within the product $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ and prove that the projection onto the first factor is an isomorphism;
+\item we prove that the $1$-stabilisation exists at the level of curves with a divisor constructing the contraction directly, then argue that it descends to a morphism between moduli spaces of weighted curves.
+\end{enumerate}
 
@@
 
-The idea of this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
-
-Let $\mathfrak{P}=\mathfrak{Pic}^d_{\cC/\MM_1}$ with the stability condition that 
-\[\omega_\pi\otimes \mathcal L^{\otimes 3}\]
- is $\pi$-ample.
+The idea behind this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
+
+Let $\mathfrak{P}=\mathfrak{Pic}^{d,rm{st}}_{\cC/\MM_1}$ with the stability condition that the line bundle $\omega_\pi\otimes \mathcal L^{\otimes 3}$ on the universal curve is $\pi$-relatively ample.
+
 We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
-More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields}), where the section is not $0$ on any irreducible component of the curve.
-Alternatively one can think of the moduli functor of a line bundle with a section up to scalar as the hom-stack $\Hom_{\MM_1}(\C,[\Aaff^1/\Gm])$, again requiring the section not to be $0$ and the total degree of the line bundle to be $d$.
-
-We shall first construct the contraction over $\MM^{\rm{div}}$ and then show that it descends to $\MM^{\rm{wt}}$.
-
-Let $E$ be the locus inside the universal curve spanned by elliptic tails; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $E$.
+More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields} and Section \ref{section:p-fields} above), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
+Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\mathcal C,[\Aaff^1/\Gm])$; then again one picks the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
+
+We shall construct the contraction over $\MM_1^{\rm{div}}$ first, and then show that it descends to $\MM_1^{\rm{wt}}$.
+
+Let $E$ be the locus inside the universal curve spanned by elliptic tails of weight $0$; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $E$.
 We shall also denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$ (and its various pullbacks), which is a Cartier divisor as well.
 
-We write 
+Consider the following line bundle on the universal curve over $\MM_1^{\rm{div}}$: 
 \begin{equation}\label{eq:linebundlecontraction}
@@
 \end{equation} where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
-Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so if the contraction morphism is well defined it will contract this locus.
+Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so the Proj construction applied to it will contract this locus.
 
 \begin{prop}\label{1-stabilization-div}
- The $1$-stabilisation $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$ is defined by the line bundle $\mathcal N$:
+In the following diagram $\hat\cC$ is a family of weighted $1$-stable curves and $\phi$ is a regular morphism:
+
  \bcd
@@
  \ecd
+This defines the $1$-stabilisation morphism $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$.
 \end{prop}
 
-We shall prove this proposition through a series of lemmas.
-The first one is a technical tool drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base change to generically chosen curves inside $\MM_1^{\rm{div}}$.
-In the following it will allow us to check that $\mathcal N$ is semi-ample and that $\pi_*\mathcal N$ is locally free assuming that $\cC\to T$ is a smoothing over the spectrum of a discrete valuation ring.
+We need to check that $\mathcal N$ is $\pi$-semi-ample (regularity of $\phi$) and that $\pi_*\mathcal N$ is locally free (flatness of $\hat\pi$).
+Both these facts are clear generically, but less so on points of $E$ and $\mathfrak D^1$.
+We shall check this by exploiting the next lemma, which is a nice technical gadget drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base-change to generic curves inside $\MM_1^{\rm{div}}$, allowing us to work with a smoothing of the elliptic tail over a DVR scheme $T$.
 

### 2017-12-18 draft.tex
revising sec 3

@@
 
-We need to check that $\mathcal N$ is $\pi$-semi-ample (regularity of $\phi$) and that $\pi_*\mathcal N$ is locally free (flatness of $\hat\pi$).
+We need to prove that $\mathcal N$ is $\pi$-semi-ample (regularity of $\phi$) and that $\pi_*\mathcal N$ is locally free (flatness of $\hat\pi$).
 Both these facts are clear generically, but less so on points of $E$ and $\mathfrak D^1$.
@@
 Let $\pi\colon\cC\to S$ be a proper family of curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\mathfrak D\subseteq S$.
-Then for every $T$ the spectrum of a DVR with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
+Then for every spectrum of a DVR $T$ with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
 \[f^*\pi_*\mathcal N\cong \pi_*f^*\mathcal N.\]
@@
 \end{proof}
-Now recall that $\mathcal N$ is trivial on elliptic tails and of positive degree everywhere else.
+Now recall that in our case $\mathcal N$ is trivial on elliptic tails and of positive degree everywhere else.
 The rank of $\R^1\pi_*\mathcal N$ can be checked on the fibers \cite[Theorem III.12.11]{HAR}, so we see that it is $0$ outside $\mathfrak D^1$ and $1$ on it.
@@
 \begin{lem}\label{lemma:semiample}
-The line bundle $\mathcal N$ is $\pi$ semi-ample, i.e. the natural map
+The line bundle $\mathcal N$ is $\pi$-semi-ample, i.e. the natural map
 \[\pi^*\pi_*\mathcal N^{\otimes n}\to \mathcal N^{\otimes n}\]
-is surjective.
+is surjective for $n\gg 0$ (in fact $n=1$ suffices).
 \end{lem}
@@
 We are left to check on points belonging to an elliptic tail; thanks to the above Lemma we can reduce to the case that $C$ is the central fiber of a one-parameter smoothing of the elliptic tail.
-This has been proved by Smyth~\cite[Lemma~2.12]{SMY1}.
+This has been dealt with by Smyth~\cite[Lemma~2.12]{SMY1}.
 \end{proof}
@@
 On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ we see that $\R^1\pi_*\mathcal N=0$, so $\pi_*\mathcal N$ satisfies Cohomology and Base Change and its rank is determined by Riemann-Roch.
-Given a point $x$ on the boundary $\mathfrak{D}^1$, we can always find a DVR $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank looking at $\pi_*f^*\mathcal N$ over the DVR scheme $T.$ But now $f^*\mathcal N$ is flat over $T$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free over $T$.
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can pick a DVR scheme $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank at $x$ by looking at $\pi_*f^*\mathcal N$ over $T.$ Now $f^*\mathcal N$ is flat over $T$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free (constant rank).
 \end{proof}
@@
  \bcd
- (C,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat C=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ (\cC_S,D_S)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat \cC_S=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(D_S))\ar[ld,"\hat\pi"] \\
  & S &
  \ecd
-where $\phi$ is proper and birational morphism since $\mathcal N$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal N$ is locally free. 
-To verify that this define a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{C}$ has reduced fibers and only nodes and cusps as singularities.
-
-Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $T$ chosen as in Lemma~\ref{DVR} so that the construction commutes with base change.
-Furthermore we can pick $f\colon T\to \MM_1$ so that the total space $\cC_T$ is regular, so we are in the hypotheses of Smyth's contraction Lemma~\cite[Lemma~2.13]{SMY1}
+where $\phi$ is a proper and birational morphism since $\mathcal N$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal N$ is locally free. 
+To verify that this defines a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{\cC}_S$ has reduced fibers and only nodes and cusps as singularities.
+
+Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $T$ chosen as in Lemma~\ref{DVR}, so that the construction commutes with base change.
+Furthermore we can pick $f\colon T\to S$ such that the total space $\cC_T$ is regular, so we may just apply Smyth's Contraction Lemma~\cite[Lemma~2.13]{SMY1}.
 
@@
 it is enough to verify that there is an isomorphism
- $\rm{pr}_1^*\hat\cC\cong\rm{pr}_2^*\hat\cC$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
-
- This follows from the fact that $\pr_i^*\hat\cC$ are obtained from applying the Proj construction to 
+ $\rm{pr}_1^*\hat \cC_S\cong\rm{pr}_2^*\hat \cC_S$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
+
+ This follows from the fact that $\pr_i^*\hat \cC_S$ are obtained from applying the Proj construction to 
  $\rm{pr}_i^*\pi_{S,*}\mathcal{N}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal N$, by flatness of $S'\to S$. Thus it is enough to show that 
  \[\rm{pr}_1^*\mathcal N\cong \rm{pr}_2^*\mathcal N.\]
-  But $\mathcal N$ is the pullback of a line bundle on $\MM_1^{\rm{div}}$, thus the desired isomorphism follows from the commutativity of the following diagram
+  But $\mathcal N$ is the pullback of a line bundle on $\MM_1^{\rm{div}}$, thus the desired isomorphism follows from the commutativity of the diagram
 
@@
 \begin{prop}
-The $1$-stabilisation with divisors descends to the level of weighted curves:
-\bcd
-\MM_1^{\rm{div}}\ar[r]\ar[d] & \MM_1^{(1),\rm{div}}\ar[d] \\
-\MM_1^{\rm{wt}}\ar[r] & \MM_1^{(1),\rm{wt}}
+The $1$-stabilisation just defined for curves with a divisor induces an analogue morphism on weighted curves:
+\bcd
+\MM_1^{\rm{div}}\ar[r]\ar[d]\ar[dr,phantom,"\curvearrowright"] & \MM_1^{\rm{div}}(1)\ar[d] \\
+\MM_1^{\rm{wt}}\ar[r,"\exists"] & \MM_1^{\rm{wt}}(1)
 \ecd
@@
 \begin{proof}
-{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose sections $s_i$ such that their sum as a relative Cartier divisor $D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
-If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to taking an {\'e}tale cover we can assume there are sections $s_i$ of $\cC_S\xrightarrow{\pi_S} S$ that define a lifting $S\to \MM_1^{\rm{div}}$ and thus through the above construction a morphism $\xi\colon S\to  \MM_1^{(1),\rm{wt}}.$
-
-In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{(1),\rm{wt}}$ we need to verify that  $\rm{pr}_1(\xi)\cong\rm{pr}_2(\xi)$ and the cocycle condition is satisfied, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
-
-This boils down to checking that for two different choices of a lifting $S\xrightarrow{s_i,\;s'_i}\MM_1^{\rm{div}}$ we have a unique isomorphism 
-\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D'))^{\otimes n}\right)=\hat{\mathcal C}_2.
-\]
-By construction we have a birational map 
- \bcd
-&\mathcal C \ar[dl,"\phi_1"]\ar[dr,"\phi_2"]  \\
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose smooth sections $s_i$ of the universal curve in a way that their sum as a relative Cartier divisor $D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
+If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to taking an {\'e}tale cover we can assume there are sections $s_i$ of $\cC_S\to S$ that define a lifting $S\to \MM_1^{\rm{div}}$, and thus a morphism $\xi\colon S\to  \MM_1^{\rm{wt}}(1)$ through the above construction.
+
+In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{\rm{wt}}(1)$ we need to verify that  $\rm{pr}_1^*(\xi)\cong\rm{pr}_2^*(\xi)$ and the cocycle condition is satisfied, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
+
+This boils down to checking that for two different choices of a lifting $D_1,D_2\colon S\to\MM_1^{\rm{div}}$ there exists a unique isomorphism 
+\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_1))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_2))^{\otimes n}\right)=\hat{\mathcal C}_2.
+\]
+By construction there is a birational map $\psi$
+ \bcd
+&\cC_S \ar[dl,"\phi_1" above left]\ar[dr,"\phi_2"]  \\
  \hat{\mathcal C}_1\ar[rr,dashed, "\psi"] & &\hat{\mathcal C}_2.
@@
 
-We want to show that it extends to a regular morphism. 
-First of all notice that $ \hat{\mathcal C}_i$ is normal, $i=1,2$.
-Indeed, since $S$ is smooth and the singularities of the fibers are in co-dimension 1, $ \hat{\mathcal C}_i$ is regular in codimension 1.
-Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy the ($S_2$) condition of Serre, also the total space does \cite[Thorem~23.9]{MAT}.
-Then, since the fibers are geometrically connected, Zariski's connectedness theorem implies that
-\[\phi_{i,*}\OO_{\mathcal C}\cong \OO_{\hat{\mathcal C}_i} \]
- Moreover notice that by construction $\operatorname{Ex}(\phi_1)\cong \operatorname{Ex}(\phi_2),$ so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then a standard argument \cite[Lemma 1.15]{debarre}
-shows that $\phi_2$ factors through $\phi_1$ and vice versa. This proves the regularity of $\psi$ and its inverse. Notice that $\psi$ is unique as it is the only extension of $\phi_2\circ\phi_1^{-1}$.
+We want to show that $\psi$ extends to a regular morphism. 
+Notice that $ \hat{\mathcal C}_i$ is normal, $i=1,2$.
+Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hat{\mathcal C}_i$ is regular in codimension $1$.
+Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy Serre's condition $S_2$, so does the total space of $\hat\cC_i$ by \cite[Thorem~23.9]{MAT}.
+Then, since the geometric fibers of $\phi_i$ are either points or $p_a=1$ subcurves, and in either case connected, Zariski's connectedness theorem implies that
+\[\phi_{i,*}\OO_{\cC_S}\cong \OO_{\hat{\mathcal C}_i}. \]
+ Moreover by construction $\operatorname{Exc}(\phi_1)=\operatorname{Exc}(\phi_2)$ is the locus of elliptic tails of weight $0$, so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then \cite[Lemma 1.15]{debarre}
+implies that $\phi_2$ factors through $\phi_1$, and viceversa.
+This proves the regularity of $\psi$ and its inverse.
+Notice that $\psi$ is unique as it is the only extension of $\phi_2\circ\phi_1^{-1}$.
 \end{proof}
@@
 \bcd
-\mathcal Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
+\Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
+\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
 \ecd
@@
 \bcd
-\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 \\
+C \ar[rr,"\phi"]\ar[dr,"\pi" below left] & & \hat C\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 \\
 & S & & &
 \ecd
-where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisation (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams
-\bcd
-\cC\ar[r,"\phi"]\ar[d,"\psi"] &  \hat\cC\ar[r,"f"]\ar[d,"\hat\psi"] & \PP^4 \ar[d,"\id_\PP"]\\
-\cC'\ar[r,"\phi'"] &  \hat\cC'\ar[r,"f'"] & \PP^4
+where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisationdefined above (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams
+\bcd
+C\ar[r,"\phi"]\ar[d,"\psi"] &  \hat C\ar[r,"f"]\ar[d,"\hat\psi"] & \PP^4 \ar[d,"\id_\PP"]\\
+C'\ar[r,"\phi'"] &  \hat C'\ar[r,"f'"] & \PP^4
 
@@
 
-Forgetting $\hat \cC$ and keeping $f\circ\phi\colon \cC\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d).$
+Forgetting $\hat C$ and keeping $f\circ\phi\colon C\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d).$
 

### 2017-12-18 draft.tex
in sec 3 only loc vir pull commutes with push is missing

@@
 \bcd
-\cC_{\eta}\ar[r]\ar[d,"\phi_{\eta}"]  & \cC_T\ar[d,"\phi_T"]\ar[r,"f"] &\PP^4\\
-\hat{\cC}_{\eta}\ar[r,"j"]\ar[urr] & \hat{\cC_T}\ar[ur,dashed ,"g"] &
+\cC_{\eta}\ar[r]\ar[d,"\phi_{\eta}" left]  & \cC_T\ar[d,"\phi_T" left]\ar[r,"f"] & \PP^4 \\
+\hat{\cC}_{\eta}\ar[r,"j" below]\ar[urr] & \hat{\cC_T}\ar[ur,dashed ,"g" below right] &
  \ecd 
@@
 
-Observe that $f$ is constant on the fibers of $\phi$ so it factors topologically through $\hat{\cC}.$
-We can conclude as in \cite{RSPW} or show that $\phi_*\OO_{\cC_T}\cong\OO_{\hat{\cC}_T}$ and appeal to \cite[Lemma~1.15]{debarre}. To do that, consider the exact sequence:
+Observe that $f$ is constant on the fibers of $\phi_T$, so it factors topologically through $\hat{\cC}.$
+We can conclude as in \cite{RSPW} or appeal to \cite[Lemma~1.15]{debarre} using $\phi_*\OO_{\cC_T}\cong\OO_{\hat{\cC}_T}$. To see this consider the exact sequence:
 \[0\to \OO_{\hat{\cC}_T}\to\phi_*\OO_{\cC_T}\to \phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T}\to 0\]
 Since $\phi$ is an isomorphism away from the cuspidal point, the cokernel is supported in dimension $0$.
-However $\chi (\OO_{\hat{\cC}_T})=\chi(\phi_*\OO_{\cC_T})$ as we can check on $\eta$ since the Euler characteristic is constant in flat families.
-So   $\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T}=0.$
+However $\chi (\OO_{\hat{\cC}_\eta})=\chi(\phi_*\OO_{\cC_\eta})$ implies the same equality holds on the whole of $T$, since the Euler characteristic is constant in flat families.
+So $\chi(\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T})=\operatorname{length}(\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T})=0.$
 \end{proof}
@@
 \bcd
-\oM_1(\PP^4,d)\ar[d] & \mathcal Z \ar[l,swap,hook,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\MM^{\rm{wt}}_1 & \mathcal \MM^{\rm{wt}}_1\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{\rm{wt},(1)}
-\ecd
-
-From the inclusion we inherit a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
-
-Notice that the above lemma signifies that each and every component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$.
-The point is that given any stable map there is at most one factorisation through the weighted $1$-stabilisation of the curve: objects of $\oM_1(\PP^4,d)\setminus D^1$ are $1$-stable already; objects of $D^1\cap \oM_1(\PP^4,d)^\text{main}$ do factor thanks to Vakil's criterion and objects of $D^1\cap D^k$ ($k\geq 2$) do factor through a map which is constant on the cusp.\marginpar{insert figure of a typical element of $D^1\cap D^2$.} On the other hand, objects of $D^{1,\circ}=D^1\setminus(\oM_1(\PP^4,d)^\text{main}\cup\bigcup_{k\geq 2}D^k)$ do not admit any factorisation, so that $\Z$ has no corresponding component.
-
-We introduce some more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
-\bcd
-\mathcal Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
-\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)} \ar[d] \\
-\X\ar[r] & \mathfrak M_1^{(1),\rm{wt}}
-\ecd
-
-We are going to use the obstruction theory $\R^\bullet\hat{\pi}_*(\mathcal L^{\oplus 5}\oplus\mathcal P)$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1^{(1)}$ to induce a virtual class on $\Z^p$ which we would like to compare with ordinary $p$-fields.
-
-Remark that $\XP$ parametrises
-\bcd
-\cC\ar[rr,"\phi"]\ar[dr] & & \hat\cC\ar[ld] \\
+\oM_1(\PP^4,d)\ar[d] & \pazocal Z \ar[l,hook,swap,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
+\MM^{\rm{wt}}_1 & \X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
+\ecd
+
+From the inclusion $i$ we easily obtain a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
+
+Notice that the above lemma means that each and every component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$.
+Indeed given any stable map there is at most one factorisation through the weighted $1$-stabilisation of the curve: objects of $\oM_1(\PP^4,d)\setminus D^1$ are $1$-stable already; objects of $D^1\cap \oM_1(\PP^4,d)^\text{main}$ do factor through the cusp thanks to Vakil's criterion, which implies the node joining the elliptic tail to the rational tail of positive degree is a ramification point of the map; and objects of $D^1\cap D^k$ ($k\geq 2$) do factor through a map which is constant on the cusp.\marginpar{insert figure of a typical element of $D^1\cap D^2$.} On the other hand, objects of $D^{1,\circ}=D^1\setminus(\oM_1(\PP^4,d)^\text{main}\cup\bigcup_{k\geq 2}D^k)$ do not admit any factorisation, so $\Z$ has no corresponding component.
+
+We introduce two more relevant spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
+\bcd
+\Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
+\XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1{(1)} \ar[d] \\
+\X\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
+\ecd
+
+The obstruction theory $\R^\bullet\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\hat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by virtual pullback of $[\XP]$.
+In Section \ref{section:main_proof} we shall conduct on this a similar analysis to that in \cite{CL} and compare the contribution of the main component to Vakil-Zinger's reduced invariants.
+
+\begin{remark}
+The stack $\XP$ parametrises
+\bcd
+C\ar[rr,"\phi"]\ar[dr] & & \hat C\ar[ld] \\
 & S &
 \ecd
-with a line bundle $\hat{\mathcal L}$ on $\hat{\cC}$.
-Notice that by pulling back $\hat{\mathcal L}$ via $\phi$ we obtain a line bundle on $\cC$, hence a morphism $\XP\to \mathfrak{Pic}_1$.
+with a line bundle $\hat{\mathcal L}$ on $\hat{C}$.
+Notice that by pulling back $\hat{\mathcal L}$ via $\phi$ we obtain a line bundle on $C$, hence a morphism $\XP\to \mathfrak{Pic}_1$.
 This is generically an isomorphism, but has $1$-dimensional fibers over the locus of elliptic tails, due to the fact that $\Pic(\hat C)\to\Pic(C)$ has kernel $\mathbb G_{\rm a}$ when $\hat C$ has a cusp.
 
-Similarly $\Z^p$ parametrises
-\bcd
-\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[ld,"\hat\pi"] \ar[r,"f"] & \PP^4\\
+On the other hand notice that
+\[ \X\times_{\mathfrak M_1^{\rm{wt}}(1)} \mathfrak M_1^{\rm{div}}(1) \to \mathfrak M_1^{\rm{div}} \]
+is an isomorphism.\marginpar{FIX ME: when the divisor contains the node} Indeed given a line bundle $\mathcal L$ on $C$ and a section $s_0\in\Gamma(C,\mathcal L)$ which does not vanish on any irreducible component, there is exactly one line bundle $\hat{\mathcal L}$ on the $1$-stabilisation of $C$ and one section $\hat s_0\in\Gamma(\hat C,\hat{\mathcal L})$ that pull back to $(\mathcal L,s_0)$, due to the following:
+\end{remark}
+
+\begin{lem}\marginpar{CHECK ME}
+Let $\nu\colon(\PP^1,p)\to \hat C$ be the pointed normalisation of the cusp.
+Then $0\neq s\in\Gamma(\PP^1,\OO_{\PP^1}(d))$ with $s(p)=0$ only if $s'(p)=0$ determines a unique line bundle $\hat{\mathcal L}$ on $\hat C$ to which $s$ descends.
+\end{lem}
+\begin{proof}
+The key point is that the sections of $\hat{\mathcal L}$ pull back to a $d$-dimensional subspace of $\Gamma(\PP^1,\OO_{\PP^1}(d))$ that can be identified as follows: they are those sections $\sigma$ such that $s(p)\sigma'(p)=s'(p)\sigma(p)$ in any trivialisation of $\OO_{\PP^1}(d)$ near $p$ if $s(p)\neq 0$, and those constant to second order at $p$ otherwise.
+\end{proof}
+\begin{remark}
+Similarly the stack $\Z^p$ parametrises
+\bcd
+C\ar[rr,"\phi"]\ar[dr,"\pi" below left] & & \hat C\ar[ld,"\hat\pi"] \ar[r,"f"] & \PP^4\\
 & S & &
 \ecd
-with a $p$-field $\psi\in H^0(\hat\cC,f^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi}$.
-\begin{remark}
-why we cannot include $\Z^p$ into $p$-fields
+with a $p$-field $\psi\in H^0(\hat C,f^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi})$.
+
+We were not able to compare $\Z^p$ with $\oM_1(\PP^4,d)^p$ directly, since denoting by $\hat{\mathcal L}=f^*\OO_{\PP^4}(1)$ and by $\mathcal L=\phi^*\hat{\mathcal L}$ we only have a map $\R^1\hat\pi_*\hat{\mathcal L}\to\R^1\pi_*\mathcal L$ on $\Zp$ which is not an isomorphism (dually, since $\phi^*\omega_{\hat\pi}=\omega_{\pi}(E)$, the $p$-fields on $C$ that we get by pulling back from $\hat C$ vanish on elliptic tails).
 \end{remark}
 
-As anticipated, we may endow $\Z^p$ with a virtual class by ``localised virtual pullback'': indeed $\XP$ is a smooth Artin stack, and:
-\[
-\mathfrak C_{\Z^p/\XP} \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1^{(1)}}} \subseteq \alpha^* h^1/h^0(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1^{(1)}}})_\sigma
+As anticipated we may endow $\Z^p$ with a localised virtual cycle by ``localised virtual pullback'': indeed $\XP$ is a smooth Artin stack, and:
+\[
+\mathfrak C_{\Z^p/\XP} \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}} \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)_\sigma
 \]
@@
 Compare with \cite[Proposition~2.5]{CL}.
-\section{Splitting the cone and proof of the Main Theorem}
+
+\section{Splitting the cone and proof of the Main Theorem}\label{section:main_proof}
 We are finally in a position to study the cone $\mathfrak{C}_{\tZp/\tXP}.$ This is essentially going to be a word-by-word repetition of the arguments in \cite{CLpfields}.

### 2017-12-21 draft.tex
current dropbox version

@@
 
-\begin{lem}\label{lem:classificationsing}(Classification of CM genus $1$ singularities)
+\begin{lem}(Classification of CM genus $1$ singularities)
 The Cohen-Macaulay genus $1$ singularities with $m$ branches are all and only obtained by gluing a genus $0$ singularity with $k$ branches with a Smyth's $m-k$-elliptic fold.
-We call such a singularity a \textbf{(k,m)-type} genus $1$ singularity.
 Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
@@
 \end{enumerate}
-\noindent{For $m=2$} two possibilities
+\noindent{For $m=23$} two possibilities
 \item $a_1$ is non zero, then we have the tacnode;
@@
 
-Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $ a genus $1$ singularity.
+Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $a genus $1$ singularity.
 
@@
 It is well know \cite[IV, \S~3]{serre} that  $\omega_{\hat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ locally satisfying:
-\[\omega\in \nu_* \omega_{\overline{C}}\otimes K(\overline{C})(U)\;\;\;\text{s.t.}\;\;\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*f\omega) =0\;\;\;\forall \,f\in\,\OO_C(U).\]
-Let $\hat{C}$ be a genus $1$ curve with only one singularity which is a genus $1$ singularity of $(k,m)$-type
- Using the explicit local description of genus $1$ singularities that we worked out in Lemma~\ref{lem:classificationsing}, we see that 
-\[\omega_C\hookrightarrow \nu_*\omega_{\overline{C}}(p_1+\dots p_k+2 p_{k+1}\dots+2p_m)=\nu_*\left(\OO_{\PP^1}(-1)\oplus\dots\oplus\OO_{\PP^1}\oplus\dots \OO_{\PP^1}\right)\]
-and the kernel of the inclusion is supported on the singular point. We then have an inclusion
-\[H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}})\hookrightarrow H^0(\nu_*\left(\OO_{\PP^1}(-1)\oplus\dots\oplus\OO_{\PP^1}\oplus\dots \OO_{\PP^1}\right)\otimes\hat{L})^{-1})=0;\]
-where the last equality follows from the fact that $\hat{L}){-1}$ has degree less or equal to $0$ on every irreducible component of $\hat{C}.$
-
-We conclude showing how to smooth $f\colon C\to \PP^r$ given $\hat{F}\colon\hat{C}\to\PP^r.$
+\[\omega\in \nu_* \omega_{\overline{C}}\otimes K(\overline{C})(U)\;\;\;\text{s.t.}\;\;\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*f\omega) =0\;\;\;\forall \,f\in\,\OO_C(U)\]
 
@@
 \section{From $p$-fields to the quintic three-fold}\label{section:p-fields}
-
 We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
@@
 Compare with \cite[Proposition~2.5]{CL}.
-
 \section{Splitting the cone and proof of the Main Theorem}\label{section:main_proof}

### 2017-12-22 draft.tex
more on g=1 sing

@@
  \begin{dfn}
- Let $C$ be a reduced curve over a field $k$ and $p\in C$ a singular point.
-We define the \emph{genus of the singularity} in $p$ to be the quantity: $$g(p)=\delta(p)-b(p)+1,$$ where $\delta(p)=\dim_k\OO_{\overline C}/\OO_C,$ $\overline{C}$ is the normalisation of $C$, and $b(p)$ is the number of branches at $p.$
+ Let $C$ be a reduced curve over a field $k=\bar k$ and $p\in C$ a singular point.
+We define the \emph{genus of the singularity} in $p$ to be the quantity: \[g(p)=\delta(p)-b(p)+1,\] where $\delta(p)=\dim_k(\nu_*\OO_{\overline C}/\OO_C)\otimes k(p),$ $\nu\colon\overline{C}\to C$ is the normalisation of $C$ at $p$, and $b(p)$ is the number of branches of $C$ at $p.$
  \end{dfn}
+
  \begin{prop}\label{prop:smoothability2}
- Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a $n$-marked genus $1$ curve $(E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus $1$ subcurve, and $R_i$ are rational tails.
+ Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a genus $1$ curve $C=E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i$, where $E$ is the maximal connected arithmetic genus $1$ subcurve contracted by $f$, and $R_i$ are rational tails of positive degree.
 
@@
 \begin{lem}(Classification of CM genus $1$ singularities)
-The Cohen-Macaulay genus $1$ singularities with $m$ branches are all and only obtained by gluing a genus $0$ singularity with $k$ branches with a Smyth's $m-k$-elliptic fold.
+The Cohen-Macaulay (i.e. reduced) genus $1$ singularities with $m$ branches are obtained by gluing a genus $0$ singularity with $k$ branches together with a Smyth's $(m-k)$-elliptic fold.
 Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
@@
 \begin{proof}
-The proof follows the technique already used by Smyth \cite[Appendix~A]{SMY1} to classify the Goreinstein genus $1$ singularities.
-The question of classifying singularities in local analytic, so as in \cite[Appendix~A]{SMY1} we use the following notation:
-$R$ denote the analytic local ring of the singularity; 
-$\widetilde{R}=k[[t_1]\oplus\dots\oplus k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ is the maximal ideal in $R$  and $\mathfrak{m}_{\widetilde{R}}$ the maximal ideal in $\widetilde{R}.$
-
-Let us recall that to describe $R$ as a polynomial ring, it is enough to find a basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=(e_1,\dots e_s)$ where the $e_i$ are some regular functions in $\widetilde{R}.$ Indeed, once given such a basis, $R$ can be recognized as $k[x_1,\dots x_s]/I$ where $I$ is the kernel of the ring homomorphism
-\begin{align}\label{eq:singularity}
-k[[x_1,\dots x_s]]&\rightarrow R\subset k[[t_1]\oplus\dots\oplus k[[t_m]]\\
-\;\;x_i\;\; &\rightarrow \;\; e_i.\;\;
-\end{align}
-It has been observed by Smyth \cite[Proposition~A.3]{SMY1} that $R$ being the local ring of a genus $1$ singularity implies:
-\[\mathfrak{m}^2_{\widetilde{R}}\subset R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is codimension $1$},\]
-which allows him to say that, after Gauss elimination, we have $e_1,\dots e_{m-1}$ generators of $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$ of the following form
+We extend the argument given by Smyth \cite[Appendix~A]{SMY1} to classify the Goreinstein genus $1$ singularities.
+We study the analytic germ of the singularity, so we adopt Smyth's notation: $R$ denotes the completion of the local ring of $C$ at the singularity;
+$\widetilde{R}=k[[t_1]]\oplus\dots\oplus k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ is the maximal ideal of $R$  and $\mathfrak{m}_{\widetilde{R}}$ the one in $\widetilde{R}.$
+
+Let us recall that to describe $R$ as a quotient polynomial ring, it is enough to find a$k$-basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=(e_1,\ldots, e_s)$ where the $e_i$ are some elements in $\widetilde{R}.$ Indeed, once given such a basis, it is a consequence of completeness that $R$ can be recognized as $k[[x_1,\ldots, x_s]]/I$, where $I$ is the kernel of the ring homomorphism
+\begin{align*}\label{eq:singularity}
+k[[x_1,\ldots, x_s]]&\rightarrow R\subset k[[t_1]]\oplus\dots\oplus k[[t_m]]\\
+\;\;x_i\;\; &\mapsto \;\; e_i\;\;
+\end{align*}
+Smyth observes that $\widetilde R/R$ is graded by:
+\[ (\widetilde R/R)_i:=\mathfrak m_{\widetilde R}^i/(\mathfrak m_{\widetilde R}^i\cap R)+\mathfrak m_{\widetilde R}^{i+1}\]
+Furthermore:
+\begin{enumerate}
+\item $m=\delta(p)=\sum_{i\geq 0}\dim_k(\widetilde R/R)_i;$
+\item $1=g(p)=\sum_{i\geq 1}\dim_k(\widetilde R/R)_i;$
+\item if $(\widetilde R/R)_i=(\widetilde R/R)_j=0$ then $(\widetilde R/R)_{i+j}=0$.
+\end{enumerate}
+From (3) and (2) it follows that $\dim_k(\widetilde R/R)_1=1$ and $\dim_k(\widetilde R/R)_i=0$ for $i\geq 2$. Then the exact sequence:
+\[ 0\to \frac{\mathfrak m_{\widetilde R}^2}{\mathfrak m_{\widetilde R}^2\cap R}\to\frac{\mathfrak m_{\widetilde R}}{\mathfrak m_{\widetilde R}\cap R}\to (\widetilde R/R)_1\to 0\]
+entails that:
+\[\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak m_R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is a codimension $1$ $k$-subspace},\]
+After Gaussian elimination, the generators $e_1,\dots e_{m-1}$ of $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$ assume the following form:
 \begin{align*}
-e_1=& (t_1 \,0\dots\,0\, a_1 t_m)\\
-e_2=&( 0\,t_2\,0\dots\, a_2 t_m)\\
-&\dots\\
-e_{m-1}=&(0\dots\,t_{m-1}\, a_{m-1}t_m ).
+e_1&= (t_1, 0, \ldots, 0, a_1 t_m) \\
+e_2&= (0, t_2, \ldots, 0, a_2 t_m) \\
+ & \ldots \\
+e_{m-1} &= (0, 0,\ldots, t_{m-1}, a_{m-1}t_m).
 \end{align*}
-with $a_{1},\dots, a_{m-1}\,\in \k.$ At this point Smyth restricts his attention on Gorenstein singularities and he shows that under the Gorenstein assumption and when $m\geq 3$: we can choose all the $a_i$ to be $1$; $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we are  done.
-Otherwise we have:
-
-\noindent{For $m\geq 3$} three possibilities:
+with $a_{1}, \ldots, a_{m-1}\in k.$ At this point Smyth restricts his attention to Gorenstein singularities and shows that under this assumption he can choose all the $a_i$ to be $1$; furthermore if $m\geq 3$ it holds $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$, thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and the goal is reached.
+For $m=1,2$ he finds extra generators and show they satisfy the equation of a cusp (resp.
+a tacnode).
+
+Removing the Gorenstein restriction we have three possibilities for $m\geq 3$:
 \begin{enumerate}
-\item At least two of the $a_i$ are non zero.
-\item Only one of the $a_i$ is non zero
-\item All the $a_i$ are zero
+\item At least two of the $a_i$'s are non-zero, say $i=1,2$: then $a_1a_2t_m^2=e_1\cdot e_2$ so $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and we are done as above.
+It is easily seen that  $e_1,\dots e_{m-1}$ satisfy the equations of a $(k,m-k)$ singularity where $k$ is the number of $a_i$'s that are $0$.
+\item Only one of the $a_i$ is non-zero, say $a_1=1$: then $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}+(t_m^2)$ and by adjoining $e_m=t_m^2$ to the $e_i$'s we see that they generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and they satisfy the equation of a tacnode $(e_1^2-e_m)e_m=0$ and $e_ie_j=0$ for $i\neq j$ and $(i,j)\neq(1,m)$, so this is an $(m-2,2)$ singularity.
+\item Finally all the $a_i$ are zero: then we have to add $t_m^2,\ t_m^3$ to generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we obviously find an $(m-1,1)$ singularity.
 \end{enumerate}
-\noindent{For $m=23$} two possibilities
-\item $a_1$ is non zero, then we have the tacnode;
-\item  $a_1$ is zero
-\noindent{For $m= 1$} As in Smyth's we prove that in this  case $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$ which means the singularity is a cusp. 
-\end{proof}
+\noindent Similarly for $m=2$ there are two possibilities: the tacnode (corresponding to $a_1\neq 0$) and the union of a cusp with a non-coplanar line (for $a_1=0$), with equations:
+\[ k[[x,y,z]]/(xz,yz,y^2-x^3)\]
+\noindent For $m= 1$ the only possible singularity is the cusp: indeed it can be proven that $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$. 
+\end{proof}
+
 \begin{lem}
@@
 We exhibit explicit smoothings for the above singularities.
-Start with two families $\cC^0\to T$ and $\cC^1\to T$ over a DVR scheme, respectively of smooth rational curves and smooth elliptic curves, with $T$ a DVR scheme, e.g. consider two trivial families.
-
- Then blow up respectively $k$ smooth points $p_1,\dots p_k$ and  $m-k$ smooth points $q_{k+1},\dots q_{m-k}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0.$
-
-On  $\widetilde{\cC}^0\xrightarrow{\pi_0} \cC^0\to T$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} \cC^1\to T$ there exist $\pi_0$, respectively $\pi_1$ semi-ample line bundles which are trivial on the proper transform of the central fibers and very ample every where else.
-If we started with the trivial families we can take \begin{align*}
-\mathcal L_0&=\pi_0^*\OO_{\cC^0}(p_1\times T+\dots+ p_k\times T)(-F_1-\dots -F_k),\\
- \mathcal L_1&=\pi_1^*\OO_{\cC^1}(q_{k+1}\times T+\dots+ q_{m-k}\times T)(-F_{k+1}-\dots -F_{m-k})
+Start with two families $(\cC^0;\sigma_0,p_1,\ldots,p_k)\to T$ and $(\cC^1;\sigma_1,q_{k+1},\ldots,q_m)\to T$ respectively of smooth $(k+1)$-pointed rational curves and smooth $(m-k+1)$-pointed elliptic curves over a DVR scheme $T$, e.g.
+consider two trivial families.
+
+ Then blow up the trace of $p_1,\dots p_k$ and $q_{k+1},\dots q_{m}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0$ to get families $\widetilde{\cC}^0\xrightarrow{\pi_0} {\cC}^0$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} {\cC}^1$ respectively.
+
+We can now find semi-ample line bundles which are trivial on the strict transform of the central fiber and ample everywhere else, namely
+\begin{align*}
+\mathcal L_0&=\pi_0^*\OO_{\cC^0}(p_1+\ldots+ p_k)(-F_1-\ldots -F_k),\\
+ \mathcal L_1&=\pi_1^*\OO_{\cC^1}(q_{k+1}+\ldots+ q_{m})(-F_{k+1}-\ldots -F_{m})
 \end{align*}
-where we denoted by $F_j$ the exceptional divisors of both the blow ups.
-We can then contract respectively  $\;\pi_0^*(\cC^0)_0(-F_1-\dots -F_k)\;$ and $\;\pi_1^*(\cC^1)_0(-F_{k+1}-\dots -F_{m-k}).$
-
-The contracted families   $\;\hat{\cC}^0\to T\;$ and $\;\hat{\cC}^1\to T\;$ have still generic smooth fibers of genus $0$ and $1$ respectively and, by construction: $(\hat{\cC}^0)_0$ has a genus $0$ singularities with $k$ branches and $(\hat{\cC}^)_0$ has an $m-k$ elliptic curves\cite[Lemma~2.12]{SMY1}.
-
-Choose $\sigma_0$ and $\sigma_1$ two sections of $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ passing through the singular points in the central fibers and let $\hat{\cC}\to T$ the family of curves obtained identifying $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$, endowed with their reduced structures.
-Then $\hat{\cC}$ has nodal generic fiber and one of our genus 1 singularities as central fibers.
-
-Choose now a simultaneous smoothing of the generic fiber, e.g.
-if the families were trivial this is clearly possible; a generic direction of the two parameter family obtained this way is a smoothing of our singularity.
+where we denoted by $F_j$ the exceptional divisors of the blow-ups.
+
+We can then use them to give contraction maps.
+The contracted families   $\;\hat{\cC}^0\to T\;$ and $\;\hat{\cC}^1\to T\;$ still have smooth generic fibers of genus $0$ and $1$ respectively and, by construction, $(\hat{\cC}^0)_0$ has a genus $0$ singularity with $k$ branches and $(\hat{\cC}^1)_0$ has a Smyth's $(m-k)$-elliptic point \cite[Lemma~2.12]{SMY1}.
+
+Observe now that $\sigma_0$ and $\sigma_1$ induce sections of the contracted curves $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ passing through the singular points of the central fiber.
+Let $\hat{\cC}\to T$ the family of curves obtained by gluing $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$ (pushout).
+Then $\hat{\cC}$ has a nodal generic fiber which can clearly be further smoothed.
+
 \end{proof}
@@
 \begin{proof}\ref{prop:smoothability2}
- The argument to prove that if $f$ is smoothable then it has to factors through a genus $1$ singularity is exactly the same used by Vakil to show that the tangent vectors have to be linearly dependent in the image and thus we do not repeat it but we refer the reader to \cite{Vre}.
-
-Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C} $a genus $1$ singularity.
-
-Let $\hat{\cC}$ be a smoothing of $\hat{C}$ and $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on the smoothing, which exists because deforming line bundles on curves is unobstructed.
-We are first going to show that we can extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ and then argue how to get a smoothing of $f$ from $\hat{F}.$
-
-For the first part, all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
-Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0.$
-
-Since all the curve we are considering are Cohen-Maculay, they have a dualising pure sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
+ The argument that if $f$ is smoothable then it has to factor through a genus $1$ singularity was given by Vakil when he showed that the tangent vectors have to be linearly dependent in the image \cite[Lemma 5.9]{Vre}.
+
+Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C}$ a genus $1$ singularity in a way that at least one branch is not contracted.
+
+We show that we can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$.\footnote{This is in general not possible: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar non-Gorenstein singularity with local equation $y^2-x^5=0$.
+Then a compatible smoothing can be found only if the rational tail is attached to a Weierstrass point of the genus $2$ curve, as can be seen by computing the stable model of the ramphoid cusp.
+This example was kindly suggested to us by Prof.
+D.I.
+Smyth.}
+Assume that $\hat C$ has a $(k,m-k)$-singularity.
+Then we can pick a smoothing $\cC$ of $C$ such that, when resolving the $A_n$ singularities at the nodes, i.e.
+when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal balanced genus one subcurve contracted by $f^{\rm{ss}}$; then there are $m-k$ rational tails of positive degree directly adjacent to $E$, and the other $k$ rational tails are further away.
+Moreover the rational tails can be made to agree in length with the corresponding ones in $\hat C$.
+We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, resulting in an $(m-k+h)$-fold point with $h\leq k$; at this point use $f^*\OO_{\PP}(1)$ (add markings away from the genus $1$ singularity as necessary) to further contract the branches of degree $0$.
+Notice that $f^*\OO_{\PP}(1)$ has no $H^1$ because at least one branch is of positive degree, so it satisfies cohomology and base change, making it possible to verify that the result of this second contraction is a $(k,m-k)$-singularity.\marginpar{check: maybe need positive degree on one of the $m-k$ branches?} So the central fiber of $\hat \cC$ is isomorphic to $\hat C$.
+
+Let $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on $\hat{\cC}$, which exists because deforming line bundles on curves is unobstructed.
+In order to extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
+Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ \cite{Wang}.
+
+Since all the curve we are considering are Cohen-Maculay, they have a dualising sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
 \[H^1(\hat{C},\hat{L})=(H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}}))^{\vee}.\]
-It is well know \cite[IV, \S~3]{serre} that  $\omega_{\hat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ locally satisfying:
-\[\omega\in \nu_* \omega_{\overline{C}}\otimes K(\overline{C})(U)\;\;\;\text{s.t.}\;\;\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*f\omega) =0\;\;\;\forall \,f\in\,\OO_C(U)\]
+It is known \cite[IV, \S~3]{serre} that  $\omega_{\hat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ (where $\nu\colon\bar C\to\hat C$ is the normalisation) satisfying: for every open $U\subseteq\hat C$ a rational $1$-form $\omega\in \nu_*\left( \omega_{\overline{C}}\otimes K(\overline{C})\right)(U)$ is a section of $\omega_{\hat C}(U)$ iff
+\[\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*(f)\omega) =0 \quad \quad \forall f\in\OO_C(U)\]
 
@@
 \[
- 0_{\overline{V}}^![\overline C^{\rm{gst}}]=0_{\overline V_2}^!(0_{\overline{V_1}}^![\overline C^{\rm{gst}}])=0_{\overline V_2}^!([N_{\overline C^{\rm{gst}}\cap (0\oplus \overline V_2)}\overline C^{\rm{gst}}])
+ 0_{\overline{V}}^![\overline C^{\rm{gst}}]=0_{\overline V_2}^!(0_{\overline{V}_1}^![\overline C^{\rm{gst}}])=0_{\overline V_2}^!([N_{\overline C^{\rm{gst}}\cap (0\oplus \overline V_2)}\overline C^{\rm{gst}}])
 \]
@@
 \ecd
-We know from the previous section that the last cycle can be split into two parts, one (call it $N_1$) supported on a sub-line bundle of $\overline V_2$ on $\tilde\Delta$, the other one (call it $N_2$) suypported on the zero section of $\overline V_2$.
+We know from the previous section that the cycle in the last bracket can be split into two parts, one (call it $N_1$) supported on a sub-line bundle of $\overline V_2$ on $\tilde\Delta$, the other one (call it $N_2$) supported on the zero section of $\overline V_2$.
 
@@
 The dimension of $\tZ^{\rm{gst}}$ is $5d+3$, being locally a $5(d+1)$ vector bundle over a dimension $-2$ stack; so $\tZ^{p,\rm{gst}}$, which is a line bundle on the former, has dimension $5d+4$.
-The coarse moduli cone has then dimension $5d+6$, as can be argued from \ref{lem:open_cones}.
-$\overline V_1\rvert_{\tZ^{p,\rm{gst}}}$ has rank $5$, so $0_{\overline{V_1}}^![\overline C^{\rm{gst}}]$ is a cycle of dimension $5d+1$.
+The coarse moduli cone has then dimension $5d+6$, as can be argued from Lemma \ref{lem:open_cones}.
+$\overline V_1\rvert_{\tZ^{p,\rm{gst}}}$ has rank $5$, so $0_{\overline{V_1}}^![\overline C^{\rm{gst}}]$ is represented by a cycle of dimension $5d+1$.
+We shall exploit the commutativity of Gysin pullback with proper pushforward.
+
+For $N_1$ we conclude easily from the above facts, since $\deg(0_{\overline V_2}^![N_1])=\deg(0_{V_2}^!\gamma_*[N_1])$, but $\gamma_*[N_1]\in A_{5d+1}(F)$ must be trivial, since $F$ has dimension $5d$, being a line bundle on $\Delta$ which is a divisor in $\Z^{\rm{main}}$.
+
+On the other hand $N_2\subseteq \overline{V}_2$ admits a further splitting into $N_{2,\mu}\subseteq \overline V_{2,\mu}$ according to the number $k$ of rational tails of the generic element of the boundary component on which they are supported and a partition of the degree $\mu\vdash d$ in $k$ many parts.
+There exists a comparison morphism:
+\[\beta_{\mu}\colon D^\mu\tZp\to D^\mu\Z=D^\mu\oM_1(\PP^4,d)\to \pazocal W_{\mu}\]
+where $\pazocal W_{\mu}\subseteq\prod_{i=1}^k \M{0}{1}{\PP^4}{d_i}$ is defined by requiring that the maps do attain the same value at the markings.
+$\beta_{\mu}$ is obtained by forgetting the $p$-field,  the Vakil-Zinger blow-up and the $k$-pointed elliptic curve contracted by the map to $\PP^4$.
+This has the nice property that $\overline V_2$ is the pullback along $\beta_{\mu}$ of a vector bundle on $\pazocal W_{\mu}$.
+Namely the universal curve over each factor can be glued to the other ones along the given sections, producing a genus $0$ non-Gorenstein (unless $k=2$) singularity to which the universal maps to $\PP^4$ descend by the property of pushouts:
+\bcd
+\overline \cC_\mu \ar[d,"\bar\pi"]\ar[r,"\bar f"] & \PP^4 \\
+\pazocal W_\mu &
+\ecd
+The sheaf $V_\mu:=\bar\pi_*\bar f^*\OO_{\PP^4}(5)$ is indeed a vector bundle of rank $5d+1$ on $\pazocal W_\mu$, as can be checked by Riemann-Roch and the normalisation sequence (the topological type of the curve is constant near the singularity), and $\overline V_{2,\mu}=\beta_{\mu}^* V_\mu$.
+Finally the actual dimension of $\pazocal W_\mu$ is $5d+4-2k <5d+1$ for $k\geq 2$ by Kleiman-Bertini theorem, so $\beta_{\mu,*}[N_{2,\mu}]=0$.
+
 \end{proof}

### 2017-12-22 draft.tex
some more margin notes

@@
 
+\begin{remark}
+ The genus and number of branches are not sufficient to tell these singularities apart anymore, neither is the embedding dimension. A numerical invariant that distinguishes them is:
+\[ \dim_k R/I_p \]
+where $I_p=\operatorname{Ann}_R(\widetilde R/R)$ is the conductor ideal at the singular point. \marginpar{prove it or at least say what numbers it gives}
+\end{remark}
+
 \begin{lem}
@@
 Moreover the rational tails can be made to agree in length with the corresponding ones in $\hat C$.
-We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, resulting in an $(m-k+h)$-fold point with $h\leq k$; at this point use $f^*\OO_{\PP}(1)$ (add markings away from the genus $1$ singularity as necessary) to further contract the branches of degree $0$.
-Notice that $f^*\OO_{\PP}(1)$ has no $H^1$ because at least one branch is of positive degree, so it satisfies cohomology and base change, making it possible to verify that the result of this second contraction is a $(k,m-k)$-singularity.\marginpar{check: maybe need positive degree on one of the $m-k$ branches?} So the central fiber of $\hat \cC$ is isomorphic to $\hat C$.
+We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, resulting in an $(m-k+h)$-fold point with $h\leq k$; at this point use $f^*\OO_{\PP^r}(1)$ (add markings away from the genus $1$ singularity as necessary) to further contract the branches of degree $0$.
+Notice that $f^*\OO_{\PP^r}(1)$ has no $H^1$ because at least one branch is of positive degree, so it satisfies cohomology and base change, making it possible to verify that the result of this second contraction is a $(k,m-k)$-singularity.\marginpar{check: maybe need positive degree on one of the $m-k$ branches?} So the central fiber of $\hat \cC$ is isomorphic to $\hat C$.
 
@@
 Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ \cite{Wang}.
+Once done this we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC\to\hat{\cC}\xrightarrow{\hat F}\PP^r$.
 
@@
 \[\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*(f)\omega) =0 \quad \quad \forall f\in\OO_C(U)\]
+
+From this description it is patent that the pullback of $\omega_{\hat C}$ to the normalisation restricts to a line bundle of degree $-1$ or $0$ on every branch, according to it being one of the $k$ or $m-k$ components.
+Hence it can be seen from the normalisation exact sequence and Serre duality that $H^1(\hat{C},\hat{L})=0$ as soon as $\hat L$ has positive degree on one of the branches.
 
@@
 \end{lem}
-\marginpar{check \cite{KLcosection}}
+\marginpar{check \cite{KLcosection}, probably needs the proper morphism to be surjective}
 

### 2018-01-05 draft_merged.tex
reviewing intro and sec 1 after Francesca's merge

--- 2017-12-22 draft.tex
@@
 \newcommand{\PP}{\mathbb P}
+\renewcommand{\k}{\mathbf k}
 \newcommand{\OO}{\mathcal O}
@@
 \newcommand{\Aaff}{\mathbb A}
-\newcommand{\A}{\mathcal A}
-\newcommand{\B}{\mathcal B}
+\newcommand{\A}{\pazocal A}
+\newcommand{\B}{\pazocal B}
 \newcommand{\X}{\pazocal X}
@@
 \begin{abstract}
-abstract
+
+We prove that the $1$-stabilisation morphism, replacing elliptic tails
+with cusps, is well-defined at the level of genus $1$ weighted-stable
+curves. We use this to endow a substack of $\oM_1(\PP^4,d)$ with a
+virtual class that ignores the boundary contribution of maps with a
+contracted elliptic tail. We thus prove that Vakil-Zinger's reduced
+invariants of the quintic threefold can be computed as Smyth-Viscardi's
+$1$-stable (i.e. cuspidal) invariants. To do so we adapt Jun Li's
+techniques of $p$-fields and local equations for the moduli space.
+
 \end{abstract}
@@
 
-The moduli stack of stable maps to projective space is a fundamental object in Gromov-Witten theory, since any moduli space of maps to a projective variety is cut inside the former by a number of equations induced by those of $X\subseteq \PP^r$.
+The moduli stack of stable maps to the projective space $\PP^r$ is of fundamental importance in Gromov-Witten theory, since any moduli space of maps to a projective variety $X\subseteq \PP^r$ is cut inside the former by a number of equations induced by generators of $\pazocal I_{X/\PP^r}$.
 Yet its structure in higher genus is still largely mysterious.
 
-Recall that in genus zero $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension.
-Furthermore for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$ the sheaf $\pi_*f^*E$ is a vector bundle on $\M{0}{n}{\PP^r}{d}$.
-\bcd
-\mathcal C_{0,n}(\PP^r,d)\ar[r,"f"]\ar[d,"\pi"] & \PP^r\times \M{0}{n}{\PP^r}{d} \\
-\M{0}{n}{\PP^r}{d} &
-\ecd
-
-It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that, if $i\colon X\hookrightarrow \PP^r$ is a complete intersection of degree $(l_1,\ldots,l_k)$ and we denote by $j$ the corresponding inclusion of moduli spaces of maps,
+Recall that in genus zero $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension $r-3+d(r+1)+n$.
+Furthermore the rational Gromov-Witten theory of a complete intersection $i\colon X\hookrightarrow \PP^r$ of degree $(l_1,\ldots,l_k)$ can be determined as a twisted theory for $\PP^r$ and thus computed via localisation: for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$ the sheaf $\pi_*f^*E$ is a vector bundle on $\M{0}{n}{\PP^r}{d}$, where we have denoted by $\pi$ the projection from the universal curve and by $f$ the universal stable map.
+%\bcd
+%\mathcal C_{0,n}(\PP^r,d)\ar[r,"f"]\ar[d,"\pi"] & \PP^r%\times \M{0}{n}{\PP^r}{d} \\
+%\M{0}{n}{\PP^r}{d} &
+%\ecd
+It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that the following \emph{hyperplane property} holds
 %$$\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}\hookrightarrow\M{0}{n}{\PP^r}{d}$$
-then the following equality holds:%, which is expected from the interpretation of Chern classes as zero loci of sections (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic):
+%then the following equality holds:, which is expected from the interpretation of Chern classes as zero loci of sections (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic):
 $$j_*[\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}]^{\operatorname{vir}}=c_{\operatorname{top}}(E)\cap[\M{0}{n}{\PP^r}{d}].$$
-This so-called ``hyperplane property'' allows us to compute GW invariants of complete intersections as twisted invariants of projective space, which enables us to perform computations by localisation.
-
-The situation in higher genera is much more intricate: the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional, and the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle.
-The enumerative meaning of the invariants is affected by the appearance of unexpected components, representing degenerate contributions from curves of lower genera.
-
-The situation in genus $1$ is better understood: the geometry of the moduli space of genus one stable maps to projective space $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre}.
+%This, so-called ``hyperplane property'', allows us to compute GW invariants of complete intersections as twisted invariants of projective space, where computations can be done via localisation.
+
+For $g\geq 1$ the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional, and the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle.
+The enumerative meaning of the invariants is spoilt by degenerate contributions from curves of lower genera, represented by boundary components of the moduli space where a subcurve of positive genus is contracted.
+
+The situation in genus $1$ is better understood: the geometry of $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre}.
 Contrary to higher genus, the closure of the locus of maps the source of which is a smooth elliptic curve is an irreducible component of $\M{1}{n}{\PP^r}{d}$, which is usually called the \emph{main component}.
+Its boundary points were characterised in \cite{Vre} as follows: $[f\colon C\to \PP^r]\in\oM_1(\PP^r,d)$ is smoothable, i.e.
+it can be made into the special fiber of a $1$-dimensional family the generic fiber of which is a non-constant map from a smooth elliptic curve, if and only if either $f$ is not constant on the minimal genus $1$ subcurve $E$ of $C$, or the image of the tangent vectors to the rational tails are linearly dependent in $T_{f(E)}\PP^r.$  In Section~\ref{sec:section1} we give a new proof of this fact~\ref{prop:smoothability} using Hu-Li's local equations for the moduli space; furthermore we provide a different characterisation of the smoothable maps as those that factor through a non-degenerate map from a Cohen-Macaulay genus~$1$ singularity \ref{prop:smoothability2}, which we classify extending an argument due to Smyth.
 %One of the reasons for this (in fact the only reason in genus one) is that there are maps from reducible curves with a genus $g$ core that is contracted and some rational tails that carry all the degree; if $f\colon C\to \PP^r$ is such a map, then $H^1(C,f^*\mathcal O_{\PP^r}(1))\neq 0$, as can be easily seen from the normalisation sequence.
 
-In an attempt to extract the enumerative information hidden within Kontsevich's moduli space, Vakil and Zinger managed to desingularise the main component by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}).
-The end result $\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}$ is a stack on which $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ is a vector bundle, which allows them to define a notion of \emph{reduced invariants} for complete intersections in $\PP^r$, based on the hyperplane property:  %The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc.
+From the enumerative point of view, it would be ideal to isolate the contribution to the invariants given by the main component.
+In an attempt to extract this information hidden within Kontsevich's moduli space, 
+Vakil and Zinger managed to desingularise the main component by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}).
+The end result $\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}$ is a smooth and irreducible stack on which $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ is a vector bundle.
+This fact allowed them to define a notion of \emph{reduced invariants} for complete intersections in $\PP^r$ by mimicking the hyperplane property of the genus $0$ theory.
+%The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc.
 and taking the fiber product
@@
 This paved the way to the definition of reduced invariants.
+
 \begin{dfn}
 Let $X$ be a complete intersection of degree $(l_1,\ldots,l_k)$ in $\PP^r$.
-The genus one reduced Gromov-Witten invariants of $X$ are defined by integrating against: $$[\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}]\cap c_{\rm{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i))).$$
+The genus $1$ reduced invariants of $X$ are defined by integrating against: $$ c_{\rm{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i)))\cap[\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}].$$
 \end{dfn}
 
-Recently there has been a different attempt to discard some of the unwanted components.
-Viscardi \cite{VISC} has introduced a series of \emph{alternate compactifications} of the moduli space of maps from elliptic curves, based on Smyth's work on the birational geometry of $\oM_{1,n}$.
-In Viscardi's space $\oM_{1,n}^{(m)}(X,\beta)$ maps that contract an elliptic curve with at most $m$ rational tails are destabilised, and replaced by maps from $l$-elliptic fold singularities with $l\leq m$.
-
-The main result of this paper is that reduced invariants of the quintic three-fold can be recovered from Viscardi's alternate compactification.
+Recently there has been a different attempt to discard some of the boundary components.
+Based on Smyth's work on the birational geometry of $\oM_{1,n}$ \cite{SMY1,SMY2}, Viscardi \cite{VISC} has introduced a series of \emph{alternate compactifications} of the moduli space of maps from smooth elliptic curves.
+Compared to Kontsevich's space of stable maps, in Viscardi's space $\oM_{1,n}^{(m)}(X,\beta)$ maps that contract a genus $1$ curve with at most $m$ rational tails are destabilised, and replaced by maps from $l$-elliptic singularities with $l\leq m$.
+
+The main result of the present paper is that reduced invariants of the quintic threefold can be recovered from Viscardi's alternate compactifications.
 
 \begin{thm}
-Let $X$ be a generic smooth quintic three-fold. Then:
-\[
-N_1^{\rm{red}}(X,d)=N_1^{\rm{cusp}}(X,d)
+Let $X_5\subseteq\PP^4$ be a generic smooth quintic threefold. Then:
+\[
+N_1^{\rm{red}}(X_5,d)=N_1^{\rm{cusp}}(X_5,d),
 \]
 where:
-\[N_1^{\rm{red}}(X,d):=\deg \left([\widetilde{\pazocal M}_{1}(\PP^4,d)^{\rm{main}}]\cap c_{\rm{top}}(\tilde\pi_*\tilde f^*(\mathcal O_{\PP^4}(5)))\right)\]
+\[N_1^{\rm{red}}(X_5,d):=\deg \left(c_{\rm{top}}(\tilde\pi_*\tilde f^*(\mathcal O_{\PP^4}(5)))\cap [\widetilde{\pazocal M}_{1}(\PP^4,d)^{\rm{main}}]\right)\]
 and
-\[N_1^{\rm{cusp}}(X,d):=\deg [\Mone{1}{X}{d}]^{\rm{vir}}.
+\[N_1^{\rm{cusp}}(X_5,d):=\deg [\Mone{1}{X_5}{d}]^{\rm{vir}}.
 \]
@@
 
-The insight for this fact comes from the following formula, the proof of which was first given by J. Li and A. Zinger \cite{LZ} in the symplectic category:
-
-$$N_1(X,d)=N_1^{\rm{red}}(X,d)+\frac{1}{12}N_0(X,d).$$
-Noticing that the genus $0$ contribution to this formula only comes from the boundary component with a single rational tail of degree $d$ suggests that removing such component would provide a more direct approach to reduced invariants.
-This is precisely what Viscardi's space of 1-stable maps does.
-
-\textcolor{red}{Li-Zinger's formula was later proved in the algebro-geometric setting by H.-W.
+Below we will suppress the subscript $5$ from $X_5$.
+The insight for this theorem comes from the following formula, the proof of which was first given by J.
+Li and A.
+Zinger \cite{LZ} in the symplectic category:
+\begin{equation}\label{eq:VakilZinger}
+N_1(X,d)=N_1^{\rm{red}}(X,d)+\frac{1}{12}N_0(X,d).
+\end{equation}
+The first proof of Li-Zinger's formula in the algebro-geometric setting is due to H.-W.
 Chang and J.
 Li in \cite{CL}.
-This was only the final of a series of papers where they developed the theory of stable maps with $p$-fields and applied it together with the techniques of cosection-localised virtual classes \cite{KLcosection}.
-$p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$; indeed Chang and Li managed to include the unwanted part of the obstruction theory in the moduli space, and by these means endow a well-understood space (very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.}
-\textcolor{blue}{To prove Li-Zinger formula in the algebro-geometric setting, one would like to understand how the virtual class of  $\oM_1(X,d)$ splits on the various component of the moduli space, but this seems to be unaccesible.
-To overcome this difficulty, Chang Li developed the theory of stable maps with $p$- fields.}
-
-The proof of our main theorem follows from adapting the techniques of Chang and Li to Viscardi's moduli spaces. We show the following:
+Their splitting of the intrinsic normal cone makes it patent that the genus $0$ contribution to the right hand side only comes from the boundary component with a single rational tail of degree $d$.
+This suggests that removing such a component would provide a more direct approach to reduced invariants for the quintic threefold.
+This is precisely what Viscardi's space of $1$-stable maps does.
+
+%To prove the result we essentially need to understand how the various component of the moduli space contribute to the invariants, so we have to look at the algebraic techniques that  have been used to prove~\eqref{eq:VakilZinger}.
+
+%Indeed, after the symplectic proof, Li-Zinger's formula was proved .
+The latter is only the final a series of papers where they developed the theory of stable maps with $p$-fields and applied it together with the techniques of cosection-localised virtual classes \cite{KLcosection}.
+$p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$; indeed Chang and Li managed to include the unwanted part of the obstruction theory in the moduli space, and by these means endow a well-understood space (very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.
+The proof of our main theorem follows from adapting the techniques of Chang and Li to Viscardi's moduli spaces. Here is an outline of the proof.
+
+%Alternatively, if one does not want to use the theory of stable maps with fields, the idea would be to follow the alternative proof of~\eqref{eq:VakilZinger} recently proposed by \cite{preprint}.
+In that case, they still consider the Hu-Li blow up of the moduli space of weighted curve and they then look at $\tM_1(X)\hookrightarrow \tM_1(\PP^4) $, where $X$ is the quintic threefold and study directly the cone of $\tM_1(X).$ Following~\cite{preprint} steps, we can attack directly $\tM_1(X)^{(1)}$ and show that only the main component has a non trivial contribution to the invariants.
+
+%In both cases the comparison with the genus~1 invariants comes from the following comparison result.
+%We show the following:
+We first consider a moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p$.
+In the work of Chang and Li, $p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$.
+By introducing the moduli space of maps with $p$-fields the authors manage to include the unwanted part of the obstruction theory into the moduli space, and to endow a well-understood space (indeed very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.
+Paralleling their proof, i.e.
+using cosection localised virtual cycles \cite{KLcosection} and the deformation to the normal cone $(X_5\subseteq \PP^4)\rightsquigarrow(X_5\subseteq N_{X/\PP^4})$, we see that:
 \begin{prop}
-There exists a well-defined $1$-stabilisation morphism at the level of weighted pre-stable curves:
-\[
-\MM_{1,n}^{\rm{wt}}\to \MM_{1,n}^{(1),\rm{wt}}
+$\deg\virloc{\Mone{1}{\PP^4}{d}^p}=\deg\vir{\Mone{1}{X}{d}}.$
+\end{prop}
+Indeed it is enough to notice that all the constructions in \cite{CLpfields} carry over to the setting of a family of Gorenstein (not necessarily nodal) curves.
+
+We then need the following comparison morphism.
+\begin{prop}
+There exists a well-defined $1$-stabilisation morphism at the level of weighted-stable curves:
+\[
+\MM_{1,n}^{\rm{wt,st}}\to \MM_{1,n}^{\rm{wt,st}}(1)
 \]
@@
 \[
-\MM_{1,n}^{\rm{wt}}\times_{\MM_{1,n}^{(1),\rm{wt}}}\Mone{1}{\PP^4}{d}^p
-\]
-is endowed with a virtual class counting $1$-stable maps to the quintic three-fold (the arguments in \cite{CLpfields} carry over almost unchanged).
-On the other hand we find a way to compare the main contribution of this space with Vakil-Zinger reduced invariants.
-A dimensional computation shows that this is the only enumeratively meaningful component.
+\Z:=\MM_{1,n}^{\rm{wt,st}}\times_{\MM_{1,n}^{\rm{wt,st}}}\Mone{1}{\PP^4}{d}
+\]
+is a substack of $\oM_1(\PP^4,d)$ avoiding the boundary component with one rational tail of degree $d$.
+
+It is harder to compare the fiber product
+\[
+\Zp:=\MM_{1,n}^{\rm{wt,st}}\times_{\MM_{1,n}^{\rm{wt,st}}}\Mone{1}{\PP^4}{d}
+\]
+with $\oM_1(\PP^4,d)^p$.
+Yet $\Zp$ is endowed with a cosection-localised virtual class counting $1$-stable maps to the quintic threefold (by cosection-localised virtual pullback).
+The same splitting arguments as in \cite{CLpfields} allow us to evince a main contribution which coincides with Vakil-Zinger's reduced invariants.
+On the other hand a dimensional computation shows that this is the only enumeratively meaningful component.
+
+\subsection*{Future directions}
 
 \subsection*{Outline of the paper}
-maybe table of notations
-\section{Genus one stable maps to $\PP^r$ - Equations, components and alternate compactifications}
+
+\subsection*{Table of notations} We work over an algebraically closed field $\k$ of characteristic $0$.
+
+$T$ is the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
+
+Subcurves are always connected.
+
+\section{$\oM_1(\PP^r,d)$ - Components, equations  and alternate compactifications}\label{sec:section1}
 
 \subsection{Local equations and components}
-We start by recalling a description of the global geometry of $\M{1}{n}{\PP^r}{d}$.
-Besides the main component, which we have defined in the Introduction, for every positive integer $k$ and partitions $\lambda\vdash d$ into $k$ parts and $\mu\vdash n$ into $k$ parts such that no $(\lambda_i,\mu_i)_{i=1}^k$ is either $(0,1)$ or $(0,2)$, there is a \emph{boundary} irreducible component $D_{\lambda,\mu}(\PP^r,d)$ defined to be the closure of the locus where:
+We start by recalling a description of the global geometry of $\oM_1(\PP^r,d)$.
+Besides the main component, which was defined in the Introduction, for every positive integer $k$ and partition $\lambda\vdash d$ into $k$ parts such that no $\lambda_i=0$, there is an irreducible \emph{boundary component} $D_{\lambda}(\PP^r,d)$ defined to be the closure of the locus where:
 \begin{description}
-\item[i] the source curve is obtained by gluing a smooth elliptic curve with $k$ many $\PP^1$'s as rational tails,
-\item[ii] the map contracts the core elliptic curve to a point, and
-\item[iii] the rational tail $R_i$ has degree $\lambda_i$ and $\mu_i$-many marked points.
+\item[i] the source curve is obtained by gluing a smooth elliptic curve $E$ with $k$ many $\PP^1$'s as rational tails $R_i$,
+\item[ii] the map contracts the elliptic curve $E$ to a point, and
+\item[iii] the map has degree $\lambda_i$ on the rational tail $R_i$.
 \end{description}
-Indeed $D_{\lambda,\mu}(\PP^r,d)$ is the image of the gluing morphism from the fiber product:
-$$\M{1}{k}{\PP^r}{0}\times_{\PP^r}\prod_{i=1}^k\M{0}{\mu_i+1}{\PP^r}{\lambda_i}.$$
-
-The minimal arithmetic genus $1$ subcurve is called the \emph{core}. We then have:
+Indeed $D_{\lambda}(\PP^r,d)$ is the image of the gluing morphism from the fiber product:
+$$\M{1}{k}{\PP^r}{0}\times_{\PP^r}\prod_{i=1}^k\M{0}{1}{\PP^r}{\lambda_i}.$$
+
+\noindent The \emph{minimal} arithmetic genus $1$ subcurve is called the \emph{core} or the \emph{circuit}. %We then have:
 \begin{prop}\label{prop:components}
-\emph{(1)} The ones that we have described above are all the irreducible components of $\M{1}{n}{\PP^r}{d}$, %The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{\text{stable}\ (\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\rm{main}\}$,
-i.e.
-$$\M{1}{n}{\PP^r}{d}=\M{1}{n}{\PP^r}{d}^{\rm{main}}\cup\bigcup_{\lambda,\mu}D_{\lambda,\mu}(\PP^r,d).$$
-
-\emph{(2)} A map $[f]$ lies in the boundary of the main component  if and only if:
+\emph{(1)} All the irreducible components of $\oM_1(\PP^r,d)$ have been described above: %The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{\text{stable}\ (\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\rm{main}\}$,
+\[\oM_1(\PP^r,d)=\oM_1(\PP^r,d)^{\rm{main}}\cup\bigcup_{\lambda}D_{\lambda}(\PP^r,d).\]
+
+\emph{(2)} A map $[f]$ lies in \emph{the boundary of the main component}  if and only if:
 \begin{itemize}
-\item either $f$ is non-constant on an irreducible component of the core,
-\item or if $(E\ {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^k R_i,f)$ is a stable map with $k$ rational tails, where $E$ is the maximal contracted genus one subcurve, then $\{\operatorname{d}\!f(T_{q_i}R_i)\}_{i=1}^k$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
+\item either $f$ is non-constant on at least one irreducible component of the core,
+\item or if $(E\ {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^k R_i,f)$ is a stable map with $k$ rational tails, where $E$ is the \emph{maximal} contracted genus $1$ subcurve, then $\{\operatorname{d}\!f(T_{q_i}R_i)\}_{i=1}^k$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
 \end{itemize}
@@
 %This has led to the study of explicit local equation for the moduli space of stable maps in a smooth (relative to a moduli space of decorated curves) ambient space \cite{HL}, which we shall now briefly explain.
-We now review Hu-Li's procedure \cite{HL} to find local equations of $\M{1}{n}{\PP^r}{d}$ in a smooth ambient space.
-These are useful in describing the structure of the intrinsic normal cone and its splitting.
+We now review Hu-Li's procedure for finding local equations of $\oM_1(\PP^r,d)$ in a smooth ambient space \cite{HL}.
+They will be useful when describing the structure of the intrinsic normal cone and its splitting.
 
 Recall that a map $C\to\PP^r$ is given by a line bundle $L$ on $C$ together with $r+1$ sections in $H^0(C,L)$ that generate the line bundle.
-It is therefore natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1,n}=\mathfrak{Pic}(\cC_{1,n}\to\MM_{1,n})$.
-Hu and Li actually work on a local chart of the algebraic stack $\mathfrak M_{1,n}^{\rm{div}}$, parametrising families of pre-stable curves with a relative Cartier divisor of degree $d$. 
+It is therefore natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1}=\mathfrak{Pic}(\cC_{1}\to\MM_{1})$.
+Hu and Li actually work over a local chart of the algebraic stack $\mathfrak M_{1}^{\rm{div}}$, parametrising families of prestable curves with a relative Cartier divisor (of total degree $d$).
  %The problem is that this cone is not smooth, due to the jumps in the dimension of the fiber at the boundary of the moduli space.
@@
 
-Let $[f\colon C\to \PP^r]$ be a point of $\M{1}{n}{\PP^r}{d}$: we may fix homogeneous coordinates on $\PP^r$ in such a way that $D_0=f^{-1}\{x_0=0\}$ is a simple smooth divisor on $C$ (i.e.
+Let $[f\colon C\to \PP^r]$ be a point of $\oM_1(\PP^r,d)$: we may fix homogeneous coordinates on $\PP^r$ in such a way that $D_0:=f^{-1}\{x_0=0\}$ is a simple divisor contained supported on the smooth locus of $C$ (i.e.
 a $d$-uple of smooth points); this property will then hold in a neighbourhood of $[f]$.
-This gives a map from an \'{e}tale chart $\pazocal U$ of $\M{1}{n}{\PP^r}{d}$ to an \'{e}tale chart $\pazocal V$ of $\mathfrak M_{1,n}^{\rm{div}}$, that we may assume to land in the locus where the divisor is made of $d$ distinct smooth points.
-Notice that this locus is smooth over $\mathfrak M_{1,n}$ by the deformation theory of smooth subschemes.
-A morphism to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ sections of $\mathcal O_C(D)$: the morphism can be written as $[1:u_1:\ldots:u_r]$, where $1$ means the given section of $\mathcal O_C\to\mathcal O_C(D)$.
+This gives a morphism from an \'{e}tale chart $\pazocal U$ of $\oM_1(\PP^r,d)$ to an \'{e}tale chart $\pazocal V$ of $\mathfrak M_{1}^{\rm{div}}$, that we may assume to land in the locus where the divisor consists of $d$ distinct smooth points.
+Notice that this locus is smooth over $\mathfrak M_{1}$ by the deformation theory of smooth subschemes.
+A map to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ sections of $\mathcal O_C(D)$: the map can be written as $[1:u_1:\ldots:u_r]$, where $1$ denotes the given section of $\mathcal O_C\to\mathcal O_C(D)$.
 
@@
 
-Furthermore, \'{e}tale locally on $\M{1}{n}{\PP^r}{d}$, we may pick extra sections $\mathcal A$ and $\mathcal B$ of $\mathcal C_{1,n}(\PP^r,d)$ such that 
+Furthermore, \'{e}tale locally on $\oM_1(\PP^r,d)$, we may pick extra sections $\pazocal A$ and $\pazocal B$ of $\cC:=\mathcal C_{1}(\PP^r,d)\to\oM_1(\PP^r,d)$ such that:
 \begin{enumerate}
-\item they pass through the core elliptic curve;
+\item they pass through the core genus $1$ curve;
 \item they are distinct smooth points disjoint from the support of $\pazocal D_0$. 
 \end{enumerate}
-On  $\pazocal V$ we have that  $\pi_*\OO_{\cC}(\pazocal D+\mathcal A)$ is a vector bundle and $\pi_*\OO_{\cC}(\pazocal D)$ is carved inside it by requiring that the restriction map $\pi_*\OO_{\cC}(\pazocal D+\mathcal A)\to\pi_*\OO_{\cC}(\pazocal D+\mathcal A)\rvert_{\mathcal A}$ is zero.
+Now  $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)$ is a vector bundle on $\pazocal V$ and $\pi_*\OO_{\cC}(\pazocal D)$ is carved inside it by requiring that the restriction map $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\to\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\rvert_{\pazocal A}$ be zero.
 
 \begin{prop}\label{prop:smoothability}
-\emph{(1)} \'{E}tale locally on $\M{1}{n}{\PP^r}{d}$, there is a locally closed embedding of $\M{1}{n}{\PP^r}{d}$ inside the vector bundle $V:=\Spec(\pi_*\OO_{\cC}(\pazocal D+\A)^{\oplus r})$ over $\pazocal V$:
-\bcd
-\M{1}{n}{\PP^r}{d} & \pazocal U\ar[l,"\acute{e}t"]\ar[r,hook]\ar[d] & V\ar[dl] \\
-\MM_{1,n}^{\rm{div}} & \pazocal V\ar[l,"\acute{e}t"] &
-\ecd
-Notice that $V$ is smooth.
+\emph{(1)} \'{E}tale locally on $\oM_1(\PP^r,d)$, there is a locally closed embedding of $\oM_1(\PP^r,d)$ inside the vector bundle $V:=\Spec(\pi_*\OO_{\cC}(\pazocal D+\pazocal A)^{\oplus r})$ over $\pazocal V$:
+\bcd
+\oM_1(\PP^r,d) & \pazocal U\ar[l,"\acute{e}t"]\ar[r,hook]\ar[d] & V\ar[dl] \\
+\MM_{1}^{\rm{div}} & \pazocal V\ar[l,"\acute{e}t"] &
+\ecd
+Notice that $V$ is smooth since $\pazocal V$ is.
 %It is obtained by imposing the nondegeneracy and stability conditions \emph{(open)} on the vanishing locus of the restriction of the universal section of $\pi_*\mathcal L(\A)^{\oplus r}$ to $\A$ \emph{(closed)}.
@@
 
-\emph{(3)} Call $\varphi\colon \pi_*\OO_{\cC}(\pazocal D+\A-\B)\to\pi_*\OO_{\cC}(\pazocal D+\A)_{|\A}$ the map induced by restricting to $\A$.
-
- If we choose a suitable basis of $\pi_*\OO_{\cC}(\pazocal D+\A-\B)$, $\varphi$ can be written in a very explicit form: let $D=\sum_{i=1}^d\delta_i$, then  
+\emph{(3)} Call $\varphi\colon \pi_*\OO_{\cC}(\pazocal D+\A-\B)\to\pi_*\OO_{\cC}(\pazocal D+\A)_{|\A}$ the map induced on the first factor by restricting to $\A$.
+Locally on $\pazocal V$, $\pi_*\OO_{\cC}(\pazocal D+\A-\B)$ can be written as a sum of line bundles: let $D=\sum_{i=1}^d\delta_i$, then
  \[\varphi=\oplus\varphi_i\colon\oplus_{i=1}^d \pi_*\mathcal O_{\cC}(\delta_i+\A-\B)\to \pi_*\OO_{\cC}(\pazocal D+\A)_{|\A}.\] 
-  Furthermore, after choosing trivializations for the line bundles above,  $\varphi_i\colon\mathcal O_\pazocal V\to\mathcal O_\pazocal V$ is given by multiplication by \[\prod_{q\in[\A,\delta_i]}\zeta_q,\]
-   where $\zeta_q$ is the smoothing variable on $\mathfrak M_1$ corresponding to the node $q$, and $[\A,\delta_i]$ are all the nodes separating $\A$ (i.e. the core) from the point $\delta_i$.
+  After choosing a trivialisation for each of the line bundles above,  $\varphi_i\colon\mathcal O_\pazocal V\to\mathcal O_\pazocal V$ is given by multiplication by \[\prod_{q\in[\A,\delta_i]}\zeta_q,\]
+   where $\zeta_q$ is the smoothing coordinate on $\mathfrak M_1$ corresponding to the node $q$, and $[\A,\delta_i]$ denotes the set of nodes separating $\A$ (the core) from the point $\delta_i$.
 \end{prop}
-We refer the reader to \cite[Lemma~4.10, Proposition~4.13]{HL} for full details; we are going to review the key ideas in \S\ref{sec:equations}, where we adapt the theory to $\Mone{1}{\PP^r}{d}$.
-We include here a proof of Proposition~\ref{prop:smoothability}-(2) based on the local equations.
+We refer the reader to \cite[Lemma~4.10, Proposition~4.13]{HL} for the details; we are going to review the key ideas in \S\ref{sec:equations}, where we find local equations for $\Mone{1}{\PP^r}{d}$.
+We include here a proof of Proposition~\ref{prop:components}-(2) based on Hu-Li's equations.
 
@@
 $\delta_i$ belongs to the $h$-th rational tail, by $E(h)$ the set of nodes separating the core from the $h$-th rational tail.
-The equations take then the following form
- $$\sum_{h=1}^k(\prod_{q\in E(h)}\zeta_q)(\sum_{i\in D(h)}w_i^j)=0,\ j=1,\ldots,r$$
- which can be assembled in matrix form
- $$W\cdot\underline\zeta:=(\sum_{i\in D(h)}w_i^j)_{j,h}\cdot(\prod_{q\in E(h)}\zeta_q)_h=0.$$
+The equations will then take the following form:
+ $$\sum_{h=1}^k\left(\prod_{q\in E(h)}\zeta_q\right)\left(\sum_{i\in D(h)}w_i^j\right)=0,\ j=1,\ldots,r,$$
+ which can be assembled in matrix form as follows:
+ $$W\cdot\underline\zeta:=\left(\sum_{i\in D(h)}w_i^j\right)_{j,h}\cdot\left(\prod_{q\in E(h)}\zeta_q\right)_h=0.$$
  We see that smoothability is equivalent to the linear dependence of the rows of the above matrix $W$.
@@
 
-\subsection{Viscardi's compactifications}
+\subsection{Smyth-Viscardi's compactifications}
 For any homology class $\beta\in H_2(X,\mathbb Z)$, let $\pazocal M_{1,n}(X,\beta)$ be the stack of maps $f\colon C\to X$ from a \emph{smooth} elliptic curve with $n$ marked points, satisfying  $f_{*}\left [C\right ]=\beta$.
 The moduli spaces of $m$-stable maps give alternate compactifications of $\pazocal M_{1,n}(X,\beta)$.
-  \begin{dfn} Let $C$ be a reduced, connected, proper curve of arithmetic genus one, and let $p_1,\dots,p_n\in C$ be smooth, distinct points.
+\begin{dfn} Let $C$ be a reduced, connected, projective curve of arithmetic genus $1$ over $\k$, and let $p_1,\dots,p_n\in C$ be smooth, distinct points.
 A map $f\colon C\to X$ is said to be \emph{$m$-stable} if the following conditions hold:
@@
  \item $C$ has only nodes and elliptic $l$-fold points, $l\leq m$, as singularities.
- \item For any connected subcurve $E\subset C$ of arithmetic genus one on which $f$ is constant, 
- \[|\left\{E\cap \overline{C\setminus E}\right\}\cup\left\{p_i : p_i \in E\right\}| > m.\]
+ \item For any connected subcurve $E\subset C$ of arithmetic genus $1$ on which $f$ is constant, 
+ \[\left|\left\{E\cap \overline{C\setminus E}\right\}\cup\left\{p_i : p_i \in E\right\}\right| > m.\]
  \item $f$ has no non-trivial infinitesimal automorphisms.
@@
 \end{dfn}
-Recall that a $k$-rational $p\in C$ is called an \emph{elliptic $m$-fold point} if 
+Recall that a $\k$-rational $p\in C$ is called an \emph{elliptic $m$-fold point} if:
 \[
@@
 \begin{cases}
-k[[x,y]]/(y^2-x^3) & \textit{if } m=1\\
-k[[x,y]]/(x(x-y^2))& \textit{if } m=2\\
-k[[x,y]]/ I_m & \textit{if } m\geq 3
+\k[[x,y]]/(y^2-x^3) &  m=1\\
+\k[[x,y]]/(x(x-y^2))&  m=2\\
+\k[[x,y]]/ I_m &  m\geq 3
 \end{cases}
 \] 
-where $I_m=(x_hx_i-x_hx_j : i,j,h\in\left\{1,\dots,m-1\right\})$ and $i,j,h$ are distinct.
-
- Viscardi's main result \cite[Thm. 3.6]{VISC} is:
+where $I_m=\left(x_hx_i-x_hx_j : i,j,h\in\left\{1,\dots,m-1\right\}\right)$ and $i,j,h$ are distinct.
+
+ Viscardi's main result \cite[Thm. 3.6]{VISC} is the following:
 % that the associated moduli functor gives a compactification of $\mathcal M_{1,n}(X,\beta)$ (alternative to Kontsevich' moduli space).
 \begin{thm}
-The moduli functor of $m$-stable maps in a fixed homology class $\overline{\pazocal{M}}^{(m)}_{1,n}(X,\beta)$ is represented by a proper DM stack of finite type.
+The moduli functor of $m$-stable maps  $\overline{\pazocal{M}}^{(m)}_{1,n}(X,\beta)$ is represented by a proper Deligne-Mumford stack of finite type over $\k$.
 \end{thm}
 \begin{remark}\label{remark:sprouting}
-We think that the algorithm presented by Viscardi to prove properness of the moduli space oversees a case.
-The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ constant on a genus one connected sub-curve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $f'\colon \cC'_T\to\PP^r_T$, where $\cC'_0$ has a genus $1$ Gorenstein singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
+We think that the algorithm proposed by Viscardi to prove the properness of his moduli spaces oversees a case.
+The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ is constant on a genus $1$ connected subcurve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $f'\colon \cC'_T\to\PP^r_T$, where $\cC'_0$ has a genus $1$ \emph{Gorenstein} singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
 A counterexample is the following.
 
-Consider the stable map $[f]$ in $\overline{\mathcal M}_{1,0}(\PP^3,4)$ from an elliptic bridge $R_1\sqcup_{q_1}E\sqcup_{q_2} R_2$ to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e.
-its image is the non-Gorenstein singularity: \[D:=\Spec\left(\mathbb C[x,y,z]/(x,y)\right)\cup \Spec\left(\mathbb C[x,y,z]/(z,y^2-x^3)\right).\]
-Notice that $\operatorname{d}\!f(T_{q_2}R_2)=0$, so there is a non-trivial linear relation
-\[0\cdot\operatorname{d}\!f(T_{q_1}R_1)+1\cdot\operatorname{d}\!f(T_{q_2}R_2)=0\] and the map is smoothable.
+Consider the stable map $[f]$ in $\oM_{1}(\PP^3,4)$ from an elliptic bridge $C:=R_1{}_{q_1}\!\sqcup E\sqcup_{q_2} R_2$ to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e.
+its image is the non-Gorenstein singularity:
+\[D:=\Spec\left(\k[x,y,z]/(x,y)\right)\cup \Spec\left(\k[x,y,z]/(z,y^2-x^3)\right).\] 
+Notice that $\operatorname{d}\!f(T_{q_2}R_2)=0$, so there is a non-trivial linear relation:
+\[0\cdot\operatorname{d}\!f(T_{q_1}R_1)+1\cdot\operatorname{d}\!f(T_{q_2}R_2)=0,\]
+and hence the map is smoothable.
 Viscardi claims that the map factors through the family $\cC'_T$, obtained by contracting $E$ to a tacnode.
-Notice that the image of $f'$ would still need to be $D$, since there is at most one indeterminacy point of $\cC'\dashrightarrow\PP^r_T$ at the singularity.
-However our $f$ \emph{does not factorise} through the tacnode.
-Indeed we would have a birational morphism between two singular curves with the same $\delta$ invariant and common normalisation, so $f'\colon C'\to D$ would need to be an isomorphism, which is a contradiction.
- We suggest that in this case the correct procedure would be to sprout $(R_1,q_1).$
+Notice that the image of $f'$ would still be $D$, since there is at most one indeterminacy point of $\cC'_T\dashrightarrow\PP^r_T$, located at the singularity.
+However in our example $f$ cannot factor through the tacnode.
+Indeed in that case we would have a birational morphism between two singular curves with the same $\delta$ invariant and the same normalisation, so $f'\colon C'\to D$ would be an isomorphism, which is a contradiction.
+ We suggest that in this case the correct procedure would be to sprout $(R_1,q_1)$.
 \begin{center}
@@
 Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $T$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}.
-As described in \cite[Theorem~3.6, Step~1]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_T\to\PP^r_{T}$, for which we may suppose that $C_0$ is nodal and $f:=F_0$ is stable.
-
-If $f$ is not constant on the minimal genus $1$ subcurve \cite{SMY1}, then it is already $m$-stable and there is nothing to say.
-Otherwise let $E\subset C$ be the maximal connected genus $1$ subcurve where $f$ is constant and let $R_1\sqcup\dots\sqcup R_m=\overline{C/E}$.
+As described in \cite[Theorem~3.6, Step~1]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_T\to\PP^r_{T}$, for which we may suppose that $C:=\cC_0$ is and nodal and reduced $f:=F_0$ is stable.
+
+If $f$ is not constant on the minimal genus $1$ subcurve, then it is already $m$-stable and there is nothing to say.
+Otherwise let $E\subset C$ be the maximal connected genus $1$ subcurve where $f$ is constant and let $R_1\sqcup\ldots\sqcup R_m=\overline{C/E}$.
 
@@
  %In other words, the first derivatives of the sections $s_0,\dots,s_r$ defining $f$, satisfy a non trivial linear relation around $q_1,\dots,q_m =E\cup\bar{C/E}$.
- Consider a maximal one with all non-zero coefficients.  Possibly after relabelling this relation looks like
+ Consider a maximal one with all non-zero coefficients.  Possibly after relabelling, such a relation looks like:
  \begin{equation*}\label{eq:linrelation}
- \alpha_1\operatorname{d}\!f(T_{q_{1}}R_{1})+\ldots +\alpha_j \operatorname{d}\!f(T_{q_{j}}R_{j})=0
+ \alpha_1\operatorname{d}\!f(T_{q_{1}}R_{1})+\ldots +\alpha_j \operatorname{d}\!f(T_{q_{j}}R_{j})=0.
  \end{equation*}
- In this case we blow-up $\mathcal{C}$ in $q_{j+1},\ldots, q_m$.
+ In this case we blow-up $\mathcal{C}_T$ in $q_{j+1},\ldots, q_m$.
 The induced map $\tilde{F_0}$ is constant on the exceptional divisors $G_{j+1},\ldots, G_m$ and we can complete the above linear relation to
@@
 Now this \emph{sprouting} \cite[Section 2.3]{SMY2} ensures that the sections descend to the corresponding elliptic $m$-fold singularity.
+Notice that, for every $m_1\leq m_2$, there is a morphism from an $m_2$-elliptic singularity to an $m_1$-elliptic point that is birational on the target and contracts $m_2-m_1$ branches of the source to the singular point.
 At this point proceed with Step~2 of Viscardi's algorithm.
@@
 
-The irreducible components of Viscardi's moduli space $\overline{\pazocal{M}}^{(m)}_{1,n}(\PP^r,d)$ are well understood too \cite[Thm.~5.9]{VISC}; indeed they have a similar description to the ones of Kontsevich's space.
+The irreducible components of Viscardi's moduli space $\overline{\pazocal{M}}^{(m)}_{1,n}(\PP^r,d)$ are also well understood \cite[Thm.~5.9]{VISC}; indeed they have a similar description to the ones of Kontsevich's space.
 The main advantage of the $m$-stable compactification is that the number of components drops as $m$ increases.
 
-In particular the space $\overline{\pazocal{M}}^{(1)}_{1,n}(\PP^r,d)$ we will consider in the next sections does not have the boundary divisor $D_{(d),(n)}(\PP^r,d).$
+In particular the space $\Mone{1}{\PP^r}{d}$ we will consider in the next sections has not got the boundary component $D_{(d)}(\PP^r,d)$.
 % \begin{cor}\cite[Cor.~5.10]{VISC}
@@
 
- \subsection{A different characterization of smoothability}
+ \subsection{A different characterisation of smoothability}
  Inspired by Viscardi's alternate compactification, we give yet another characterisation of smoothable maps in genus $1.$
@@
 \[ \dim_k R/I_p \]
-where $I_p=\operatorname{Ann}_R(\widetilde R/R)$ is the conductor ideal at the singular point. \marginpar{prove it or at least say what numbers it gives}
+where 
+\[I_p=\operatorname{Ann}_R(\widetilde R/R)=\left\{f\in\, R\;\rvert\; f\cdot\widetilde{R}\subseteq R\right\}\]
+ is the conductor ideal at the singular point. 
+ Using the explicit description of $\mathfrak{m}_R$ we gave in the classification Lemma we can easily understand the generators of $I_p$ and check that for a $(k,m-k)$ singularity  we have 
+ \[ \dim_k R/I_p=m-k.\]
 \end{remark}
@@
 
-We show that we can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$.\footnote{This is in general not possible: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar non-Gorenstein singularity with local equation $y^2-x^5=0$.
-Then a compatible smoothing can be found only if the rational tail is attached to a Weierstrass point of the genus $2$ curve, as can be seen by computing the stable model of the ramphoid cusp.
-This example was kindly suggested to us by Prof.
-D.I.
-Smyth.}
+We first show that:
+\begin{claim}
+ We can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$~\ref{rem:compatible_smoothing}.
+ \end{claim}
+\begin{proof}
  Assume that $\hat C$ has a $(k,m-k)$-singularity. 
-Then we can pick a smoothing $\cC$ of $C$ such that, when resolving the $A_n$ singularities at the nodes, i.e.
-when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal balanced genus one subcurve contracted by $f^{\rm{ss}}$; then there are $m-k$ rational tails of positive degree directly adjacent to $E$, and the other $k$ rational tails are further away.
-Moreover the rational tails can be made to agree in length with the corresponding ones in $\hat C$.
-We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, resulting in an $(m-k+h)$-fold point with $h\leq k$; at this point use $f^*\OO_{\PP^r}(1)$ (add markings away from the genus $1$ singularity as necessary) to further contract the branches of degree $0$.
-Notice that $f^*\OO_{\PP^r}(1)$ has no $H^1$ because at least one branch is of positive degree, so it satisfies cohomology and base change, making it possible to verify that the result of this second contraction is a $(k,m-k)$-singularity.\marginpar{check: maybe need positive degree on one of the $m-k$ branches?} So the central fiber of $\hat \cC$ is isomorphic to $\hat C$.
+Pick a smoothing $\cC$ of $C$ such that after resolving the $A_n$ singularities at the nodes, i.e.
+when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal balanced genus one subcurve \cite[Proposition~2.11]{SMY1} contracted by $f^{\rm{ss}}$,
+ then there are $m-k$ rational tails of positive degree directly adjacent to $E$ and the other $k$ rational tails are further away, possibly at different distances.
+ Notice that $f^{\rm{ss}}$ is defined since $C^{\rm{ss}}$ differs from $C$ only for $-2$ curves.
+
+ We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, namely
+\[\mathcal L=\omega_{\cC^{\rm{ss}}/T}\left( \sum_{F\subseteq E}(l+1-l(F,Z)F\right),\] 
+whose 
+  resulting contraction $\bar{C}$ gives a $(m-k+h)$-fold point with $h\leq k$.
+Notice that $\bar{C}$ comes with a map $\rho$ to $\hat{C}$ and at this point use $\rho^*\hat{f}^*\OO_{\PP^r}(1)$ to perform the second contraction.
+If necessary, we add markings $p_1+\dots p_N=\Sigma$ on the degree $0$ rational components away from the genus $1$ singularity and on the degree $0$ branches of the $(m-k+h)$-fold which are not contracted by $\rho.$
+
+Since $\rho^*\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ has no $H^1$ it satisfies cohomology and base change.
+Then we can check  that the result of this second contraction is a $(k,m-k)$-singularity just looking at the vanishing orders of the sections of $\rho^*\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ on the central fiber $\bar{C}$ of the first contraction.
+These sections are constant on the degree 0 branches we did not mark and so  we conclude that the dependence relation among  the tangent vectors of the branches at the singular point of the second contraction only involve the $m-k$ rational tail image of the ones adjacent to $E$.
+
+Since $\hat{C}$ with the added markings $\Sigma$ is stable, the morphism $\cC^{\rm{ss}}\to\cC$ we just constructed factors through a morphism
+$\cC\to\hat{\cC}$ whose central fibers are $C$ and $\hat{C}$ and compatible with $f$ and $\hat{f}.$
+\end{proof}
 
@@
 In order to extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
-Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ \cite{Wang}.
+Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ .
 Once done this we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC\to\hat{\cC}\xrightarrow{\hat F}\PP^r$.
@@
 Hence it can be seen from the normalisation exact sequence and Serre duality that $H^1(\hat{C},\hat{L})=0$ as soon as $\hat L$ has positive degree on one of the branches.
-
  \end{proof}
+\begin{remark}\label{rem:compatible_smoothing}
+In general is not possible to find compatible smoothings: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar singularity with local equation $y^2-x^5=0$.
+Then a compatible smoothing can be found only if the rational tail is attached to a Weierstrass point of the genus $2$ curve, as can be seen by computing the semi-stable model of the ramphoid cusp.
+This example was kindly suggested to us by Prof.
+D.I.
+Smyth.
+
+\end{remark}
 
@@
 
-\begin{comment}
- Moreover, inspired by Viscardi's alternate compactification, we express a sufficient condition for smoothability in yet another way.
- \begin{prop}
-Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a ($n$-marked) genus one curve of the form $(E {}_{p_1,\ldots,p_m}\sqcup_{q_1,\ldots,q_m}\bigsqcup_{i=1}^m R_i,f)$, where $E$ is the maximal connected contracted arithmetic genus one subcurve, and $R_i$ are the rational tails (chains of $\PP^1$ along which $f$ has positive degree).
- If $f$ factorises through a \emph{non-degenerate} (i.e.
-having positive degree along at least one of the branches of the singularity) map $f'\colon C'\to\PP^r$ from an elliptic $k$-fold singularity, with $k\leq m$, then  $\operatorname{d}\!f(T_{q_i}R_i)$ are linearly dependent in $T_{f(E)}\PP^r$.
- \end{prop}
- \begin{proof}
- Let $\xymatrix{C\ar[r]^{\pi} &C'\ar[r]^{f'} &\PP^r}$ be the factorization of $f$. Then $E'=\operatorname{Exc}(\pi)\subseteq E$ and 
-  $\overline{C\setminus E'}=(S_1,q'_1)\sqcup\dots\sqcup (S_k,q'_k)\to (C',p)$ 
-  is the normalization of the elliptic $k$-fold point. By hypothesis, $f=f'\circ\pi$ and $f$ is non-constant on $R_1,\dots R_m.$ Being $f'$ non-degenerate implies that there exists a subset
-  $\left\{S_1,\ldots S_j\right\}\subseteq\left\{S_1,\ldots S_k\right\}$ 
-  such that \[(S_1,q'_1)\cong (R_{i_1}, q_{i_1}),\ldots, (S_j,q'_j)\cong (R_{i_j}, q_{i_j}),\;\;\left\{i_1,\dots,i_j\right\}\subseteq \left\{1,\dots,m\right\}.\] 
-By Smyth's characterisation of elliptic $k$-fold singularities, \cite[Lem.~2.2]{SMY1}, we obtain a non trivial linear relation 
-  \begin{equation*}
-  \label{eq:dep}\alpha_1\operatorname{d}\!\pi(T_{q_{i_1}}R_{i_1})+\ldots+\alpha_j \operatorname{d}\!\pi(T_{q_{i_j}}R_{i_j})+\alpha_{j+1}\operatorname{d}\!\pi(T_{q_{j+1}}S_{j+1})+\ldots+\alpha_k \operatorname{d}\!\pi(T_{q_k}S_k)=0
-  \end{equation*}
-  since all the coefficients are non-zero, $j\neq0$, and the second half of the formula can be ignored, we've got what we wanted.
-  \end{proof}
-
-  \begin{rem}\label{remark:cuspunionline} 
-The viceversa is not true, as Remark \ref{remark:sprouting} shows.
-\end{rem}
-
-In order to achieve the original goal of Gromov-Witten theory, i.e.
-the enumeration of smooth curves of genus $g$ in a target variety, mathematicians have been trying either to eliminate the unwanted components of Kontsevich's space (e.g.
-degenerate contributions from lower genus curves and multiple covers of lower degree curves) by defining alternate compactifications, or to concentrate the attention on the main component (i.e.
-find a suitable fundamental class supported on it).
-
-It is a matter of fact that the virtual dimension of the moduli space of maps to a three-fold $X$ is independent of the genus.
-In this context it was plausible to test the better enumerative properties of reduced invariants; in fact, Li-Zinger \cite{LZ} in the symplectic category and, later on, Chang-Li \cite{CL} in the algebraic one, proved a comparison formula for the quintic three-fold $X_5\subseteq\PP^4$ (or, more generally, for a complete intersection three-fold $X$ of degree $(l_1,\ldots,l_k)$ in $\PP^r$ with $\sum l_i\leq r+1$) of the form
-$$GW_1(X)=\widetilde{GW}_1(X)+c\cdot GW_0(X).$$
-We notice that the genus zero contribution to this formula comes from the boundary component with a single rational tail of degree $d$, while elliptic bridges and degenerate contributions with more rational tails do not matter to the genus one Gromov-Witten count.
-This suggests that removing the component with elliptic tails would provide a more direct and efficient definition of reduced invariants.
-We plan to do so by comparing the ordinary space of stable maps with Viscardi's space of 1-stable maps.
-\end{comment}
-
-\section{From $p$-fields to the quintic three-fold}\label{section:p-fields}
-We shall introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, endow it with a $0$-dimensional virtual class, and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
-This is a word-by-word repetition of the arguments in \cite{CLpfields}, once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
-Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it should otherwise be skipped.
-
-First we introduce the notion of the \emph{cone of sections} of a smooth object $\pazocal Z$ over a family of curves $\cC$: let $B$ be any base (algebraic stack) and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
-curves; let $\mathcal L$ be a line bundle on $\cC$.
-Then there is an algebraic stack over $B$ representing sections of $\mathcal L$, and it can be defined as $C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L)$; this is because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
-More generally, the cone of section $\mathfrak S$ of $\pazocal Z$ is defined by the universal diagram:
-\bcd
-& \pazocal Z\ar[d] \\
+\section{From $p$-fields to the quintic three-fold}
+We introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, we endow it with a $0$-dimensional virtual class and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
+This is a word-by-word repetition of the arguments in \cite{CLpfields} once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
+Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it could otherwise be skipped.
+\subsection{Moduli of sections}
+\begin{dfn}
+ Let $B$ be an algebraic stack and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
+curves.
+Let $\mathcal Z$ be an  Artin stack smooth over  $\cC$ such that the morphism to $\cC$ is representable and quasi- projective.
+For any $ S\to B$  the \emph{cone of section} of $\mathcal Z$ over $S$ is defined by:
+ \[\mathfrak{S}(S)=\left\{\cC_S\;\text{morphisms}\; s\colon \cC_S\to\mathcal Z_S\right\};\]
+ the arrow in $\mathfrak{S}(S)$ are defined in the obvious way.
+ The groupoid $\mathfrak{S}$ is an algebraic stack \cite[Proposition~2.3]{CL}.
+
+\end{dfn}
+ To fix notation, let us write down the following diagram
+ \bcd
+& \mathcal Z\ar[d] \\
 \cC_{\mathfrak S}\ar[r]\ar[ur,bend left,"\mathfrak e"]\ar[d,"\pi_{\mathfrak S}"] & \cC\ar[d,"\pi"] \\
@@
 \ecd
-The previous case can be recovered by setting $\pazocal Z=\rm{Vb}(\mathcal L)$. The morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
-\[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\pazocal Z/\cC}\]
-Notice that in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$.
-The construction for a general smooth $\pazocal Z$ is way more flexible.
-The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex, but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
-
-Let us now establish some further notation: let $\w\in k[x_0,\ldots,x_4]_5$ be a homogeneous polynomial such that $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold under consideration.
-In this section we shall denote by $\rm{M}:=\oM_1^{(1)}(\PP^4,d)$, by $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ the universal $1$-stable curve and map over it, by $\L_{\rm M}=f_{\rm M}^*\OO_{\PP^4}(1)$ and by $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}$.
-Furthermore we shall write $\hM$ for $\MM_1^{(1)}$ and $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$.
-
-\begin{lem}
- $\hP$ is a smooth Artin stack of dimension $0$. Furthermore there is a compatible triple of dual perfect obstruction theories:
- \bcd
- \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
- \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
- \ecd
- implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
-\end{lem}
-\begin{proof}
- The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
-
- The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
-
- The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
-The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
-The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
-
- The last claim follows from functoriality of virtual pullback \cite{Manolache-pullback}.
-\end{proof}
-
-We proceed to define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
+where $\mathfrak e$ denotes the tautological evaluation map. 
+Let us see some examples of the above construction we will be interested in.
+
+ In the rest of the section we use the following notations:
+$\hM$ for $\MM_1^{(1)}$, $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$ and $\lambda\colon\hM\to\hP$ for the canonical forgetful map.
+\subsubsection*{Sections of line bundles}
+When $\mathcal Z=\rm{Vb}(\mathcal L),$ then the algebraic stack  $\mathfrak{G}\to B$ representing sections of $\mathcal L$,  can be described as   
+\[C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L).\]
+ This is essentially because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality. 
+\subsubsection*{Moduli of stable maps and 1-stable maps} 
+Let $X\hookrightarrow \PP^n$ be a projective variety and 
+\[\mathcal Z_X=(\operatorname{Tot}(\mathcal{L}^{\oplus n+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^n} X\]
+where $\mathcal L_{\pP}$ is the universal line bundle on $\pP,$ induced from $f_{\oM_{1,n}(X,\beta)}^*\OO_{X}(1)$ via the natural map from the space of maps to the Picard.
+Then the moduli space of stable maps $\oM_{1,n}(X,\beta)$ is an open inside the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}.$ This is the point of view we already took for $X=\PP^n$ in  \S~\ref{sec:equations} to describe the equations of the moduli space of maps relative to $\MM^{\rm{div}}.$
+
+Analogously, the moduli space of 1-stable maps, e.g. $\oM_1^{(1)}(\PP^n,d)$, can be thought as an open inside the moduli of sections of 
+\[\hat{\mathcal Z}=(\operatorname{Tot}(\hat{\mathcal{L}}^{\oplus n+1}_{\hP})-0_{\cC_{\hP}})\]
+over $\hat{\cC}_{\hP}.$
+
+\subsubsection*{Moduli space of 1-Stable Maps with fields}
+ Denote with $\rm{M}$ the moduli space of 1-stable maps  $\oM_1^{(1)}(\PP^4,d)$ and we write $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}.$ 
+ Moreover,
+ $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ are the universal $1$-stable curve and map over it.
+We define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
 
 \begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))$ parametrises $1$-stable maps
+ The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))\] parametrises $1$-stable maps
  \bcd
@@
 
-We shall abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. %This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
+We  abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. 
+This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
+
+Otherwise, in parallel with the above description on the moduli space of 1-stable maps,  $\pazocal P$ can be thought as a (open in a) moduli space of sections of the bundle $\rm{Vb}(\hat{\mathcal L}_{\hP}^{\oplus 5}\oplus \mathcal P_{\hP}).
+$
 %\bcd
@@
 
+\subsection{Obstruction theories}
+In the notation of the previous section,
+ the morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
+\[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\mathcal Z/\cC}\]
+The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex and the fact that $\mathcal Z\to\cC$ is smooth,
+but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves, to conclude that the same results apply when the fibers of $\cC\to B$ are l.c.i curves.
+
+In the examples considered above we get:
+ in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$;
+%The construction for a general smooth $\pazocal Z$ is way more flexible.
+
+in the case of the moduli space $\rm{M}=\oM_1^{(1)}(\PP^4,d)$ we get an obstruction theory relative to  $\hP$ given by $ \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$;
+
+in the case of 1- stable maps with fields $\pazocal P$ we get $\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}).$
+
+On the moduli space of 1-stable map we have another natural perfect obstruction theory relative to $\hM,$ which is the standard one defined by Behrend-Fantechi \cite[Proposition 6.3]{BF}.
+The next result explain how to compare the two.
+\begin{lem}
+ $\hP$ is a smooth Artin stack of dimension $0$. Furthermore there is a compatible triple of dual perfect obstruction theories:
+ \bcd
+ \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \ecd
+ implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
+\end{lem}
+\begin{proof}
+ The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+
+ The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
+
+ The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
+The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
+The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
+
+ Finally, the fact that  $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard virtual class for the moduli space of maps follows from functoriality of virtual pullback \cite{Manolache-pullback}.
+\end{proof}
+Finally notice that the relative perfect obstruction theory for $\pazocal P$ fits in the following exact triangle:
 \begin{lem}
@@
 \end{lem}
-See \cite[Proposition 3.1]{CLpfields}.
-Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
-In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the existence of a cosection of the obstruction bundle whose degeneracy locus is the afore-mentioned substack, and the machinery of cosection localised virtual classes \cite{KLcosection}.
+This follows from the general theory of moduli spaces of sections recalled above.
+
+Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0.$ In the next section we show that this cycles is actually supported on the proper sub-stack $\Mone{1}{X}{d}$ where
+ $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold defined by a homogeneous polynomial
+ $\w\in k[x_0,\ldots,x_4]_5.$
+
+% Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
+In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the
+\subsection{Cosection Localization}
+We show the existence of a cosection of the obstruction bundle whose degeneracy locus is the proper substack $\Mone{1}{X}{d}.$ The machinery of cosection localised virtual classes \cite{KLcosection}.
 Recall their Theorem 1.1:
@@
 \ecd
-(here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base) we obtain a cosection of the relative obstruction sheaf
+%here and in future $\oplus$ at the level of geometric vector bundles means the fiber product over the base
+ we obtain a cosection of the relative obstruction sheaf
 \begin{equation}\label{eqn:cosection}
@@
 The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
-$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.
-
-We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle, and we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
+
+Moreover, Chang-Li prove that
+$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.\marginpar{Why is this needed}
+
+We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle:
+\[[\pazocal P]^{\rm{vir}}_{\sigma_1}=0^{!}_{\sigma_1,\rm{loc}}[\mathfrak{C}_{\pazocal P/\hP}]\;\in\; A_0(\Mone{1}{X}{d}).\]
+
+We we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
 \begin{thm}
@@
 \end{thm}
-This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}$.
+
+\subsection{Sketch of the proof}
+This is done in two steps: first we compare the invariants coming from $\Mone{1}{\PP^4}{d}^p$ with the ones coming from $\Mone{1}{N_{X/\PP^4}}{d}^p$, where $N_{X/\PP^4}$ is the normal of the quintic in $\PP^4.$
+
+Second we compare the latter invariants with $\deg[\Mone{1}{X}{d}]^{\rm{vir}}.$
+
+\subsubsection*{Step~1}
+This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}.$
+The idea is: construct a perfect obstruction theory for $\Mone{1}{V}{d}^p$ relative to $\hP$ which is compatible with the obstruction theories of the fibers $\Mone{1}{V_t}{d}^p;$ then construct a family version of the cosection and the fact that for compatible obstruction theories taking cosection localized cycles commutes with Gysin pull-back to conclude this Step.
 
@@
 \end{lem}
-See \cite[Lemma 4.1]{CLpfields}. This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\pazocal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
-
-\bcd
-& \pazocal Z'\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & V\ar[d] \\
+This is just a computation in local coordinates.
+This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\mathcal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
+
+\bcd
+& \mathcal Z'\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & V\ar[d] \\
 & \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
@@
 
-Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\pazocal Z:=\pazocal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
+Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\mathcal Z:=\mathcal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
 The general theory explained above provides an obstruction theory for $\pazocal V\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
@@
 \begin{lem}
- A dual perfect obstruction theory is given by \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
+ A dual perfect obstruction theory is given by 
+ \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
  The restriction of $\phi_{\pazocal V/\hP\times\Aaff^1_t}$ to a fiber
@@
 Of course $h^0(\mathbb E'_{\pazocal V/\hP})\simeq\mathbb T_{\pazocal V/\hP}$, but the previous lemma hints at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\pazocal V/\hP})$ contains one factor $\R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}$ too many, so that restricting to the fibers we would find a different obstruction theory with respect to the standard one.
-A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber (i.e.
-applying $\iota_t^!$) we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
-
-This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to $\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP}$, where the latter fits into an exact triangle:
-\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]} \]
-
-A further complication comes from the fact that we need to work with cosection localised cycles.
+A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber, i.e.
+applying $\iota_t^!,$ we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
+
+This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to 
+\[\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP},\]
+ where the latter fits into an exact triangle:
+\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]}.\]
+Furthermore the lifted obstruction theory is compatible with the one the fibers, 
+\begin{lem}
+There is the following commutative diagram of exact triangles:
+\bcd
+\hat{\pi}_{\pazocal V_c *}\OO_{\hat\cC_{\pazocal V_c}}[-1]\ar[r] & \mathbb E_{\pazocal V_c/\hP} \ar[r] &\mathbb E_{\pazocal V/\hP}\rvert_{\pazocal V_c}\\
+\mathbb{T}^{\geq 1}_{\pazocal V_c/\pazocal V}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\pazocal V_c/\hP}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\pazocal V/\hP}\rvert_{\pazocal V_c} \ar[u]
+\ecd
+\end{lem}
+The proof is exactly the same given in \cite[\S~4.6]{CL}.
+
+Since we are working with cosection localised cycles, this is not yet enough to conclude.
  A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
@@
 \[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
-It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is $\Mone{1}{X}{d}\times\Aaff^1_t$.
+It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is 
+\[\Mone{1}{X}{d}\times\Aaff^1_t.\]
 
@@
 So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\pazocal P$ when $t\neq 0$.
-It is proved in \cite[Theorem 5.2]{KLcosection} that the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
+It is proved in \cite[Theorem 5.2]{KLcosection} that, given compatible perfect obstruction theories, the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
 \[
@@
 where we have denoted by $\pazocal Q:=\Mone{1}{X}{d}$.
-
+\subsubsection*{Step~2}
 We are left with proving that $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $[\Mone{1}{X}{d}]^{\rm{vir}}$.
-We shall introduce more shorthand notation: $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$.
-Chang and Li notice that there is a perfect obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})$ compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
+In the rest of the section we use the following notation $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$. 
+The idea is now to conclude finding a perfect obstruction theory for $v\colon\pazocal N\to\pazocal Q$ compatible with the ones of $\pazocal N\to\hP$ and $\pazocal Q\to\hP$ and then prove a cosection localized version of Manolache's virtual pull-back construction~\cite{Manolache-pullback}.
+
+Chang and Li proved indeed that there is a perfect obstruction theory 
+\[\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})\]
+ compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
 Then \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\pazocal N/\pazocal Q}$ is supported inside
@@
 \[
- v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0'))
-\]
-Finally they notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as $[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]$ along the fibers, and this is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
-
-Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves.
+ v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0')=\pazocal Q)
+\]
+sending $[\pazocal Q]^{\rm{vir}}$ to $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}.$
+
+To conclude it is now enough to compute the degree of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}.$
+Since we are just interested in what happens on $A_0(\pazocal Q)$, we only have to compute $\deg(v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}(\zeta)$ for $\zeta$ a closed point.
+This is done in \cite[Theorem 5.7]{CLpfields} and the same considerations work in our case since the construction of the localized pull-back is completely analogous.
+%They notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as 
+%\[[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]\] along the fibers.
+This is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
+
+Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves but every step generalizes automatically in our setting; let us recall that in the end, the moduli space of 1-stable maps should be though as the moduli space of stable maps with the boundary divisor of elliptic tails contracted.
 
@@
 This is generically an isomorphism, but has $1$-dimensional fibers over the locus of elliptic tails, due to the fact that $\Pic(\hat C)\to\Pic(C)$ has kernel $\mathbb G_{\rm a}$ when $\hat C$ has a cusp.
-
+\end{remark}
 On the other hand notice that
 \[ \X\times_{\mathfrak M_1^{\rm{wt}}(1)} \mathfrak M_1^{\rm{div}}(1) \to \mathfrak M_1^{\rm{div}} \]
-is an isomorphism.\marginpar{FIX ME: when the divisor contains the node} Indeed given a line bundle $\mathcal L$ on $C$ and a section $s_0\in\Gamma(C,\mathcal L)$ which does not vanish on any irreducible component, there is exactly one line bundle $\hat{\mathcal L}$ on the $1$-stabilisation of $C$ and one section $\hat s_0\in\Gamma(\hat C,\hat{\mathcal L})$ that pull back to $(\mathcal L,s_0)$, due to the following:
+is an isomorphism. We just check on points.
+\marginpar{I am not sure, CHECK ME.}
+\begin{comment}
+Given a line bundle $\mathcal L$ on $C$ and a section $s_0\in\Gamma(C,\mathcal L)$  there is exactly one line bundle $\hat{\mathcal L}$ on the $1$-stabilisation of $C$ and one section $\hat s_0\in\Gamma(\hat C,\hat{\mathcal L})$ that pull back to $(\mathcal L,s_0)$.
+Let us denote with $p$ the node separating the elliptic tail and the $\PP^1$, which we think as pointed normalisation $\nu\colon(\PP^1,p)\to \hat C$ of the cusp.
+There are just two cases to be consider: $s_0$ does not vanish on the elliptic curve; the section is identically $0$ on $E$.
+
+In the first case, $\nu(s_0\rvert_{\PP^1})$ is a smooth divisor $\hat{D}_0$ in $\hat$ and the line bundle $\OO_{\hat{C}}(\hat{D}_0)$ together with the defining section equation $\hat{s}_0$ of the smooth sub-scheme  $\nu(s_0\rvert_{\PP^1})$ pull-back to $\mathcal L$ and $s_0.$
+
+If $D_0$ contains the node, notice that since $p$ is not Cartier in $C$, the section $s_0$ vanishes in $p$ at least with order two, i.e.  
 \end{remark}
@@
 Let $\nu\colon(\PP^1,p)\to \hat C$ be the pointed normalisation of the cusp.
-Then $0\neq s\in\Gamma(\PP^1,\OO_{\PP^1}(d))$ with $s(p)=0$ only if $s'(p)=0$ determines a unique line bundle $\hat{\mathcal L}$ on $\hat C$ to which $s$ descends.
+Then $0\neq s\in\Gamma(\PP^1,\OO_{\PP^1}(d))$ with $s(p)=0$  determines a unique line bundle $\hat{\mathcal L}$ on $\hat C$ to which $s$ descends  only if $s'(p)=0$.
 \end{lem}
@@
 \end{proof}
+\end{comment}
+
 \begin{remark}
@@
 
-As anticipated we may endow $\Z^p$ with a localised virtual cycle by ``localised virtual pullback'': indeed $\XP$ is a smooth Artin stack, and:
-\[
-\mathfrak C_{\Z^p/\XP} \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}} \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)_\sigma
-\]
-
+As anticipated we may endow $\Z^p$ with a localised virtual cycle by ``localised virtual pullback''.
+Indeed, consider on $\Z^p$ the perfect obstruction theory $\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)$ and the induces cosection
+\[\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p\]
+whose degeneracy locus is
+\[\pazocal D(\alpha^*\sigma)=\pazocal D(\sigma)\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
+Then we have that
+\begin{align*}
+\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\\
+& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)_\sigma\\
+&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)_{\alpha^*\sigma}
+\end{align*}
+and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}.$
+\begin{color}{red}
 \begin{lem}
-localised virtual pullback commutes with pushforward
-\end{lem}
+localised virtual pullback commutes with pushforward. In particular,
+\[\alpha_* [\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}=[{\Mone{1}{\PP^4}{d}^p}]^{\rm{vir}}_{\sigma,\rm{loc}}\] 
+\end{lem}
+\end{color}
 \marginpar{check \cite{KLcosection}, probably needs the proper morphism to be surjective}

### 2018-01-05 draft_merged.tex
reviewed sec 1

@@
 We think that the algorithm proposed by Viscardi to prove the properness of his moduli spaces oversees a case.
-The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ is constant on a genus $1$ connected subcurve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $f'\colon \cC'_T\to\PP^r_T$, where $\cC'_0$ has a genus $1$ \emph{Gorenstein} singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
+The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ is constant on a genus $1$ connected subcurve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $\hat f\colon \hat \cC_T\to\PP^r_T$, where $\hat \cC_0$ has a genus $1$ \emph{Gorenstein} singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
 A counterexample is the following.
@@
 and hence the map is smoothable.
-Viscardi claims that the map factors through the family $\cC'_T$, obtained by contracting $E$ to a tacnode.
-Notice that the image of $f'$ would still be $D$, since there is at most one indeterminacy point of $\cC'_T\dashrightarrow\PP^r_T$, located at the singularity.
+Viscardi claims that the map factors through the family $\hat\cC_T$, obtained by contracting $E$ to a tacnode.
+Notice that the image of $\hat f$ would still be $D$, since there is at most one indeterminacy point of $\hat\cC_T\dashrightarrow\PP^r_T$, located at the singularity.
 However in our example $f$ cannot factor through the tacnode.
-Indeed in that case we would have a birational morphism between two singular curves with the same $\delta$ invariant and the same normalisation, so $f'\colon C'\to D$ would be an isomorphism, which is a contradiction.
+Indeed in that case we would have a birational morphism between two singular curves with the same $\delta$ invariant and the same normalisation, so $\hat f\colon \hat C\to D$ would be an isomorphism, which is a contradiction.
  We suggest that in this case the correct procedure would be to sprout $(R_1,q_1)$.
@@
  \begin{dfn}
- Let $C$ be a reduced curve over a field $k=\bar k$ and $p\in C$ a singular point.
-We define the \emph{genus of the singularity} in $p$ to be the quantity: \[g(p)=\delta(p)-b(p)+1,\] where $\delta(p)=\dim_k(\nu_*\OO_{\overline C}/\OO_C)\otimes k(p),$ $\nu\colon\overline{C}\to C$ is the normalisation of $C$ at $p$, and $b(p)$ is the number of branches of $C$ at $p.$
+ Let $C$ be a reduced curve over $\k$ and $p\in C$ a singular point.
+We define the \emph{genus of the singularity} in $p$ to be the quantity: \[g(p)=\delta(p)-b(p)+1,\] where $\delta(p)=\dim_{\k}(\nu_*\OO_{\overline C}/\OO_C)\otimes k(p),$ $\nu\colon\overline{C}\to C$ is the normalisation of $C$ at $p$, and $b(p)$ is the number of branches of $C$ at $p.$
  \end{dfn}
@@
  \begin{prop}\label{prop:smoothability2}
- Let $[f\colon C\to \PP^r]$ be a degenerate stable map from a genus $1$ curve $C=E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i$, where $E$ is the maximal connected arithmetic genus $1$ subcurve contracted by $f$, and $R_i$ are rational tails of positive degree.
+ Let $[f\colon C\to \PP^r]$ be a stable map from a genus $1$ curve $C=E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i$, where $E$ is the maximal genus $1$ subcurve contracted by $f$, and the $R_i$'s are rational tails on which $f$ has positive degree.
 
@@
 
-\begin{lem}(Classification of CM genus $1$ singularities)
-The Cohen-Macaulay (i.e. reduced) genus $1$ singularities with $m$ branches are obtained by gluing a genus $0$ singularity with $k$ branches together with a Smyth's $(m-k)$-elliptic fold.
+\begin{lem}(Classification of Cohen-Macaulay genus $1$ singularities)
+The CM (i.e. reduced) genus $1$ singularities with $m$ branches are obtained by gluing a genus $0$ singularity with $k$ branches together with a Smyth's $(m-k)$-elliptic fold.
 Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
@@
 We extend the argument given by Smyth \cite[Appendix~A]{SMY1} to classify the Goreinstein genus $1$ singularities.
-We study the analytic germ of the singularity, so we adopt Smyth's notation: $R$ denotes the completion of the local ring of $C$ at the singularity;
-$\widetilde{R}=k[[t_1]]\oplus\dots\oplus k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ is the maximal ideal of $R$  and $\mathfrak{m}_{\widetilde{R}}$ the one in $\widetilde{R}.$
-
-Let us recall that to describe $R$ as a quotient polynomial ring, it is enough to find a$k$-basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=(e_1,\ldots, e_s)$ where the $e_i$ are some elements in $\widetilde{R}.$ Indeed, once given such a basis, it is a consequence of completeness that $R$ can be recognized as $k[[x_1,\ldots, x_s]]/I$, where $I$ is the kernel of the ring homomorphism
+We study the analytic germ of the singularity and we adopt Smyth's notation: $R$ denotes the completion of the local ring of $C$ at the singularity;
+$\widetilde{R}=\k[[t_1]]\oplus\ldots\oplus \k[[t_m]]$ its integral closure; $\mathfrak{m}_R$ the maximal ideal of $R$  and $\mathfrak{m}_{\widetilde{R}}$ that of $\widetilde{R}.$
+
+Let us recall that to describe $R$ as a quotient polynomial ring, it is enough to find a $\k$-basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=\langle e_1,\ldots, e_s\rangle_{\k}$ where the $e_i$'s are some elements in $\widetilde{R}.$ Indeed, once given such a basis, it is a consequence of completeness that $R$ can be recognized as $\k[[x_1,\ldots, x_s]]/I$, where $I$ is the kernel of the ring homomorphism
 \begin{align*}\label{eq:singularity}
-k[[x_1,\ldots, x_s]]&\rightarrow R\subset k[[t_1]]\oplus\dots\oplus k[[t_m]]\\
+\k[[x_1,\ldots, x_s]]&\rightarrow R\subset \k[[t_1]]\oplus\ldots\oplus \k[[t_m]]\\
 \;\;x_i\;\; &\mapsto \;\; e_i\;\;
@@
 \begin{enumerate}
-\item $m=\delta(p)=\sum_{i\geq 0}\dim_k(\widetilde R/R)_i;$
-\item $1=g(p)=\sum_{i\geq 1}\dim_k(\widetilde R/R)_i;$
+\item $m=\delta(p)=\sum_{i\geq 0}\dim_\k(\widetilde R/R)_i;$
+\item $1=g(p)=\sum_{i\geq 1}\dim_\k(\widetilde R/R)_i;$
 \item if $(\widetilde R/R)_i=(\widetilde R/R)_j=0$ then $(\widetilde R/R)_{i+j}=0$.
 \end{enumerate}
-From (3) and (2) it follows that $\dim_k(\widetilde R/R)_1=1$ and $\dim_k(\widetilde R/R)_i=0$ for $i\geq 2$. Then the exact sequence:
+From (3) and (2) it follows that $\dim_\k(\widetilde R/R)_1=1$ and $\dim_\k(\widetilde R/R)_i=0$ for $i\geq 2$. Then the exact sequence:
 \[ 0\to \frac{\mathfrak m_{\widetilde R}^2}{\mathfrak m_{\widetilde R}^2\cap R}\to\frac{\mathfrak m_{\widetilde R}}{\mathfrak m_{\widetilde R}\cap R}\to (\widetilde R/R)_1\to 0\]
 entails that:
-\[\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak m_R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is a codimension $1$ $k$-subspace},\]
-After Gaussian elimination, the generators $e_1,\dots e_{m-1}$ of $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$ assume the following form:
+\[\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak m_R,\qquad \mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}\subseteq \mathfrak{m}_{\widetilde{R}}/\mathfrak{m}^2_{\widetilde{R}}\;\;\text{is a codimension $1$ $\k$-subspace}.\]
+Obviously $\mathfrak{m}^2_{R}\subseteq\mathfrak{m}^2_{\widetilde{R}}$.
+Hence $s$ is at least $m-1$.
+After relabelling we may assume $e_1,\dots e_{m-1}$ generate $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$, and after Gaussian elimination they take the following form:
 \begin{align*}
@@
  & \ldots \\
-e_{m-1} &= (0, 0,\ldots, t_{m-1}, a_{m-1}t_m).
+e_{m-1} &= (0, 0,\ldots, t_{m-1}, a_{m-1}t_m)
 \end{align*}
-with $a_{1}, \ldots, a_{m-1}\in k.$ At this point Smyth restricts his attention to Gorenstein singularities and shows that under this assumption he can choose all the $a_i$ to be $1$; furthermore if $m\geq 3$ it holds $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$, thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and the goal is reached.
-For $m=1,2$ he finds extra generators and show they satisfy the equation of a cusp (resp.
+with $a_{1}, \ldots, a_{m-1}\in \k.$ At this point Smyth restricts his attention to Gorenstein singularities and shows that under this assumption he can choose all the $a_i$ to be $1$; furthermore $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ holds if $m\geq 3$, thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and the goal is reached.
+For $m=1$ (resp.
+$2$) he finds extra generators and shows they satisfy the equation of a cusp (resp.
 a tacnode).
@@
 \item At least two of the $a_i$'s are non-zero, say $i=1,2$: then $a_1a_2t_m^2=e_1\cdot e_2$ so $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and we are done as above.
-It is easily seen that  $e_1,\dots e_{m-1}$ satisfy the equations of a $(k,m-k)$ singularity where $k$ is the number of $a_i$'s that are $0$.
-\item Only one of the $a_i$ is non-zero, say $a_1=1$: then $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}+(t_m^2)$ and by adjoining $e_m=t_m^2$ to the $e_i$'s we see that they generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and they satisfy the equation of a tacnode $(e_1^2-e_m)e_m=0$ and $e_ie_j=0$ for $i\neq j$ and $(i,j)\neq(1,m)$, so this is an $(m-2,2)$ singularity.
-\item Finally all the $a_i$ are zero: then we have to add $t_m^2,\ t_m^3$ to generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we obviously find an $(m-1,1)$ singularity.
+It is easily seen that  $e_1,\ldots, e_{m-1}$ satisfy the equations of a $(k,m-k)$ singularity where $k$ is the number of $a_i$'s that are zero.
+\item Only one of the $a_i$'s is non-zero, say $a_1=1$: then $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}+(t_m^2)$ and by adjoining $e_m=t_m^2$ to the $e_i$'s we see that they generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and they satisfy the equation of a tacnode $(e_1^2-e_m)e_m=0$ and $e_ie_j=0$ for $i\neq j$ and $(i,j)\neq(1,m)$, so this is an $(m-2,2)$ singularity.
+\item Finally all the $a_i$'s are zero: then we have to add $t_m^2,\ t_m^3$ to generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we obviously find an $(m-1,1)$ singularity.
 \end{enumerate}
 \noindent Similarly for $m=2$ there are two possibilities: the tacnode (corresponding to $a_1\neq 0$) and the union of a cusp with a non-coplanar line (for $a_1=0$), with equations:
-\[ k[[x,y,z]]/(xz,yz,y^2-x^3)\]
+\[ \k[[x,y,z]]/(xz,yz,y^2-x^3)\]
 \noindent For $m= 1$ the only possible singularity is the cusp: indeed it can be proven that $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$. 
@@
  The genus and number of branches are not sufficient to tell these singularities apart anymore, neither is the embedding dimension. A numerical invariant that distinguishes them is:
-\[ \dim_k R/I_p \]
+\[ \dim_\k R/I_p \]
 where 
@@
  is the conductor ideal at the singular point. 
- Using the explicit description of $\mathfrak{m}_R$ we gave in the classification Lemma we can easily understand the generators of $I_p$ and check that for a $(k,m-k)$ singularity  we have 
- \[ \dim_k R/I_p=m-k.\]
+ Using the explicit description of $R$ given in the lemma above, we can easily find generators of $I_p$ and check that for a $(k,m-k)$ singularity we have:
+ \[ \dim_\k R/I_p=m-k.\]
 \end{remark}
@@
 
- Then blow up the trace of $p_1,\dots p_k$ and $q_{k+1},\dots q_{m}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0$ to get families $\widetilde{\cC}^0\xrightarrow{\pi_0} {\cC}^0$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} {\cC}^1$ respectively.
+ Then perform a blow-up along the trace of $p_1,\dots p_k$ and $q_{k+1},\dots q_{m}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0$ to get families $\widetilde{\cC}^0\xrightarrow{\pi_0} {\cC}^0$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} {\cC}^1$ respectively.
 
@@
 Let $\hat{\cC}\to T$ the family of curves obtained by gluing $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$ (pushout).
-Then $\hat{\cC}$ has a nodal generic fiber which can clearly be further smoothed.
-
+Then $\hat{\cC}$ has a nodal generic fiber which clearly can be further smoothed.
 \end{proof}
@@
 \begin{claim}
- We can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$~\ref{rem:compatible_smoothing}.
+ We can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$. See Remark \ref{rem:compatible_smoothing} below
  \end{claim}
@@
 Pick a smoothing $\cC$ of $C$ such that after resolving the $A_n$ singularities at the nodes, i.e.
-when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal balanced genus one subcurve \cite[Proposition~2.11]{SMY1} contracted by $f^{\rm{ss}}$,
+when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal \emph{balanced} genus $1$ subcurve \cite[Proposition~2.11]{SMY1} contracted by $f^{\rm{ss}}$,
  then there are $m-k$ rational tails of positive degree directly adjacent to $E$ and the other $k$ rational tails are further away, possibly at different distances.
- Notice that $f^{\rm{ss}}$ is defined since $C^{\rm{ss}}$ differs from $C$ only for $-2$ curves.
-
- We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, namely
+ %Notice that $f^{\rm{ss}}$ is defined since $C^{\rm{ss}}$ differs from $C$ only for $-2$ curves.
+
+ We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, namely:
 \[\mathcal L=\omega_{\cC^{\rm{ss}}/T}\left( \sum_{F\subseteq E}(l+1-l(F,Z)F\right),\]
-whose 
-  resulting contraction $\bar{C}$ gives a $(m-k+h)$-fold point with $h\leq k$.
-Notice that $\bar{C}$ comes with a map $\rho$ to $\hat{C}$ and at this point use $\rho^*\hat{f}^*\OO_{\PP^r}(1)$ to perform the second contraction.
-If necessary, we add markings $p_1+\dots p_N=\Sigma$ on the degree $0$ rational components away from the genus $1$ singularity and on the degree $0$ branches of the $(m-k+h)$-fold which are not contracted by $\rho.$
-
-Since $\rho^*\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ has no $H^1$ it satisfies cohomology and base change.
-Then we can check  that the result of this second contraction is a $(k,m-k)$-singularity just looking at the vanishing orders of the sections of $\rho^*\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ on the central fiber $\bar{C}$ of the first contraction.
-These sections are constant on the degree 0 branches we did not mark and so  we conclude that the dependence relation among  the tangent vectors of the branches at the singular point of the second contraction only involve the $m-k$ rational tail image of the ones adjacent to $E$.
-
-Since $\hat{C}$ with the added markings $\Sigma$ is stable, the morphism $\cC^{\rm{ss}}\to\cC$ we just constructed factors through a morphism
-$\cC\to\hat{\cC}$ whose central fibers are $C$ and $\hat{C}$ and compatible with $f$ and $\hat{f}.$
+where $Z$ is the core, $l(\cdot,\cdot)$ is the distance function on the dual graph and $l$ is the maximum value attained by $l(\cdot,Z)$ on $E$.
+Let us call $\bar\cC$ the family of curves obtained from this contraction; notice that $f^{\rm{ss}}$ descends to a $\bar f\colon\bar\cC\to PP^r$.
+The central fiber $\bar{C}$ has an $(m-k+h)$-fold elliptic point with $h\leq k$, and it still has a contraction map $\rho$ to $\hat{C}$.
+
+If necessary we may add markings $p_1+\ldots+ p_N=\Sigma$ on all the $f$-contracted rational components away from the genus $1$ singularity, and on the branches of the $(m-k+h)$-fold that are not contracted by $\rho$.
+Now use $\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ to perform a second contraction.
+Since it has no $H^1$, it satisfies cohomology and base change, and we can check that the result of this second contraction is a $(k,m-k)$-singularity simply by looking at the vanishing orders of the sections on $\bar{C}$.
+%These sections are constant on the branches of the singularity to which we have not added any marking, so we conclude that the dependence relation among  the tangent vectors of the branches at the singular point of the second contraction only involve the $m-k$ rational tail image of the ones adjacent to $E$.
+
+%Since $\hat{C}$ with the added markings $\Sigma$ is stable, the morphism $\cC^{\rm{ss}}\to\cC$ we just constructed factors through a morphism
+%$\cC\to\hat{\cC}$ whose central fibers are $C$ and $\hat{C}$ and compatible with $f$ and $\hat{f}.$
 \end{proof}
@@
 In order to extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
-Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ .
-Once done this we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC\to\hat{\cC}\xrightarrow{\hat F}\PP^r$.
-
-Since all the curve we are considering are Cohen-Maculay, they have a dualising sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
+Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ \cite{Wang}.
+Once this is done we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC\to\hat{\cC}\xrightarrow{\hat F}\PP^r$.
+
+Since all the curves we are considering are Cohen-Maculay, they have a dualising sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
 \[H^1(\hat{C},\hat{L})=(H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}}))^{\vee}.\]
@@
 \begin{remark}\label{rem:compatible_smoothing}
-In general is not possible to find compatible smoothings: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar singularity with local equation $y^2-x^5=0$.
+In general is not possible to find compatible smoothings as above: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar singularity with local equation $y^2-x^5=0$.
 Then a compatible smoothing can be found only if the rational tail is attached to a Weierstrass point of the genus $2$ curve, as can be seen by computing the semi-stable model of the ramphoid cusp.
@@
 \begin{remark}
-The ideas above are similar to those employed in \cite[Theorem 4.5.1]{RSPW} to show that $\pazocal{VZ}_{1,n}(\PP^r,d)$ is smooth, where the latter is defined by requiring the factorisation property for the map through a Smyth's singularity after sprouting.
+The ideas above are similar to those employed in \cite[Theorem 4.5.1]{RSPW} to show that $\pazocal{V\!Z}_{1,n}(\PP^r,d)$ is smooth, where the latter is defined by requiring the factorisation property for the map through a Smyth's singularity after sprouting.
 \end{remark}

### 2018-01-06 draft_merged.tex
moved notation

@@
 
-\subsection*{Table of notations} We work over an algebraically closed field $\k$ of characteristic $0$.
-
-$T$ is the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
+\subsection*{Notations and conventions} We work over an algebraically closed field $\k$ of characteristic $0$.
+
+Throughout the paper we shall have fixed a homogeneous polynomial $\mathbf w\in\k[x_0,\ldots,x_4]_5$ of degree $5$ such that $X=V(\mathbf w)\subseteq\PP^4$ is a generic quintic threefold.
+Furthermore let us consider a fixed positive integer $d$ determining all the homology classes $d[\ell]\in A_1(\PP^4)$, line bundle weights, etc.
+that we shall take into account.
+
+Let $\MM_{1,n}$ denote the algebraic stack of prestable $n$-marked curves of arithmetic genus $1$.
+In the following definitions, by \emph{special point} we mean the preimage of a node or a marking in the normalisation.
+\begin{dfn}
+Let $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ be the stack of \emph{weighted-stable} curves of genus $1$ with $n$ markings and total weight $d$: every geometric point of $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ represents a connected reduced nodal projective curve of arithmetic genus $1$ with $n$ distinct smooth markings and an integer-valued function on the dual graph, such that it is compatible with specialisation maps and the sum of the values on all the vertices is $d$; furthermore we require that it takes nonnegative values, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
+\end{dfn}
+There is an \'{e}tale non-separated morphism $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.
+
+We shall denote by $\pi\colon \cC\to \MM_{1,n}$ the universal curve (and use similar notation for all its pullbacks).
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$ of $\cC\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ with universal line bundle $\mathcal{L}$.
+We shall often use shorthand notation $\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ and $\mathfrak P$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$.
+Let $\lambda$ denote the projection $\mathfrak P\to \MM$.
+
+\begin{dfn}
+Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective reduced connected $n$-marked curves of arithmetic genus $1$ that are weighted-stable with total weight $d$, i.e.
+the weight is nonnegative, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component  of weight $0$ has at least \emph{two} special points).
+\end{dfn}
+
+We shall denote by $\hat\pi\colon \hat\cC\to \MM_{1,n}(1)$ the universal curve (and use similar notation for all its pullbacks).
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$ of $\hat\cC\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ with universal line bundle $\hat{\mathcal{L}}$.
+We shall often use shorthand notation $\hat\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ and $\hat{\mathfrak P}$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$.
+Let $\hat\lambda$ denote the projection $\hat{\mathfrak P}\to \hat\MM$.
+
+$T$ shall often the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
 
@@
 curves.
-Let $\mathcal Z$ be an  Artin stack smooth over  $\cC$ such that the morphism to $\cC$ is representable and quasi- projective.
-For any $ S\to B$  the \emph{cone of section} of $\mathcal Z$ over $S$ is defined by:
- \[\mathfrak{S}(S)=\left\{\cC_S\;\text{morphisms}\; s\colon \cC_S\to\mathcal Z_S\right\};\]
- the arrow in $\mathfrak{S}(S)$ are defined in the obvious way.
- The groupoid $\mathfrak{S}$ is an algebraic stack \cite[Proposition~2.3]{CL}.
+Let $\mathcal Z$ be an algebraic stack smooth representable and quasi-projective over $\cC$.
+The \emph{cone of sections} of $\mathcal Z$ over $\cC$ is a $B$-stack $\mathfrak S$ defined by:
+ \[\mathfrak{S}(S\to B)=\left\{\text{sections of}\ \mathcal Z_S\to\cC_S\right\};\]
+
+ The groupoid $\mathfrak{S}$ is an algebraic stack representable and quasi-projective over $B$ \cite[Proposition~2.3]{CL}.
 
@@
 \ecd
-where $\mathfrak e$ denotes the tautological evaluation map. 
+where $\mathfrak e$ denotes the universal section. 
 Let us see some examples of the above construction we will be interested in.
 
- In the rest of the section we use the following notations:
-$\hM$ for $\MM_1^{(1)}$, $\hP$ for $\mathfrak{Pic}_{\hat\cC\to\hM}$ and $\lambda\colon\hM\to\hP$ for the canonical forgetful map.
-\subsubsection*{Sections of line bundles}
+\subsubsection*{Direct image cones}
 When $\mathcal Z=\rm{Vb}(\mathcal L),$ then the algebraic stack  $\mathfrak{G}\to B$ representing sections of $\mathcal L$,  can be described as   
@@
  This is essentially because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
-\subsubsection*{Moduli of stable maps and 1-stable maps} 
-Let $X\hookrightarrow \PP^n$ be a projective variety and 
-\[\mathcal Z_X=(\operatorname{Tot}(\mathcal{L}^{\oplus n+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^n} X\]
-where $\mathcal L_{\pP}$ is the universal line bundle on $\pP,$ induced from $f_{\oM_{1,n}(X,\beta)}^*\OO_{X}(1)$ via the natural map from the space of maps to the Picard.
-Then the moduli space of stable maps $\oM_{1,n}(X,\beta)$ is an open inside the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}.$ This is the point of view we already took for $X=\PP^n$ in  \S~\ref{sec:equations} to describe the equations of the moduli space of maps relative to $\MM^{\rm{div}}.$
+
+\subsubsection*{Moduli of stable maps and $1$-stable maps} 
+Let $X\hookrightarrow \PP^r$ be a projective variety and 
+\[\mathcal Z_X=(\operatorname{Tot}(\mathcal{L}^{\oplus r+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^r} X.\]
+Then the moduli space of stable maps $\oM_{1,n}(X,\beta)$ is an open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$: the morphism $\oM_{1,n}(X,\beta)\to \pP$ is given by the line bundle $f^*\OO_{\PP^r}(1)$ on the universal curve, that to $\mathfrak{S}_X$ by its sections $[s_0:\ldots:s_r]$, and the stability condition is open.
+This is the point of view we have already taken for $X=\PP^n$ in  \S~\ref{sec:equations}Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps relative to $\MM^{\rm{div}}$.
 
@@
 %and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$
-
-Let us start with some notation. In the following by \emph{special point} we mean the preimage of a node or a marking on the normalisation.
-\begin{dfn}
-Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ be the stack of \emph{prestable} (nodal and reduced), projective, connected, arithmetic genus one, $n$-marked curves that are \emph{stably weighted} with total weight $d$, i.e.
-for every geometric point of $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ there is an integer-valued function on the set of irreducible components of the corresponding curve, such that it is compatible with specialisation maps and the sum of the integers is $d$; furthermore we require that it takes nonnegative values, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
-\end{dfn}
-Remark that there is an \'{e}tale, non-separated morphism $\mathfrak M_{1,n}^{\operatorname{wt}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.
-
-\begin{dfn}
-Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective, reduced, connected, arithmetic genus one, $n$-marked curves that are stably weighted with total weight $d$, i.e.
-the weight is nonnegative, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component  of weight $0$ has at least \emph{two} special points).
-\end{dfn}
 

### 2018-01-07 draft_merged.tex
Update draft_merged.tex

@@
 \renewcommand{\L}{\mathcal L}
-\newcommand{\hL}{\hat{\mathcal L}}
+\newcommand{\hL}{\widehat{\mathcal L}}
 \newcommand{\C}{\mathfrak C}
 \newcommand{\cC}{\mathcal C}
+\newcommand{\hC}{\widehat{\mathcal C}}
 \newcommand{\Z}{\pazocal Z}
@@
 \newcommand{\pP}{\mathfrak P}
-\newcommand{\hP}{\hat{\mathfrak P}}
-\newcommand{\hM}{\hat{\mathfrak M}}
+\newcommand{\hP}{\widehat{\mathfrak P}}
+\newcommand{\hM}{\widehat{\mathfrak M}}
 \newcommand{\oM}{\overline{\pazocal M}}
@@
 
-We shall denote by $\hat\pi\colon \hat\cC\to \MM_{1,n}(1)$ the universal curve (and use similar notation for all its pullbacks).
-We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$ of $\hat\cC\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ with universal line bundle $\hat{\mathcal{L}}$.
-We shall often use shorthand notation $\hat\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ and $\hat{\mathfrak P}$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$.
-Let $\hat\lambda$ denote the projection $\hat{\mathfrak P}\to \hat\MM$.
+We shall denote by $\hat{\pi}\colon \widehat{\cC}\to \MM_{1,n}(1)$ the universal curve (and use similar notation for all its pullbacks).
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$ of $\widehat{\cC}\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ with universal line bundle $\widehat{\mathcal{L}}$.
+We shall often use shorthand notation $\widehat{\MM}$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ and $\widehat{\mathfrak P}$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$.
+Let $\hat{\lambda}$ denote the projection $\widehat{\mathfrak P}\to \widehat{\MM}$.
 
@@
 Let $X\hookrightarrow \PP^r$ be a projective variety and 
-\[\mathcal Z_X=(\operatorname{Tot}(\mathcal{L}^{\oplus r+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^r} X.\]
+\[\mathcal Z_X=(\operatorname{Vb}(\mathcal{L}^{\oplus r+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^r} X.\]
 Then the moduli space of stable maps $\oM_{1,n}(X,\beta)$ is an open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$: the morphism $\oM_{1,n}(X,\beta)\to \pP$ is given by the line bundle $f^*\OO_{\PP^r}(1)$ on the universal curve, that to $\mathfrak{S}_X$ by its sections $[s_0:\ldots:s_r]$, and the stability condition is open.
-This is the point of view we have already taken for $X=\PP^n$ in  \S~\ref{sec:equations}Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps relative to $\MM^{\rm{div}}$.
-
-Analogously, the moduli space of 1-stable maps, e.g. $\oM_1^{(1)}(\PP^n,d)$, can be thought as an open inside the moduli of sections of 
-\[\hat{\mathcal Z}=(\operatorname{Tot}(\hat{\mathcal{L}}^{\oplus n+1}_{\hP})-0_{\cC_{\hP}})\]
-over $\hat{\cC}_{\hP}.$
-
-\subsubsection*{Moduli space of 1-Stable Maps with fields}
- Denote with $\rm{M}$ the moduli space of 1-stable maps  $\oM_1^{(1)}(\PP^4,d)$ and we write $\mathcal P_{\rm M}=\L_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}.$ 
- Moreover,
- $(\hat\pi_{\rm M},f_{\rm M})\colon \hat\cC_{\rm M}\to \rm M\times \PP^4$ are the universal $1$-stable curve and map over it.
-We define the moduli space of $p$-fields as the cone of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$.
+This is the point of view we have already taken for $X=\PP^n$ in Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps relative to $\MM^{\rm{div}}$.
+
+Analogously, the moduli space of 1-stable maps $\oM_1^{(1)}(\PP^n,d)$ can be thought of as an open inside the moduli space of sections of 
+\[\widehat{\mathcal Z}_X=(\operatorname{Vb}(\widehat{\mathcal{L}}^{\oplus r+1}_{\hP})-0_{\widehat{\cC}})\]
+over $\widehat{\cC}_{\hP}.$
+
+\subsubsection*{Moduli of $1$-stable maps with fields}
+ For this section denote by $\rm{M}$ the moduli space of $1$-stable maps $\oM_1^{(1)}(\PP^4,d)$ and by $\widehat{\mathcal P}_{\rm M}=\hL_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}.$ 
+ As usual let
+ $(\hat\pi_{\rm M},\hat f_{\rm M})\colon \hC_{\rm M}\to \rm M\times \PP^4$ be the universal $1$-stable curve and map.
+The moduli space of $p$-fields is defined as the cone of sections of the line bundle $\widehat{\mathcal P}_{\rm M}$ over $\hC_{\rm M}$.
 
 \begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\mathcal P_{\rm M}))\] parametrises $1$-stable maps
- \bcd
- \hat\cC_S\ar[r,"f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
+ The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\widehat{\mathcal P}_{\rm M}))\] parametrises $1$-stable maps
+ \bcd
+ \hat\cC_S\ar[r,"\hat f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
  S &
  \ecd
- with a $p$-field $\hat\psi\in H^0(\hat\cC_S,f_{S}^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_{S}})$.
+ with a $p$-field $\hat\psi\in H^0(\hC_S,\hat f_{S}^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_{S}})$.
 \end{dfn}
 
-We  abbreviate $\pazocal P:=\Mone{1}{\PP^4}{d}^p$. 
-This should be thought of as the space of sections of the line bundle $\mathcal P_{\rm M}$ over $\hat\cC_{\rm M}$:
-
-Otherwise, in parallel with the above description on the moduli space of 1-stable maps,  $\pazocal P$ can be thought as a (open in a) moduli space of sections of the bundle $\rm{Vb}(\hat{\mathcal L}_{\hP}^{\oplus 5}\oplus \mathcal P_{\hP}).
+We abbreviate $\widehat{\pazocal P}:=\Mone{1}{\PP^4}{d}^p$.
+Employing the above description of the moduli space of $1$-stable maps,  $\pazocal P$ can also be thought as an open in the moduli space of sections of the vector bundle $\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus \widehat{\mathcal P}_{\hP}).
 $

### 2018-01-08 draft_merged.tex
sec 2 omogeneizzata nella notazione

@@
 \newcommand{\hM}{\widehat{\mathfrak M}}
+\newcommand{\hrM}{\widehat{\rm{M}}}
 \newcommand{\oM}{\overline{\pazocal M}}
@@
 \newcommand{\w}{\mathbf{w}}
-\newcommand{\PtoM}{\rho}
+\newcommand{\PtoM}{\lambda}
 \newcommand{\vir}[1]{[#1]^{\rm{vir}}}
 \newcommand{\virloc}[1]{[#1]^{\rm{vir}}_{\rm{loc}}}
+\newcommand{\dvr}{\Delta}
 
@@
 \newcommand{\Isom}{\text{Isom}}
-\newcommand{\Spec}{\operatorname{Spec}}
+\newcommand{\Spec}{\underline{\operatorname{Spec}}}
 \newcommand{\Proj}{\operatorname{Proj}}
@@
 
+Let $\rm{M}:=\M{1}{n}{X}{\beta}$ denote the moduli stack of $n$-pointed genus $1$ stable maps to $X$ in the homology class $\beta$, with universal curve and stable map $(\pi,f)\colon\cC_{\rm M}\to \rm M\times X$.
+Similarly let $\hrM:=\oM_{1,n}^{(1)}(X,\beta)$ denote the moduli stack of $1$-stable maps to $X$, with universal curve and stable map $(\hat\pi,\hat f)\colon\hC_{\hrM}\to \hrM\times X$.
+
 Let $\MM_{1,n}$ denote the algebraic stack of prestable $n$-marked curves of arithmetic genus $1$.
@@
 We shall often use shorthand notation $\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ and $\mathfrak P$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$.
-Let $\lambda$ denote the projection $\mathfrak P\to \MM$.
+Let $\PtoM$ denote the projection $\mathfrak P\to \MM$.
 
@@
 We shall often use shorthand notation $\widehat{\MM}$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ and $\widehat{\mathfrak P}$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$.
-Let $\hat{\lambda}$ denote the projection $\widehat{\mathfrak P}\to \widehat{\MM}$.
-
-$T$ shall often the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
+Let $\hat{\PtoM}$ denote the projection $\widehat{\mathfrak P}\to \widehat{\MM}$.
+
+$\dvr$ shall always denote the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
 
@@
 and hence the map is smoothable.
-Viscardi claims that the map factors through the family $\hat\cC_T$, obtained by contracting $E$ to a tacnode.
-Notice that the image of $\hat f$ would still be $D$, since there is at most one indeterminacy point of $\hat\cC_T\dashrightarrow\PP^r_T$, located at the singularity.
+Viscardi claims that the map factors through the family $\hC_T$, obtained by contracting $E$ to a tacnode.
+Notice that the image of $\hat f$ would still be $D$, since there is at most one indeterminacy point of $\hC_T\dashrightarrow\PP^r_T$, located at the singularity.
 However in our example $f$ cannot factor through the tacnode.
@@
 \begin{claim}
- We can produce smoothings $\cC$ of $C$ and $\hat\cC$ of $\hat C$ with a contraction map $\cC\to\hat\cC$ compatible with the given $C\to\hat C$. See Remark \ref{rem:compatible_smoothing} below
+ We can produce smoothings $\cC$ of $C$ and $\hC$ of $\hat C$ with a contraction map $\cC\to\hC$ compatible with the given $C\to\hat C$. See Remark \ref{rem:compatible_smoothing} below
  \end{claim}
@@
 
-\section{From $p$-fields to the quintic three-fold}
-We introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, we endow it with a $0$-dimensional virtual class and show that its degree coincides with the genus $1$ cuspidal invariants of the quintic three-fold $X$ up to a sign.
-This is a word-by-word repetition of the arguments in \cite{CLpfields} once noticed that they carry over to the situation where we work over a family of Gorenstein (not necessarily nodal) curves.
-Our aim in this section is to improve the legibility of our paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it could otherwise be skipped.
+\section{From $p$-fields to the quintic threefold}
+We introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, we endow it with a cosection-localised $0$-dimensional virtual class supported on a proper substack (depending on the polynomial $\w$), and we show that its degree coincides with the genus $1$ cuspidal invariants of the quintic threefold $X$ up to a sign.
+This is a word-by-word repetition of the arguments in \cite{CLpfields} once noticed that they carry over to the situation where we work with a family of Gorenstein (not necessarily nodal) curves.
+Our aim in this section is to improve the legibility of this paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it can otherwise be skipped.
 \subsection{Moduli of sections}
@@
 \end{dfn}
- To fix notation, let us write down the following diagram
+ To fix the notation let us draw the following diagram:
  \bcd
@@
 \subsubsection*{Direct image cones}
-When $\mathcal Z=\rm{Vb}(\mathcal L),$ then the algebraic stack  $\mathfrak{G}\to B$ representing sections of $\mathcal L$,  can be described as   
+When $\mathcal Z=\rm{Vb}(\mathcal L)$ for a line bundle $\mathcal L$ on $\cC$, the algebraic stack  $\mathfrak{S}\to B$ representing sections of $\mathcal L$ can be constructed as:   
 \[C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L).\]
- This is essentially because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has the desired modular interpretation by Serre duality.
+ This is essentially because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has got the desired modular interpretation by Serre duality.
 
 \subsubsection*{Moduli of stable maps and $1$-stable maps} 
-Let $X\hookrightarrow \PP^r$ be a projective variety and 
-\[\mathcal Z_X=(\operatorname{Vb}(\mathcal{L}^{\oplus r+1}_{\pP})-0_{\cC_{\pP}})\times_{\PP^r} X.\]
-Then the moduli space of stable maps $\oM_{1,n}(X,\beta)$ is an open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$: the morphism $\oM_{1,n}(X,\beta)\to \pP$ is given by the line bundle $f^*\OO_{\PP^r}(1)$ on the universal curve, that to $\mathfrak{S}_X$ by its sections $[s_0:\ldots:s_r]$, and the stability condition is open.
-This is the point of view we have already taken for $X=\PP^n$ in Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps relative to $\MM^{\rm{div}}$.
-
-Analogously, the moduli space of 1-stable maps $\oM_1^{(1)}(\PP^n,d)$ can be thought of as an open inside the moduli space of sections of 
-\[\widehat{\mathcal Z}_X=(\operatorname{Vb}(\widehat{\mathcal{L}}^{\oplus r+1}_{\hP})-0_{\widehat{\cC}})\]
+Let $X\subseteq \PP^r$ be a projective variety and let $\mathcal Z_X$ be defined by the following cartesian diagram over $\cC$:
+\bcd
+\mathcal Z_X\ar[r,"/\Gm"]\ar[d,hook]\ar[dr,phantom,"\Box"] & X\times \cC\ar[d,hook] \\
+\mathcal L^{\oplus r+1}\setminus 0_{\cC}\ar[r,"/\Gm"] & \PP^r\times\cC
+\ecd
+Then $\oM_1(X,\beta)$, the moduli space of stable maps to $X$, is an open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$: the morphism $\oM_1(X,\beta)\to \pP$ is given by the line bundle $f^*\OO_{\PP^r}(1)$ on the universal curve over $\oM_1(X,\beta)$, that to $\mathfrak{S}_X$ by its sections $[s_0:\ldots:s_r]$ corresponding to the universal stable map $f$, and the stability condition is an open one.
+This is the point of view we have already taken for $X=\PP^n$ in Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps.
+
+Analogously the moduli space of $1$-stable maps $\oM_1^{(1)}(X,\beta)$ can be thought of as an open inside the moduli space of sections of 
+\[\widehat{\mathcal Z}_X=(\operatorname{Vb}(\widehat{\mathcal{L}}^{\oplus r+1}_{\hP})\setminus 0_{\widehat{\cC}})\times_{\PP^r} X\]
 over $\widehat{\cC}_{\hP}.$
 
-\subsubsection*{Moduli of $1$-stable maps with fields}
- For this section denote by $\rm{M}$ the moduli space of $1$-stable maps $\oM_1^{(1)}(\PP^4,d)$ and by $\widehat{\mathcal P}_{\rm M}=\hL_{\rm M}^{\otimes -5}\otimes\omega_{\hat\pi_{\rm M}}.$ 
- As usual let
- $(\hat\pi_{\rm M},\hat f_{\rm M})\colon \hC_{\rm M}\to \rm M\times \PP^4$ be the universal $1$-stable curve and map.
-The moduli space of $p$-fields is defined as the cone of sections of the line bundle $\widehat{\mathcal P}_{\rm M}$ over $\hC_{\rm M}$.
+\subsubsection*{Moduli of $1$-stable maps with $p$-fields}
+ In this section we denote by $\hrM$ the moduli space of $1$-stable maps $\oM_1^{(1)}(\PP^4,d)$ and by $\widehat{\mathcal P}_{\hrM}=\hL_{\hrM}^{\otimes -5}\otimes\omega_{\hat\pi_{\hrM}}.$
+
+The moduli space of $p$-fields is defined as the cone of sections of the line bundle $\widehat{\mathcal P}_{\hrM}$ over $\hC_{\hrM}$.
 
 \begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\rm M,*}(\widehat{\mathcal P}_{\rm M}))\] parametrises $1$-stable maps
- \bcd
- \hat\cC_S\ar[r,"\hat f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
+ The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\hrM,*}(\widehat{\mathcal P}_{\hrM}))\] parametrises $1$-stable maps
+ \bcd
+ \hC_S\ar[r,"\hat f_S"]\ar[d,"\hat\pi_S"] & \PP^4 \\
  S &
@@
 We abbreviate $\widehat{\pazocal P}:=\Mone{1}{\PP^4}{d}^p$.
-Employing the above description of the moduli space of $1$-stable maps,  $\pazocal P$ can also be thought as an open in the moduli space of sections of the vector bundle $\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus \widehat{\mathcal P}_{\hP}).
+Employing the above description of the moduli space of $1$-stable maps,  $\widehat{\pazocal P}$ can also be thought as an open in the moduli space of sections of the vector bundle $\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus \widehat{\mathcal P}_{\hP}).
 $
@@
 %& \rm{Vb}(\mathcal P_{\rm M})\ar[d] \\
-%\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
+%\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hC_{\rm M}\ar[d,"\hat\pi_{\rm M}"] \\
 %\pazocal P \ar[r,"\PtoM"] & \rm M
@@
 \subsection{Obstruction theories}
-In the notation of the previous section,
- the morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
+Sticking to the same notation as above, the morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
 \[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\mathcal Z/\cC}\]
-The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}, and it is enough to notice that it relies on general properties of obstruction theories and the cotangent complex and the fact that $\mathcal Z\to\cC$ is smooth,
-but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves, to conclude that the same results apply when the fibers of $\cC\to B$ are l.c.i curves.
-
-In the examples considered above we get:
- in the case of a line bundle we recover $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$;
-%The construction for a general smooth $\pazocal Z$ is way more flexible.
-
-in the case of the moduli space $\rm{M}=\oM_1^{(1)}(\PP^4,d)$ we get an obstruction theory relative to  $\hP$ given by $ \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$;
-
-in the case of 1- stable maps with fields $\pazocal P$ we get $\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}).$
-
-On the moduli space of 1-stable map we have another natural perfect obstruction theory relative to $\hM,$ which is the standard one defined by Behrend-Fantechi \cite[Proposition 6.3]{BF}.
-The next result explain how to compare the two.
+The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}.
+We notice at this point that this results applies as well when the fibers of $\cC\to B$ are l.c.i curves, since the proof relies on general properties of obstruction theories and the cotangent complex and the fact that $\mathcal Z\to\cC$ is smooth,
+but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
+
+Let us review the examples above:
+\begin{itemize}
+ \item for the direct image cone of a line bundle $\mathcal L$ the dual obstruction theory is $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$;
+ \item the moduli space $\hrM=\oM_1^{(1)}(\PP^4,d)$ has a dual obstruction theory relative to $\hP$ given by $ \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})$;
+ \item in the case of $1$-stable maps with $p$-fields $\widehat{\pazocal P}=\oM_1^{(1)}(\PP^4,d)^p$ we get $\mathbb E_{\widehat{\pazocal P}/\hP}=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}}).$
+\end{itemize}
+
+There is a different obstruction theory on the moduli space of $1$-stable maps relative to $\hM$, which is the one introduced by Behrend and Fantechi for spaces of morphisms \cite[Proposition 6.3]{BF}.
+The two obstruction theories are compatible.
 \begin{lem}
@@
  \bcd
- \lambda^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\rm M/\hP} \ar[r]\ar[d] &  \mathbb T_{\rm M/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
- \R^\bullet\hat\pi_{\rm M,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})\ar[r] & \R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
- \ecd
- implying that $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\rm M$.
+ \hat\PtoM^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\hrM/\hP} \ar[r]\ar[d] &  \mathbb T_{\hrM/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\hrM,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(f_{\hrM}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \ecd
+ implying that $\mathbb T_{\hrM/\hP}\to \mathbb E_{\hrM/\hP}:=\R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \mathcal L_{\hrM})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\hrM$.
 \end{lem}
 \begin{proof}
- The first statement follows from deformation theory: the projection $\lambda\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
-
- The fact that $\mathbb T_{\rm M/\hM}\to \mathbb E_{\rm M/\hM}:=\R^\bullet\hat\pi_{\rm M,*}(f_{\rm M}^* T_{\PP^4})$ is a perfect obstruction theory when $\hat\cC\to\rm M$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
+ The first statement follows from deformation theory: the projection $\hat\PtoM\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+
+ The fact that $\mathbb T_{\hrM/\hM}\to \mathbb E_{\hrM/\hM}:=\R^\bullet\hat\pi_{\hrM,*}(f_{\hrM}^* T_{\PP^4})$ is a perfect obstruction theory when $\hC\to\hrM$ is a family of Gorenstein curves is proved in \cite[Proposition 6.3]{BF}.
 
@@
 
- Finally, the fact that  $\mathbb T_{\rm M/\hP}\to \mathbb E_{\rm M/\hP}:=\R^\bullet\hat\pi_{\rm M,*}(\bigoplus_0^4 \mathcal L_{\rm M})$ gives the standard virtual class for the moduli space of maps follows from functoriality of virtual pullback \cite{Manolache-pullback}.
+ Finally the fact that  $\mathbb T_{\hrM/\hP}\to \mathbb E_{\hrM/\hP}:=\R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \mathcal L_{\hrM})$ gives the standard virtual class for the moduli space of maps follows from functoriality of virtual pullbacks \cite{Manolache-pullback}.
 \end{proof}
-Finally notice that the relative perfect obstruction theory for $\pazocal P$ fits in the following exact triangle:
+
+Next consider the moduli space of $1$-stable maps with $p$-fields $\widehat{\pazocal P}$.
 \begin{lem}
- There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P}),\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}))\] for the triangle:
- \bcd
- \pazocal P\ar[rr,"\PtoM"]\ar[dr] & & \rm M\ar[dl] \\
+ There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal P_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}\oplus\mathcal P_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}))\] for the triangle:
+ \bcd
+ \widehat{\pazocal P}\ar[rr,"\hat\PtoM"]\ar[dr] & & \hrM\ar[dl] \\
  & \hP &
@@
 \end{lem}
-This follows from the general theory of moduli spaces of sections recalled above.
-
-Notice that the virtual rank of $\mathbb E_{\pazocal P/\hP}:=\R^\bullet\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0.$ In the next section we show that this cycles is actually supported on the proper sub-stack $\Mone{1}{X}{d}$ where
- $X=V(\w)\subseteq\PP^4$ is the smooth quintic three-fold defined by a homogeneous polynomial
- $\w\in k[x_0,\ldots,x_4]_5.$
+\noindent This follows from the general theory of moduli of sections recalled above.
+
+\smallskip
+
+Notice that the virtual rank of $\mathbb E_{\widehat{\pazocal P}/\hP}:=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}\oplus\mathcal P_{\widehat{\pazocal P}})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
+However $\widehat{\pazocal P}$ is not proper.
+In the next section we describe Chang-Li's cosection (depending on the choice of $\w\in\k[x_0,\ldots,x_4]_5$) of the obstruction bundle, and show that the corresponding localised cycle is supported on the proper subtack $\Mone{1}{X}{d}$ where $X=V(\w)$ is the quintic threefold, that is the degeneracy locus of the cosection.
 
@@
 In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the
-\subsection{Cosection Localization}
-We show the existence of a cosection of the obstruction bundle whose degeneracy locus is the proper substack $\Mone{1}{X}{d}.$ The machinery of cosection localised virtual classes \cite{KLcosection}.
-Recall their Theorem 1.1:
+\subsection{Cosection localisation}
+Recall Kiem-Li's machinery of cosection localised virtual classes \cite[Theorem 1.1]{KLcosection}:
 
@@
 Then $(\pazocal{M},\sigma)$ has a localized virtual cycle
-$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).
-$$
+$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).$$
 This cycle enjoys the usual properties of the virtual cycles; it relates to
@@
 
-We are now going to construct the cosection as in \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by tensoring of line bundles:
-\[ h_1\colon\rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal P_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
+We are going to construct the cosection paralleling \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by iterated tensoring of line bundles:
+\[ h_1\colon\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus\widehat{\mathcal P}_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
 By differentiating it and pulling it back along the universal evaluation
 \bcd
-& \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal P_{\hP})\ar[d] \\
-\hat \cC_{\pazocal P}\ar[ur,bend left,"\mathfrak e"]\ar[d,"\hat\pi_{\pazocal P}"]\ar[r] & \hat\cC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
-\pazocal P \ar[r] & \rm \hP
+& \rm{Vb}(\hL_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\widehat{\mathcal P}_{\hP})\ar[d] \\
+\hC_{\widehat{\pazocal P}}\ar[ru,bend left,start anchor=north, end anchor=west,"\mathfrak e"]\ar[d,"\hat\pi_{\widehat{\pazocal P}}"]\ar[r] & \hC_{\hP}\ar[d,"\hat\pi_{\hP}"] \\
+\widehat{\pazocal P} \ar[r] & \rm \hP
 \ecd
@@
  \begin{split}
- \sigma_1\colon\rm{Ob}_{\pazocal P/\hP}=\R^1\hat\pi_{\pazocal P,*}(\mathcal L_{\pazocal P}^{\oplus 5}\oplus\mathcal P_{\pazocal P})\to \R^1\hat\pi_{\pazocal P,*}(\omega_{\hat\pi_{\pazocal P}})\simeq \OO_{\pazocal P} \\
+ \sigma_1\colon\rm{Ob}_{\widehat{\pazocal P}/\hP}=\R^1\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}})\to \R^1\hat\pi_{\widehat{\pazocal P},*}(\omega_{\hat\pi_{\widehat{\pazocal P}}})\simeq \OO_{\widehat{\pazocal P}} \\
  \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
@@
 
-The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$, but then $\psi=0$ by smoothness of $\w$.
-
-Moreover, Chang-Li prove that
-$\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\pazocal P}\to\OO_{\pazocal P}$ with the same degeneracy locus.\marginpar{Why is this needed}
+The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$.
+But $\w(u)=0$ and $\partial_i\w(u)=0$ never happen simultaneously by smoothness of $X$, so it has to be $\psi=0$.
+
+Moreover Chang and Li prove that $\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\widehat{\pazocal P}}\to\OO_{\widehat{\pazocal P}}$ with the same degeneracy locus.
+This is a technical expedient to show that the relative intrinsic normal cone is contained in the closed substack of the obstruction bundle determined by the cosection.
 
 We may thus endow $\Mone{1}{\PP^4}{d}^p$ with a localised virtual cycle:
-\[[\pazocal P]^{\rm{vir}}_{\sigma_1}=0^{!}_{\sigma_1,\rm{loc}}[\mathfrak{C}_{\pazocal P/\hP}]\;\in\; A_0(\Mone{1}{X}{d}).\]
-
-We we want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
+\[\virloc{\widehat{\pazocal P}}=0^{!}_{\sigma_1,\rm{loc}}[\mathfrak{C}_{\widehat{\pazocal P}/\hP}]\;\in\; A_0\left(\Mone{1}{X}{d}\right).\]
+
+We want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
 \begin{thm}
@@
 \subsection{Sketch of the proof}
-This is done in two steps: first we compare the invariants coming from $\Mone{1}{\PP^4}{d}^p$ with the ones coming from $\Mone{1}{N_{X/\PP^4}}{d}^p$, where $N_{X/\PP^4}$ is the normal of the quintic in $\PP^4.$
+This is achieved in two steps: we first compare the invariants of $\Mone{1}{\PP^4}{d}^p$ with the ones coming from $\Mone{1}{N_{X/\PP^4}}{d}^p$, where $N_{X/\PP^4}$ is the normal bundle of the quintic in $\PP^4.$
 
@@
 \subsubsection*{Step~1}
-This is achieved in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}.$
-The idea is: construct a perfect obstruction theory for $\Mone{1}{V}{d}^p$ relative to $\hP$ which is compatible with the obstruction theories of the fibers $\Mone{1}{V_t}{d}^p;$ then construct a family version of the cosection and the fact that for compatible obstruction theories taking cosection localized cycles commutes with Gysin pull-back to conclude this Step.
+This is attained in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}.$
+%The idea is: construct a perfect obstruction theory for $\Mone{1}{V}{d}^p$ relative to $\hP$ which is compatible with the obstruction theories of the fibers $\Mone{1}{V_t}{d}^p;$ then construct a family version of the cosection and the fact that for compatible obstruction theories taking cosection localized cycles commutes with Gysin pull-back to conclude this Step.
 
@@
 \end{lem}
-This is just a computation in local coordinates.
-This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\mathcal Z'$ over $\hat\cC_{\hP\times\Aaff^1}$:
+%This is just a computation in local coordinates.
+This allows a description of the moduli space of maps to $V$ as the cone of sections of a certain smooth object $\mathcal Z'$ over $\hC_{\hP\times\Aaff^1}$:
 
@@
 & \rm{Vb}(\mathcal L_{\hP}^{\oplus 5})\setminus\{0\}\oplus\rm{Vb}(\mathcal L^{\otimes 5}_{\hP})\ar[d] \ar[r] & \rm{Vb}(\OO_{\PP^4}(5))\times\Aaff^1_t\\
-\hat \cC_{\oM_1^{(1)}(V)}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat{\pi}_{\oM_1^{(1)}(V)}"]\ar[r] & \hat\cC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
+\hC_{\oM_1^{(1)}(V)}\ar[uur,bend left,"\mathfrak e"]\ar[d,"\hat{\pi}_{\oM_1^{(1)}(V)}"]\ar[r] & \hC_{\hP\times\Aaff^1_t}\ar[d,"\hat\pi_{\hP\times\Aaff^1_t}"] & \\
 \Mone{1}{V}{(d,0)} \ar[r] & \rm \hP\times\Aaff^1_t &
@@
 
-Similarly $\pazocal V:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\mathcal Z:=\mathcal Z'\oplus\rm{Vb}(\mathcal P_{\hP})$.
-The general theory explained above provides an obstruction theory for $\pazocal V\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
+Similarly $\widehat{\pazocal V}:=\Mone{1}{V}{(d,0)}^p$ can be defined as the cone of sections of $\mathcal Z:=\mathcal Z'\oplus\rm{Vb}(\widehat{\mathcal P}_{\hP})$.
+The general theory explained above provides an obstruction theory for $\widehat{\pazocal V}\to\hP\times\Aaff^1_t$ \cite[Proposition 4.2]{CLpfields}:
 
 \begin{lem}
- A dual perfect obstruction theory is given by 
- \[\phi_{\pazocal V/\hP\times\Aaff^1_t}\colon\mathbb T_{\pazocal V/\hP\times\Aaff^1_t}\to\mathbb E_{\pazocal V/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal H\oplus\mathcal P_{\pazocal V})\] where $f_{\pazocal V}\colon \hat\cC_{\pazocal V}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0\]
- The restriction of $\phi_{\pazocal V/\hP\times\Aaff^1_t}$ to a fiber
- \[
- \pazocal V_t=\left\{\begin{array}{lr} \pazocal P & t\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & t=0 \end{array}\right.
-\] gives the standard obstruction theory of $\pazocal V_t\to\hP$.
+ A dual perfect obstruction theory is given by:
+ \[\phi_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}\colon\mathbb T_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}\to\mathbb E_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\widehat{\pazocal V}}(f_{\widehat{\pazocal V}}^*\mathcal H\oplus\widehat{\mathcal P}_{\widehat{\pazocal V}})\]
+ where $f_{\widehat{\pazocal V}}\colon \hC_{\widehat{\pazocal V}}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by the exact sequence:
+ \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0.\]
+The restriction of $\phi_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}$ to a fiber
+ \[
+ \widehat{\pazocal V}_c=\left\{\begin{array}{lr} \widehat{\pazocal P} & c\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & c=0 \end{array}\right.
+\]
+gives the standard obstruction theory of $\widehat{\pazocal V}_c\to\hP$.
 \end{lem}
@@
 \bcd
-\pazocal V_t\ar[rr,hook,"\iota_t"]\ar[dr] & & \pazocal V \ar[dl] \\
+\widehat{\pazocal V}_t\ar[rr,hook,"\iota_t"]\ar[dr] & & \widehat{\pazocal V} \ar[dl] \\
 & \hP &
 \ecd
-The cone of sections interpretation provides us with an obstruction theory relative to $\pazocal V\to \hP$ given by:
-\[
- \mathbb E'_{\pazocal V/\hP}:=\R^\bullet\hat\pi_{\pazocal V}(f_{\pazocal V}^*\mathcal K\oplus\mathcal P_{\pazocal V})
+The cone of sections interpretation provides us with an obstruction theory relative to $\widehat{\pazocal V}\to \hP$ given by:
+\[
+ \mathbb E'_{\widehat{\pazocal V}/\hP}:=\R^\bullet\hat\pi_{\widehat{\pazocal V}}(f_{\widehat{\pazocal V}}^*\mathcal K\oplus\widehat{\mathcal P}_{\widehat{\pazocal V}})
 \]
@@
 \]
-Of course $h^0(\mathbb E'_{\pazocal V/\hP})\simeq\mathbb T_{\pazocal V/\hP}$, but the previous lemma hints at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\pazocal V/\hP})$ contains one factor $\R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}$ too many, so that restricting to the fibers we would find a different obstruction theory with respect to the standard one.
-A confirmation of this fact is that $\mathbb E'_{\pazocal V/\hP}$ equips $\pazocal V$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber, i.e.
-applying $\iota_t^!,$ we get $[\pazocal V_t]^{\rm{vir}}\in A_0(\pazocal V_t)$.
-
-This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the obstruction theory to 
-\[\phi_{\pazocal V/\hP}\colon\mathbb T_{\pazocal V/\hP}\to\mathbb E_{\pazocal V/\hP},\]
- where the latter fits into an exact triangle:
-\[ \R^1\hat\pi_{\pazocal V,*}\OO_{\hat\cC_{\pazocal V}}[-2]\to\mathbb E_{\pazocal V/\hP}\xrightarrow{\nu}\mathbb E_{\pazocal V/\hP}\xrightarrow{[1]}.\]
-Furthermore the lifted obstruction theory is compatible with the one the fibers, 
+Of course $h^0(\mathbb E'_{\widehat{\pazocal V}/\hP})\simeq\mathbb T_{\widehat{\pazocal V}/\hP}$, but the previous lemma and the difference between $\mathcal H$ and $\mathcal K$ hint at the fact that the obstruction sheaf $h^1 (\mathbb E'_{\widehat{\pazocal V}/\hP})$ contains one factor $\R^1\hat\pi_{\widehat{\pazocal V},*}\OO_{\hC_{\widehat{\pazocal V}}}\simeq \OO_{\widehat{\pazocal V}}$ too many, so that restricting $\mathbb E'_{\widehat{\pazocal V}/\hP}$ to the fibers we would not find their standard obstruction theory.
+A confirmation of this fact is given by observing that $\mathbb E'_{\widehat{\pazocal V}/\hP}$ equips $\widehat{\pazocal V}$ with a $0$-dimensional cycle, while we are looking for a $1$-dimensional cycle such that restricting to any fiber, i.e.
+applying $\iota_t^!,$ we get $[\widehat{\pazocal V}_t]^{\rm{vir}}\in A_0(\widehat{\pazocal V}_t)$.
+
+This issue is solved in \cite[\S\S4.5-6]{CLpfields} by lifting the standard obstruction theory $\phi'_{\widehat{\pazocal V}/\hP}$ to a different, specifically tailored one: 
+\[\phi_{\widehat{\pazocal V}/\hP}\colon\mathbb T_{\widehat{\pazocal V}/\hP}\to\mathbb E_{\widehat{\pazocal V}/\hP},\]
+ where the latter two-term complex fits into an exact triangle:
+\[ \R^1\hat\pi_{\widehat{\pazocal V},*}\OO_{\hC_{\widehat{\pazocal V}}}[-2]\to\mathbb E_{\widehat{\pazocal V}/\hP}\xrightarrow{\nu}\mathbb E'_{\widehat{\pazocal V}/\hP}\xrightarrow{[1]}\]
+Furthermore the lifted obstruction theory is compatible with the standard one for the fibers.
 \begin{lem}
-There is the following commutative diagram of exact triangles:
-\bcd
-\hat{\pi}_{\pazocal V_c *}\OO_{\hat\cC_{\pazocal V_c}}[-1]\ar[r] & \mathbb E_{\pazocal V_c/\hP} \ar[r] &\mathbb E_{\pazocal V/\hP}\rvert_{\pazocal V_c}\\
-\mathbb{T}^{\geq 1}_{\pazocal V_c/\pazocal V}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\pazocal V_c/\hP}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\pazocal V/\hP}\rvert_{\pazocal V_c} \ar[u]
-\ecd
-\end{lem}
-The proof is exactly the same given in \cite[\S~4.6]{CL}.
-
-Since we are working with cosection localised cycles, this is not yet enough to conclude.
+For every $c\in\k$ we have a commutative diagram:\marginpar{the lower one is not exact}
+\bcd
+\hat{\pi}_{\widehat{\pazocal V}_c *}\OO_{\hC_{\widehat{\pazocal V}_c}}[-1]\ar[r] & \mathbb E_{\widehat{\pazocal V}_c/\hP} \ar[r] &\mathbb E_{\widehat{\pazocal V}/\hP}\rvert_{\widehat{\pazocal V}_c}\\
+\mathbb{T}^{\geq 1}_{\widehat{\pazocal V}_c/\widehat{\pazocal V}}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\widehat{\pazocal V}_c/\hP}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\widehat{\pazocal V}/\hP}\rvert_{\widehat{\pazocal V}_c} \ar[u]
+\ecd
+\end{lem}
+For the proof see \cite[\S~4.6]{CL}.
+
+%Since we are working with cosection localised cycles, this is not yet enough to conclude.
  A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
 \[
- \rm{Vb}(\mathcal L_{\hP}^{\oplus 5}\oplus\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{(\pr_2,\pr_3)}\rm{Vb}(\mathcal L_{\hP}^{\otimes 5}\oplus\mathcal P_{\hP})\xrightarrow{\cdot}\rm{Vb}(\omega_{\hat\pi_{\hP}})
+ \rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus\hL_{\hP}^{\otimes 5}\oplus\widehat{\mathcal P}_{\hP})\xrightarrow{(\pr_2,\pr_3)}\rm{Vb}(\hL_{\hP}^{\otimes 5}\oplus\widehat{\mathcal P}_{\hP})\xrightarrow{\cdot}\rm{Vb}(\omega_{\hat\pi_{\hP}})
 \]
@@
 \[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
-It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\pazocal V}\to \OO_{\pazocal V}$ and that the degeneracy locus of $\bar\sigma$ is 
+It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\widehat{\pazocal V}}\to \OO_{\widehat{\pazocal V}}$ and that the degeneracy locus of $\bar\sigma$ is
 \[\Mone{1}{X}{d}\times\Aaff^1_t.\]
@@
 Recall that the sections $(x,y)$ are required to satisfy $\w(x)-ty=0$.
-So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\pazocal P$ when $t\neq 0$.
-It is proved in \cite[Theorem 5.2]{KLcosection} that, given compatible perfect obstruction theories, the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that \cite[Proposition 4.9]{CLpfields}:
-\[
- \iota_{t\neq0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\pazocal P]^{\rm{vir}}_{\rm{\sigma}}\in A_0(\pazocal Q),\quad \iota_{0}^![\pazocal V]^{\rm{vir}}_{\rm{\bar\sigma}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}\in A_0(\pazocal Q)
-\]
-where we have denoted by $\pazocal Q:=\Mone{1}{X}{d}$.
+So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\widehat{\pazocal P}$ when $t\neq 0$.
+It is proved in \cite[Theorem 5.2]{KLcosection} that, given compatible perfect obstruction theories, the construction of a cosection localised virtual cycle is compatible with Gysin pullbacks, so that by \cite[Proposition 4.9]{CLpfields}:
+\[
+ \iota_{t\neq0}^![\widehat{\pazocal V}]^{\rm{vir}}_{\rm{\bar\sigma}}=[\widehat{\pazocal P}]^{\rm{vir}}_{\rm{\sigma}}\in A_0(\widehat{\pazocal Q}),\quad \iota_{0}^![\widehat{\pazocal V}]^{\rm{vir}}_{\rm{\bar\sigma}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}\in A_0(\widehat{\pazocal Q})
+\]
+where we have denoted by $\widehat{\pazocal Q}:=\Mone{1}{X}{d}$.
 \subsubsection*{Step~2}
-We are left with proving that $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $[\Mone{1}{X}{d}]^{\rm{vir}}$.
-In the rest of the section we use the following notation $\pazocal N:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $v\colon\pazocal N\to\pazocal Q$. 
-The idea is now to conclude finding a perfect obstruction theory for $v\colon\pazocal N\to\pazocal Q$ compatible with the ones of $\pazocal N\to\hP$ and $\pazocal Q\to\hP$ and then prove a cosection localized version of Manolache's virtual pull-back construction~\cite{Manolache-pullback}.
-
-Chang and Li proved indeed that there is a perfect obstruction theory 
-\[\mathbb E_{\pazocal N/\pazocal Q}:=\R^{\bullet}\hat\pi_{\pazocal N,*}(\mathcal L^{\otimes 5}_{\pazocal N}\oplus \mathcal P_{\pazocal N})\]
- compatible with $\mathbb E_{\pazocal N/\hP}$ and $v^*\mathbb E_{\pazocal Q/\hP}$, so that $\mathbb E_{\pazocal N/\pazocal Q}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\pazocal Q$.
-Then \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\pazocal N/\pazocal Q}$ is supported inside
-\[
- h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\pazocal N/\pazocal Q})_{|D(\sigma_0')}
+We are left with proving that $\deg[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $\deg[\Mone{1}{X}{d}]^{\rm{vir}}$.
+In the rest of the section we use the following notation: $\widehat{\pazocal N}:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $\hat v\colon\widehat{\pazocal N}\to\widehat{\pazocal Q}$. 
+We now find a perfect obstruction theory for $\hat v\colon\widehat{\pazocal N}\to\widehat{\pazocal Q}$ compatible with the ones of $\widehat{\pazocal N}\to\hP$ and $\widehat{\pazocal Q}\to\hP$, and then use a cosection-localised version of Manolache's virtual pullback construction~\cite{Manolache-pullback}.
+
+Indeed Chang and Li proved that there is a perfect obstruction theory 
+\[\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}}:=\R^{\bullet}\hat\pi_{\widehat{\pazocal N},*}(\hL^{\otimes 5}_{\widehat{\pazocal N}}\oplus \widehat{\mathcal P}_{\widehat{\pazocal N}})\]
+ compatible with $\mathbb E_{\widehat{\pazocal N}/\hP}$ and $\hat v^*\mathbb E_{\widehat{\pazocal Q}/\hP}$, so that $\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\widehat{\pazocal Q}$.
+Then in \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\widehat{\pazocal N}/\widehat{\pazocal Q}}$ is supported inside
+\[
+ h^1/h^0(\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}})\rvert_{D(\sigma_0')}
 \]
@@
 \[
- v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}\colon A_*(\pazocal Q)\to A_*(D(\sigma_0')=\pazocal Q)
-\]
-sending $[\pazocal Q]^{\rm{vir}}$ to $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}.$
-
-To conclude it is now enough to compute the degree of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}.$
-Since we are just interested in what happens on $A_0(\pazocal Q)$, we only have to compute $\deg(v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}(\zeta)$ for $\zeta$ a closed point.
-This is done in \cite[Theorem 5.7]{CLpfields} and the same considerations work in our case since the construction of the localized pull-back is completely analogous.
-%They notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\pazocal Q}$ is symmetric, so it can be represented as 
+ \hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}\colon A_*(\widehat{\pazocal Q})\to A_*(D(\sigma_0')=\widehat{\pazocal Q})
+\]
+sending $[\widehat{\pazocal Q}]^{\rm{vir}}$ to $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}.$
+
+To conclude it is now enough to compute the degree of $\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}.$
+Since we are only interested in what happens to $A_0(\widehat{\pazocal Q})$, we just need to compute $\deg(\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}[\zeta])$ for a closed point $\zeta$.
+This is done in \cite[Theorem 5.7]{CLpfields} and the same considerations work in our case.
+%They notice that the fibers of $v$ are vector spaces and the obstruction theory $\mathbb E_{\pazocal N/\widehat{\pazocal Q}}$ is symmetric, so it can be represented as 
 %\[[T_{v^{-1}(\xi)}\xrightarrow{0}T^*_{v^{-1}(\xi)}]\] along the fibers.
-This is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\pazocal Q},\rm{loc}}$ on $A_0(\pazocal Q)$ \cite[Theorem 5.7]{CLpfields}.
-
-Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on working with families of \emph{nodal} curves but every step generalizes automatically in our setting; let us recall that in the end, the moduli space of 1-stable maps should be though as the moduli space of stable maps with the boundary divisor of elliptic tails contracted.
+This is enough since we are only interested in the action of $v^!_{\mathbb E_{\pazocal N/\widehat{\pazocal Q}},\rm{loc}}$ on $A_0(\widehat{\pazocal Q})$ \cite[Theorem 5.7]{CLpfields}.
+
+Hopefully we have managed to convince the reader that the subtle intersection theory perpetuated in \cite{CLpfields} does not rely at all on the hypothesis that the families of curves we are working with are \emph{nodal}, but \emph{l.c.i.} curves are well-behaved enough so that all the proofs carry over to the situation of our interest.
 
@@
 \begin{prop}\label{1-stabilization-div}
-In the following diagram $\hat\cC$ is a family of weighted $1$-stable curves and $\phi$ is a regular morphism:
-
- \bcd
- (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat\cC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+In the following diagram $\hC$ is a family of weighted $1$-stable curves and $\phi$ is a regular morphism:
+
+ \bcd
+ (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
  & \MM_1^{\rm{div}} &
@@
 Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hat{\mathcal C}_i$ is regular in codimension $1$.
-Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy Serre's condition $S_2$, so does the total space of $\hat\cC_i$ by \cite[Thorem~23.9]{MAT}.
+Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy Serre's condition $S_2$, so does the total space of $\hC_i$ by \cite[Thorem~23.9]{MAT}.
 Then, since the geometric fibers of $\phi_i$ are either points or $p_a=1$ subcurves, and in either case connected, Zariski's connectedness theorem implies that
@@
 
-The obstruction theory $\R^\bullet\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\hat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by virtual pullback of $[\XP]$.
+The obstruction theory $\R^\bullet\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\widehat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by virtual pullback of $[\XP]$.
 In Section \ref{section:main_proof} we shall conduct on this a similar analysis to that in \cite{CL} and compare the contribution of the main component to Vakil-Zinger's reduced invariants.
@@
 
-There is a way around this: in a neighbourhood $V\subseteq \XP$ of $[C\to\hat C,\OO_{\hat C}(D)]$ we can write the universal line bundle $\mathcal L_V$ as $\OO_{\hat\cC_V}(\pazocal D + p-p_0)$.
+There is a way around this: in a neighbourhood $V\subseteq \XP$ of $[C\to\hat C,\OO_{\hat C}(D)]$ we can write the universal line bundle $\mathcal L_V$ as $\OO_{\hC_V}(\pazocal D + p-p_0)$.
 Indeed we can pick a local section $p_0$ through the minimal genus $1$ subcurve, so that $\mathcal L_V(p_0)$ becomes effective.
@@
 $C(\hat\pi_*\mathcal L)$ is the kernel of the vector bundle map:
-\[ \hat\pi_*\OO_{\hat\cC}(\A+\pazocal D+p-p_0)\xrightarrow{\varphi}\hat\pi_*\OO_{\A}(\A)\]
+\[ \hat\pi_*\OO_{\hC}(\A+\pazocal D+p-p_0)\xrightarrow{\varphi}\hat\pi_*\OO_{\A}(\A)\]
 Up to shrinking $V$ we may write:
-\[\hat\pi_*\OO_{\hat\cC}(\A+\pazocal D+p-p_0)\cong\bigoplus_{i=1}^d\hat\pi_*\OO_{\hat\cC}(\A+\pazocal \delta_i+p-p_0)\oplus\hat\pi_*\OO_{\hat\cC}(\A+p-p_0)\]
+\[\hat\pi_*\OO_{\hC}(\A+\pazocal D+p-p_0)\cong\bigoplus_{i=1}^d\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i+p-p_0)\oplus\hat\pi_*\OO_{\hC}(\A+p-p_0)\]
 \end{lem}
 Compare with \cite[Lemma 4.10]{HL}.
-Denote by \[\varphi_i\colon\hat\pi_*\OO_{\hat\cC}(\A+\pazocal \delta_i+p-p_0)\to\hat\pi_*\OO_{\A}(\A)\] (and similarly $\varphi_p$) the composite of the inclusion with $\varphi$.
+Denote by \[\varphi_i\colon\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i+p-p_0)\to\hat\pi_*\OO_{\A}(\A)\] (and similarly $\varphi_p$) the composite of the inclusion with $\varphi$.
 
@@
 \begin{lem}\label{lem:open_cones}
-Let $\tilde{\rho}\colon \tZp\to\tXP$ be the natural map and $\mathbb {E}_{\tZp/\tXP}=\R\hat\pi_*(\mathcal L^{\oplus 5}\oplus\mathcal P)$  the relative perfect obstruction theory for $\tilde{\rho},$ then $\mathfrak{C}_{\tZp/\tXP}$ has the following properties:
+Let $\tilde{\rho}\colon \tZp\to\tXP$ be the natural map and $\mathbb {E}_{\tZp/\tXP}=\R\hat\pi_*(\mathcal L^{\oplus 5}\oplus\widehat{\mathcal P})$  the relative perfect obstruction theory for $\tilde{\rho},$ then $\mathfrak{C}_{\tZp/\tXP}$ has the following properties:
 \begin{enumerate}
@@
 Moreover $\tZ^{\circ}$ is unobstructed on its image, which is an open of $\tXP$, because $\R^1\hat{\pi}_*\mathcal L=0$.
-So the normal cone is $[\tZ^{p,\circ}/\hat{\pi}_*\mathcal L^{\oplus 5}]$, which is the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}=[0\oplus \R^1\hat{\pi}_*\mathcal P/\hat{\pi}_*\mathcal L^{\oplus 5}\oplus 0]$.
+So the normal cone is $[\tZ^{p,\circ}/\hat{\pi}_*\mathcal L^{\oplus 5}]$, which is the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}=[0\oplus \R^1\hat{\pi}_*\widehat{\mathcal P}/\hat{\pi}_*\mathcal L^{\oplus 5}\oplus 0]$.
 \item We know that $\tZ^{p,gst,\circ}$ is a line bundle over $\tZ^{gst,\circ}$.
@@
 
-In order to prove the first we proceed as in \cite[\S5]{CLpfields}: notice that the obstruction theory $\mathbb E$ splits as $\mathbb E_1\oplus\mathbb E_2$ where $\mathbb E_1=\R\hat\pi_*(\mathcal L^{\oplus 5})$ and $\mathbb E_2=\R\hat\pi_*(\mathcal P)$.
+In order to prove the first we proceed as in \cite[\S5]{CLpfields}: notice that the obstruction theory $\mathbb E$ splits as $\mathbb E_1\oplus\mathbb E_2$ where $\mathbb E_1=\R\hat\pi_*(\mathcal L^{\oplus 5})$ and $\mathbb E_2=\R\hat\pi_*(\widehat{\mathcal P})$.
 When we restrict ourselves to $\tZ^{p,\rm{main}}$ we see that $\mathbb E_1$ is the closure of its own zero section; it follows that:
@@
  \]
-by projection formula and since $\phi_*\OO_{\cC_{\tZ^{p,\rm{main}}}}=\OO_{\hat\cC_{\tZ^{p,\rm{main}}}}$. The result follows then from the projection formula for Chern classes.
+by projection formula and since $\phi_*\OO_{\cC_{\tZ^{p,\rm{main}}}}=\OO_{\hC_{\tZ^{p,\rm{main}}}}$. The result follows then from the projection formula for Chern classes.
 \end{proof}
@@
 \[
- \beta\colon F_1\to h^1/h^0(\mathbb E) \quad \text{and} \quad \beta'\colon F_1\to \tilde{V}:=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\mathcal P)
+ \beta\colon F_1\to h^1/h^0(\mathbb E) \quad \text{and} \quad \beta'\colon F_1\to \tilde{V}:=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\widehat{\mathcal P})
 \]
@@
 They then introduce the notion of \emph{homogeneity} for substacks of $\tilde V$: write 
-\[\tilde V=\tilde V_1\oplus\tilde V_2\;\;\text{ with} \;\;\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})\;\; \text{and}\;\; \tilde V_2=\R^1\hat{\pi}_*(\mathcal P),\]
+\[\tilde V=\tilde V_1\oplus\tilde V_2\;\;\text{ with} \;\;\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})\;\; \text{and}\;\; \tilde V_2=\R^1\hat{\pi}_*(\widehat{\mathcal P}),\]
  and $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ the projection.
@@
 
-Finally Chang and Li point out that the coarse moduli cone $C^{\rm{gst}}$ is $(0,1)$-homogeneous \cite[Proposition 6.7]{CLpfields}: recalling the interpretation of $\Mone{1}{\PP^4}{d}^p$ as an open inside the cone of sections of $\mathcal V=\rm{Vb}(\mathcal L^{\oplus 5}\oplus \mathcal P)$ over $\hat\cC_{\mathfrak{Pic}_1^{(1)}}$, the desired $\Gm$-action on the fibers of $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ is induced by endowing $\rm{Vb}(\mathcal L^{\oplus 5}\oplus \mathcal P)$ with the $\Gm$-action that is trivial on the fibers of every copy of $\rm{Vb}(\mathcal L)$, and has character $1$ on those of $\rm{Vb}(\mathcal P)$, with an underlying trivial action on $\mathfrak{Pic}_1^{(1)}$.
-This influences the obstruction theory  $\R^\bullet\hat\pi_*\left(\mathfrak e^* T_{\mathcal V/\hat\cC_{\mathfrak{Pic}_1^{(1)}}}\right)$ of $\Mone{1}{\PP^4}{d}^p$ in the obvious way, and consequently $\mathbb E$ on $\tZp$.
+Finally Chang and Li point out that the coarse moduli cone $C^{\rm{gst}}$ is $(0,1)$-homogeneous \cite[Proposition 6.7]{CLpfields}: recalling the interpretation of $\Mone{1}{\PP^4}{d}^p$ as an open inside the cone of sections of $\mathcal V=\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ over $\hC_{\mathfrak{Pic}_1^{(1)}}$, the desired $\Gm$-action on the fibers of $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ is induced by endowing $\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ with the $\Gm$-action that is trivial on the fibers of every copy of $\rm{Vb}(\mathcal L)$, and has character $1$ on those of $\rm{Vb}(\widehat{\mathcal P})$, with an underlying trivial action on $\mathfrak{Pic}_1^{(1)}$.
+This influences the obstruction theory  $\R^\bullet\hat\pi_*\left(\mathfrak e^* T_{\mathcal V/\hC_{\mathfrak{Pic}_1^{(1)}}}\right)$ of $\Mone{1}{\PP^4}{d}^p$ in the obvious way, and consequently $\mathbb E$ on $\tZp$.
 
@@
 
-Since $\tZ^{p,\rm{gst}}\cong\operatorname{Tot}_{\tZ^{\rm{gst}}}\left(\R^1\hat{\pi}_*\mathcal P\right)$ we compactify considering
-\[\overline{\gamma}\colon \overline{\tZ^{p,\rm{gst}}}:=\PP\left(\R^1\hat{\pi}_*\mathcal P\oplus \OO_{\tZ^{\rm{gst}}}\right)\to \tZ^{\rm{gst}}\]
+Since $\tZ^{p,\rm{gst}}\cong\operatorname{Tot}_{\tZ^{\rm{gst}}}\left(\R^1\hat{\pi}_*\widehat{\mathcal P}\right)$ we compactify considering
+\[\overline{\gamma}\colon \overline{\tZ^{p,\rm{gst}}}:=\PP\left(\R^1\hat{\pi}_*\widehat{\mathcal P}\oplus \OO_{\tZ^{\rm{gst}}}\right)\to \tZ^{\rm{gst}}\]
 and extend $\tilde{V}_1,\tilde{V}_2$ via:

### 2018-01-09 draft_merged.tex
fixed notation in the first approach

@@
 
-Throughout the paper we shall have fixed a homogeneous polynomial $\mathbf w\in\k[x_0,\ldots,x_4]_5$ of degree $5$ such that $X=V(\mathbf w)\subseteq\PP^4$ is a generic quintic threefold.
-Furthermore let us consider a fixed positive integer $d$ determining all the homology classes $d[\ell]\in A_1(\PP^4)$, line bundle weights, etc.
+Throughout the paper we shall have fixed a homogeneous polynomial $\mathbf w\in\k[x_0,\ldots,x_4]_5$ of degree $5$ such that $X=V(\mathbf w)\subseteq\PP^4$ is a generic smooth quintic threefold.
+Furthermore let us consider a fixed positive integer $d$ determining all the homology classes $\beta=d[\ell]\in A_1(\PP^4)$, line bundle weights, etc.
 that we shall take into account.
 
-Let $\rm{M}:=\M{1}{n}{X}{\beta}$ denote the moduli stack of $n$-pointed genus $1$ stable maps to $X$ in the homology class $\beta$, with universal curve and stable map $(\pi,f)\colon\cC_{\rm M}\to \rm M\times X$.
-Similarly let $\hrM:=\oM_{1,n}^{(1)}(X,\beta)$ denote the moduli stack of $1$-stable maps to $X$, with universal curve and stable map $(\hat\pi,\hat f)\colon\hC_{\hrM}\to \hrM\times X$.
+Let $\M{1}{n}{X}{\beta}$ denote Kontsevich's moduli stack of $n$-pointed genus $1$ stable maps to $X$ in the homology class $\beta$.
+We may use the shorthand $\rm M$ for a moduli space of stable maps, and always denote by $(\pi,f)\colon\cC_{\rm M}\to \rm M\times X$ the universal curve and stable map.
+Similarly let $\hrM:=\oM_{1,n}^{(1)}(X,\beta)$ denote Viscardi's moduli stack of $1$-stable maps to $X$, with universal curve and stable map $(\hat\pi,\hat f)\colon\hC_{\hrM}\to \hrM\times X$.
 
@@
 \begin{dfn}
-Let $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ be the stack of \emph{weighted-stable} curves of genus $1$ with $n$ markings and total weight $d$: every geometric point of $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ represents a connected reduced nodal projective curve of arithmetic genus $1$ with $n$ distinct smooth markings and an integer-valued function on the dual graph, such that it is compatible with specialisation maps and the sum of the values on all the vertices is $d$; furthermore we require that it takes nonnegative values, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
+Let $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ be the stack of \emph{weighted-stable} curves of genus $1$ with $n$ markings and total weight $d$: every geometric point of $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ represents a connected, reduced, nodal, projective curve of arithmetic genus $1$ with $n$ distinct smooth markings and an integer-valued function $\rm{wt}$ on the dual graph.
+Such a function assumes only nonnegative values, the sum of which on all the vertices of the dual graph is $d$; $\rm{wt}$ is compatible with the specialisation maps, and we further impose the following stability condition: every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
 \end{dfn}
-There is an \'{e}tale non-separated morphism $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, the weight assignment coming from the degree of the map to $\PP^r$.
-
-We shall denote by $\pi\colon \cC\to \MM_{1,n}$ the universal curve (and use similar notation for all its pullbacks).
-We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$ of $\cC\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ with universal line bundle $\mathcal{L}$.
+There is an \'{e}tale non-separated morphism $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, the weight coming from the degree of the map to $\PP^r$.
+We shall denote by $\pi\colon \cC\to \MM_{1,n}$ the universal curve (and use similar notation for its pullbacks).
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$ of $\pi\colon \cC\to \MM_{1,n}$ with universal line bundle $\mathcal{L}$, subject to the stability condition that $\omega_\pi^{\rm{log}}\otimes\mathcal L^{\otimes 3}$ is $\pi$-ample, and the requirement that the total degree of $\mathcal L$ on the fibers of $\cC$ is $d$.
+Let $\PtoM$ denote the projection $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, where the weight comes from the degree of the line bundle.
+The forgetful map $\rm M=\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ factors through $\PtoM$ by declaring $\mathcal L_{\rm M}:=f^*\OO_{\PP^r}(1)$.
 We shall often use shorthand notation $\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ and $\mathfrak P$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$.
-Let $\PtoM$ denote the projection $\mathfrak P\to \MM$.
 
@@
 \begin{itemize}
- \item argue in two different ways that there is a natural fashion to associate a weighted $1$-stable curve to a weighted-stable nodal curve of genus $1$, essentially by replacing elliptic tails of weight $0$ by cusps, which results in a morphism:
+ \item argue in two different ways that there is a natural fashion to associate a weighted $1$-stable (i.e.
+at worst cuspidal) curve to a weighted-stable (nodal) curve of genus $1$, replacing elliptic tails of weight $0$ by cusps, which results in a morphism:
  \[\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)\]
 extending the identity on the locus of smooth elliptic curves;
- \item introduce the fiber product 
+ \item introduce the fiber product:
  \[\Z:= \mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)\]
- and show that it is a closed substack of $\oM_1(\PP^4,d)$, isomorphic to it outside the boundary divisor $D^1$;
- \item introduce the fiber product \[\Zp:=\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)^p \]
- and endow it with an obstruction theory and a cosection thereof, which are pulled back from  $\pazocal M^{(1)}_{1,n}(\PP^4,d)^p$; unfortunately we will not be able to compare them directly with $\oM_1(\PP^4,d)^p$;
- \item explain along the way all the notation one needs in order to understand the previous sentences.
+ and show that it is a closed substack of $\oM_1(\PP^4,d)$, isomorphic to it outside the boundary divisor with a contracted elliptic tail;
+ \item introduce the fiber product:
+ \[\Zp:=\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)^p \]
+ and endow it with an obstruction theory and a cosection thereof, which are pulled back from $\oM^{(1)}_{1,n}(\PP^4,d)^p$.
+Unfortunately we will not be able to compare them directly with $\oM_1(\PP^4,d)^p$; nonetheless in the next sections we will manage to approach the localised virtual class of $\Zp$ directly by adapting Chang and Li's techniques \cite{CL}.
 \end{itemize}
@@
 
-Note that the only type of nodal curves that we are getting rid of are the ones with an elliptic tail of weight zero.
+%Note that the only type of nodal curves that we are getting rid of are the ones with an elliptic tail of weight zero.
 
@@
 \begin{enumerate}
- \item we adopt the strategy of constructing the graph of such a morphism within the product $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ and prove that the projection onto the first factor is an isomorphism;
+ \item we first construct a substack of the product $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ which plays the role of the graph of such a morphism, and then check that the projection onto the first factor is an isomorphism;
 \item we prove that the $1$-stabilisation exists at the level of curves with a divisor constructing the contraction directly, then argue that it descends to a morphism between moduli spaces of weighted curves.
@@
 
-Let $\mathcal C$ and $\mathcal C'$ be the universal curves over $\mathfrak{M}:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ and $\mathfrak{M}':=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ respectively.
-Abusing notation, we will still write $\mathcal C$ and $\mathcal C'$ for their pullbacks to the product $\mathfrak{M}\times\mathfrak{M}'$ along the two projections.
+Recall the shorthand notation $\MM=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}$ and $\hM=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$, with universal curves $\pi\colon \cC\to \MM$ and $\hat\pi\colon\hC\to\hM$ respectively.
+Abusing notation we will still write $\cC$ and $\hC$ for their pullbacks to the product $\MM\times\hM$ along the two projections.
 The proof of the theorem follows from two Lemmas:
@@
 \begin{lem}\label{lemma:def_X}
- There is a locally closed substack $\mathcal X\subseteq\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ representing morphisms $C\to C'$ that contract weight-zero elliptic tails to cusps and are weight-preserving isomorphisms everywhere else.
+ There is a locally closed substack $\mathcal X\subseteq\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ representing morphisms $C\to \widehat{C}$ that contract elliptic tails of weight $0$ to cusps and are weight-preserving isomorphisms everywhere else.
 \end{lem}
@@
 \begin{lem}\label{lamma:projection_iso}
- The first projection $\pr_1\colon \operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')\to\mathfrak M$ restricted to $\mathcal X$ is an isomorphism with $\mathfrak M$.
+ The first projection $\pr_1\colon \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)\to\MM$ restricted to $\mathcal X$ is an isomorphism with $\MM$.
 \end{lem}
@@
 \begin{proof}\ref{lemma:def_X}
-Recall that $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ is an algebraic stack; in fact the map to $\mathfrak{M}\times\mathfrak{M}'$ is representable (by algebraic spaces) \cite{OlssonHOM}.
+Recall that $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ is an algebraic stack; in fact the map to $\MM\times\hM$ is representable by algebraic spaces \cite{OlssonHOM}.
+Let $\phi\colon\cC\to\hC$ denote the universal morphism.
 We now proceed to construct $\mathcal X$ as a locally closed substack in the space of morphisms.
@@
 
-\item[Step 1] Consider
- \[\pi\colon\mathfrak{P}=\mathfrak{Pic}^{tot deg=d,st}_{1,n}\to\mathfrak{M},\ \pi'\colon\mathfrak{P}'=\mathfrak{Pic}^{tot deg=d,st}_{1,n}(1)\to\mathfrak{M}'\]
-  the Picard stacks of $\cC\to\mathfrak{M}$ and $\cC'\to\mathfrak{M'}$ with universal line bundles $\mathfrak{L}$ and $\mathfrak{L'}$, where $\pi$ and $\pi'$ are defined by taking the multi-degree of line bundles.
-We can now look at the algebraic stack $\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$ with universal morphism
- $\Phi$ and natural projection $\Pi$ to $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$.
-We claim that there exists a locally closed substack $\mathcal{Y'}\subseteq \operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$ representing those morphisms that \emph{preserve the line bundles}.
-Indeed, given a chart
- \begin{equation*}%\label{equation:Spoints} 
- S\to\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C'),
-  \end{equation*} 
-   the locus of $s\in S$ where $\Phi_s^*\mathfrak{L}'_s\cong\mathfrak{L}_s$ is nothing else than the locus $T$ where the two sections $\mathfrak{L}_S$ and $\Phi_S^*\mathfrak{L}'_S$ of $\mathfrak{P}(S)\to\mathfrak{M}(S)$ coincide.
-In other words, we are looking at the fiber product
+\item[Step 1] We first lift the problem to the level of Picard stacks in order to transmute the property of being weight-preserving into the more manageable one of preserving the line bundles.
+Recall the notation:
+ \[\PtoM\colon\mathfrak P=\mathfrak{Pic}^{tot deg=d,st}_{1,n}\to\MM,\quad \hat\PtoM\colon\hP=\mathfrak{Pic}^{tot deg=d,st}_{1,n}(1)\to\hM\]
+  for the Picard stacks of $\pi$ and $\hat \pi$ respectively, with universal line bundles $\L$ and $\hL$.
+The projections $\PtoM$ and $\hat \PtoM$ are defined by taking the multi-degree of a line bundle.
+We can now look at the algebraic stack $\operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$ with universal morphism
+ $\Phi$ and natural projection $\Pi$ to $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
+There exists a locally closed substack $\mathcal{Y'}\subseteq \operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$ representing those morphisms that \emph{preserve the line bundles}.
+Indeed, given a smooth chart $S\to\operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$, the locus of $s\in S$ where $\Phi_s^*\hL_s\cong\mathcal{L}_s$ is nothing but the locus $T$ where the two sections $\mathcal{L}_S$ and $\Phi_S^*\hL_S$ of $\mathfrak{P}(S)\to\MM(S)$ are isomorphic.
+In other words we are looking at the fiber product
   \[\xymatrix{T\ar[r]\ar[d]&\mathfrak{P}\ar[d]^{\Delta}\\
-  S\ar[r]&\mathfrak{P}\times_{\mathfrak{M}}\mathfrak{P}}\]
-Being $\mathfrak{P}\to\mathfrak{M}$ representable by locally separated algebraic spaces \cite[Theorem~8.3.1]{neron}, $\Delta$ is a quasi-compact locally closed immersion \cite[\href{http://stacks.math.columbia.edu/tag/04YU}{Tag 04YU}]{stacks-project}, so in particular $T\subseteq S$ is locally closed.
+  S\ar[r]&\mathfrak{P}\times_{\MM}\mathfrak{P}}\]
+Being $\mathfrak{P}\to\MM$ representable by locally separated algebraic spaces \cite[Theorem~8.3.1]{neron}, $\Delta$ is a quasi-compact locally closed immersion \cite[\href{http://stacks.math.columbia.edu/tag/04YU}{Tag 04YU}]{stacks-project}, so in particular $T\subseteq S$ is locally closed.
 
@@
 
-Given a chart $S\to\operatorname{Mor}_{\mathfrak{P}\times\mathfrak{P}'}(\mathcal C,\mathcal C')$, the locus of $s\in S$ where $\Phi_s$ is marking-preserving is the equaliser of the two sections
-\bcd
-S \ar[r,shift left, "\times\sigma_i'" above]\ar[r,shift right,"\times\Phi\circ\sigma_i" below] & \mathcal C_S'\times_S\ldots\times_S \mathcal C_S'
-\ecd
-This defines a closed subscheme of $S$, since $\mathcal C_S'\to S$ is separated.
-
-As regards surjectivity, since $\Phi$ is proper and the dimension of the fiber is upper semicontinuous \cite[\href{http://stacks.math.columbia.edu/tag/0D4I}{Tag 0D4I}]{stacks-project}, the locus in $\mathcal C_S'$ where the fiber of $\Phi$ is empty is open.
-Its image in $S$ is open by flatness of $\cC'\to S$ \cite[\href{http://stacks.math.columbia.edu/tag/01UA}{Tag 01UA}]{stacks-project}, and the complement of it is the locus we need.
-
-\item[Step 3] Let $\mathcal{X}'$ be the image of $\mathcal Y$ under $\Pi$.
-This is a constructible substack of $\operatorname{Mor}_{\mathfrak{M}\times\mathfrak{M}'}(\mathcal C,\mathcal C')$ by Chevalley's theorem \cite[Theorem 5.9.4]{LMB}.
+Given a chart $S\to\operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$, the locus of $s\in S$ where $\Phi_s$ is marking-preserving is the equaliser of the two sections:
+\bcd
+S \ar[r,shift left, "\times\hat\sigma_i" above]\ar[r,shift right,"\times\Phi\circ\sigma_i" below] & \hC_S\times_S\ldots\times_S \hC_S
+\ecd
+This defines a closed subscheme of $S$, since $\hC_S\to S$ is separated.
+
+As regards surjectivity, since $\Phi$ is proper and the dimension of the fiber is upper semicontinuous \cite[\href{http://stacks.math.columbia.edu/tag/0D4I}{Tag 0D4I}]{stacks-project}, the locus in $\hC_S$ where the fiber of $\Phi$ is empty is open.
+Its image in $S$ is open by flatness of $\hC_S\to S$ \cite[\href{http://stacks.math.columbia.edu/tag/01UA}{Tag 01UA}]{stacks-project}, and the complement of the latter is the locus we need.
+
+\item[Step 3] We may now get back to $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
+Let $\mathcal{X}'$ be the image of $\mathcal Y$ under $\Pi$.
+This is a constructible substack of $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ by Chevalley's theorem \cite[Theorem 5.9.4]{LMB}.
 Recall that to show that a constructible set is open (respectively closed) it is enough to check that it contains all the generisations of its points (respectively all the specialisations) \cite[\href{http://stacks.math.columbia.edu/tag/0DQN}{Tag 0DQN}\href{http://stacks.math.columbia.edu/tag/0903}{Tag 0903}]{stacks-project}.
@@
 
-It is clear that being surjective and marking-preserving are closed conditions, as above.
-The requirement that $\phi$ can be covered by a line bundle-preserving map can be translated into the following combinatorial conditions:
+It can be shown as above that being surjective and marking-preserving are closed conditions.
+The requirement that $\phi$ can be covered by a line bundle-preserving morphism can be translated into the following combinatorial conditions:
 
 \begin{enumerate}
-\item\emph{$\phi$ contracts only weight zero components.} We show that this is open.
-Assume that $S$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $S\to\mathcal X'$ such that $\phi_0\colon\mathcal C_0\to \mathcal C_0'$ does not contract any positive weight component.
-Suppose there exists an irreducible component $D_\eta\subseteq C_{\eta}$ of positive weight $d_W$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e.
-$\left\{c\in \mathcal{C}_{S} | \dim_c\phi^{-1}(\phi(c))\geq 1\right\}$, is closed by semicontinuity of fiber dimension, hence it contains all the components $D_i\subseteq C_0$ to which $D_\eta$ specialises.
-At least one of them has positive weight, since the sum of their weights is $d_W$, which is a contradiction.
-
-\item\emph{$\phi$ has degree 1 on every non contracted component} or, equivalently, there is an $S$-dense open in $\mathcal C'_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
-This is an open and closed condition; we show it is open. Let $S$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property. Since $\phi_S$ is proper, we may consider 
-\[\phi_{S,*}[\mathcal C_{S}]=\sum n_i[\mathcal C'_{S,i}]\in A_2(\cC'_S)\].
-Applying Gysin pull-back to $0$ (which is a regular closed point of the base) \cite[Prop.
-10.1(a)]{FUL}, we see that all the $n_i$'s are 1 for those $\cC'_i$'s such that $0^![\cC'_i]\neq 0$.
-On the other hand there is no irreducible component of $\cC'$ supported on $\cC'_\eta$.
+\item\emph{$\phi$ contracts only components of weight $0$.} We show that this is open.
+Assume that $\dvr$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $\dvr\to\mathcal X'$ such that $\phi_0\colon\cC_0\to \hC_0$ does not contract any component of positive weight.
+Suppose there exists an irreducible component $D_\eta\subseteq \cC_{\eta}$ of positive weight $d_D$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e.
+$\left\{c\in \cC_{\dvr} | \dim_c\phi^{-1}(\phi(c))\geq 1\right\}$, is closed by semicontinuity of fiber dimension, hence it contains all the components $D_i\subseteq \cC_0$ to which $D_\eta$ specialises.
+At least one of them has positive weight, since the sum of their weights is $d_D$, which is a contradiction.
+
+\item\emph{$\phi$ has degree 1 on every non contracted component} or, equivalently, for every $S\to\mathcal X'$ there is an $S$-dense open in $\hC_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
+This is an open and closed condition; we show it is open. Let $\dvr$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property. Since $\phi_\dvr$ is proper, we may consider 
+\[\phi_{\dvr,*}[\cC_{\dvr}]=\sum n_i[\hC_{\dvr,i}]\in A_2(\hC_\dvr).\] Applying Gysin pull-back to $0$ (which is a regular closed point of the base) \cite[Prop.
+10.1(a)]{FUL}, we see that all the $n_i$'s are 1 for those $\hC_i$'s such that $0^![\hC_i]\neq 0$.
+On the other hand there is no irreducible component of $\hC$ supported on $\hC_\eta$.
 
 \item\emph{$\phi$ is weight-preserving.} This is again an open condition, as we can see from the weighted dual graphs.
-Let $\tilde \phi$ be the map induced at the level of weighted dual graphs $\Gamma(\cC)\to\Gamma(\cC')$.
+Let $\Gamma(\phi)$ be the map induced at the level of weighted dual graphs $\Gamma(\cC_\dvr)\to\Gamma(\hC_\dvr)$.
 It is compatible with the specialisation maps:
 \bcd
-\Gamma(\cC_0)\ar[r,"\tilde\phi_0"]\ar[d,"\rm{sp}"] & \Gamma(\cC'_0)\ar[d,"\rm{sp}"] \\
-\Gamma(\cC_{\eta})\ar[r,"\tilde\phi_\eta"]& \Gamma(\cC'_\eta)
+\Gamma(\cC_0)\ar[r,"\Gamma(\phi_0)"]\ar[d,"\rm{sp}"] & \Gamma(\hC_0)\ar[d,"\rm{sp}"] \\
+\Gamma(\cC_{\eta})\ar[r,"\Gamma(\phi_\eta)"]& \Gamma(\hC_\eta)
 \ecd
@@
 \]
-$\tilde{\phi}_\eta$ has to be weight-preserving as well.
+$\Gamma(\phi_\eta)$ has to be weight-preserving as well.
 \end{enumerate}
 
-\item[Step 4] We have seen that, if $\phi$ contracts a connected subcurve $E$ of the fiber, it must have zero weight.
-Since the target only has nodes and cusps as singularities, and the markings are required to be smooth points, we observe that $E$ must be of arithmetic genus one by weighted stability and $|\overline{C\setminus E}\cap E|\leq 2$, i.e.
+\item[Step 4] We have imposed that, if $\phi$ contracts a subcurve $E$ of the fiber, it must have weight $0$.
+Since the fibers of $\hC$ only have nodes and cusps as singularities, and the markings are required to be smooth points, we observe that $E$ must be unmarked and have arithmetic genus $1$ by weighted stability; furthermore $\left|E\cap\overline{C\setminus E}\right|\leq 2$, i.e.
 $E$ is either an elliptic tail or an elliptic bridge.
@@
 \item $\phi$ contracts an elliptic tail to a cusp and is an isomorphism everywhere else, or there is no elliptic tail to start with and $\phi$ is an isomorphism;
-\item the elliptic tail/bridge is contracted to a smooth point/node, then a non-separating node or a cusp must be created somewhere else in order to preserve the arithmetic genus.
+\item the elliptic tail/bridge is contracted to a smooth point/node, then a non-separating node or a cusp must appear somewhere else in the fiber of $\hC$ in order to preserve the arithmetic genus.
 \end{enumerate} 
 We want to avoid the second scenario, so we define the open substack $\mathcal X\subseteq \mathcal X'$ as follows.
-Given $\mathcal{C}_S\to\mathcal C_S'\in\mathcal X'(S)$, let $U'\subseteq \mathcal C'$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U')}\colon\phi_S^{-1}(U')\to U'$ is an isomorphism and $Z'$ its closed complement in $\mathcal C_S'$.
-Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(Z')}\colon \phi^{-1}(Z')\to S$ are geometrically connected.
+Given $\mathcal{C}_S\to\hC_S\in\mathcal X'(S)$, let $U\subseteq \hC$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U)}\colon\phi_S^{-1}(U)\to U$ is an isomorphism, and $V$ its closed complement in $\hC_S$.
+Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(V)}\colon \phi^{-1}(V)\to S$ are geometrically connected.
 \end{description} 
+This concludes the construction of the locally closed substack $\mathcal X\subseteq \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
  \end{proof}
@@
  This result will follow from an application of Zariski's Main Theorem for algebraic spaces.
-First we claim that the projection is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points.
-Hence we need to say that, given $\phi\colon C\to C'$ a $k$-point of $\X$, we have
+First we claim that the projection $\pr_{1|\mathcal X}\colon\mathcal X\to \MM$ is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points.
+Hence we need to say that, given $\phi\colon C\to \widehat{C}$ a $K$-point of $\X$, we have
 $\operatorname{Aut}(\phi)\subseteq\operatorname{Aut}(C)$. Recall that automorphisms of $\phi$ are commutative diagrams:
-\bcd C\ar[r,"\phi"]\ar[d,"\psi"] & C'\ar[d,"\psi'"] \\ C\ar[r,"\phi"] & C' \ecd
- Now $\psi'$ is determined by $\psi$ due to our description of $\phi$.
-
-Secondly $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion
-\bcd
-\eta'=\Spec(K')\ar[r]\ar[d] & \eta=\Spec(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
-S'=\Spec(R')\ar[r]\ar[urr,dashed,"\exists?", left] & S=\Spec(R)\ar[r] & \mathfrak M
-\ecd
-Let $\pi \colon \mathcal C_S\to S$ be the family of nodal curves on $S$; there are three cases to consider:
-\begin{enumerate}
-\item the central fiber contains no elliptic tail, then the same is true for $\mathcal C_\eta$, hence $\phi_\eta$ is an isomorphism. We can extend $\phi_\eta$ as follows:
-\bcd
-\cC_\eta\arrow{r}{\sim}[swap]{\phi_\eta}\ar[d,hook,"\iota"] & \cC'_\eta\ar[d,hook,"\iota\circ\phi_\eta^{-1}"] \\
-\cC_S\ar[r,"\id_\cC"] & \cC_S=:\cC'_S
-\ecd
-Another extension $\phi'\colon \mathcal C_S\cong \mathcal C_S'$ would be isomorphic to the previous one via:
-\bcd
-\cC_S\ar[r,"\phi'"]\ar[d,"\id"] &\cC_S'\ar[d,"(\phi')^{-1}"] \\
-\cC_S\ar[r,"\id"] & \cC_S
+\bcd C\ar[r,"\phi"]\ar[d,"\psi"] & \widehat{C}\ar[d,"\hat\psi"] \\ C\ar[r,"\phi"] & \widehat{C} \ecd
+ Now $\hat\psi$ is determined by $\psi$ due to how $\phi$ behaves (contracting elliptic tails and being an isomorphism everywhere else).
+
+Secondly $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion:
+\bcd
+\eta'=\operatorname{Spec}(K')\ar[r]\ar[d] & \eta=\operatorname{Spec}(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
+\dvr'=\operatorname{Spec}(R')\ar[r]\ar[urr,dashed,"\exists?", left] & \dvr=\operatorname{Spec}(R)\ar[r] & \MM
+\ecd
+Let $\pi \colon \cC_\dvr\to \dvr$ be the family of nodal curves on $\dvr$; there are three cases to consider:
+\begin{enumerate}[label=(\alph*)]
+\item the central fiber contains no elliptic tail, then the same is true for $\cC_\eta$, hence $\phi_\eta$ is an isomorphism. We can extend $\phi_\eta$ as follows:
+\bcd
+\cC_\eta\arrow{r}{\sim}[swap]{\phi_\eta}\ar[d,hook,"\iota"] & \hC_\eta\ar[d,hook,"\iota\circ\phi_\eta^{-1}"] \\
+\cC_\dvr\ar[r,"\id_\cC"] & \cC_\dvr=:\hC_\dvr
+\ecd
+Another extension $\phi'\colon \cC_\dvr\cong \hC_\dvr$ would be isomorphic to the previous one via:
+\bcd
+\cC_\dvr\ar[r,"\phi'"]\ar[d,"\id"] &\hC_\dvr\ar[d,"(\phi')^{-1}"] \\
+\cC_\dvr\ar[r,"\id"] & \cC_\dvr
 \ecd
@@
 \end{enumerate}
-If instead $\mathcal C_0$ has got an elliptic tail, then we have two possibilities:
-\begin{enumerate}
+If instead $\cC_0$ has got an elliptic tail, then we have two possibilities:
+\begin{enumerate}[label=(\alph*)]
 \setcounter{enumi}{1}
-\item $\mathcal C_{\eta}$ has an elliptic tail as well; that is the image of $S\to\MM$ is contained in the boundary, so we can find a lift
-\bcd
- & \MM_{1,1}\times\MM_{0,1+n}^\text{wt}\ar[d] & \\
- S\ar[r]\ar[ur,dashed] & \mathfrak D_{\{1,\emptyset\},\{0,n\}}\ar[r,hook] &\MM.
-\ecd
- Then $\mathcal C_S$ is the push-out of a family of rational curves $\mathcal R_S$ and a family of genus one curves $\mathcal Z_S$:
+\item $\cC_{\eta}$ has got an elliptic tail as well; that is the image of $\dvr\to\MM$ is contained in the boundary, so we can find a lift
+\bcd
+ & \MM_{1,1}\times\MM_{0,1+n}^{\rm{wt}=d,\rm{st}}\ar[d] & \\
+ \dvr\ar[r]\ar[ur,dashed] & \mathfrak D_{\{1,\emptyset\},\{0,n\}}\ar[r,hook] &\MM.
+\ecd
+ Then $\cC_\dvr$ is the pushout of a family of rational curves $\mathcal R_\dvr$ and a family of genus one curves $\mathcal Z_\dvr$:
 %The map $S\to\partial \mathfrak M_{1,n}$ lifts to the normalisation of the boundary, i.e.
-$\mathfrak M_{0,n_0+1}\times\mathfrak M_{1,n_1+1}$, which gives two families of pointed curves on $S$; there is a map from the push-out to $\mathcal C_S$ by the universal property, and it is proper bijective and flat (crit\`{e}re de platitude par fibres \cite[\href{http://stacks.math.columbia.edu/tag/039A}{Tag 039A}]{stacks-project}).
+$\mathfrak M_{0,n_0+1}\times\mathfrak M_{1,n_1+1}$, which gives two families of pointed curves on $S$; there is a map from the pushout to $\mathcal C_S$ by the universal property, and it is proper bijective and flat (crit\`{e}re de platitude par fibres \cite[\href{http://stacks.math.columbia.edu/tag/039A}{Tag 039A}]{stacks-project}).
 \begin{equation}\label{eq:pushout}
 \begin{tikzcd}
-S\ar[d]\ar[r] & \mathcal R_S \ar[d] \\
-\mathcal Z_S\ar[r] & \mathcal C_S
+\dvr\ar[d]\ar[r] & \mathcal R_\dvr \ar[d] \\
+\mathcal Z_\dvr\ar[r] & \cC_\dvr
 \end{tikzcd}
 \end{equation}
-Recall that the cuspidal curve $\cC'_K$ can be characterised as the push-out of the following diagram:
+Recall that the cuspidal curve $\hC_K$ can be characterised as the pushout of the following diagram:
 \bcd
 2K\ar[r]\ar[d] & \mathcal R_K\ar[d] \\
-K\ar[r] & \mathcal C'_K.
-\ecd
-Since the smooth section $S\to\mathcal R_S$ defines a Cartier divisor, it makes sense to take its double and we can thus define $\cC'_S$ by means of the similar diagram:
-\bcd
-2S\ar[r]\ar[d] & \mathcal R_S\ar[d] \\
-S\ar[r] & \mathcal C'_S
-\ecd
-The morphism $\phi_S\colon\cC_S\to\cC'_S$ extending $\phi_\eta$ is then defined by exploiting the description of $\cC_S$ as a push-out \eqref{eq:pushout}, and the morphisms $\id\colon\mathcal R_S\to \mathcal R_S$ and $\pr_{\mathcal Z_S}\colon\mathcal Z_S\to S$.
-\item If $\mathcal C_S$ smoothens the elliptic tail, then $\phi_\eta$ is an isomorphism.
-We may assume that $S$ is the spectrum of a complete DVR with algebraically closed residue field \cite[Theorem 7.10]{LMB}.
-Then we may pick one smooth section for each rational component of $\cC_0$ and extend them to sections of $\cC_S\to S$ by Grothendieck's existence theorem; let us denote by $\Sigma$ the Cartier divisor that is the sum of all such sections.
-Let $Z$ be the elliptic tail in the central fiber; then we claim that $\omega_{\cC_S/S}(Z)\otimes\mathcal O_{\cC_S}(\Sigma)$ is $\pi_S$ semi-ample, ample on the generic fiber, and gives the contraction of the elliptic tail to the cusp in the central fiber.
+K\ar[r] & \hC_K.
+\ecd
+Since the smooth section $\dvr\to\mathcal R_\dvr$ defines a Cartier divisor, it makes sense to take its double and we can thus define $\hC_\dvr$ by means of the similar diagram:
+\bcd
+2\dvr\ar[r]\ar[d] & \mathcal R_\dvr\ar[d] \\
+\dvr\ar[r] & \hC_\dvr
+\ecd
+The morphism $\phi_\dvr\colon\cC_\dvr\to\hC_\dvr$ extending $\phi_\eta$ is then defined by exploiting the description of $\cC_\dvr$ as a pushout \eqref{eq:pushout}, and the morphisms $\id\colon\mathcal R_\dvr\to \mathcal R_\dvr$ and $\pr_{\mathcal Z_\dvr}\colon\mathcal Z_\dvr\to \dvr$ to the upper right and bottom left corners of the last diagram respectively.
+\item If $\cC_\dvr$ does smooth the elliptic tail, then $\phi_\eta$ is an isomorphism.
+We may assume that $\dvr$ is the spectrum of a complete DVR with algebraically closed residue field \cite[Theorem 7.10]{LMB}.
+Then we may pick a smooth section for each rational component of $\cC_0$ and extend them to sections of $\cC_\dvr\to \dvr$ by Grothendieck's existence theorem; let us denote by $\Sigma$ the Cartier divisor that is the sum of all such sections.
+Let $Z$ be the elliptic tail in the central fiber; then we claim that $\omega_{\cC_\dvr/\dvr}(Z)\otimes\mathcal O_{\cC_\dvr}(3\Sigma)$ is $\pi_\dvr$ semi-ample, ample on the generic fiber, and gives the contraction of the elliptic tail to the cusp in the central fiber.
 We shall not prove the claim here, since this is the core of the second approach.
 \end{enumerate}
-Finally, observe that the map is bijective by construction and $\mathfrak M$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \mathfrak M$ is an isomorphism by Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
+Finally observe that the map is bijective by construction and $\MM$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \MM$ is an isomorphism by Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
  \end{proof}
@@
 More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields} and Section \ref{section:p-fields} above), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
-Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\mathcal C,[\Aaff^1/\Gm])$; then again one picks the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
+Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\cC,[\Aaff^1/\Gm])$; then again one picks the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
 
@@
 This boils down to checking that for two different choices of a lifting $D_1,D_2\colon S\to\MM_1^{\rm{div}}$ there exists a unique isomorphism 
-\[\hat{\mathcal C}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_1))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_2))^{\otimes n}\right)=\hat{\mathcal C}_2.
+\[\hat{\cC}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_1))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_2))^{\otimes n}\right)=\hat{\cC}_2.
 \]
@@
 &\cC_S \ar[dl,"\phi_1" above left]\ar[dr,"\phi_2"]  \\
- \hat{\mathcal C}_1\ar[rr,dashed, "\psi"] & &\hat{\mathcal C}_2.
+ \hat{\cC}_1\ar[rr,dashed, "\psi"] & &\hat{\cC}_2.
  \ecd
@@
 We want to show that $\psi$ extends to a regular morphism. 
-Notice that $ \hat{\mathcal C}_i$ is normal, $i=1,2$.
-Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hat{\mathcal C}_i$ is regular in codimension $1$.
+Notice that $ \hat{\cC}_i$ is normal, $i=1,2$.
+Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hat{\cC}_i$ is regular in codimension $1$.
 Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy Serre's condition $S_2$, so does the total space of $\hC_i$ by \cite[Thorem~23.9]{MAT}.
 Then, since the geometric fibers of $\phi_i$ are either points or $p_a=1$ subcurves, and in either case connected, Zariski's connectedness theorem implies that
-\[\phi_{i,*}\OO_{\cC_S}\cong \OO_{\hat{\mathcal C}_i}. \]
+\[\phi_{i,*}\OO_{\cC_S}\cong \OO_{\hat{\cC}_i}. \]
  Moreover by construction $\operatorname{Exc}(\phi_1)=\operatorname{Exc}(\phi_2)$ is the locus of elliptic tails of weight $0$, so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then \cite[Lemma 1.15]{debarre}
@@
 \Z \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\mathfrak M_1^{\rm{wt}}\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
+\MM_1^{\rm{wt}}\ar[r] & \MM_1^{\rm{wt}}(1)
 \ecd
@@
 \oM_1(\PP^4,d)\ar[d] & \pazocal Z \ar[l,hook,swap,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d) \ar[d] \\
-\MM^{\rm{wt}}_1 & \X\ar[l,swap,"\sim"]\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
+\MM^{\rm{wt}}_1 & \X\ar[l,swap,"\sim"]\ar[r] & \MM_1^{\rm{wt}}(1)
 \ecd
@@
 \XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1{(1)} \ar[d] \\
-\X\ar[r] & \mathfrak M_1^{\rm{wt}}(1)
+\X\ar[r] & \MM_1^{\rm{wt}}(1)
 \ecd
@@
 On the other hand notice that
-\[ \X\times_{\mathfrak M_1^{\rm{wt}}(1)} \mathfrak M_1^{\rm{div}}(1) \to \mathfrak M_1^{\rm{div}} \]
+\[ \X\times_{\MM_1^{\rm{wt}}(1)} \MM_1^{\rm{div}}(1) \to \MM_1^{\rm{div}} \]
 is an isomorphism. We just check on points.

### 2018-01-09 draft_merged.tex
notazione in Sec.3 e localised virtual pullback commuta con pushforward

@@
 \newtheorem{prop}[thm]{Proposition}
+\newtheorem{defprop}[thm]{Definition-Proposition}
 \newtheorem{cor}[thm]{Corollary}
@@
 \begin{dfn}
-Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective reduced connected $n$-marked curves of arithmetic genus $1$ that are weighted-stable with total weight $d$, i.e.
+Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective connected, reduced, $n$-marked, projective curves of arithmetic genus $1$ that are weighted-stable with total weight $d$, i.e.
 the weight is nonnegative, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least \emph{two} special points).
 \end{dfn}
-
-We shall denote by $\hat{\pi}\colon \widehat{\cC}\to \MM_{1,n}(1)$ the universal curve (and use similar notation for all its pullbacks).
-We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$ of $\widehat{\cC}\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ with universal line bundle $\widehat{\mathcal{L}}$.
+\begin{remark}
+ It follows from the miniversal deformation of the cusp that being at worst cuspidal (i.e. having only nodes and cusps as singolarity) is an open condition on the base of any family of curves.
+\end{remark}
+
+We shall denote by $\hat{\pi}\colon \widehat{\cC}\to \MM_{1,n}(1)$ the universal curve (and use similar notation for its pullbacks).
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$ of $\widehat{\cC}\to \mathfrak M_{1,n}(1)$ with universal line bundle $\widehat{\mathcal{L}}$ subject to similar stability conditions to the one spelled out for nodal curves.
 We shall often use shorthand notation $\widehat{\MM}$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}(1)$ and $\widehat{\mathfrak P}$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}(1)$.
@@
 
-$\dvr$ shall always denote the spectrum of a discrete valuation ring (DVR) with closed point $0$ and generic point $\eta$.
+We sometimes work on $\MM_{1,n}^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor, which we may ask to be weighted stable in order to make this space compatible with $\MM$ and $\mathfrak P$ above.
+More precisely $\MM_{1,n}^{\rm{div}}$ can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields} and Section \ref{section:p-fields} below), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
+Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\cC,[\Aaff^1/\Gm])$; then we pick the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
+The morphism $\MM_{1,n}^{\rm{div}}\to\mathfrak P$ is obtained by declaring $\mathcal L_{\MM_{1,n}^{\rm{div}}}:=\OO_{\cC}(\pazocal D)$, where $\pazocal D$ is the universal Cartier divisor.
+$\MM_{1,n}^{\rm{div}}(1)$ is defined similarly starting with weighted $1$-stable curves.
+
+We shall always denote the spectrum of a discrete valuation ring (DVR) by $\dvr$, with closed point $0$ and generic point $\eta$.
 
@@
 
-\section{From $p$-fields to the quintic threefold}
+\section{From $p$-fields to the quintic threefold}\label{section:p-fields}
 We introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, we endow it with a cosection-localised $0$-dimensional virtual class supported on a proper substack (depending on the polynomial $\w$), and we show that its degree coincides with the genus $1$ cuspidal invariants of the quintic threefold $X$ up to a sign.
@@
 \begin{lem}\label{lemma:def_X}
- There is a locally closed substack $\mathcal X\subseteq\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ representing morphisms $C\to \widehat{C}$ that contract elliptic tails of weight $0$ to cusps and are weight-preserving isomorphisms everywhere else.
+ There is a locally closed substack $\X\subseteq\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ representing morphisms $C\to \widehat{C}$ that contract elliptic tails of weight $0$ to cusps and are weight-preserving isomorphisms everywhere else.
 \end{lem}
@@
 \begin{lem}\label{lamma:projection_iso}
- The first projection $\pr_1\colon \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)\to\MM$ restricted to $\mathcal X$ is an isomorphism with $\MM$.
+ The first projection $\pr_1\colon \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)\to\MM$ restricted to $\X$ is an isomorphism with $\MM$.
 \end{lem}
@@
 Let $\phi\colon\cC\to\hC$ denote the universal morphism.
-We now proceed to construct $\mathcal X$ as a locally closed substack in the space of morphisms.
+We now proceed to construct $\X$ as a locally closed substack in the space of morphisms.
 
@@
  $\Phi$ and natural projection $\Pi$ to $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
-There exists a locally closed substack $\mathcal{Y'}\subseteq \operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$ representing those morphisms that \emph{preserve the line bundles}.
+There exists a locally closed substack $\pazocal{Y}'\subseteq \operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$ representing those morphisms that \emph{preserve the line bundles}.
 Indeed, given a smooth chart $S\to\operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$, the locus of $s\in S$ where $\Phi_s^*\hL_s\cong\mathcal{L}_s$ is nothing but the locus $T$ where the two sections $\mathcal{L}_S$ and $\Phi_S^*\hL_S$ of $\mathfrak{P}(S)\to\MM(S)$ are isomorphic.
@@
 \item[Step 2] 
-Furthermore there is a closed substack $\mathcal Y\subseteq \mathcal Y'$ representing \emph{surjective morphisms that preserve the markings}.
+Furthermore there is a closed substack $\pazocal{Y}\subseteq \pazocal{Y}'$ representing \emph{surjective morphisms that preserve the markings}.
 
@@
 \item[Step 3] We may now get back to $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
-Let $\mathcal{X}'$ be the image of $\mathcal Y$ under $\Pi$.
+Let $\X'$ be the image of $\pazocal{Y}$ under $\Pi$.
 This is a constructible substack of $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ by Chevalley's theorem \cite[Theorem 5.9.4]{LMB}.
@@
 \item\emph{$\phi$ contracts only components of weight $0$.} We show that this is open.
-Assume that $\dvr$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $\dvr\to\mathcal X'$ such that $\phi_0\colon\cC_0\to \hC_0$ does not contract any component of positive weight.
+Assume that $\dvr$ is a DVR scheme with closed point $0$ and generic point $\eta$, and we are given $\dvr\to\X'$ such that $\phi_0\colon\cC_0\to \hC_0$ does not contract any component of positive weight.
 Suppose there exists an irreducible component $D_\eta\subseteq \cC_{\eta}$ of positive weight $d_D$ which is contracted by $\phi_{\eta}.$ The contracted locus, i.e.
@@
 
-\item\emph{$\phi$ has degree 1 on every non contracted component} or, equivalently, for every $S\to\mathcal X'$ there is an $S$-dense open in $\hC_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
+\item\emph{$\phi$ has degree 1 on every non contracted component} or, equivalently, for every $S\to\X'$ there is an $S$-dense open in $\hC_S$ such that the restriction of $\phi_S$ to its preimage is an isomorphism.
 This is an open and closed condition; we show it is open. Let $\dvr$ be a DVR scheme as above and assume that $\phi_0$ satisfies the property. Since $\phi_\dvr$ is proper, we may consider 
@@
 \end{enumerate} 
-We want to avoid the second scenario, so we define the open substack $\mathcal X\subseteq \mathcal X'$ as follows.
-Given $\mathcal{C}_S\to\hC_S\in\mathcal X'(S)$, let $U\subseteq \hC$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U)}\colon\phi_S^{-1}(U)\to U$ is an isomorphism, and $V$ its closed complement in $\hC_S$.
-Then $\mathcal X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(V)}\colon \phi^{-1}(V)\to S$ are geometrically connected.
+We want to avoid the second scenario, so we define the open substack $\X\subseteq \X'$ as follows.
+Given $\mathcal{C}_S\to\hC_S\in\X'(S)$, let $U\subseteq \hC$ be the \emph{maximal} $S$-dense open subset such that $\phi_S|_{\phi_S^{-1}(U)}\colon\phi_S^{-1}(U)\to U$ is an isomorphism, and $V$ its closed complement in $\hC_S$.
+Then $\X$ is the open locus \cite[\href{http://stacks.math.columbia.edu/tag/055G}{Tag 055G}]{stacks-project} where the fibers of $\pi|_{\phi^{-1}(V)}\colon \phi^{-1}(V)\to S$ are geometrically connected.
 \end{description} 
-This concludes the construction of the locally closed substack $\mathcal X\subseteq \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
+This concludes the construction of the locally closed substack $\X\subseteq \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$.
  \end{proof}
@@
  This result will follow from an application of Zariski's Main Theorem for algebraic spaces.
-First we claim that the projection $\pr_{1|\mathcal X}\colon\mathcal X\to \MM$ is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points.
+First we claim that the projection $\pr_{1|\X}\colon\X\to \MM$ is \emph{representable by algebraic spaces}: by \cite[\href{http://stacks.math.columbia.edu/tag/04Y5}{Tag 04Y5}]{stacks-project} we only need to check that it is faithful, and by \cite[Theorem 2.2.5]{CONR} it is enough to look at geometric points.
 Hence we need to say that, given $\phi\colon C\to \widehat{C}$ a $K$-point of $\X$, we have
@@
 
-Secondly $\pr_{1|\mathcal X}$ is \emph{proper}: this can be seen using the valuative criterion:
-\bcd
-\eta'=\operatorname{Spec}(K')\ar[r]\ar[d] & \eta=\operatorname{Spec}(K)\ar[r]\ar[d] & \mathcal X \ar[d] \\
+Secondly $\pr_{1|\X}$ is \emph{proper}: this can be seen using the valuative criterion:
+\bcd
+\eta'=\operatorname{Spec}(K')\ar[r]\ar[d] & \eta=\operatorname{Spec}(K)\ar[r]\ar[d] & \X \ar[d] \\
 \dvr'=\operatorname{Spec}(R')\ar[r]\ar[urr,dashed,"\exists?", left] & \dvr=\operatorname{Spec}(R)\ar[r] & \MM
@@
 \end{enumerate}
-Finally observe that the map is bijective by construction and $\MM$ is normal, hence $\pi_{|\mathcal X}\colon\mathcal X\to \MM$ is an isomorphism by Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
+Finally observe that the map is bijective by construction and $\MM$ is normal, hence $\pi_{|\X}\colon\X\to \MM$ is an isomorphism by Zariski's main theorem (as in \cite[\href{http://stacks.math.columbia.edu/tag/082I}{Tag 082I}]{stacks-project}).
  \end{proof}
@@
 The idea behind this construction is essentially due to Hassett \cite[\S2]{HassettHyeon} and it has recently been reviewed and simplified in \cite[\S3.7]{RSPW}.
-
-Let $\mathfrak{P}=\mathfrak{Pic}^{d,rm{st}}_{\cC/\MM_1}$ with the stability condition that the line bundle $\omega_\pi\otimes \mathcal L^{\otimes 3}$ on the universal curve is $\pi$-relatively ample.
-
-We work over $\MM_1^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor.
-More precisely, this can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields} and Section \ref{section:p-fields} above), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
-Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\cC,[\Aaff^1/\Gm])$; then again one picks the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
+For simplicity we will work with unmarked curves, which is indeed the case of interest when looking at the Gromov-Witten theory of a Calabi-Yau threefold.
 
@@
 
-Let $E$ be the locus inside the universal curve spanned by elliptic tails of weight $0$; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $E$.
+Let $\pazocal E$ be the locus inside the universal curve spanned by elliptic tails of weight $0$; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $\pazocal E$.
 We shall also denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$ (and its various pullbacks), which is a Cartier divisor as well.
@@
 \begin{equation}\label{eq:linebundlecontraction}
-\mathcal N:=\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D),
-\end{equation} where $D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$ (so $\mathcal O_{\cC}(D)$ is the pullback of the universal line bundle on $\pP$).
-Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so the Proj construction applied to it will contract this locus.
+\mathcal N:=\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D),
+\end{equation} where $\pazocal D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$.
+Notice that $\mathcal N$ is trivial on the locus of elliptic tails, so the Proj construction applied to $\mathcal N$ will contract this locus.
 
@@
  \bcd
- (\cC,D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hC=\operatorname{Proj}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(D))\ar[ld,"\hat\pi"] \\
+ (\cC,\pazocal D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hC=\underline{\operatorname{Proj}}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(\pazocal D))\ar[ld,"\hat\pi"] \\
  & \MM_1^{\rm{div}} &
  \ecd
-This defines the $1$-stabilisation morphism $\MM_1^{\rm{div}}\to\MM_1^{(1),\rm{div}}$.
+This defines the $1$-stabilisation morphism $\MM_1^{\rm{div}}\to\MM_1^{\rm{div}}(1)$.
 \end{prop}
@@
 We need to prove that $\mathcal N$ is $\pi$-semi-ample (regularity of $\phi$) and that $\pi_*\mathcal N$ is locally free (flatness of $\hat\pi$).
-Both these facts are clear generically, but less so on points of $E$ and $\mathfrak D^1$.
-We shall check this by exploiting the next lemma, which is a nice technical gadget drawn from \cite{RSPW}: it implies that the $\Proj$ construction we perform commutes with base-change to generic curves inside $\MM_1^{\rm{div}}$, allowing us to work with a smoothing of the elliptic tail over a DVR scheme $T$.
+Both these facts are clear generically, but less so on points of $\pazocal E$ and $\mathfrak D^1$.
+We shall check this by exploiting the next lemma, which is a nice technical gadget taken from \cite{RSPW}: the $\Proj$ construction we are interested in commutes with base-change to generically chosen curves inside $\MM_1^{\rm{div}}$, allowing us to work with a smoothing of the elliptic tail over a DVR scheme $\dvr$.
 
@@
 Let $\pi\colon\cC\to S$ be a proper family of curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\mathfrak D\subseteq S$.
-Then for every spectrum of a DVR $T$ with closed point $0$ and generic point $\eta$, and for every morphism $f\colon T\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
-\[f^*\pi_*\mathcal N\cong \pi_*f^*\mathcal N.\]
+Then for every spectrum of a DVR $\dvr$ with closed point $0$ and generic point $\eta$, and for every morphism $f\colon \dvr\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
+\[f^*\pi_*\mathcal N\cong \pi_{\dvr,*}f_\cC^*\mathcal N.\]
 %We have denoted with $\mathfrak{D}^1$ the Cartier divisor image of the locus spanned by elliptic tails.
@@
 The argument can be found in \cite[Lemmma~3.7.2.2]{RSPW}.
-\begin{color}{gray}{
+\begin{comment}{
 Let $K^{\bullet}$ the complex of locally free sheaves on $S$ which satisfy cohomology and base change, i.e. such that for any $T\xrightarrow{f} S$  we get
@@
 It immediately follows that $ \rm{L}_2f^*\R^1\pi_*\mathcal M=0.$ Finally notice that since the image of $f$ is not contained in the boundary divisor $f^*g\neq 0$ and thus injective of sheaves as $T$ is a DVR.
-We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.}\end{color}
+We can then conclude $ \rm{L}_1f^*\R^1\pi_*\mathcal M=0$ as well which implies the Lemma.}\end{comment}
 \end{proof}
@@
 On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ we see that $\R^1\pi_*\mathcal N=0$, so $\pi_*\mathcal N$ satisfies Cohomology and Base Change and its rank is determined by Riemann-Roch.
-Given a point $x$ on the boundary $\mathfrak{D}^1$, we can pick a DVR scheme $T$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank at $x$ by looking at $\pi_*f^*\mathcal N$ over $T.$ Now $f^*\mathcal N$ is flat over $T$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free (constant rank).
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can pick a DVR scheme $\dvr$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank at $x$ by looking at $\pi_*f^*\mathcal N$ over $\dvr.$ Now $f^*\mathcal N$ is flat over $\dvr$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free (constant rank).
 \end{proof}
@@
  \bcd
- (\cC_S,D_S)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hat \cC_S=\operatorname{Proj}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(D_S))\ar[ld,"\hat\pi"] \\
+ (\cC_S,\pazocal D_S)\ar[rr,"\phi_S"]\ar[dr,"\pi_S"] & & (\hC_S=\underline{\operatorname{Proj}}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(\pazocal D_S))\ar[ld,"\hat\pi_S"] \\
  & S &
  \ecd
-where $\phi$ is a proper and birational morphism since $\mathcal N$ is $\pi$-semi-ample and $\hat{\pi}$ is flat since $\pi_*\mathcal N$ is locally free. 
+where $\phi_S$ is a proper and birational morphism since $\mathcal N$ is $\pi_S$-semi-ample and $\hat{\pi}_S$ is flat since $\pi_{S,*}\mathcal N$ is locally free. 
 To verify that this defines a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{\cC}_S$ has reduced fibers and only nodes and cusps as singularities.
 
-Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $T$ chosen as in Lemma~\ref{DVR}, so that the construction commutes with base change.
-Furthermore we can pick $f\colon T\to S$ such that the total space $\cC_T$ is regular, so we may just apply Smyth's Contraction Lemma~\cite[Lemma~2.13]{SMY1}.
+Since these properties only concern the fibers of $\hat{\pi}$ we can verify them after base change to a DVR scheme $\dvr$ chosen as in Lemma~\ref{DVR}, so that the construction commutes with base-change.
+Furthermore we can pick $f\colon \dvr\to S$ such that the total space $\cC_\dvr$ is regular, so we may just apply Smyth's Contraction Lemma~\cite[Lemma~2.13]{SMY1}.
 
@@
 \bcd
-\MM_1^{\rm{div}}\ar[r]\ar[d]\ar[dr,phantom,"\curvearrowright"] & \MM_1^{\rm{div}}(1)\ar[d] \\
+\MM_1^{\rm{div}}\ar[r]\ar[d]\ar[dr,phantom,"\circlearrowright"] & \MM_1^{\rm{div}}(1)\ar[d] \\
 \MM_1^{\rm{wt}}\ar[r,"\exists"] & \MM_1^{\rm{wt}}(1)
@@
 \begin{proof}
-{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose smooth sections $s_i$ of the universal curve in a way that their sum as a relative Cartier divisor $D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
-If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, up to taking an {\'e}tale cover we can assume there are sections $s_i$ of $\cC_S\to S$ that define a lifting $S\to \MM_1^{\rm{div}}$, and thus a morphism $\xi\colon S\to  \MM_1^{\rm{wt}}(1)$ through the above construction.
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose smooth sections $s_i$ of the universal curve in a way that their sum as a relative Cartier divisor $\pazocal D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
+If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, this observation allows us to define a lifting $S\to \MM_1^{\rm{div}}$, and thus a morphism $\xi\colon S\to  \MM_1^{\rm{wt}}(1)$ through the construction of Proposition \ref{1-stabilization-div}.
 
@@
 
-This boils down to checking that for two different choices of a lifting $D_1,D_2\colon S\to\MM_1^{\rm{div}}$ there exists a unique isomorphism 
-\[\hat{\cC}_1=\operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_1))^{\otimes n}\right)\cong \operatorname{Proj}_S\left((\omega_{\pi}(E)\otimes\mathcal O_{\cC}(3D_2))^{\otimes n}\right)=\hat{\cC}_2.
-\]
-By construction there is a birational map $\psi$
+This boils down to checking that for two different choices of a lifting $\pazocal D_1,\pazocal D_2\colon S\to\MM_1^{\rm{div}}$ there exists a unique isomorphism 
+\[\hC_1=\underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D_1))^{\otimes n}\right)\cong \underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D_2))^{\otimes n}\right)=\hC_2.
+\]
+By construction there is a birational map $\psi$:
  \bcd
 &\cC_S \ar[dl,"\phi_1" above left]\ar[dr,"\phi_2"]  \\
- \hat{\cC}_1\ar[rr,dashed, "\psi"] & &\hat{\cC}_2.
+ \hC_1\ar[rr,dashed, "\psi"] & &\hC_2.
  \ecd
@@
 We want to show that $\psi$ extends to a regular morphism. 
-Notice that $ \hat{\cC}_i$ is normal, $i=1,2$.
-Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hat{\cC}_i$ is regular in codimension $1$.
+Notice that $ \hC_i$ is normal, $i=1,2$.
+Indeed since $S$ is smooth and the singularities of the fibers are in codimension $1$, $ \hC_i$ is regular in codimension $1$.
 Moreover since both $S$ (smooth) and the fibers (Cohen-Macaulay) satisfy Serre's condition $S_2$, so does the total space of $\hC_i$ by \cite[Thorem~23.9]{MAT}.
 Then, since the geometric fibers of $\phi_i$ are either points or $p_a=1$ subcurves, and in either case connected, Zariski's connectedness theorem implies that
-\[\phi_{i,*}\OO_{\cC_S}\cong \OO_{\hat{\cC}_i}. \]
+\[\phi_{i,*}\OO_{\cC_S}\cong \OO_{\hC_i}. \]
  Moreover by construction $\operatorname{Exc}(\phi_1)=\operatorname{Exc}(\phi_2)$ is the locus of elliptic tails of weight $0$, so in particular $\phi_2$ contracts all fibers of $\phi_1.$ Then \cite[Lemma 1.15]{debarre}
@@
 \subsection{Fiber products and induced obstruction theories}
+In this last part of the section we exploit the $1$-stabilisation morphism to introduce some auxiliary spaces with a virtual class that are going to be useful in comparing cuspidal with reduced invariants of the quintic threefold.
 Let $\Z$ be defined by the pullback diagram:
@@
 
-Objects of $\Z$ over $S$ consist of diagrams
-\bcd
-C \ar[rr,"\phi"]\ar[dr,"\pi" below left] & & \hat C\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 \\
+Objects of $\Z$ over a scheme $S$ consist of diagrams:
+\bcd
+C \ar[rr,"\phi"]\ar[dr,"\pi" below left] & & \widehat C\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 \\
 & S & & &
 \ecd
-where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisationdefined above (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams
-\bcd
-C\ar[r,"\phi"]\ar[d,"\psi"] &  \hat C\ar[r,"f"]\ar[d,"\hat\psi"] & \PP^4 \ar[d,"\id_\PP"]\\
-C'\ar[r,"\phi'"] &  \hat C'\ar[r,"f'"] & \PP^4
+where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisation (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams:
+\bcd
+C\ar[r,"\phi"]\ar[d,"\psi"] &  \widehat C\ar[r,"f"]\ar[d,"\hat\psi"] & \PP^4 \ar[d,"\id_\PP"]\\
+C'\ar[r,"\phi'"] &  \widehat C'\ar[r,"f'"] & \PP^4
 
@@
 
-Forgetting $\hat C$ and keeping $f\circ\phi\colon C\to\PP^4$, we obtain a morphism $i\colon\Z\to\oM_1(\PP^4,d).$
+Forgetting $\widehat C$ and keeping $f\circ\phi\colon C\to\PP^4$, we obtain a morphism \[i\colon\Z\to\oM_1(\PP^4,d).\]
 
@@
 
-We can check properness using the valuative criterion. We argue as in \cite[Theorem 4.3]{RSPW}. Let $T$ be a DVR scheme with generic point $\eta;$ consider a diagram:
-\bcd
-\cC_{\eta}\ar[r]\ar[d,"\phi_{\eta}" left]  & \cC_T\ar[d,"\phi_T" left]\ar[r,"f"] & \PP^4 \\
-\hat{\cC}_{\eta}\ar[r,"j" below]\ar[urr] & \hat{\cC_T}\ar[ur,dashed ,"g" below right] &
+We can check properness using the valuative criterion. We argue as in \cite[Theorem 4.3]{RSPW}. Let $\dvr$ be a DVR scheme with generic point $\eta;$ consider a diagram:
+\bcd
+\cC_{\eta}\ar[r]\ar[d,"\phi_{\eta}" left]  & \cC_\dvr\ar[d,"\phi_\dvr" left]\ar[r,"f"] & \PP^4 \\
+\hC_{\eta}\ar[r,"j" below]\ar[urr] & \hC_\dvr\ar[ur,dashed ,"g" below right] &
  \ecd 
@@
 
-Observe that $f$ is constant on the fibers of $\phi_T$, so it factors topologically through $\hat{\cC}.$
-We can conclude as in \cite{RSPW} or appeal to \cite[Lemma~1.15]{debarre} using $\phi_*\OO_{\cC_T}\cong\OO_{\hat{\cC}_T}$. To see this consider the exact sequence:
-\[0\to \OO_{\hat{\cC}_T}\to\phi_*\OO_{\cC_T}\to \phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T}\to 0\]
+Observe that $f$ is constant on the fibers of $\phi_\dvr$, so it factors topologically through $\hC.$
+We can conclude as in \cite{RSPW} or appeal to \cite[Lemma~1.15]{debarre} using $\phi_*\OO_{\cC_\dvr}\cong\OO_{\hC_\dvr}$. To see this consider the exact sequence:
+\[0\to \OO_{\hC_\dvr}\to\phi_*\OO_{\cC_\dvr}\to \phi_*\OO_{\cC_\dvr}/\OO_{\hC_\dvr}\to 0\]
 Since $\phi$ is an isomorphism away from the cuspidal point, the cokernel is supported in dimension $0$.
-However $\chi (\OO_{\hat{\cC}_\eta})=\chi(\phi_*\OO_{\cC_\eta})$ implies the same equality holds on the whole of $T$, since the Euler characteristic is constant in flat families.
-So $\chi(\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T})=\operatorname{length}(\phi_*\OO_{\cC_T}/\OO_{\hat{\cC}_T})=0.$
+However $\chi (\OO_{\hC_\eta})=\chi(\phi_*\OO_{\cC_\eta})$ implies the same equality holds on the whole of $\dvr$, since the Euler characteristic is constant in flat families.
+So $\chi(\phi_*\OO_{\cC_\dvr}/\OO_{\hC_\dvr})=\operatorname{length}(\phi_*\OO_{\cC_\dvr}/\OO_{\hC_\dvr})=0.$
 \end{proof}
@@
 
-From the inclusion $i$ we easily obtain a description of the irreducible components of $\Z$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
+ A description of the irreducible components of $\Z$ can be easily obtained from the inclusion $i$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
 
@@
 
-We introduce two more relevant spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
+We introduce two more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
 \bcd
@@
 
-The obstruction theory $\R^\bullet\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\widehat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by virtual pullback of $[\XP]$.
-In Section \ref{section:main_proof} we shall conduct on this a similar analysis to that in \cite{CL} and compare the contribution of the main component to Vakil-Zinger's reduced invariants.
+The obstruction theory $\R^\bullet\hat{\pi}_*(\hL^{\oplus 5}\oplus\widehat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by localised virtual pullback of $[\XP]$.
+%In Section \ref{section:main_proof} we shall analyse this cycle adapting the arguments in \cite{CL}.
 
@@
 \bcd
-C\ar[rr,"\phi"]\ar[dr] & & \hat C\ar[ld] \\
+\cC_S \ar[rr,"\phi_S"]\ar[dr] & & \hC_S\ar[ld] \\
 & S &
 \ecd
-with a line bundle $\hat{\mathcal L}$ on $\hat{C}$.
-Notice that by pulling back $\hat{\mathcal L}$ via $\phi$ we obtain a line bundle on $C$, hence a morphism $\XP\to \mathfrak{Pic}_1$.
-This is generically an isomorphism, but has $1$-dimensional fibers over the locus of elliptic tails, due to the fact that $\Pic(\hat C)\to\Pic(C)$ has kernel $\mathbb G_{\rm a}$ when $\hat C$ has a cusp.
+with a line bundle $\hL_S$ on $\hC_S$.
+Notice that by pulling back $\hL_S$ via $\phi_S$ we obtain a line bundle on $\cC_S$, hence a morphism $\XP\to \mathfrak{Pic}_1$.
+This is generically an isomorphism, but has $1$-dimensional fibers over the locus of elliptic tails, due to the fact that $\Pic(\widehat C)\to\Pic(C)$ has kernel $\mathbb G_{\rm a}$ when $\widehat C$ has a cusp.
 \end{remark}
-On the other hand notice that
-\[ \X\times_{\MM_1^{\rm{wt}}(1)} \MM_1^{\rm{div}}(1) \to \MM_1^{\rm{div}} \]
-is an isomorphism. We just check on points.
-\marginpar{I am not sure, CHECK ME.}
+%On the other hand notice that
+%\[ \X\times_{\MM_1^{\rm{wt}}(1)} \MM_1^{\rm{div}}(1) \to \MM_1^{\rm{div}} \]
+%is an isomorphism. We just check on points.
+%\marginpar{I am not sure, CHECK ME.}
 \begin{comment}
@@
 \bcd
-C\ar[rr,"\phi"]\ar[dr,"\pi" below left] & & \hat C\ar[ld,"\hat\pi"] \ar[r,"f"] & \PP^4\\
+\cC_S\ar[rr,"\phi_S"]\ar[dr,"\pi_S" below left] & & \hC_S\ar[ld,"\hat\pi_S"] \ar[r,"f_S"] & \PP^4_S\\
 & S & &
 \ecd
-with a $p$-field $\psi\in H^0(\hat C,f^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi})$.
-
-We were not able to compare $\Z^p$ with $\oM_1(\PP^4,d)^p$ directly, since denoting by $\hat{\mathcal L}=f^*\OO_{\PP^4}(1)$ and by $\mathcal L=\phi^*\hat{\mathcal L}$ we only have a map $\R^1\hat\pi_*\hat{\mathcal L}\to\R^1\pi_*\mathcal L$ on $\Zp$ which is not an isomorphism (dually, since $\phi^*\omega_{\hat\pi}=\omega_{\pi}(E)$, the $p$-fields on $C$ that we get by pulling back from $\hat C$ vanish on elliptic tails).
+with a $p$-field $\psi\in H^0(\hC_S,f_S^*\OO_{\PP^4}(-5)\otimes\omega_{\hat\pi_S})$.
+
+We were not able to compare $\Z^p$ with $\oM_1(\PP^4,d)^p$ directly, since denoting by $\hL=f^*\OO_{\PP^4}(1)$ and by $\mathcal L=\phi^*\hL$ we only have a map $\R^1\hat\pi_*\hL\to\R^1\pi_*\mathcal L$ on $\Zp$ which is not an isomorphism (dually, since $\phi^*\omega_{\hat\pi}=\omega_{\pi}(\pazocal E)$, the $p$-fields on $\cC$ that we get by pulling back from $\hC$ vanish on elliptic tails).
 \end{remark}
 
-As anticipated we may endow $\Z^p$ with a localised virtual cycle by ``localised virtual pullback''.
+\subsection{Cosection Localized Virtual Pull-Back}
+In this section we define an analogous of virtual pull-back \cite{Manolache} for localised cycles and we show that this operation commutes with proper push-forward. 
+For the non expert reader, we first recall the basic construction of \cite{KLcosection}.
+Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ over $Y$ be a vector bundle admitting a cosection
+\[E\xrightarrow{\sigma}\OO_Y\]
+surjective on an open $U$ and denote by $Y(\sigma)=Y\setminus E(\sigma).$ We use the following notation:
+\[G=\operatorname{Ker}\left(E\rvert_U\to\OO_Y\rvert_U\right),\qquad E(\sigma)=E\rvert_{Y(\sigma)}\cup G.\]
+ In the above setting we want to define a localized Gysin map
+ \[s^!_{\sigma,\rm{loc}}\colon A_*(E(\sigma))\to A_*(Y(\sigma)).\]
+ Let $B\in Z_*(E(\sigma)$ be a cycle represented by a closed integral sub-stack. If $B\subset  E\rvert_{Y(\sigma)}$ then
+ \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma))\]
+ and there is nothing to say as this is just the standard Gysin morphism.
+ Suppose now $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then choose a variety $X\xrightarrow{\nu} Y$ such that:
+ \begin{itemize}\label{cond:deflocal}
+ \item $\nu$ is proper and $\nu(X)\cap U\neq\emptyset$;
+ \item The pull-back along $\nu$ of the cosection $\tilde{\sigma}=\nu^*\sigma$ give a surjective morphism
+ \[\nu^*E\xrightarrow{\tilde{\sigma}}\OO_X(D)\to 0\]
+ for $D$ a Cartier divisor in $X.$ Notice that the restriction of $\nu$ to the divisor give a proper morphism $D\xrightarrow{\nu(\sigma)} Y(\sigma);$
+ \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb Z.$
+ \end{itemize}
+ We the define
+ \[s^!_{\sigma,\rm{loc}}[B]:=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
+ In \cite[\S~2]{KLcosection} they prove that: such an $X$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent from the choice of $X;$ the construction preserves rational equivalences and thus define the wanted morphism.
+ \begin{remark}
+ If we consider as cycle in $E(\sigma)$ $[Y]$ thought as zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$
+ \end{remark}
+  Once defined such a operation, to get Theorem~1.1 in \cite{KLcosection} one would still need to show that: the same operation can be defined when we have a cosection of a vector bundle stacks $\mathbb E$ (easy to do if we have a surjection from a genuine vector bundle $E\to\mathbb E$, which is the situation in our case); the relative cone $\mathfrak C_{Y/S}\subseteq\mathbb{E}(\sigma),$ a sufficient condition for the latter to hold is that the cosection of the relative obstruction lifts to a cosection of the absolute obstruction \cite[Corollary~4.5]{KLcosecion}.
+\begin{defprop}
+Let consider the cartesian diagram of algebraic stacks
+\bcd
+Y'\ar[r,"\varphi'"]\ar[d,"\rho'"] & Y\ar[d,"\rho"]\\
+S'\ar[r,"\varphi"] & S
+\ecd
+such that $\rho$ is a morphism of DM type admitting a perfect obstruction theory $\mathbb E_{Y/S}.$ Assume furthermore that we have a cosection 
+\[\OO b_{Y/S}\to \OO_Y\]
+lifting to a cosection of the absolute obstruction sheaf.
+Then we can define a localised virtual cycle on $Y'$ supported on $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ where $\sigma'=\varphi'^*\sigma.$
+Pulling back along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=\varphi'^*\mathbb E_{Y/S}.$ Furthermore, we can pull back the cosection 
+\[\OO b_{Y'/S'}\cong \varphi^* \OO b_{Y/S}\xrightarrow{\sigma'}\OO_{Y'}.\]
+Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well and it is plain that the degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that
+\[\varphi'^*\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y'/S'}(\sigma').\]
+Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
+\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
+By \cite[Corollary 5.4]{KLcosection} or by cartesianity of the diagram plus the discussion above,
+\[\mathfrak{C}_{Y'/S'}\subseteq \varphi'^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
+and we can thus define the localized virtual pull-back to be:
+\[\varphi'^!_{\rm{loc}}[Y]^{\rm{vir}}_{\rm{loc}}=[Y']_{\rm{loc}}^{\rm{vir}}=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}],\]
+compare also with \cite[Theorem~5.2]{KLcosection}
+\end{defprop}
+
+The above construction applies to $\Z^p$.
 Indeed, consider on $\Z^p$ the perfect obstruction theory $\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)$ and the induces cosection
@@
 and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}.$
-\begin{color}{red}
-\begin{lem}
-localised virtual pullback commutes with pushforward. In particular,
-\[\alpha_* [\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}=[{\Mone{1}{\PP^4}{d}^p}]^{\rm{vir}}_{\sigma,\rm{loc}}\] 
-\end{lem}
-\end{color}
-\marginpar{check \cite{KLcosection}, probably needs the proper morphism to be surjective}
+\begin{lem}\label{lem:comutativity}
+In the setting of the localised virtual-pullback definition, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$ then
+for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$
+\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)) 
+\end{equation}
+where $\varphi^{\mathbb{E}}\colon \varphi'^*\mathbb{E}(\sigma')\to \mathbb{E}(\sigma)$ is the natural induced morphism.
+\end{lem}
+\begin{proof}
+If $B'\subset \mathbb{E}\rvert_{Y'(\sigma')}$ then $\varphi(\sigma)(B')\subset \mathbb{E}\rvert_{Y(\sigma)}$
+thus the localised Gysin morphism are just $s^!_{\mathbb{E}\rvert_{Y'(\sigma')}}$, $s^!_{\mathbb{E}\rvert_{Y(\sigma)}}$ and the fact they commute with proper push-forward is already well known, see \cite{Kresh} or simply \cite[Chapter~4]{Fulton} if we assume the existence of global resolutions.
+
+Let now $B'$ be a (integral) cycle in $\mathbb{E}(\sigma')$ not contained in  the restriction of the vector bundle stack to the degeneracy locus of $\sigma'.$ Then, accordingly to the construction recalled at the beginning of this section,
+ \[s^!_{\sigma',\rm{loc}}[B']:=k^{-1} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')).\]
+ where $\nu'\colon X\to Y'$ and $\nu'*\sigma'$ satisfy conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
+ $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi} Y$ and the pull-back $\nu^*\sigma,$ the first two conditions in \eqref{cond:deflocal} are satisfied for any $B\in A_*(\mathbb E(\sigma)).$ 
+ Consider 
+ \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B'):=B.\]
+ Suppose first that $B'\to B$ is generically finite of degree $h$, then $\widetilde{B}\to B$ satisfy the last condition in \eqref{cond:deflocal} and
+ \begin{align*}
+ \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= k^{-1}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
+ &=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
+ &=h\, s_{\sigma,\rm{loc}}^![B]\\
+ &=s_{\sigma,\rm{loc}}^!(\varphi^{\mathbb{E}}_*[B'])
+ \end{align*}
+If instead $B'\to B$ is not generically finite, then the RHS  in \eqref{eq:commcos} is zero. Let us show that the same is true for the LHS. By \cite[Lemma~2.7]{KLcosection}, to show that 
+\[\operatorname{LHS}=\nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)=0\,\in A_*(Y(\sigma)),\]
+with $[\widetilde{B}]\in \, Z_*(G),$
+it is enough to show that $\nu_*^{\mathbb{E}}[\widetilde B]$ is zero in $A_*(\mathbb{E})$ where $\nu^{\mathbb{E}}$ is the natural morphism induced by $\nu.$ Then it is immediate, indeed since  $\nu^{\mathbb{E}}=\varphi^{\mathbb{E}}\circ\nu'^{\mathbb{E}}$  and we assumed $\varphi^{\mathbb{E}}\colon B'\to B$ has fibers of positive dimension, $\nu_*^{\mathbb{E}}[\widetilde B]=0$ by definition of proper push-forward.
+
+\end{proof}
 
@@
 \end{cor}
+\begin{proof}
+We show that
+\[\alpha_*[\Z^p]^{\alpha^*\sigma_1,\rm{vir}}_{\rm{loc}}=[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\sigma_1,\rm{loc}},\]
+then the statement follow given that $\alpha$ is generically 1 to 1.
+Notice  first of all that the 1-stabilisation $\mathfrak{M}_1^{\rm{w}}\to \mathfrak{M}_1^{1,\rm{w}}$ is proper.
+As usual, we use the lifting criterion and thus we have to show that, up to a base change, the dashed arrow and the $\mathcal C$ in the following commutative diagram exist
+\bcd
+\mathcal C_{\eta}\ar[d,"\phi_{\eta}"] \ar[r,dashed, hookrightarrow] &\mathcal C\ar[d, dashed, "\phi"]\\
+\hat{\mathcal C_{\eta}}\ar[r, hookrightarrow] &\hat{\mathcal{C}}
+\ecd
+where the family are over a DVR $T$ and $\eta$ is its generic point.
+We can in fact assume that $\phi_{\eta}$ is an isomorphism and then notice that it is enough to consider the semi-stable model of $\hat{\mathcal C}.$
+Thus, since the 1-stabilisation $\phi$ is generically an isomorphism it follows that
+\[\phi_*[\mathfrak{M}_1^{\rm{w}}]=[\mathfrak{M}_1^{1,\rm{w}}]\]
+and analogously,
+\[\phi_*[\XP]=[\mathfrak{Pic_1{(1)}}]\]
+Finally, recall that the deformation to the normal cone construction ensures the commutativity of
+\bcd
+A_*(\XP)\ar[r,"\zeta'"]\ar[d,"\phi_*"] & A_*(\mathfrak C_{\Z^p/\XP}) \ar[d,"\phi(\sigma)_*"]\\
+A_*(\mathfrak{Pic_1{(1)}})\ar[r,"\zeta"] & A_*(\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}})
+\ecd
+and thus 
+\[\phi(\sigma)_*[\mathfrak C_{\Z^p/\XP}]\cong [\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}].\]
+The identity at the level of virtual classes now follows from the definition of cosection localised virtual class and Lemma~\ref{lem:comutativity}.
+\end{proof}
 

### 2018-01-09 draft_merged.tex
part. revised loc vir pb commutes with pf

@@
 \bcd
-\Z^p \ar[r,"\alpha"]\ar[d]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
+\Z^p \ar[r,"\alpha"]\ar[d,"\gamma"]\ar[rd,phantom,"\Box"] & \overline{\mathcal M}_1^{(1)}(\PP^4,d)^p \ar[d] \\
 \XP \ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \mathfrak{Pic}_1{(1)} \ar[d] \\
@@
 
-\subsection{Cosection Localized Virtual Pull-Back}
-In this section we define an analogous of virtual pull-back \cite{Manolache} for localised cycles and we show that this operation commutes with proper push-forward. 
-For the non expert reader, we first recall the basic construction of \cite{KLcosection}.
-Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ over $Y$ be a vector bundle admitting a cosection
+\subsection{Cosection-localised virtual pullback}
+In this section we slightly generalise the notion of virtual pullback \cite{Manolache-pullback} to localised cycles and we show that this operation commutes with proper pushforward. 
+We start by recalling the construction of \cite{KLcosection} for the benefit of the non-expert reader.
+
+Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ be a vector bundle over $Y$ admitting a cosection
 \[E\xrightarrow{\sigma}\OO_Y\]
-surjective on an open $U$ and denote by $Y(\sigma)=Y\setminus E(\sigma).$ We use the following notation:
+surjective on an open $U\subseteq Y$; denote by $Y(\sigma)$ the complement $Y\setminus U.$ Recall the following notation from \cite{KLcosection}:
 \[G=\operatorname{Ker}\left(E\rvert_U\to\OO_Y\rvert_U\right),\qquad E(\sigma)=E\rvert_{Y(\sigma)}\cup G.\]
- In the above setting we want to define a localized Gysin map
+ Kiem and Li define a localized Gysin map:
  \[s^!_{\sigma,\rm{loc}}\colon A_*(E(\sigma))\to A_*(Y(\sigma)).\]
- Let $B\in Z_*(E(\sigma)$ be a cycle represented by a closed integral sub-stack. If $B\subset  E\rvert_{Y(\sigma)}$ then
- \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma))\]
- and there is nothing to say as this is just the standard Gysin morphism.
- Suppose now $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then choose a variety $X\xrightarrow{\nu} Y$ such that:
+ Let $[B]\in Z_*(E(\sigma))$ be a cycle represented by a closed integral substack. If $B\subset  E\rvert_{Y(\sigma)}$ then
+  they just consider the standard Gysin morphism: \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma)).\]
+ Suppose now that $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then we may choose a variety $X\xrightarrow{\nu} Y$ such that:
  \begin{itemize}\label{cond:deflocal}
  \item $\nu$ is proper and $\nu(X)\cap U\neq\emptyset$;
- \item The pull-back along $\nu$ of the cosection $\tilde{\sigma}=\nu^*\sigma$ give a surjective morphism
+ \item the pullback along $\nu$ of the cosection $\nu^*\sigma=:\tilde{\sigma}$ extends to a surjective morphism
  \[\nu^*E\xrightarrow{\tilde{\sigma}}\OO_X(D)\to 0\]
- for $D$ a Cartier divisor in $X.$ Notice that the restriction of $\nu$ to the divisor give a proper morphism $D\xrightarrow{\nu(\sigma)} Y(\sigma);$
- \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb Z.$
+ for a Cartier divisor $D\subseteq X.$ The restriction of $\nu$ to the divisor gives a proper morphism $\nu(\sigma)\colon D\to Y(\sigma);$
+ \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb N.$
  \end{itemize}
- We the define
- \[s^!_{\sigma,\rm{loc}}[B]:=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
- In \cite[\S~2]{KLcosection} they prove that: such an $X$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent from the choice of $X;$ the construction preserves rational equivalences and thus define the wanted morphism.
+ The localised Gysin pullback is then defined as:
+ \[s^!_{\sigma,\rm{loc}}[B]:=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
+ In \cite[\S~2]{KLcosection} they prove that: such $(X,\nu,\widetilde B)$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent of the above choices; the construction preserves rational equivalences and thus defines the desired morphism on Chow groups.
  \begin{remark}
- If we consider as cycle in $E(\sigma)$ $[Y]$ thought as zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$
+ If we consider $[Y]$ as a cycle in $E(\sigma)$, thought of as the zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$
  \end{remark}
-  Once defined such a operation, to get Theorem~1.1 in \cite{KLcosection} one would still need to show that: the same operation can be defined when we have a cosection of a vector bundle stacks $\mathbb E$ (easy to do if we have a surjection from a genuine vector bundle $E\to\mathbb E$, which is the situation in our case); the relative cone $\mathfrak C_{Y/S}\subseteq\mathbb{E}(\sigma),$ a sufficient condition for the latter to hold is that the cosection of the relative obstruction lifts to a cosection of the absolute obstruction \cite[Corollary~4.5]{KLcosecion}.
+  Kiem and Li then proceed to extend the cosection-localised Gysin pullback to vector bundle stacks $h^1/h^0(\mathbb E)$ (this is relatively easy in the presence of a global resolution, which is the case in the situation at hand); they show that the intrinsic normal cone $\mathfrak C_{Y/S}$ is contained in the closed substack $h^1/h^0(\mathbb{E})(\sigma),$ at least when the cosection of the relative obstruction bundle lifts to a cosection of the absolute obstruction bundle \cite[Corollary~4.5]{KLcosection}.
 \begin{defprop}
-Let consider the cartesian diagram of algebraic stacks
-\bcd
-Y'\ar[r,"\varphi'"]\ar[d,"\rho'"] & Y\ar[d,"\rho"]\\
+Consider a cartesian diagram of stacks:
+\bcd
+Y'\ar[r,"\varphi'"]\ar[d,"\rho'"]\ar[dr,phantom,"\Box"] & Y\ar[d,"\rho"]\\
 S'\ar[r,"\varphi"] & S
@@
 \[\OO b_{Y/S}\to \OO_Y\]
-lifting to a cosection of the absolute obstruction sheaf.
-Then we can define a localised virtual cycle on $Y'$ supported on $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ where $\sigma'=\varphi'^*\sigma.$
-Pulling back along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=\varphi'^*\mathbb E_{Y/S}.$ Furthermore, we can pull back the cosection 
+that lifts to a cosection of the absolute obstruction sheaf $\OO b_Y$.
+Then we can define a localised virtual pullback operation: \[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}\colon A_*(S')\to A_{*-\operatorname{rk}(\mathbb E)}(Y'(\sigma'))\] where $\sigma'=(\varphi')^*(\sigma)$ and $Y'(\sigma')=Y(\sigma)\times_{Y} Y'$.
+\end{defprop}
+Replace $S'$ by a primitive cycle in it, i.e.
+assume that $S'$ is irreducible and reduced.
+Recall that pulling back $\mathbb E_{Y/S}$ along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=(\varphi')^*\mathbb E_{Y/S}.$ Furthermore notice that we can pullback the cosection:
 \[\OO b_{Y'/S'}\cong \varphi^* \OO b_{Y/S}\xrightarrow{\sigma'}\OO_{Y'}.\]
-Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well and it is plain that the degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that
-\[\varphi'^*\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y'/S'}(\sigma').\]
-Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
-\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
-By \cite[Corollary 5.4]{KLcosection} or by cartesianity of the diagram plus the discussion above,
+Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well. The degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that:
+\[h^1/h^0(\mathbb E_{Y'/S'})(\sigma')=(\varphi')^*h^1/h^0(\mathbb E_{Y/S})(\sigma).\]
+%Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
+%\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
+By \cite[Corollary 4.5]{KLcosection} and by the cartesian diagram above,
 \[\mathfrak{C}_{Y'/S'}\subseteq \varphi'^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
-and we can thus define the localized virtual pull-back to be:
-\[\varphi'^!_{\rm{loc}}[Y]^{\rm{vir}}_{\rm{loc}}=[Y']_{\rm{loc}}^{\rm{vir}}=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}],\]
-compare also with \cite[Theorem~5.2]{KLcosection}
-\end{defprop}
+thus we can define the localised virtual pullback of $[S']$ to be:
+\[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}[S']=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}].\]
+%compare also with \cite[Theorem~5.2]{KLcosection}
 
 The above construction applies to $\Z^p$.
-Indeed, consider on $\Z^p$ the perfect obstruction theory $\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)$ and the induces cosection
-\[\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p\]
-whose degeneracy locus is
-\[\pazocal D(\alpha^*\sigma)=\pazocal D(\sigma)\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
+Indeed consider on $\Z^p$ the perfect obstruction theory: \[\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)\] and the induced cosection
+$\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p$
+with degeneracy locus:
+\[\pazocal D(\alpha^*\sigma)=\Mone{1}{X}{d}\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
 Then we have that
 \begin{align*}
-\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\\
-& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)_\sigma\\
-&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)_{\alpha^*\sigma}
+\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
+& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)(\sigma)\\
+&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
 \end{align*}
-and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}.$
+and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].$
 \begin{lem}\label{lem:comutativity}
-In the setting of the localised virtual-pullback definition, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$ then
+With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. then
 for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$

### 2018-01-10 draft_merged.tex
finished reviewing loc vir pb commutes with pf

@@
 By \cite[Corollary 4.5]{KLcosection} and by the cartesian diagram above,
-\[\mathfrak{C}_{Y'/S'}\subseteq \varphi'^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
+\[\mathfrak{C}_{Y'/S'}\subseteq (\varphi')^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
 thus we can define the localised virtual pullback of $[S']$ to be:
@@
 \mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
-& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}\right)(\sigma)\\
+& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)(\sigma)\\
 &\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
@@
 \begin{lem}\label{lem:comutativity}
-With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. then
-for any $[B']\in A_*(\varphi'^*\mathbb{E}(\sigma'))$
-\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)) 
+With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$.
+For every cycle $[B']\in A_*(S')$,
+\[\phi'_*\circ(\rho')^!_{\mathbb E_{Y'/S'}}[B']=(\rho)^!_{\mathbb E_{Y/S}}\circ\phi_*[B]\in A_*(Y(\sigma)).\]
+
+\end{lem}
+\begin{proof}
+Consider the following diagram:
+\bcd
+A_*(S')\ar[r]\ar[d] & A_*(\mathfrak C_{Y'/S'}) \ar[r]\ar[d] & A_*(h^1/h^0(\mathbb E_{Y'/S'})(\sigma'))\ar[r,"s_{\sigma',\rm{loc}}^!"]\ar[d] & A_*(Y'(\sigma'))\ar[d] \\
+A_*(S)\ar[r] & A_*(\mathfrak C_{Y/S}) \ar[r] & A_*(h^1/h^0(\mathbb E_{Y/S})(\sigma))\ar[r,"s_{\sigma,\rm{loc}}^!"] & A_*(Y(\sigma))
+\ecd
+Only the left-most square is not classical. Hence we are left with showing that for every cycle $[B']\in A_*(h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma'))$ we have:
+\begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)),
 \end{equation}
-where $\varphi^{\mathbb{E}}\colon \varphi'^*\mathbb{E}(\sigma')\to \mathbb{E}(\sigma)$ is the natural induced morphism.
-\end{lem}
-\begin{proof}
-If $B'\subset \mathbb{E}\rvert_{Y'(\sigma')}$ then $\varphi(\sigma)(B')\subset \mathbb{E}\rvert_{Y(\sigma)}$
-thus the localised Gysin morphism are just $s^!_{\mathbb{E}\rvert_{Y'(\sigma')}}$, $s^!_{\mathbb{E}\rvert_{Y(\sigma)}}$ and the fact they commute with proper push-forward is already well known, see \cite{Kresh} or simply \cite[Chapter~4]{Fulton} if we assume the existence of global resolutions.
-
-Let now $B'$ be a (integral) cycle in $\mathbb{E}(\sigma')$ not contained in  the restriction of the vector bundle stack to the degeneracy locus of $\sigma'.$ Then, accordingly to the construction recalled at the beginning of this section,
- \[s^!_{\sigma',\rm{loc}}[B']:=k^{-1} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')).\]
- where $\nu'\colon X\to Y'$ and $\nu'*\sigma'$ satisfy conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
- $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi} Y$ and the pull-back $\nu^*\sigma,$ the first two conditions in \eqref{cond:deflocal} are satisfied for any $B\in A_*(\mathbb E(\sigma)).$ 
- Consider 
- \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B'):=B.\]
- Suppose first that $B'\to B$ is generically finite of degree $h$, then $\widetilde{B}\to B$ satisfy the last condition in \eqref{cond:deflocal} and
+where $\varphi^{\mathbb{E}}\colon h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')\to h^1/h^0(\mathbb{E}_{Y/S})(\sigma)$ is induced by the morphism of vector bundle stacks.
+
+If $B'\subset h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$ then $\varphi^{\mathbb E}(B')\subset h^1/h^0(\mathbb{E}_{Y/S})\rvert_{Y(\sigma)}$,
+thus the localised Gysin morphisms coincide with $s^!_{h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}}$ and $s^!_{h^1/h^0(\mathbb{E}_{Y/S})\rvert_{Y(\sigma)}}$, and their commutativity with proper pushforward is well-known, see \cite{Kresch} (or \cite[Chapter~3]{FUL} if we assume the existence of global resolutions).
+
+Assume then that $B'$ is a prime cycle in $h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')$ not contained in $h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$.
+Then, according to the construction recalled at the beginning of this section,
+ \[s^!_{\sigma',\rm{loc}}[B']:=\frac{1}{k} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')),\]
+ where $\nu'\colon X\to Y'$, $(\nu')^*(\sigma')$ and $\widetilde B$ satisfy the conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
+ $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi'} Y$ and the pull-back $\nu^*(\sigma)$, the first two conditions in \eqref{cond:deflocal} are satisfied. How about
+ \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B')=:B?\]
+ Suppose first that $B'\to B$ is generically finite of degree $h$; then $\widetilde{B}\to B$ satisfies the last condition in \eqref{cond:deflocal} and has degree $hk$, so:
  \begin{align*}
- \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= k^{-1}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
- &=k^{-1} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
+ \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= \frac{1}{k}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
+ &=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
  &=h\, s_{\sigma,\rm{loc}}^![B]\\
- &=s_{\sigma,\rm{loc}}^!(\varphi^{\mathbb{E}}_*[B'])
+ &=s_{\sigma,\rm{loc}}^!(\varphi^{\mathbb{E}}_*[B']).
  \end{align*}
-If instead $B'\to B$ is not generically finite, then the RHS  in \eqref{eq:commcos} is zero. Let us show that the same is true for the LHS. By \cite[Lemma~2.7]{KLcosection}, to show that 
-\[\operatorname{LHS}=\nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)=0\,\in A_*(Y(\sigma)),\]
-with $[\widetilde{B}]\in \, Z_*(G),$
-it is enough to show that $\nu_*^{\mathbb{E}}[\widetilde B]$ is zero in $A_*(\mathbb{E})$ where $\nu^{\mathbb{E}}$ is the natural morphism induced by $\nu.$ Then it is immediate, indeed since  $\nu^{\mathbb{E}}=\varphi^{\mathbb{E}}\circ\nu'^{\mathbb{E}}$  and we assumed $\varphi^{\mathbb{E}}\colon B'\to B$ has fibers of positive dimension, $\nu_*^{\mathbb{E}}[\widetilde B]=0$ by definition of proper push-forward.
-
+If instead $B'\to B$ is not generically finite, then the right-hand side in formula \eqref{eq:commcos} is zero.
+In order to show that the same is true for the left-hand side it is enough to appeal to \cite[Lemma~2.7]{KLcosection}, since $\nu_*^{\mathbb{E}}[\widetilde B]=(\nu')_*^{\mathbb E}\circ \phi^{\mathbb E}_*[\widetilde B]=0.$ %to show that
+%\[\operatorname{LHS}=\nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)=0\,\in A_*(Y(\sigma)),\]
+%with $[\widetilde{B}]\in \, Z_*(G),$
+%it is enough to show that $\nu_*^{\mathbb{E}}[\widetilde B]$ is zero in $A_*(\mathbb{E})$ where $\nu^{\mathbb{E}}$ is the natural morphism induced by $\nu.$ Then it is immediate, indeed since  $\nu^{\mathbb{E}}=\varphi^{\mathbb{E}}\circ\nu'^{\mathbb{E}}$  and we assumed $\varphi^{\mathbb{E}}\colon B'\to B$ has fibers of positive dimension, $\nu_*^{\mathbb{E}}[\widetilde B]=0$ by definition of proper push-forward.
 \end{proof}
@@
 \end{cor}
+
+This descends from the following lemma and the fact that $\XP$ and $\mathfrak{Pic}_1(1)$ are birational.
+
+\begin{lem}
+ The $1$-stabilisation $\mathfrak{M}_1^{\rm{wt,st}}\to \mathfrak{M}_1^{\rm{wt,st}}(1)$ is a proper morphism.
+\end{lem}
 \begin{proof}
-We show that
-\[\alpha_*[\Z^p]^{\alpha^*\sigma_1,\rm{vir}}_{\rm{loc}}=[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\sigma_1,\rm{loc}},\]
-then the statement follow given that $\alpha$ is generically 1 to 1.
-Notice  first of all that the 1-stabilisation $\mathfrak{M}_1^{\rm{w}}\to \mathfrak{M}_1^{1,\rm{w}}$ is proper.
-As usual, we use the lifting criterion and thus we have to show that, up to a base change, the dashed arrow and the $\mathcal C$ in the following commutative diagram exist
+Use the valuative criterion: let $\dvr$ be a DVR scheme with generic point $\eta$; we have to fill in the upper right part of the following diagram:
 \bcd
 \mathcal C_{\eta}\ar[d,"\phi_{\eta}"] \ar[r,dashed, hookrightarrow] &\mathcal C\ar[d, dashed, "\phi"]\\
-\hat{\mathcal C_{\eta}}\ar[r, hookrightarrow] &\hat{\mathcal{C}}
-\ecd
-where the family are over a DVR $T$ and $\eta$ is its generic point.
+\hC_{\eta}\ar[r, hookrightarrow] &\hC
+\ecd
+We may in fact assume that $\phi_{\eta}$ is an isomorphism, and then it is enough to take the semistable model of $\hC.$
+\end{proof}
+%We show that
+%\[\alpha_*[\Z^p]^{\alpha^*\sigma_1,\rm{vir}}_{\rm{loc}}=[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\sigma_1,\rm{loc}},\]
+%then the statement follow given that $\alpha$ is generically 1 to 1.
+%Notice  first of all that  As usual, we use the lifting criterion and thus we have to show that, up to a base change, the dashed arrow and the $\mathcal C$ in the following commutative diagram exist
+
+%where the family are over a DVR $T$ and $\eta$ is its generic point.
 We can in fact assume that $\phi_{\eta}$ is an isomorphism and then notice that it is enough to consider the semi-stable model of $\hat{\mathcal C}.$
-Thus, since the 1-stabilisation $\phi$ is generically an isomorphism it follows that
-\[\phi_*[\mathfrak{M}_1^{\rm{w}}]=[\mathfrak{M}_1^{1,\rm{w}}]\]
-and analogously,
-\[\phi_*[\XP]=[\mathfrak{Pic_1{(1)}}]\]
-Finally, recall that the deformation to the normal cone construction ensures the commutativity of
-\bcd
-A_*(\XP)\ar[r,"\zeta'"]\ar[d,"\phi_*"] & A_*(\mathfrak C_{\Z^p/\XP}) \ar[d,"\phi(\sigma)_*"]\\
-A_*(\mathfrak{Pic_1{(1)}})\ar[r,"\zeta"] & A_*(\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}})
-\ecd
-and thus 
-\[\phi(\sigma)_*[\mathfrak C_{\Z^p/\XP}]\cong [\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}].\]
-The identity at the level of virtual classes now follows from the definition of cosection localised virtual class and Lemma~\ref{lem:comutativity}.
-\end{proof}
+%Thus, since the 1-stabilisation $\phi$ is generically an isomorphism it follows that
+%\[\phi_*[\mathfrak{M}_1^{\rm{w}}]=[\mathfrak{M}_1^{1,\rm{w}}]\]
+%and analogously,
+%\[\phi_*[\XP]=[\mathfrak{Pic_1{(1)}}]\]
+%Finally, recall that the deformation to the normal cone construction ensures the commutativity of
+%\bcd
+%A_*(\XP)\ar[r,"\zeta'"]\ar[d,"\phi_*"] & A_*(\mathfrak C_{\Z^p/\XP}) \ar[d,"\phi(\sigma)_*"]\\
+%A_*(\mathfrak{Pic_1{(1)}})\ar[r,"\zeta"] & A_*(\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}})
+%\ecd
+%and thus 
+%\[\phi(\sigma)_*[\mathfrak C_{\Z^p/\XP}]\cong [\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1{(1)}}}].\]
+%The identity at the level of virtual classes now follows from the definition of cosection localised virtual class and %Lemma~\ref{lem:comutativity}.
+%\end{proof}
 

### 2018-01-15 draft_merged.tex
final review

@@
 \usepackage[english]{babel}
+\usepackage[margin=1.6in]{geometry}
 \usepackage{amsmath}
@@
 \newcommand{\tZp}{\widetilde{\pazocal Z}^p}
+\newcommand{\oZp}{\overline{\Z}^{p,\rm{gst}}}
 \newcommand{\MM}{\mathfrak M}
@@
 \newtheorem*{teo*}{Theorem}
+\newtheorem*{matteo*}{Main Theorem}
 \newtheorem{ipotesi}{ipotesi}
@@
 
-\title{Reduced GW invariants from cuspidal curves}
+\title{Reduced invariants from cuspidal maps}
 \author{L.Battistella, F.Carocci, C.Manolache}
 \date{\today}
+
+\setcounter{tocdepth}{1}
 \begin{document}
@@
 
-We prove that the $1$-stabilisation morphism, replacing elliptic tails
-with cusps, is well-defined at the level of genus $1$ weighted-stable
-curves. We use this to endow a substack of $\oM_1(\PP^4,d)$ with a
-virtual class that ignores the boundary contribution of maps with a
-contracted elliptic tail. We thus prove that Vakil-Zinger's reduced
-invariants of the quintic threefold can be computed as Smyth-Viscardi's
-$1$-stable (i.e. cuspidal) invariants. To do so we adapt Jun Li's
-techniques of $p$-fields and local equations for the moduli space.
+We provide a modular interpretation of Vakil-Zinger reduced invariants of the quintic threefold in genus $1$.
+Inspired by Li-Zinger's formula, we prove they coincide with $1$-stable invariants, arising from Smyth-Viscardi's alternate compactification where elliptic tails are replaced by cusps.
 
@@
 \maketitle
-
-\section*{Introduction}
+\tableofcontents
+
+\section{Introduction}
 
@@
 
-Recall that in genus zero $\M{0}{n}{\PP^r}{d}$ is a smooth stack of the expected dimension $r-3+d(r+1)+n$.
-Furthermore the rational Gromov-Witten theory of a complete intersection $i\colon X\hookrightarrow \PP^r$ of degree $(l_1,\ldots,l_k)$ can be determined as a twisted theory for $\PP^r$ and thus computed via localisation: for any split vector bundle $E=\oplus_{i} \mathcal O_{\PP^r}(l_i)$ the sheaf $\pi_*f^*E$ is a vector bundle on $\M{0}{n}{\PP^r}{d}$, where we have denoted by $\pi$ the projection from the universal curve and by $f$ the universal stable map.
-%\bcd
-%\mathcal C_{0,n}(\PP^r,d)\ar[r,"f"]\ar[d,"\pi"] & \PP^r%\times \M{0}{n}{\PP^r}{d} \\
-%\M{0}{n}{\PP^r}{d} &
-%\ecd
-It is a matter of functoriality of virtual fundamental classes \cite{KON} \cite{CKL} \cite{KKP} that the following \emph{hyperplane property} holds
-%$$\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}\hookrightarrow\M{0}{n}{\PP^r}{d}$$
-%then the following equality holds:, which is expected from the interpretation of Chern classes as zero loci of sections (if $X$ is cut by a generic section $s\in H^0(\PP^r,E)$, then the induced section $\tilde s=\pi_*f^*(s)$ is also generic):
-$$j_*[\bigsqcup_{\beta\in A_1(X)\colon i_*(\beta)=d}\M{0}{n}{X}{\beta}]^{\operatorname{vir}}=c_{\operatorname{top}}(E)\cap[\M{0}{n}{\PP^r}{d}].$$
-%This, so-called ``hyperplane property'', allows us to compute GW invariants of complete intersections as twisted invariants of projective space, where computations can be done via localisation.
-
-For $g\geq 1$ the moduli space $\M{g}{n}{\PP^r}{d}$ is neither irreducible, nor pure dimensional, and the sheaf $\pi_*f^*\mathcal O_{\PP^r}(l)$ is not a vector bundle.
-The enumerative meaning of the invariants is spoilt by degenerate contributions from curves of lower genera, represented by boundary components of the moduli space where a subcurve of positive genus is contracted.
-
-The situation in genus $1$ is better understood: the geometry of $\M{1}{n}{\PP^r}{d}$ has been widely studied since \cite{Vre}.
-Contrary to higher genus, the closure of the locus of maps the source of which is a smooth elliptic curve is an irreducible component of $\M{1}{n}{\PP^r}{d}$, which is usually called the \emph{main component}.
-Its boundary points were characterised in \cite{Vre} as follows: $[f\colon C\to \PP^r]\in\oM_1(\PP^r,d)$ is smoothable, i.e.
-it can be made into the special fiber of a $1$-dimensional family the generic fiber of which is a non-constant map from a smooth elliptic curve, if and only if either $f$ is not constant on the minimal genus $1$ subcurve $E$ of $C$, or the image of the tangent vectors to the rational tails are linearly dependent in $T_{f(E)}\PP^r.$  In Section~\ref{sec:section1} we give a new proof of this fact~\ref{prop:smoothability} using Hu-Li's local equations for the moduli space; furthermore we provide a different characterisation of the smoothable maps as those that factor through a non-degenerate map from a Cohen-Macaulay genus~$1$ singularity \ref{prop:smoothability2}, which we classify extending an argument due to Smyth.
-%One of the reasons for this (in fact the only reason in genus one) is that there are maps from reducible curves with a genus $g$ core that is contracted and some rational tails that carry all the degree; if $f\colon C\to \PP^r$ is such a map, then $H^1(C,f^*\mathcal O_{\PP^r}(1))\neq 0$, as can be easily seen from the normalisation sequence.
-
-From the enumerative point of view, it would be ideal to isolate the contribution to the invariants given by the main component.
-In an attempt to extract this information hidden within Kontsevich's moduli space, 
-Vakil and Zinger managed to desingularise the main component by performing a sequence of blow-ups on an underlying space of weighted curves \cite{VZpreview} \cite{VZ} (see also \cite{HL}).
-The end result $\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}$ is a smooth and irreducible stack on which $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ is a vector bundle.
-This fact allowed them to define a notion of \emph{reduced invariants} for complete intersections in $\PP^r$ by mimicking the hyperplane property of the genus $0$ theory.
-%The idea is that blowing up successively the locus of degree zero elliptic curve with one rational tail (\emph{elliptic tails}), then with two (\emph{elliptic bridges}), etc.
-and taking the fiber product
-%\bcd
-%\widetilde{\mathcal M}_{1,n}(\PP^r,d)\ar[r]\ar[d] & \M{1}{n}{\PP^r}{d}\ar[d] \\
-%\widetilde {\mathfrak M}_{1,n}^{\operatorname{wt}=d} \ar[r] & \mathfrak M_{1,n}^{\operatorname{wt}=d}
-%\ecd
-%the strict transform of the main component becomes smooth and meets the rest of the components in normal crossing fashion (the \'{e}tale local model being the union of two linear subspaces of different dimensions in affine space).
-Furthermore, the sheaves $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ contain a vector subbundle of rank $dl$ supported on the strict transform of the main component.
-This paved the way to the definition of reduced invariants.
-
-\begin{dfn}
-Let $X$ be a complete intersection of degree $(l_1,\ldots,l_k)$ in $\PP^r$.
-The genus $1$ reduced invariants of $X$ are defined by integrating against: $$ c_{\rm{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i)))\cap[\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}].$$
-\end{dfn}
-
+Contrary to the genus $0$ case, $\M{1}{n}{\PP^r}{d}$ has many irreducible components of different dimension \cite{Vre}, and the enumerative geometry of complete intersections $X\subseteq \PP^r$ is hardly accessible through this space, since the hyperplane property does not hold \cite{KKP}.
+
+On the other hand the locus of maps from a smooth elliptic curve is irreducible, and its closure is an irreducible component of $\M{1}{n}{\PP^r}{d}$ which is called the \emph{main component}.
+
+R.
+Vakil and A.
+Zinger \cite{VZ} produced a desingularisation $\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}$ of the main component, on which $\tilde\pi_*\tilde f^*\mathcal O_{\PP^r}(l)$ is a vector bundle.
+This is achieved through an iterated blow-up construction, which unfortunately makes the modular meaning of this space unclear; though an interpretation has recently been given in terms of log structures \cite{RSPW}.
+Vakil and Zinger introduced then a notion of \emph{reduced invariants} for complete intersections in $\PP^r$: if $X$ is a complete intersection of degree $(l_1,\ldots,l_k)$, its genus $1$ reduced invariants are defined by integrating against:
+\[ c_{\rm{top}}(\tilde\pi_*\tilde f^*(\oplus_{i=1}^k\mathcal O_{\PP^r}(l_i)))\cap[\widetilde{\pazocal M}_{1,n}(\PP^r,d)^{\rm{main}}].\]
 Recently there has been a different attempt to discard some of the boundary components.
-Based on Smyth's work on the birational geometry of $\oM_{1,n}$ \cite{SMY1,SMY2}, Viscardi \cite{VISC} has introduced a series of \emph{alternate compactifications} of the moduli space of maps from smooth elliptic curves.
-Compared to Kontsevich's space of stable maps, in Viscardi's space $\oM_{1,n}^{(m)}(X,\beta)$ maps that contract a genus $1$ curve with at most $m$ rational tails are destabilised, and replaced by maps from $l$-elliptic singularities with $l\leq m$.
+Based on D.I.
+Smyth's work on the birational geometry of $\oM_{1,n}$ \cite{SMY1,SMY2}, M.
+Viscardi \cite{VISC} has introduced a series of \emph{alternate compactifications} of the moduli space of maps from smooth elliptic curves, the first instance of which is $\oM_{1,n}^{(1)}(X,\beta)$, where elliptic tails are made unstable and cuspidal singularities are allowed in the source curve.
 
@@
 
-\begin{thm}
+\begin{matteo*}\label{thm:main}
 Let $X_5\subseteq\PP^4$ be a generic smooth quintic threefold. Then:
@@
 \]
-\end{thm}
-
-Below we will suppress the subscript $5$ from $X_5$.
-The insight for this theorem comes from the following formula, the proof of which was first given by J.
-Li and A.
-Zinger \cite{LZ} in the symplectic category:
-\begin{equation}\label{eq:VakilZinger}
-N_1(X,d)=N_1^{\rm{red}}(X,d)+\frac{1}{12}N_0(X,d).
-\end{equation}
-The first proof of Li-Zinger's formula in the algebro-geometric setting is due to H.-W.
+\end{matteo*}
+The insight for this result comes from the following formula, first proved by J. Li and A. Zinger \cite{LZ} in the symplectic category:
+\begin{equation*}
+N_1(X_5,d)=N_1^{\rm{red}}(X_5,d)+\frac{1}{12}N_0(X_5,d).
+\end{equation*}
+An algebro-geometric proof of Li-Zinger's formula is due to H.-W.
 Chang and J.
 Li in \cite{CL}.
-Their splitting of the intrinsic normal cone makes it patent that the genus $0$ contribution to the right hand side only comes from the boundary component with a single rational tail of degree $d$.
+Their method reveals that the genus $0$ contribution to the right hand side only comes from the boundary component with a single rational tail.
 This suggests that removing such a component would provide a more direct approach to reduced invariants for the quintic threefold.
@@
 
-%To prove the result we essentially need to understand how the various component of the moduli space contribute to the invariants, so we have to look at the algebraic techniques that  have been used to prove~\eqref{eq:VakilZinger}.
-
-%Indeed, after the symplectic proof, Li-Zinger's formula was proved .
-The latter is only the final a series of papers where they developed the theory of stable maps with $p$-fields and applied it together with the techniques of cosection-localised virtual classes \cite{KLcosection}.
-$p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$; indeed Chang and Li managed to include the unwanted part of the obstruction theory in the moduli space, and by these means endow a well-understood space (very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.
-The proof of our main theorem follows from adapting the techniques of Chang and Li to Viscardi's moduli spaces. Here is an outline of the proof.
-
-%Alternatively, if one does not want to use the theory of stable maps with fields, the idea would be to follow the alternative proof of~\eqref{eq:VakilZinger} recently proposed by \cite{preprint}.
-In that case, they still consider the Hu-Li blow up of the moduli space of weighted curve and they then look at $\tM_1(X)\hookrightarrow \tM_1(\PP^4) $, where $X$ is the quintic threefold and study directly the cone of $\tM_1(X).$ Following~\cite{preprint} steps, we can attack directly $\tM_1(X)^{(1)}$ and show that only the main component has a non trivial contribution to the invariants.
-
-%In both cases the comparison with the genus~1 invariants comes from the following comparison result.
-%We show the following:
-We first consider a moduli space of $1$-stable maps with $p$-fields $\Mone{1}{\PP^4}{d}^p$.
-In the work of Chang and Li, $p$-fields provide a way around the fact that we cannot control the geometry of $\oM_1(X,d)$ and there is no compatible perfect obstruction theory relative to the inclusion $\oM_1(X,d)\hookrightarrow \oM_1(\PP^4,d)$.
-By introducing the moduli space of maps with $p$-fields the authors manage to include the unwanted part of the obstruction theory into the moduli space, and to endow a well-understood space (indeed very similar to $\oM_1(\PP^4,d)$) with an obstruction theory counting genus $1$ curves in the quintic.
-Paralleling their proof, i.e.
-using cosection localised virtual cycles \cite{KLcosection} and the deformation to the normal cone $(X_5\subseteq \PP^4)\rightsquigarrow(X_5\subseteq N_{X/\PP^4})$, we see that:
-\begin{prop}
-$\deg\virloc{\Mone{1}{\PP^4}{d}^p}=\deg\vir{\Mone{1}{X}{d}}.$
-\end{prop}
-Indeed it is enough to notice that all the constructions in \cite{CLpfields} carry over to the setting of a family of Gorenstein (not necessarily nodal) curves.
-
-We then need the following comparison morphism.
-\begin{prop}
+Here is a rough sketch of how we prove our result. We first show:
+\begin{teo*}
 There exists a well-defined $1$-stabilisation morphism at the level of weighted-stable curves:
@@
 \MM_{1,n}^{\rm{wt,st}}\to \MM_{1,n}^{\rm{wt,st}}(1)
-\]
-\end{prop}
-The fiber product
-\[
-\Z:=\MM_{1,n}^{\rm{wt,st}}\times_{\MM_{1,n}^{\rm{wt,st}}}\Mone{1}{\PP^4}{d}
-\]
-is a substack of $\oM_1(\PP^4,d)$ avoiding the boundary component with one rational tail of degree $d$.
-
-It is harder to compare the fiber product
-\[
-\Zp:=\MM_{1,n}^{\rm{wt,st}}\times_{\MM_{1,n}^{\rm{wt,st}}}\Mone{1}{\PP^4}{d}
-\]
-with $\oM_1(\PP^4,d)^p$.
-Yet $\Zp$ is endowed with a cosection-localised virtual class counting $1$-stable maps to the quintic threefold (by cosection-localised virtual pullback).
-The same splitting arguments as in \cite{CLpfields} allow us to evince a main contribution which coincides with Vakil-Zinger's reduced invariants.
-On the other hand a dimensional computation shows that this is the only enumeratively meaningful component.
-
-\subsection*{Future directions}
-
-\subsection*{Outline of the paper}
-
-\subsection*{Notations and conventions} We work over an algebraically closed field $\k$ of characteristic $0$.
-
-Throughout the paper we shall have fixed a homogeneous polynomial $\mathbf w\in\k[x_0,\ldots,x_4]_5$ of degree $5$ such that $X=V(\mathbf w)\subseteq\PP^4$ is a generic smooth quintic threefold.
+\]replacing elliptic tails of weight $0$ with cusps.
+\end{teo*}
+We may then use this morphism to construct a substack of $\oM_1(X_5,d)$ that has no component with contracted elliptic tails:
+\[\MM_{1}^{\rm{wt,st}}\times_{\MM_{1}^{\rm{wt,st}}(1)}\Mone{1}{X_5}{d},\]
+and endow it with a virtual class with the same enumerative content of $\vir{\Mone{1}{X_5}{d}}$. However it is not easy to compare the latter directly with Vakil-Zinger's reduced invariants.
+
+Therefore we follow in Chang and Li's footsteps: we introduce the moduli space of $1$-stable maps with $p$-fields, which has the advantage of having a simpler geometry and admits a cosection-localised virtual class with the same degree as $\vir{\Mone{1}{X_5}{d}}$, see \cite{CLpfields}.
+We construct:
+\[\MM_{1}^{\rm{wt,st}}\times_{\MM_{1}^{\rm{wt,st}}(1)}\Mone{1}{\PP^4}{d}^p,\]
+and perform a desingularisation of it via the study of local equations \cite{HL}, followed by an analysis of a splitting of the intrinsic normal cone \cite{CL}, which delivers the theorem.
+
+On our way there, we review Vakil's characterisation of maps lying in the boundary of $\oM_1(\PP^r,d)^{\rm{main}}$ and prove it holds using Hu-Li's equations.
+We also review and extend Smyth's work on genus $1$ singularities, and rephrase smoothability as follows.
+
+\begin{teo*}
+A map $[f]\in\oM_1(\PP^r,d)$ contracting the minimal genus $1$ subcurve is smoothable if and only if it factors through a map from a genus $1$ singularity that does not contract any component.
+\end{teo*}
+
+%\subsection*{Future directions}
+
+\subsection{Outline of the paper}
+In \S~\ref{sec:section1} we review some classical results about the irreducible components of $\oM_1(\PP^r,d)$ and local equations for this moduli stack in a smooth ambient space.
+We recall Smyth's $m$-elliptic singularities and Viscardi's alternate compactifications  of the space of maps.
+We discuss two different proofs of Vakil's characterisation of smoothable maps to projective space: one is based on Hu-Li's local equations; for the other one we give a classification of genus $1$ singularities.
+
+In \S~\ref{section:p-fields} we adapt Chang-Li's work on $p$-fields to our situation: we introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable maps with $p$-fields, we endow it with a cosection-localised $0$-dimensional virtual class supported on a proper substack (depending on a homogeneous polynomial $\w$), and we show that its degree coincides with the genus $1$ cuspidal invariants of the quintic threefold $X_5=V(\w)$ up to a sign.
+
+In \S~\ref{sec:comparison} we argue in two different ways that there is a morphism:
+ \[\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)\]
+extending the identity on smooth elliptic curves and replacing elliptic tails of weight $0$ by cusps. We then use it to define:
+ \[\Z:= \mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d),\quad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)^p.\]
+ We show that $\Z$ is a closed substack of $\oM_1(\PP^4,d)$; unfortunately we are not able to compare $\Zp$ directly with $\oM_1(\PP^4,d)^p$.
+
+For this reason in \S\S~\ref{sec:equations} and \ref{section:main_proof} we study local equations and a desingularisation of $\Zp$, which allows us to adjust Chang-Li's splitting of the intrinsic normal cone to our case.
+Such analysis allows us to prove the main theorem.
+
+\subsection{Notations and conventions} We work over an algebraically closed field $\k$ of characteristic $0$.
+
+Throughout the paper we shall have fixed a homogeneous polynomial $\mathbf w\in\k[x_0,\ldots,x_4]_5$ of degree $5$ such that $X_5=V(\mathbf w)\subseteq\PP^4$ is a generic smooth quintic threefold.
+We usually drop the subscript and write $X$ for $X_5$.
 Furthermore let us consider a fixed positive integer $d$ determining all the homology classes $\beta=d[\ell]\in A_1(\PP^4)$, line bundle weights, etc.
@@
 \begin{dfn}
-Let $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ be the stack of \emph{weighted-stable} curves of genus $1$ with $n$ markings and total weight $d$: every geometric point of $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ represents a connected, reduced, nodal, projective curve of arithmetic genus $1$ with $n$ distinct smooth markings and an integer-valued function $\rm{wt}$ on the dual graph.
+Let $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ be the stack of \emph{weighted-stable} curves of genus $1$ with $n$ markings and total weight $d$: geometric points of $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ represent connected, reduced, nodal, projective curves of arithmetic genus $1$ with $n$ distinct smooth markings and an integer-valued function $\rm{wt}$ on the dual graph.
 Such a function assumes only nonnegative values, the sum of which on all the vertices of the dual graph is $d$; $\rm{wt}$ is compatible with the specialisation maps, and we further impose the following stability condition: every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least one special point).
 \end{dfn}
-There is an \'{e}tale non-separated morphism $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}\to\mathfrak M_{1,n}$ and the stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, the weight coming from the degree of the map to $\PP^r$.
+There is an \'{e}tale, non-separated morphism $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}\to\mathfrak M_{1,n}$.
+The stability condition is such that the forgetful map $\M{1}{n}{\PP^r}{d}\to\mathfrak M_{1,n}$ factors through $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, the weight coming from the degree of the map to $\PP^r$.
 We shall denote by $\pi\colon \cC\to \MM_{1,n}$ the universal curve (and use similar notation for its pullbacks).
-We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$ of $\pi\colon \cC\to \MM_{1,n}$ with universal line bundle $\mathcal{L}$, subject to the stability condition that $\omega_\pi^{\rm{log}}\otimes\mathcal L^{\otimes 3}$ is $\pi$-ample, and the requirement that the total degree of $\mathcal L$ on the fibers of $\cC$ is $d$.
+We shall also consider the universal Picard stack $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$ of $\pi\colon \cC\to \MM_{1,n}$ with universal line bundle $\mathcal{L}$, subject to the stability condition that $\omega_\pi^{\rm{log}}\otimes\mathcal L^{\otimes 2}$ is $\pi$-ample, and the requirement that the total degree of $\mathcal L$ on the fibers of $\cC$ is $d$.
 Let $\PtoM$ denote the projection $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}\to \mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$, where the weight comes from the degree of the line bundle.
@@
 We shall often use shorthand notation $\MM$ for $\mathfrak M_{1,n}^{\rm{wt}=d,\rm{st}}$ and $\mathfrak P$ for $\mathfrak{Pic}^{\rm{tot deg}=d,\rm{st}}_{1,n}$.
-
 \begin{dfn}
-Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} projective connected, reduced, $n$-marked, projective curves of arithmetic genus $1$ that are weighted-stable with total weight $d$, i.e.
+Let $\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)$ be the stack of \emph{at worst cuspidal} connected, reduced, $n$-marked, projective curves of arithmetic genus $1$ that are weighted-stable with total weight $d$, i.e.
 the weight is nonnegative, and every $p_a=0$ component of weight $0$ has at least three special points (every $p_a=1$ component of weight $0$ has at least \emph{two} special points).
@@
 \end{remark}
-
 We shall denote by $\hat{\pi}\colon \widehat{\cC}\to \MM_{1,n}(1)$ the universal curve (and use similar notation for its pullbacks).
@@
 
-We sometimes work on $\MM_{1,n}^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor, which we may ask to be weighted stable in order to make this space compatible with $\MM$ and $\mathfrak P$ above.
-More precisely $\MM_{1,n}^{\rm{div}}$ can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP(\R^1\pi_*\mathcal L)$ (see \cite{CLpfields} and Section \ref{section:p-fields} below), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
+Let us also introduce the stack $\MM_{1,n}^{\rm{div}}$, parametrising families of nodal curves with a relative Cartier divisor, which we ask to be weighted stable in order to make this space compatible with $\MM$ and $\mathfrak P$ above.
+More precisely $\MM_{1,n}^{\rm{div}}$ can be thought of as the open inside $C(\pi_*\mathcal L)=\Spec_\pP\operatorname{Sym}^{\bullet}(\R^1\pi_*\mathcal L^{\vee}\otimes\omega_{\pi})$ (see \cite{CLpfields} and Section \ref{section:p-fields} below), where the section of $\mathcal L$ is not $0$ on any irreducible component of the curve.
 Alternatively this is the moduli functor of a prestable curve with a line bundle and a section up to scalar, which can be thought of as the hom-stack $\Hom_{\MM_1}(\cC,[\Aaff^1/\Gm])$; then we pick the connected component where the line bundle has total degree $d$, and the open substack obtained by requiring weighted stability and the section not to vanish on any irreducible component of the curve.
@@
 
+Notice that we usually work with unmarked curves, for we are interested in the Gromov-Witten theory of a Calabi-Yau threefold, so $n=0$.
+
 We shall always denote the spectrum of a discrete valuation ring (DVR) by $\dvr$, with closed point $0$ and generic point $\eta$.
@@
 Subcurves are always connected.
+ The \emph{minimal} arithmetic genus $1$ subcurve is called the \emph{core} or the \emph{circuit}.
+
+\subsection*{Acknowledgements}
+L.B. and F.C. would like to thank F. Bernasconi, A. Dotto and Prof. D.I. Smyth for their clever suggestions.
+L.B. is supported by a Royal Society 1st Year URF and DHF Research Grant Scheme.
+C.M. is supported by 
+This work was supported by the Engineering and Physical Sciences Research Council grant EP/L015234/1: the EPSRC Centre for Doctoral Training in Geometry and Number Theory at the Interface.
 
@@
 We start by recalling a description of the global geometry of $\oM_1(\PP^r,d)$.
-Besides the main component, which was defined in the Introduction, for every positive integer $k$ and partition $\lambda\vdash d$ into $k$ parts such that no $\lambda_i=0$, there is an irreducible \emph{boundary component} $D_{\lambda}(\PP^r,d)$ defined to be the closure of the locus where:
-\begin{description}
-\item[i] the source curve is obtained by gluing a smooth elliptic curve $E$ with $k$ many $\PP^1$'s as rational tails $R_i$,
-\item[ii] the map contracts the elliptic curve $E$ to a point, and
-\item[iii] the map has degree $\lambda_i$ on the rational tail $R_i$.
-\end{description}
+Besides the main component, which was defined in the Introduction, for every positive integer $k$ and partition $\lambda\vdash d$ into $k$ positive parts, there is an irreducible \emph{boundary component} $D_{\lambda}(\PP^r,d)$ defined to be the closure of the locus where:
+\begin{enumerate}[label=(\roman*)]
+\item the source curve is obtained by gluing a smooth elliptic curve $E$ with $k$  rational tails $R_i\cong\PP^1$,
+\item the map contracts the elliptic curve $E$ to a point, 
+\item the map has degree $\lambda_i$ on the rational tail $R_i$.
+\end{enumerate}
 Indeed $D_{\lambda}(\PP^r,d)$ is the image of the gluing morphism from the fiber product:
-$$\M{1}{k}{\PP^r}{0}\times_{\PP^r}\prod_{i=1}^k\M{0}{1}{\PP^r}{\lambda_i}.$$
-
-\noindent The \emph{minimal} arithmetic genus $1$ subcurve is called the \emph{core} or the \emph{circuit}. %We then have:
+\[\left(\oM_{1,k}\times\prod_{i=1}^k\M{0}{1}{\PP^r}{\lambda_i}\right)\times_{(\PP^r)^k}\PP^r.\]
+We will denote by $D^k$ the union of all the $D_{\lambda}(\PP^r,d)$ where $\lambda$ has $k$ parts.
+
+ %We then have:
 \begin{prop}\label{prop:components}
-\emph{(1)} All the irreducible components of $\oM_1(\PP^r,d)$ have been described above: %The set of irreducible components of $\M{1}{n}{\PP^r}{d}$ is in bijection with $\{\text{stable}\ (\lambda\vdash d,\mu\vdash n)|\ \#(\text{parts})(\lambda)=\#(\text{parts})(\mu)\}\cup\{\rm{main}\}$,
+\emph{(1)} These are all the irreducible components of $\oM_1(\PP^r,d)$: 
 \[\oM_1(\PP^r,d)=\oM_1(\PP^r,d)^{\rm{main}}\cup\bigcup_{\lambda}D_{\lambda}(\PP^r,d).\]
@@
 \item either $f$ is non-constant on at least one irreducible component of the core,
-\item or if $(E\ {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^k R_i,f)$ is a stable map with $k$ rational tails, where $E$ is the \emph{maximal} contracted genus $1$ subcurve, then $\{\operatorname{d}\!f(T_{q_i}R_i)\}_{i=1}^k$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
+\item or if $f$ contracts the core, write $C=E\ {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^k R_i$,  where $E$ is the \emph{maximal} contracted genus $1$ subcurve, then $\{\operatorname{d}\!f(T_{q_i}R_i)\}_{i=1}^k$ are \emph{linearly dependent} in $T_{f(E)}\PP^r$.
 \end{itemize}
+In this case we say that $[f]$ is smoothable.
 \end{prop}
 
-This is due to R. Vakil and A. Zinger in \cite{Vre,VZpreview}. We shall later discuss a different proof of this fact based on local equations for the moduli space.
+This is due to R. Vakil and A. Zinger, see \cite[Lemma~5.9]{Vre}\cite{VZpreview}. We shall later discuss a  proof of this fact based on local equations for the moduli space.
 
@@
 Recall that a map $C\to\PP^r$ is given by a line bundle $L$ on $C$ together with $r+1$ sections in $H^0(C,L)$ that generate the line bundle.
-It is therefore natural to embed the space of stable maps as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}_{1}=\mathfrak{Pic}(\cC_{1}\to\MM_{1})$.
-Hu and Li actually work over a local chart of the algebraic stack $\mathfrak M_{1}^{\rm{div}}$, parametrising families of prestable curves with a relative Cartier divisor (of total degree $d$).
+It is therefore natural to embed $\oM_1(\PP^r,d)$ as an open inside $\pi_*\mathcal L^{\oplus r+1}$ on the universal Picard stack $\mathfrak{P}$.
+Hu and Li actually work over a local chart of $\mathfrak M_{1}^{\rm{div}}.$ 
  %The problem is that this cone is not smooth, due to the jumps in the dimension of the fiber at the boundary of the moduli space.
@@
 
-Let $[f\colon C\to \PP^r]$ be a point of $\oM_1(\PP^r,d)$: we may fix homogeneous coordinates on $\PP^r$ in such a way that $D_0:=f^{-1}\{x_0=0\}$ is a simple divisor contained supported on the smooth locus of $C$ (i.e.
-a $d$-uple of smooth points); this property will then hold in a neighbourhood of $[f]$.
-This gives a morphism from an \'{e}tale chart $\pazocal U$ of $\oM_1(\PP^r,d)$ to an \'{e}tale chart $\pazocal V$ of $\mathfrak M_{1}^{\rm{div}}$, that we may assume to land in the locus where the divisor consists of $d$ distinct smooth points.
-Notice that this locus is smooth over $\mathfrak M_{1}$ by the deformation theory of smooth subschemes.
-A map to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ sections of $\mathcal O_C(D)$: the map can be written as $[1:u_1:\ldots:u_r]$, where $1$ denotes the given section of $\mathcal O_C\to\mathcal O_C(D)$.
+Let $[f\colon C\to \PP^r]$ be a point of $\oM_1(\PP^r,d)$: we may fix homogeneous coordinates on $\PP^r$ in such a way that $D:=f^{-1}\{x_0=0\}$ is a simple divisor supported on the smooth locus of $C$, i.e.
+a $d$-uple of distinct smooth points; this property will then hold in a neighbourhood of $[f]$.
+This gives a morphism from an \'{e}tale chart $\pazocal U$ of $\oM_1(\PP^r,d)$ to an \'{e}tale chart $\pazocal V$ of $\mathfrak M_{1}^{\rm{div}}.$ We may assume that $\pazocal V$ is contained in the locus where the divisor consists of $d$ distinct smooth points; notice  that such locus is smooth over $\mathfrak M_{1}$.
+A map to $\PP^r$ shall now be thought of as a curve-divisor pair $(C,D)$ together with $r$ sections of $\mathcal O_C(D)$; the map can be written as $[1:u_1:\ldots:u_r]$, where $1$ denotes the given section of $\mathcal O_C\to\mathcal O_C(D)$.
 
@@
 
-Furthermore, \'{e}tale locally on $\oM_1(\PP^r,d)$, we may pick extra sections $\pazocal A$ and $\pazocal B$ of $\cC:=\mathcal C_{1}(\PP^r,d)\to\oM_1(\PP^r,d)$ such that:
+Furthermore, \'{e}tale locally on $\oM_1(\PP^r,d)$, we may pick extra sections $\pazocal A$ and $\pazocal B$ of the universal curve $\cC\to\oM_1(\PP^r,d)$ such that:
 \begin{enumerate}
-\item they pass through the core genus $1$ curve;
-\item they are distinct smooth points disjoint from the support of $\pazocal D_0$. 
+\item they pass through the core;
+\item they are distinct smooth points disjoint from the support of $\pazocal D$. 
 \end{enumerate}
-Now  $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)$ is a vector bundle on $\pazocal V$ and $\pi_*\OO_{\cC}(\pazocal D)$ is carved inside it by requiring that the restriction map $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\to\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\rvert_{\pazocal A}$ be zero.
+Now  $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)$ is a vector bundle on $\pazocal V$ and $\pi_*\OO_{\cC}(\pazocal D)$ is carved inside it by the vanishing of the restriction map $\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\to\pi_*\OO_{\cC}(\pazocal D+\pazocal A)\rvert_{\pazocal A}$.
 
 \begin{prop}\label{prop:smoothability}
-\emph{(1)} \'{E}tale locally on $\oM_1(\PP^r,d)$, there is a locally closed embedding of $\oM_1(\PP^r,d)$ inside the vector bundle $V:=\Spec(\pi_*\OO_{\cC}(\pazocal D+\pazocal A)^{\oplus r})$ over $\pazocal V$:
+\emph{(1)} There is a locally closed embedding of an \'{e}tale chart of $\oM_1(\PP^r,d)$ inside the vector bundle $V:=\Spec_{\pazocal V}(\pi_*\OO_{\cC}(\pazocal D+\pazocal A)^{\oplus r})$:
 \bcd
@@
 
-\emph{(2)} Assume furthermore that $\pazocal V$ is affine; then on $\pazocal V$ we have 
+\emph{(2)} Assume furthermore that $\pazocal V$ is affine; on $\pazocal V$ we then have: 
 \[\pi_*\OO_{\cC}(\pazocal D+\A)\cong \pi_*\OO_{\cC}(\pazocal D+\A-\B)\oplus \pi_*\OO_{\cC}(\pazocal D+\A)_{|\B}\] %(trivially, $\mathcal O_{\mathcal V}^{\oplus d+1}\cong\mathcal O_{\mathcal V}^{\oplus d}\oplus\mathcal O_{\mathcal V}$)
-and the restriction-to-$\A$ map is zero on the second factor.
+and restricting to $\A$ is zero on the second factor.
 
@@
 \end{prop}
+We may now choose coordinates $(w^j_i)^{j=1,\ldots,r}_{i,\ldots, d}$ on the fiber of $V\to\pazocal V$ compatible with the basis given in Proposition~\ref{prop:smoothability}~.(3) such that $\pazocal U$ is an open inside $\left\{F^1=\ldots=F^r=0\right\}\subseteq V$, where:
+\[F^j=\sum_{i=1}^d{\left(\prod_{q\in[\A,\delta_i]}\zeta_q\right)w_i^j}.\]
 We refer the reader to \cite[Lemma~4.10, Proposition~4.13]{HL} for the details; we are going to review the key ideas in \S\ref{sec:equations}, where we find local equations for $\Mone{1}{\PP^r}{d}$.
-We include here a proof of Proposition~\ref{prop:components}-(2) based on Hu-Li's equations.
+
+ We include here a proof of Proposition~\ref{prop:components}~.(2) based on Hu-Li's equations.
 
@@
  Let us start with the easiest degenerate situation: a contracted elliptic curve attached to a $\PP^1$ of degree $d$ at a single node $q$.
-Equations for the moduli space of maps around such a point look like
- \[\zeta_q\sum_{i=1}^d w_i^j=0,\;\;\;\text{for} \;\;\;j=1,\ldots,r\]
- where the $w_i$ are coordinates on the fibers of $\pi_*\mathcal O_{\cC}(D+\A-\B)$ in the basis given by $\pi_*\mathcal O_{\cC}(\delta_i+\A-\B),\ i=1,\ldots,d$.
-
-  Our point corresponds to a smoothable map if and only if the equations admit a solution with $\zeta_q\neq 0$, hence it must be $\sum_{i=1}^d w_i^j=0$ for every $j$.
-Taking a coordinate $z$ on  $\PP^1$ centred at the node $q$, we see that the $i$-th basis vector corresponds to a polynomial vanishing at $q$ and at $\delta_j,\;\forall j\neq i$.
-This can be written as
-  \[e_i(z)=z\prod_{j\neq i}\frac{(z-\delta_j)}{-\delta_j},\] 
+Equations for the moduli space of maps around such a point look like:
+ \[\zeta_q\sum_{i=1}^d w_i^j=0,\;\;\;\text{for} \;\;\;j=1,\ldots,r.\]
+
+  Our point corresponds to a smoothable map if and only if the equations admit a solution with $\zeta_q\neq 0$, that is $\sum_{i=1}^d w_i^j=0$ for every $j$.
+Taking a coordinate $z$ on  $\PP^1$ centred at the node $q$,   the $i$-th basis vector corresponds to a polynomial vanishing at $q$ and at $\delta_l,\;\forall l\neq i$.
+This can be written as:
+  \[e_i(z)=z\prod_{l\neq i}\frac{(z-\delta_l)}{-\delta_l},\] 
   where we have chosen a convenient normalisation.
-So the restriction to the rational tail of the map corresponding to the point of coordinates $(w_i^j)_{i=1,\ldots,d}^{j=1,\ldots,r}$ can be written as
-  \[[1:\sum_{i=1}^d w_i^1e_i(z):\ldots,\sum_{i=1}^d w_i^re_i(z)].\] 
+So the restriction to the rational tail of the map corresponding to the point of coordinates $(w_i^j)_{i=1,\ldots,d}^{j=1,\ldots,r}$ can be written as:
+  \[[1:\sum_{i=1}^d w_i^1e_i(z):\ldots:\sum_{i=1}^d w_i^re_i(z)].\] 
   Differentiating with respect to $z$ we see that the image of the tangent vector at $q$ is given in affine coordinates around $f(E)$ by:
@@
  More generally we may assume that the dual graph is terminally weighted \cite[\S 3.1]{HL}.
-Assume there are $k$ positive-weighted rational tails and denote by $D(h),\ h=1,\ldots,k,$ the set of indices $i$ s.t.
-$\delta_i$ belongs to the $h$-th rational tail, by $E(h)$ the set of nodes separating the core from the $h$-th rational tail.
+Assume there are $k$  rational tails of positive weight $R_h,\ h=1,\ldots,k$.
+Denote by $D(h)$ the set of indices $i$ such that $\delta_i$ belongs to the $R_h$, and by $E(h)$ the set of nodes separating the core from $R_h$.
 The equations will then take the following form:
- $$\sum_{h=1}^k\left(\prod_{q\in E(h)}\zeta_q\right)\left(\sum_{i\in D(h)}w_i^j\right)=0,\ j=1,\ldots,r,$$
+ \[\sum_{h=1}^k\left(\prod_{q\in E(h)}\zeta_q\right)\left(\sum_{i\in D(h)}w_i^j\right)=0,\ j=1,\ldots,r,\]
  which can be assembled in matrix form as follows:
@@
  We see that smoothability is equivalent to the linear dependence of the rows of the above matrix $W$.
-On the other hand, on every positive-weighted rational tail $R_h$, we can choose a suitable coordinate $z_h$ around the node $q_h$ and write the map as $$[1:p_h^1(z_h):\ldots:p_h^r(z_h)],$$ where: \[p_h^j(z_h)=\sum_{i\in D(h)}w_i^je_i^h(z_h) \quad \text{and} \quad e_i^h(z_h)=z_h\prod_{l\in D(h)\setminus\{i\}}\frac{(z_h-\delta_l)}{-\delta_l}.\] The elliptic curve is contracted to the point $[1:0:\ldots:0]$ and the tangent vector to $R_h$ at $q_h$ is mapped to the $h$-th row of $W$ (in affine coordinates around $f(E)$).
+On the other hand we can choose a suitable coordinate $z_h$ around the node $q_h$ on $R_h$ and write the map as:
+ \[[1:p_h^1(z_h):\ldots:p_h^r(z_h)],\]
+  where: 
+ \[p_h^j(z_h)=\sum_{i\in D(h)}w_i^je_i^h(z_h) \quad \text{and} \quad e_i^h(z_h)=z_h\prod_{l\in D(h)\setminus\{i\}}\frac{(z_h-\delta_l)}{-\delta_l}.\] The elliptic curve is contracted to the point $[1:0:\ldots:0]$ and the tangent vector to $R_h$ at $q_h$ is mapped to the $h$-th row of $W$ (in affine coordinates around $f(E)$).
 Again we see that the map is smoothable if and only if the image of the tangent vectors to the rational tails at the nodes are linearly dependent in $T_{f(E)}\PP^r$.
- \begin{comment}{
- Let us now address the equivalence of (1) and (3). Assume that we have a smoothing of a degenerate map $f_0\colon C_0\to\PP^r$
- \bcd
- \mathcal C\ar[d,"\pi"]\ar[r,"f"] & \PP^r\times S \\
- S &
- \ecd
- We may assume that $S$ is a DVR scheme.
-The line bundle $\mathcal L=f^*\mathcal O_{\PP^r}(1)\otimes\omega^{log}_{\mathcal C/S}$ is $S$-semiample: trivial on a subcurve of $C_0$ of arithmetic genus one, and ample everywhere else.
-Let's note that $\mathcal L$ is of  the form $\mathcal L=\omega_{\mathcal C/S}(E+\Sigma)$, where $E$ is the contracted genus 1 curve and $\Sigma$ is a Cartier divisor supported away from $E$.
-It follows from Smyth's contraction lemma \cite[Lemma 2.13]{SMY2} that $\mathcal L$ can be used to produce a smoothing family $\mathcal C'$ of a genus 1 Gorenstein singularity.
-The relative $\mathcal O(1)$ of the Proj construction defines a compatible morphism to $\PP^r$
- \bcd
- \mathcal C\ar[rr,"f"]\ar[dr]\ar[dd,"\pi"] & & \PP^r\times S\\
- & \mathcal C'=\underline{\operatorname{Proj}}_S(\sum_{n\geq 0}H^0(\mathcal C,\mathcal L^n)) \ar[ld,"\pi'"]\ar[ru,dashed,"f'"] & \\
- S & & 
- \ecd
-Expressed in terms of $(2)$, we are saying that having dependent tangent vectors corresponds to the fact that the sections of $\mathcal L$ which define the morphism to $\PP^r$ descend to section on the Goreinstein singularity.
- Viceversa, assume $f_0$ factors through a Gorenstein singularity of genus one such that $f_0'\colon C_0'\to\PP^r$ is nondegenerate (i.e.
-it does not contract all the branches of the singularity).
-We can pick compatible smoothings of $C_0$ and $C_0'$:
- \bcd
- \mathcal C\ar[rr,"\phi"]\ar[dr,"\pi" below=.1cm] & & \mathcal C'\ar[dl,"\pi'"]\\
- & S &
- \ecd
- The line bundle $L_0'=(f_0')^*\mathcal O_{\PP^r}(1)$ can be extended to a line bundle $\mathcal L'$ on $\mathcal C'$ because the Picard scheme for curves is unobstructed (and general theory of algebraisation of coherent sheaves on projective varieties); furthermore, the sections $u^0_0,\ldots,u^r_0$ can be extended to $\mathcal C'$ because $H^1(C_0',L_0')=0$ by Serre duality, the fact that $L_0'$ has positive degree on at least one of the branches of the singularity, and the fact that the dualising sheaf is trivial.
-Composing the resulting map $\mathcal C'\to \PP^r\times S$ with $\phi$ proves the desired smoothability of the original map.}
- \end{comment}
  \end{proof}
@@
 \subsection{Smyth-Viscardi's compactifications}
-For any homology class $\beta\in H_2(X,\mathbb Z)$, let $\pazocal M_{1,n}(X,\beta)$ be the stack of maps $f\colon C\to X$ from a \emph{smooth} elliptic curve with $n$ marked points, satisfying  $f_{*}\left [C\right ]=\beta$.
-The moduli spaces of $m$-stable maps give alternate compactifications of $\pazocal M_{1,n}(X,\beta)$.
-\begin{dfn} Let $C$ be a reduced, connected, projective curve of arithmetic genus $1$ over $\k$, and let $p_1,\dots,p_n\in C$ be smooth, distinct points.
+ The moduli spaces of $m$-stable maps give alternate compactifications of $\pazocal M_{1,n}(X,\beta)$, parametrising maps from smooth elliptic curves.
+\begin{dfn} Let $C$ be a connected, reduced, projective curve of arithmetic genus $1$ over $\k$, and let $p_1,\dots,p_n\in C$ be smooth, distinct points.
 A map $f\colon C\to X$ is said to be \emph{$m$-stable} if the following conditions hold:
@@
  \item $C$ has only nodes and elliptic $l$-fold points, $l\leq m$, as singularities.
- \item For any connected subcurve $E\subset C$ of arithmetic genus $1$ on which $f$ is constant, 
- \[\left|\left\{E\cap \overline{C\setminus E}\right\}\cup\left\{p_i : p_i \in E\right\}\right| > m.\]
+ \item For any subcurve $E\subset C$ of arithmetic genus $1$ on which $f$ is constant, 
+ \[\left|\left\{E\cap \overline{C\setminus E}\right\}\cup\left\{i : p_i \in E\right\}\right| > m.\]
  \item $f$ has no non-trivial infinitesimal automorphisms.
@@
 
- Viscardi's main result \cite[Thm. 3.6]{VISC} is the following:
+ Viscardi's main result \cite[Theorem~3.6]{VISC} is the following:
 % that the associated moduli functor gives a compactification of $\mathcal M_{1,n}(X,\beta)$ (alternative to Kontsevich' moduli space).
@@
 We think that the algorithm proposed by Viscardi to prove the properness of his moduli spaces oversees a case.
-The issue is that, given a map $f\colon \cC_T\to\PP^r_T$ over a DVR scheme $T$ such that $\cC_\eta$ is smooth and $f_0$ is constant on a genus $1$ connected subcurve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $\hat f\colon \hat \cC_T\to\PP^r_T$, where $\hat \cC_0$ has a genus $1$ \emph{Gorenstein} singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
+The issue is that, given a map $f\colon \cC_\dvr\to\PP^r_\dvr$ over a DVR scheme $\dvr$ such that $\cC_\eta$ is smooth and $f_0$ is constant on a genus $1$ connected subcurve $E\subseteq \cC_0$, it is not always true that $f$ descends to a map $\hat f\colon \hC_\dvr\to\PP^r_\dvr$, where $\hC_0$ has a genus $1$ \emph{Gorenstein} singularity.% Indeed, it is likely that descending to $C'$ imposes differential conditions on $f$ that go beyond just order zero.
 A counterexample is the following.
 
-Consider the stable map $[f]$ in $\oM_{1}(\PP^3,4)$ from an elliptic bridge $C:=R_1{}_{q_1}\!\sqcup E\sqcup_{q_2} R_2$ to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e.
+Consider the stable map $[f]$ in $\oM_{1}(\PP^3,4)$ from an elliptic bridge \[C:=R_1{}_{q_1}\!\sqcup E\sqcup_{q_2} R_2\] to $\PP^3$ that maps $R_1$ to the $z$-axis, contracts $E$ to the origin, and makes $(R_2,q_2)$ into the normalisation of a cusp in the $(x,y)$-plane, i.e.
 its image is the non-Gorenstein singularity:
-\[D:=\Spec\left(\k[x,y,z]/(x,y)\right)\cup \Spec\left(\k[x,y,z]/(z,y^2-x^3)\right).\] 
+\[D:=\operatorname{Spec}\left(\k[x,y,z]/(x,y)\right)\cup \operatorname{Spec}\left(\k[x,y,z]/(z,y^2-x^3)\right).\] 
 Notice that $\operatorname{d}\!f(T_{q_2}R_2)=0$, so there is a non-trivial linear relation:
@@
 and hence the map is smoothable.
-Viscardi claims that the map factors through the family $\hC_T$, obtained by contracting $E$ to a tacnode.
-Notice that the image of $\hat f$ would still be $D$, since there is at most one indeterminacy point of $\hC_T\dashrightarrow\PP^r_T$, located at the singularity.
+Viscardi claims that the map factors through the family $\hC_\dvr$, obtained by contracting $E$ to a tacnode.
+Notice that the image of $\hat f$ would still be $D$, since there is at most one indeterminacy point of $\hC_\dvr\dashrightarrow\PP^r_\dvr$, located at the singularity.
 However in our example $f$ cannot factor through the tacnode.
-Indeed in that case we would have a birational morphism between two singular curves with the same $\delta$ invariant and the same normalisation, so $\hat f\colon \hat C\to D$ would be an isomorphism, which is a contradiction.
+Indeed in that case we would have a birational morphism between two singular curves with the same $\delta$ invariant and the same normalisation, so $\hat f\colon \widehat C\to D$ would be an isomorphism, which is a contradiction.
  We suggest that in this case the correct procedure would be to sprout $(R_1,q_1)$.
@@
 However Viscardi's argument can be fixed.
-Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $T$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}.
-As described in \cite[Theorem~3.6, Step~1]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_T\to\PP^r_{T}$, for which we may suppose that $C:=\cC_0$ is and nodal and reduced $f:=F_0$ is stable.
+Let $(\mathcal{C}_\eta,F_{\eta})$ be a stable map to $\PP^r$, defined on the generic point of a DVR scheme $\dvr$; we may assume that $\mathcal C_{\eta}$ is smooth \cite[Section~3.2.1]{VISC}.
+As described in \cite[Theorem~3.6, Step~1]{VISC}, after applying nodal reduction we get a map $F\colon\mathcal C_{\dvr'}\to\PP^r_{\dvr'}$, for which we may suppose that $C:=\cC_0$ is nodal and reduced, and $f:=F_0$ is stable.
 
 If $f$ is not constant on the minimal genus $1$ subcurve, then it is already $m$-stable and there is nothing to say.
-Otherwise let $E\subset C$ be the maximal connected genus $1$ subcurve where $f$ is constant and let $R_1\sqcup\ldots\sqcup R_m=\overline{C/E}$.
+Otherwise let $E\subset C$ be the maximal genus $1$ subcurve where $f$ is constant and let $R_1\sqcup\ldots\sqcup R_m=\overline{C/E}$.
 
@@
  \end{equation*}
- In this case we blow-up $\mathcal{C}_T$ in $q_{j+1},\ldots, q_m$.
+ In this case we blow-up $\mathcal{C}_\dvr$ in $q_{j+1},\ldots, q_m$.
 The induced map $\tilde{F_0}$ is constant on the exceptional divisors $G_{j+1},\ldots, G_m$ and we can complete the above linear relation to
- \[\alpha_1\operatorname{d}\!\tilde f(T_{q_{1}}\tilde R_{1})+\ldots +\alpha_j \operatorname{d}\!\tilde f(T_{q_{j}}\tilde R_{j})+\beta_{j+1}\operatorname{d}\!\tilde f(T_{q_{j+1}}E_{j+1})+\ldots+\beta_m\operatorname{d}\!\tilde f(T_{q_{m}}E_m)=0\]
-  with any choice of non-zero coefficients $\beta$.
-Now this \emph{sprouting} \cite[Section 2.3]{SMY2} ensures that the sections descend to the corresponding elliptic $m$-fold singularity.
+ \[\alpha_1\operatorname{d}\!\tilde f(T_{q_{1}}\tilde R_{1})+\ldots +\alpha_j \operatorname{d}\!\tilde f(T_{q_{j}}\tilde R_{j})+\beta_{j+1}\operatorname{d}\!\tilde f(T_{q_{j+1}}G_{j+1})+\ldots+\beta_m\operatorname{d}\!\tilde f(T_{q_{m}}G_m)=0\]
+  with $\beta_i=1$ for all $i$.
+Now this \emph{sprouting} \cite[Section 2.3]{SMY2} ensures that the map descends to the corresponding elliptic $m$-fold singularity.
 Notice that, for every $m_1\leq m_2$, there is a morphism from an $m_2$-elliptic singularity to an $m_1$-elliptic point that is birational on the target and contracts $m_2-m_1$ branches of the source to the singular point.
-At this point proceed with Step~2 of Viscardi's algorithm.
+Proceed now with Step~2 of Viscardi's algorithm.
 
@@
 
-In particular the space $\Mone{1}{\PP^r}{d}$ we will consider in the next sections has not got the boundary component $D_{(d)}(\PP^r,d)$.
+In particular the space $\Mone{1}{\PP^r}{d}$ we will consider in the next sections has not got the boundary component $D^1$.
 % \begin{cor}\cite[Cor.~5.10]{VISC}
@@
 
- \subsection{A different characterisation of smoothability}
- Inspired by Viscardi's alternate compactification, we give yet another characterisation of smoothable maps in genus $1.$
+ \subsection{Genus $1$ singularities and smoothability}
+ Inspired by Viscardi's alternate compactification, we give another description of smoothable maps in genus $1.$ We recall the following:
  \begin{dfn}
@@
  \begin{prop}\label{prop:smoothability2}
- Let $[f\colon C\to \PP^r]$ be a stable map from a genus $1$ curve $C=E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i$, where $E$ is the maximal genus $1$ subcurve contracted by $f$, and the $R_i$'s are rational tails on which $f$ has positive degree.
-
-  Then $f$ is smoothable if and only if it factors through a Cohen-Macaulay genus $1$ singularity with positive degree on at least one of its branches.
+ Let $[f\colon C\to \PP^r]$ be a stable map from a genus $1$ curve $C=E {}_{\mathbf p}\!\sqcup_{\mathbf q}\bigsqcup_{i=1}^m R_i$, where $E$ is the maximal genus $1$ subcurve contracted by $f$, and the $R_i$ are rational tails on which $f$ has positive degree.
+
+  Then $f$ is smoothable if and only if it factors through a curve with a genus $1$ singularity $f\colon C\xrightarrow{\phi}\widehat C\xrightarrow{\hat f} \PP^r$, such that $\phi$ contracts $\operatorname{Exc}(f)$ and is an isomorphism outside it.
 \end{prop}
 
-\begin{lem}(Classification of Cohen-Macaulay genus $1$ singularities)
-The CM (i.e. reduced) genus $1$ singularities with $m$ branches are obtained by gluing a genus $0$ singularity with $k$ branches together with a Smyth's $(m-k)$-elliptic fold.
+\begin{lem}(Classification of genus $1$ singularities)
+The Cohen-Macaulay (i.e. reduced) genus $1$ singularities with $m$ branches are obtained by gluing a genus $0$ singularity with $k$ branches together with a Smyth's $(m-k)$-elliptic fold.
 Notice that $k$ may be $0$ (i.e. a point) or $1$ (i.e. a smooth rational curve).
@@
 
-Let us recall that to describe $R$ as a quotient polynomial ring, it is enough to find a $\k$-basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=\langle e_1,\ldots, e_s\rangle_{\k}$ where the $e_i$'s are some elements in $\widetilde{R}.$ Indeed, once given such a basis, it is a consequence of completeness that $R$ can be recognized as $\k[[x_1,\ldots, x_s]]/I$, where $I$ is the kernel of the ring homomorphism
+Let us recall that to describe $R$ as a quotient polynomial ring, it is enough to find a $\k$-basis for $\mathfrak{m}_R/\mathfrak{m}^2_R=\langle e_1,\ldots, e_s\rangle_{\k}$ where the $e_i$ are some elements in $\widetilde{R}.$ Indeed, once given such a basis, it is a consequence of completeness that $R$ can be recognised as $\k[[x_1,\ldots, x_s]]/I$, where $I$ is the kernel of the ring homomorphism
 \begin{align*}\label{eq:singularity}
@@
 \end{enumerate}
-From (3) and (2) it follows that $\dim_\k(\widetilde R/R)_1=1$ and $\dim_\k(\widetilde R/R)_i=0$ for $i\geq 2$. Then the exact sequence:
+From (2) and (3) it follows that $\dim_\k(\widetilde R/R)_1=1$ and $\dim_\k(\widetilde R/R)_i=0$ for $i\geq 2$. Then the exact sequence:
 \[ 0\to \frac{\mathfrak m_{\widetilde R}^2}{\mathfrak m_{\widetilde R}^2\cap R}\to\frac{\mathfrak m_{\widetilde R}}{\mathfrak m_{\widetilde R}\cap R}\to (\widetilde R/R)_1\to 0\]
@@
 Hence $s$ is at least $m-1$.
-After relabelling we may assume $e_1,\dots e_{m-1}$ generate $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$, and after Gaussian elimination they take the following form:
+After relabelling we may assume $e_1,\ldots, e_{m-1}$ generate $\mathfrak{m}_R/\mathfrak{m}^2_{\widetilde{R}}$, and after Gaussian elimination they take the following form:
 \begin{align*}
@@
 \end{align*}
-with $a_{1}, \ldots, a_{m-1}\in \k.$ At this point Smyth restricts his attention to Gorenstein singularities and shows that under this assumption he can choose all the $a_i$ to be $1$; furthermore $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ holds if $m\geq 3$, thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and the goal is reached.
+with $a_{1}, \ldots, a_{m-1}\in \k.$ At this point Smyth restricts his attention to Gorenstein singularities and shows that under this assumption he can choose all the $a_i$ to be $1$.
+Furthermore $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ holds if $m\geq 3$, thus the above are generators for $\mathfrak{m}_R/\mathfrak{m}^2_R$ and the goal is reached.
 For $m=1$ (resp.
@@
 \begin{enumerate}
-\item At least two of the $a_i$'s are non-zero, say $i=1,2$: then $a_1a_2t_m^2=e_1\cdot e_2$ so $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and we are done as above.
-It is easily seen that  $e_1,\ldots, e_{m-1}$ satisfy the equations of a $(k,m-k)$ singularity where $k$ is the number of $a_i$'s that are zero.
-\item Only one of the $a_i$'s is non-zero, say $a_1=1$: then $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}+(t_m^2)$ and by adjoining $e_m=t_m^2$ to the $e_i$'s we see that they generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and they satisfy the equation of a tacnode $(e_1^2-e_m)e_m=0$ and $e_ie_j=0$ for $i\neq j$ and $(i,j)\neq(1,m)$, so this is an $(m-2,2)$ singularity.
-\item Finally all the $a_i$'s are zero: then we have to add $t_m^2,\ t_m^3$ to generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we obviously find an $(m-1,1)$ singularity.
+\item At least two of the $a_i$ are non-zero, say $i=1,2$: then $a_1a_2t_m^2=e_1\cdot e_2$ so $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}$ and we are done as above.
+It is easily seen that  $e_1,\ldots, e_{m-1}$ satisfy the equations of a $(k,m-k)$ singularity where $k$ is the number of $a_i$ that are zero.
+\item Only one of the $a_i$ is non-zero, say $a_1=1$: then $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}^2_{R}+(t_m^2)$ and by adjoining $e_m=t_m^2$ to the $e_i$ we see that they generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and they satisfy the equation of a tacnode $(e_1^2-e_m)e_m=0$, and $e_ie_j=0$ for $i\neq j$ and $(i,j)\neq(1,m)$, so this is an $(m-2,2)$ singularity.
+\item Finally all the $a_i$ are zero: then we have to add $t_m^2,\ t_m^3$ to generate $\mathfrak{m}_R/\mathfrak{m}^2_R$ and we find an $(m-1,1)$ singularity.
 \end{enumerate}
 \noindent Similarly for $m=2$ there are two possibilities: the tacnode (corresponding to $a_1\neq 0$) and the union of a cusp with a non-coplanar line (for $a_1=0$), with equations:
-\[ \k[[x,y,z]]/(xz,yz,y^2-x^3)\]
+\[ \k[[x,y,z]]/(xz,yz,y^2-x^3).\]
 \noindent For $m= 1$ the only possible singularity is the cusp: indeed it can be proven that $\mathfrak{m}^2_{\widetilde{R}}=\mathfrak{m}_{R}$. 
@@
 \begin{remark}
- The genus and number of branches are not sufficient to tell these singularities apart anymore, neither is the embedding dimension. A numerical invariant that distinguishes them is:
+ The genus and number of branches are no more sufficient to tell these singularities apart, neither is the embedding dimension. A numerical invariant that distinguishes them is:
 \[ \dim_\k R/I_p \]
@@
 
-\begin{lem}
-Every Cohen-Macaulay genus $1$ singularity is smoothable.
+\begin{lem}\label{lem:sing_smoothability}
+Every genus $1$ singularity is smoothable.
 \end{lem}
 \begin{proof}
-We exhibit explicit smoothings for the above singularities.
-Start with two families $(\cC^0;\sigma_0,p_1,\ldots,p_k)\to T$ and $(\cC^1;\sigma_1,q_{k+1},\ldots,q_m)\to T$ respectively of smooth $(k+1)$-pointed rational curves and smooth $(m-k+1)$-pointed elliptic curves over a DVR scheme $T$, e.g.
-consider two trivial families.
-
- Then perform a blow-up along the trace of $p_1,\dots p_k$ and $q_{k+1},\dots q_{m}$ on the central fibers  $(\cC^0)_0$ and $(\cC^1)_0$ to get families $\widetilde{\cC}^0\xrightarrow{\pi_0} {\cC}^0$ and $\widetilde{\cC}^1\xrightarrow{\pi_1} {\cC}^1$ respectively.
-
-We can now find semi-ample line bundles which are trivial on the strict transform of the central fiber and ample everywhere else, namely
-\begin{align*}
-\mathcal L_0&=\pi_0^*\OO_{\cC^0}(p_1+\ldots+ p_k)(-F_1-\ldots -F_k),\\
- \mathcal L_1&=\pi_1^*\OO_{\cC^1}(q_{k+1}+\ldots+ q_{m})(-F_{k+1}-\ldots -F_{m})
-\end{align*}
-where we denoted by $F_j$ the exceptional divisors of the blow-ups.
-
-We can then use them to give contraction maps.
-The contracted families   $\;\hat{\cC}^0\to T\;$ and $\;\hat{\cC}^1\to T\;$ still have smooth generic fibers of genus $0$ and $1$ respectively and, by construction, $(\hat{\cC}^0)_0$ has a genus $0$ singularity with $k$ branches and $(\hat{\cC}^1)_0$ has a Smyth's $(m-k)$-elliptic point \cite[Lemma~2.12]{SMY1}.
-
-Observe now that $\sigma_0$ and $\sigma_1$ induce sections of the contracted curves $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ passing through the singular points of the central fiber.
-Let $\hat{\cC}\to T$ the family of curves obtained by gluing $\hat{\cC}^0\to T$ and $\hat{\cC}^1\to T$ along $\sigma_0$ and $\sigma_1$ (pushout).
-Then $\hat{\cC}$ has a nodal generic fiber which clearly can be further smoothed.
+ We explicitly construct a (semi)stable model with a contraction to the given singularity.
+Assume we start with a $(k,m-k)$-singularity $\widehat C$.
+Pick any $m$-pointed elliptic curve $(E,q_1,\ldots,q_m)$ and glue $E$ along the markings with $m$ copies of $\PP^1$ at their respective points $0$; call the rational tails $R_1,\ldots,R_m$.
+It is useful to consider the resulting curve $C$ as a point of $\oM_{1,2m}$ with markings on the rational tails given by $1$ and $\infty$.
+We now choose a smoothing $\cC_{\dvr}$ of $C$ over a DVR scheme $\dvr$, such that the total space $\cC_{\dvr}$ has an $A_1$-singularity at the nodes $q_1,\ldots,q_k$ and is regular everywhere else; furthermore extend the markings to get a horizontal Cartier divisor $\Sigma$.
+Resolving the singularities we obtain a fibered surface $\pi^{\rm{ss}}\colon\cC_{\dvr}^{\rm{ss}}\to\dvr$ such that in the central fiber the strict transforms $\widetilde R_1,\ldots,\widetilde R_k$ are at distance $1$ from the core $E$, while the other rational tails are adjacent to it.
+Call $F_1,\ldots,F_k$ the exceptional divisors of the resolution.
+As in \cite[Lemma 2.12]{SMY1} we may contract $E$, which is obviously balanced, by means of the line bundle:
+ \[\mathcal L_1:=\omega_{\pi^{\rm{ss}}}(E+\Sigma),\]
+ which results in $\overline{\cC}_{\dvr}$ with an $m$-elliptic singularity in the central fiber, $k$ of whose branches are the images of $F_1,\ldots,F_k$ and are thus unmarked.
+We may finally perform a second contraction by using the line bundle $\mathcal L_2:=\OO_{\overline{\cC}_{\dvr}}(\overline{\Sigma})$; let $\hC_{\dvr}$ denote the resulting family of curves, with singularity $\hat q$.
+Notice that $\mathcal L_2$ satisfies cohomology and base-change, hence we may simply check on the central fiber both its relative semi-ampleness and the behaviour of its sections.
+The sections will be constant along $\overline F_1,\ldots,\overline F_k$, so the linear relation among their derivatives at the Smyth's singularity will only imply the linear dependence of the tangent vectors of $\widehat R_{k+1},\ldots, \widehat R_m$ at $\hat q$; on the other hand sections of $\mathcal L_2$ along $\overline R_1,\ldots,\overline R_k$ are completely independent, and thus they embed these $\PP^1$.
+We deduce that the central fiber of $\hC_{\dvr}$ has a $(k,m-k)$-singularity.
 \end{proof}
@@
 \begin{proof}\ref{prop:smoothability2}
- The argument that if $f$ is smoothable then it has to factor through a genus $1$ singularity was given by Vakil when he showed that the tangent vectors have to be linearly dependent in the image \cite[Lemma 5.9]{Vre}.
-
-Viceversa, let us suppose that $f\colon C\to \PP^r$ factors through $\hat{f}\colon \hat{C}\to\PP^r$  with $\hat{C}$ a genus $1$ singularity in a way that at least one branch is not contracted.
-
+ The argument that if $f$ is smoothable then it has to factor through a genus $1$ singularity was essentially given by Vakil in \cite[Lemma 5.9]{Vre}. We review it here in some detail.
+
+ Pick a smoothing $F\colon\cC_{\dvr}\to \PP^r$ of $f=F_0$.
+After base-change we may assume that $\dvr$ is the spectrum of a complete DVR.
+The line bundle $\mathcal L:=F^*\OO_{\PP^r}(1)$ is trivial on every irreducible component of the central fiber contracted by $f$.
+Since every connected component of $\operatorname{Exc}(\mathcal L)=\{D\subset C : \mathcal{L}\rvert_D\simeq \OO_D\}$ has arithmetic genus $0$ or $1$, we may use the argument in \cite[Lemma 2.12]{SMY1} to show that $\mathcal L$ is $\pi_{\dvr}$-semi-ample.
+We thus get a contraction $\phi\colon \cC_{\dvr}\to \overline{\cC}_{\dvr}$ and notice that $F$ factors through $\phi$ by the construction of $\overline{\cC}_{\dvr}=\underline{\operatorname{Proj}}_{\dvr}\left(\bigoplus_{n\geq 0}\pi_{\dvr,*}\mathcal L^{\otimes n}\right)$.
+ Being a smoothing of a reduced curve, $\cC_{\dvr}$ is normal, thus $\phi$ factors through the normalisation $\nu\colon \hC_{\dvr}\to \overline{\cC}_{\dvr}$, which is a finite map by \cite[\S 8.2]{Liusbook}.
+It is now clear that $\hC_{\dvr}\to\dvr$ is a flat family of genus $1$ curves with reduced fibers, and the map $\overline{F}\circ\nu$ has positive degree on all the components of $\hC_0$.
+
+ Viceversa let us suppose that we have a factorisation:
+ \bcd
+ C\ar[rr,"f"]\ar[dr,"\phi"] & & \PP^r \\
+ & \widehat{C}\ar[ur,"\hat f"] &
+ \ecd
+ such that $\phi$ contracts $\operatorname{Exc}(f)$ and is an isomorphism everywhere else.
+We shall below make the point that $f$ is smoothable as soon as it is not constant on the core (compare also with \cite[Theorem 4.5.1]{RSPW}), so in this case we have no use for $\phi$.
+Otherwise $\phi$ contracts at least the core, and $\widehat C$ has a genus $1$ singularity at a certain point $q$.
 We first show that:
  \begin{claim}
- We can produce smoothings $\cC$ of $C$ and $\hC$ of $\hat C$ with a contraction map $\cC\to\hC$ compatible with the given $C\to\hat C$. See Remark \ref{rem:compatible_smoothing} below
+ Under these assumptions, we can produce smoothings $\cC_{\dvr}$ of $C$ and $\hC_{\dvr}$ of $\widehat{C}$ with a contraction map $\phi_{\dvr}$ extending the given $\phi$.
  \end{claim}
-\begin{proof}
- Assume that $\hat C$ has a $(k,m-k)$-singularity. 
-Pick a smoothing $\cC$ of $C$ such that after resolving the $A_n$ singularities at the nodes, i.e.
-when looking at the semistable model with regular total space $\cC^{\rm{ss}}$, the following holds: call $E$ the maximal \emph{balanced} genus $1$ subcurve \cite[Proposition~2.11]{SMY1} contracted by $f^{\rm{ss}}$,
- then there are $m-k$ rational tails of positive degree directly adjacent to $E$ and the other $k$ rational tails are further away, possibly at different distances.
- %Notice that $f^{\rm{ss}}$ is defined since $C^{\rm{ss}}$ differs from $C$ only for $-2$ curves.
-
- We may then perform a two-step contraction: by the work of Smyth we can find a line bundle contracting $E$, namely:
-\[\mathcal L=\omega_{\cC^{\rm{ss}}/T}\left( \sum_{F\subseteq E}(l+1-l(F,Z)F\right),\]
-where $Z$ is the core, $l(\cdot,\cdot)$ is the distance function on the dual graph and $l$ is the maximum value attained by $l(\cdot,Z)$ on $E$.
-Let us call $\bar\cC$ the family of curves obtained from this contraction; notice that $f^{\rm{ss}}$ descends to a $\bar f\colon\bar\cC\to PP^r$.
-The central fiber $\bar{C}$ has an $(m-k+h)$-fold elliptic point with $h\leq k$, and it still has a contraction map $\rho$ to $\hat{C}$.
-
-If necessary we may add markings $p_1+\ldots+ p_N=\Sigma$ on all the $f$-contracted rational components away from the genus $1$ singularity, and on the branches of the $(m-k+h)$-fold that are not contracted by $\rho$.
-Now use $\hat{f}^*\OO_{\PP^r}(1)(\Sigma)$ to perform a second contraction.
-Since it has no $H^1$, it satisfies cohomology and base change, and we can check that the result of this second contraction is a $(k,m-k)$-singularity simply by looking at the vanishing orders of the sections on $\bar{C}$.
-%These sections are constant on the branches of the singularity to which we have not added any marking, so we conclude that the dependence relation among  the tangent vectors of the branches at the singular point of the second contraction only involve the $m-k$ rational tail image of the ones adjacent to $E$.
-
-%Since $\hat{C}$ with the added markings $\Sigma$ is stable, the morphism $\cC^{\rm{ss}}\to\cC$ we just constructed factors through a morphism
-%$\cC\to\hat{\cC}$ whose central fibers are $C$ and $\hat{C}$ and compatible with $f$ and $\hat{f}.$
-\end{proof}
-
-Let $\hat{\mathcal L}$ an extension of $\hat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on $\hat{\cC}$, which exists because deforming line bundles on curves is unobstructed.
-In order to extend $\hat{f}$ to $\hat{F}\colon \hat{\cC}\to\PP^r$ all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hat{\mathcal{L}}.$
-Thus it is enough to verify that $H^1(\hat{C},\hat{L})=0$ \cite{Wang}.
-Once this is done we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC\to\hat{\cC}\xrightarrow{\hat F}\PP^r$.
-
-Since all the curves we are considering are Cohen-Maculay, they have a dualising sheaf $\omega_{\hat{C}}$ such that for any line bundle $\hat{L}$
-\[H^1(\hat{C},\hat{L})=(H^0(\hat{C},\hat{L}^{-1}\otimes\omega_{\hat{C}}))^{\vee}.\]
-It is known \cite[IV, \S~3]{serre} that  $\omega_{\hat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ (where $\nu\colon\bar C\to\hat C$ is the normalisation) satisfying: for every open $U\subseteq\hat C$ a rational $1$-form $\omega\in \nu_*\left( \omega_{\overline{C}}\otimes K(\overline{C})\right)(U)$ is a section of $\omega_{\hat C}(U)$ iff
-\[\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*(f)\omega) =0 \quad \quad \forall f\in\OO_C(U)\]
-
-From this description it is patent that the pullback of $\omega_{\hat C}$ to the normalisation restricts to a line bundle of degree $-1$ or $0$ on every branch, according to it being one of the $k$ or $m-k$ components.
-Hence it can be seen from the normalisation exact sequence and Serre duality that $H^1(\hat{C},\hat{L})=0$ as soon as $\hat L$ has positive degree on one of the branches.
- \end{proof}
+  A statement of this kind is in general far from true, see Remark~\ref{rem:compatible_smoothing} below.
+  The proof of this claim follows the lines of the two-step contraction described in the proof of Lemma~\ref{lem:sing_smoothability}.
+It will be useful to treat $C$ as a stable curve marked with $f^{-1}(Q)$ for a generic quadric $Q\subseteq \PP^r$.
+  \begin{proof} Assume that $\widehat C$ has a $(k,m-k)$-singularity at $q$; denote by $E:=\phi^{-1}(q)\subset C$, which is the maximal genus $1$ unmarked (i.e.
+contracted by $f$) connected subcurve of $C$.
+By assumption the components of $C$ adjacent to $E$ are marked (i.e.
+not contracted by $f$), and they can be partitioned into $R_1,\ldots,R_k$ mapping to the genus $0$ part of the $(k,m-k)$-singularity, and $R_{k+1},\ldots,R_m$ parametrising the branches of the $(m-k)$-elliptic fold.
+Let $l_i$ denote the distance of $R_i$ from the core $Z$, which can be determined from the marked dual graph.
+Let $l=\max\{l_{k+1},\ldots,l_m\}$ and $L=\max\{l_1,\ldots,l_m\}$.
+Consider a smoothing $\cC_{\dvr}$ of $C$ with an $A_{l-l_i}$ singularity at $R_i\cap E$ for $i=k+1,\ldots,m$, and an $A_{L-l_i+1}$-singularity at $R_i\cap E$ for $i=1,\ldots,k$.
+Extend the markings $f^{-1}(Q)$ to a horizontal Cartier divisor $\Sigma$.
+Let $\cC_{\dvr}^{\rm{ss}}$ be the semistable model with regular total space; notice that in the central fiber the strict transforms of $R_{k+1},\ldots,R_m$ are at distance $l$ from the core, while all other marked components are further apart.
+Let $E^{\rm{bal}}$ be the maximal unmarked balanced subcurve inside $\cC_0^{\rm{ss}}$, including all the components at distance less than $l$ from $Z$.
+We may now use Smyth's line bundle:
+ \[\mathcal L_1=\omega_{\cC^{\rm{ss}}_{\dvr}/\dvr}\left( \sum_{F\subseteq E^{\rm{bal}}}(l+1-l(F,Z))F\right)\otimes \OO_{\cC^{\rm{ss}}_{\dvr}}(\Sigma),\]
+ to perform the contraction of $E^{\rm{bal}}$, obtaining a family $\overline{\cC}_{\dvr}\to\dvr$ whose central fiber has an $m$-elliptic fold point.
+Notice that the contraction is otherwise an isomorphism, due to the stability condition.
+ As in Lemma~\ref{lem:sing_smoothability} we may then perform a second contraction by using the line bundle $\mathcal L_2:=\OO_{\overline{\cC}_{\dvr}}(\overline{\Sigma})$; we denote by $\hC_{\dvr}$ the resulting family of curves.
+It may be seen that the central fiber $\hC_0$ is isomorphic to $\widehat C$, and so is the resulting contraction up to an automorphism of $C$.
+\end{proof}
+
+Let $\hL$ be an extension of $\widehat{L}:=\hat{f}^*\OO_{\PP^r}(1)$ on $\hC$, which exists because deforming line bundles on curves is unobstructed.
+In order to extend $\hat{f}$ to $\widehat{F}\colon \hC_{\dvr}\to\PP^r$ all we have to show is that the $r+1$ sections $\hat{s}_0,\dots, \hat{s}_{r+1}$ representing the map $\hat{f}$ extend to sections of $\hL.$
+Thus it is enough to verify that $H^1(\widehat{C},\widehat{L})=0$ \cite{Wang}.
+Once this is done we are going to obtain the smoothing of the original map by precomposing with the contraction $F\colon\cC_{\dvr}\xrightarrow{\phi}\hC_{\dvr}\xrightarrow{\widehat F}\PP^r$.
+
+Since all the curves we are considering are Cohen-Maculay, they have a dualising sheaf $\omega_{\widehat{C}}$ such that for any line bundle $\widehat{L}$:
+\[H^1(\widehat{C},\widehat{L})=(H^0(\widehat{C},\widehat{L}^{-1}\otimes\omega_{\widehat{C}}))^{\vee}.\]
+It is known \cite[IV, \S~3]{serre} that  $\omega_{\widehat{C}}$ can be described as the subsheaf of $\nu_* \omega_{\overline{C}}\otimes K(\overline{C})$ (where $\nu\colon\bar C\to\widehat{C}$ is the normalisation) satisfying: for every open $U\subseteq\widehat{C}$ a rational $1$-form $\omega\in \nu_*\left( \omega_{\overline{C}}\otimes K(\overline{C})\right)(U)$ is a section of $\omega_{\widehat{C}}(U)$ if and only if:
+\[\sum_{q\in \nu^{-1}(0)}\rm{Res}(\nu^*(f)\omega) =0 \quad \quad \forall f\in\OO_{\widehat C}(U)\]
+
+From this description it is patent that the pullback of $\omega_{\widehat{C}}$ to the normalisation restricts to a line bundle of degree $-1$ or $0$ on every branch, according to it being one of the $k$ or $m-k$ components.
+Hence it can be seen from the normalisation exact sequence and Serre duality that $H^1(\widehat{C},\widehat{L})=0$ as soon as $\hat L$ has positive degree on one of the branches.
+ \end{proof}
+
  \begin{remark}\label{rem:compatible_smoothing}
-In general is not possible to find compatible smoothings as above: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar singularity with local equation $y^2-x^5=0$.
+In general it is not possible to find compatible smoothings as above: pick any genus $2$ curve with a rational tail and map it to the ramphoid cusp, a planar singularity with local equation $y^2-x^5=0$.
 Then a compatible smoothing can be found only if the rational tail is attached to a Weierstrass point of the genus $2$ curve, as can be seen by computing the semi-stable model of the ramphoid cusp.
@@
 Smyth.
-
 \end{remark}
@@
  \begin{remark}
-It is not hard to adapt Vakil's argument \cite{Vre} to show that factoring through a genus $1$ singularity is equivalent to the tangent vectors being linearly dependent in the image.
+A way around the construction of a compatible smoothing, would be to appeal to \cite[Lemma 2.9]{SMYtowards} and prove that the smoothability of $f$ only depends on its restriction to the $k$ rational tails, namely it is independent of the $k$-pointed elliptic curve that $f$ contracts.
 \end{remark}
-\begin{remark}
-The ideas above are similar to those employed in \cite[Theorem 4.5.1]{RSPW} to show that $\pazocal{V\!Z}_{1,n}(\PP^r,d)$ is smooth, where the latter is defined by requiring the factorisation property for the map through a Smyth's singularity after sprouting.
-\end{remark}
-
-\section{From $p$-fields to the quintic threefold}\label{section:p-fields}
-We introduce the moduli space $\Mone{1}{\PP^4}{d}^p$ of $1$-stable curves with $p$-fields, we endow it with a cosection-localised $0$-dimensional virtual class supported on a proper substack (depending on the polynomial $\w$), and we show that its degree coincides with the genus $1$ cuspidal invariants of the quintic threefold $X$ up to a sign.
-This is a word-by-word repetition of the arguments in \cite{CLpfields} once noticed that they carry over to the situation where we work with a family of Gorenstein (not necessarily nodal) curves.
-Our aim in this section is to improve the legibility of this paper by providing the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; it can otherwise be skipped.
+
+\section{The moduli space of $1$-stable maps with $p$-fields}\label{section:p-fields}
+We adapt Chang-Li's theory of $p$-fields to cuspidal maps.
+This is a word-by-word repetition of the arguments in \cite{CLpfields} once noticed that they carry over to families of at worst cuspidal curves.
+We provide the non-expert reader with a r\'{e}sum\'{e} of some of the key ideas contained in \cite{CLpfields}; this section can otherwise be skipped.
 \subsection{Moduli of sections}
 \begin{dfn}
- Let $B$ be an algebraic stack and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation which is representable by algebraic spaces and whose geometric fibers are reduced l.c.i.
+ Let $B$ be an algebraic stack and let $\pi\colon \cC\to B$ be a flat proper morphism of finite presentation, which is representable by algebraic spaces, and whose geometric fibers are reduced l.c.i.
 curves.
-Let $\mathcal Z$ be an algebraic stack smooth representable and quasi-projective over $\cC$.
+Let $\mathcal Z$ be an algebraic stack,  representable, quasi-projective, and smooth over $\cC$.
 The \emph{cone of sections} of $\mathcal Z$ over $\cC$ is a $B$-stack $\mathfrak S$ defined by:
@@
 When $\mathcal Z=\rm{Vb}(\mathcal L)$ for a line bundle $\mathcal L$ on $\cC$, the algebraic stack  $\mathfrak{S}\to B$ representing sections of $\mathcal L$ can be constructed as:   
-\[C(\pi_*\mathcal L)=\Spec_B(\R^1\pi_*\mathcal L).\]
- This is essentially because $\R^1\pi_*\mathcal L$ commutes with pullback, and it has got the desired modular interpretation by Serre duality.
+\[C(\pi_*\mathcal L):=\Spec_B\operatorname{Sym}^{\bullet}(\R^1\pi_*\mathcal L^{\vee}\otimes\omega_{\pi}).\]
+ This is essentially because $ \R^1\pi_*\mathcal L^{\vee}\otimes\omega_{\pi}$ commutes with pullbacks, and it has the desired modular interpretation by Serre duality.
 
 \subsubsection*{Moduli of stable maps and $1$-stable maps} 
-Let $X\subseteq \PP^r$ be a projective variety and let $\mathcal Z_X$ be defined by the following cartesian diagram over $\cC$:
-\bcd
-\mathcal Z_X\ar[r,"/\Gm"]\ar[d,hook]\ar[dr,phantom,"\Box"] & X\times \cC\ar[d,hook] \\
-\mathcal L^{\oplus r+1}\setminus 0_{\cC}\ar[r,"/\Gm"] & \PP^r\times\cC
-\ecd
-Then $\oM_1(X,\beta)$, the moduli space of stable maps to $X$, is an open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$: the morphism $\oM_1(X,\beta)\to \pP$ is given by the line bundle $f^*\OO_{\PP^r}(1)$ on the universal curve over $\oM_1(X,\beta)$, that to $\mathfrak{S}_X$ by its sections $[s_0:\ldots:s_r]$ corresponding to the universal stable map $f$, and the stability condition is an open one.
+Recall that $\mathfrak{P}$ denotes the universal Picard stack.
+Let $X\subseteq \PP^r$ be a projective variety and let $\mathcal Z_X$ be defined by the following cartesian diagram over $\cC_{\mathfrak{P}}$:
+\bcd
+\mathcal Z_X\ar[r,"/\Gm"]\ar[d,hook]\ar[dr,phantom,"\Box"] & X\times \cC_{\mathfrak{P}}\ar[d,hook] \\
+\mathcal L^{\oplus r+1}\setminus 0_{\cC}\ar[r,"/\Gm"] & \PP^r\times\cC_{\mathfrak{P}}
+\ecd
+Then $\oM_1(X,\beta)$ is the open substack of the moduli space $\mathfrak{S}_X$ of sections of $\mathcal Z_X\to\cC_{\pP}$ defined by the stability condition.
 This is the point of view we have already taken for $X=\PP^n$ in Proposition \ref{prop:smoothability} to describe the local equations of the moduli space of maps.
@@
 
-The moduli space of $p$-fields is defined as the cone of sections of the line bundle $\widehat{\mathcal P}_{\hrM}$ over $\hC_{\hrM}$.
+The moduli space of $p$-fields is defined as the cone of sections of the line bundle $\widehat{\mathcal P}_{\hrM}$ over $\hC_{\hrM}$:
 
 \begin{dfn}
- The moduli space of $1$-stable maps with $p$-fields \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\hrM,*}(\widehat{\mathcal P}_{\hrM}))\] parametrises $1$-stable maps
+ The moduli space of $1$-stable maps with $p$-fields: \[\Mone{1}{\PP^4}{d}^p:=C(\hat\pi_{\hrM,*}(\widehat{\mathcal P}_{\hrM}))\] parametrises $1$-stable maps:
  \bcd
@@
 
-We abbreviate $\widehat{\pazocal P}:=\Mone{1}{\PP^4}{d}^p$.
-Employing the above description of the moduli space of $1$-stable maps,  $\widehat{\pazocal P}$ can also be thought as an open in the moduli space of sections of the vector bundle $\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus \widehat{\mathcal P}_{\hP}).
+We use the abbreviation $\widehat{\pazocal P}:=\Mone{1}{\PP^4}{d}^p$.
+Employing the above description of the moduli space of $1$-stable maps,  $\widehat{\pazocal P}$ can also be thought of as an open in the moduli space of sections of the vector bundle $\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus \widehat{\mathcal P}_{\hP}).
 $
@@
 \subsection{Obstruction theories}
-Sticking to the same notation as above, the morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
+With the above, the morphism $\mathfrak S\to B$ admits a relative dual perfect obstruction theory:
 \[ \phi_{\mathfrak S/B}\colon \mathbb T_{\mathfrak S/B}\to \mathbb E_{\mathfrak S/B}:=\R^\bullet\pi_{\mathfrak S,*}\mathfrak e^* T_{\mathcal Z/\cC}\]
-The proof of this fact is given in \cite[Proposition 2.5]{CLpfields}.
-We notice at this point that this results applies as well when the fibers of $\cC\to B$ are l.c.i curves, since the proof relies on general properties of obstruction theories and the cotangent complex and the fact that $\mathcal Z\to\cC$ is smooth,
-but never on the specification that $\cC\to B$ be a family of \emph{nodal} curves.
+For the proof see \cite[Proposition 2.5]{CLpfields} and notice that it relies on general properties of obstruction theories and the cotangent complex, and the fact that $\mathcal Z\to\cC$ is smooth,
+but never on the specification that $\cC\to B$ is a family of \emph{nodal} curves.
 
@@
  \item for the direct image cone of a line bundle $\mathcal L$ the dual obstruction theory is $\mathbb E_{C(\pi_*\mathcal L)/B}=\R^\bullet\pi_*\mathcal L$;
- \item the moduli space $\hrM=\oM_1^{(1)}(\PP^4,d)$ has a dual obstruction theory relative to $\hP$ given by $ \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})$;
- \item in the case of $1$-stable maps with $p$-fields $\widehat{\pazocal P}=\oM_1^{(1)}(\PP^4,d)^p$ we get $\mathbb E_{\widehat{\pazocal P}/\hP}=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}}).$
+ \item the moduli space $\hrM=\oM_1^{(1)}(\PP^4,d)$ has a dual obstruction theory relative to $\hP$ given by $\mathbb{E}_{\hrM/\hP}= \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})$;
+ \item in the case of $1$-stable maps with $p$-fields $\widehat{\pazocal P}=\oM_1^{(1)}(\PP^4,d)^p$, we get $\mathbb E_{\widehat{\pazocal P}/\hP}=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}}).$
 \end{itemize}
-
-There is a different obstruction theory on the moduli space of $1$-stable maps relative to $\hM$, which is the one introduced by Behrend and Fantechi for spaces of morphisms \cite[Proposition 6.3]{BF}.
-The two obstruction theories are compatible.
+We review the compatibility of various obstruction theories for the moduli spaces mentioned above. 
 \begin{lem}
@@
  \bcd
- \hat\PtoM^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\hrM/\hP} \ar[r]\ar[d] &  \mathbb T_{\hrM/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
- \R^\bullet\hat\pi_{\hrM,*}(\OO_{\hat \cC})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(f_{\hrM}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
- \ecd
- implying that $\mathbb T_{\hrM/\hP}\to \mathbb E_{\hrM/\hP}:=\R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \mathcal L_{\hrM})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\hrM$.
+ \hat\rho ^*\mathbb T_{\hP/\hM}[-1]\ar[r]\ar[d,"\wr"] &  \mathbb T_{\hrM/\hP} \ar[r]\ar[d] &  \mathbb T_{\hrM/\hM} \ar[r,"{[}1{]}"]\ar[d] & {} \\
+ \R^\bullet\hat\pi_{\hrM,*}(\OO_{\hC})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \hL_{\hrM})\ar[r] & \R^\bullet\hat\pi_{\hrM,*}(f_{\hrM}^* T_{\PP^4})\ar[r,"{[}1{]}"] & {}
+ \ecd
+ implying that $ \mathbb E_{\hrM/\hP}=\R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \mathcal L_{\hrM})$ gives the standard Behrend-Fantechi-Viscardi virtual class on $\hrM$.
 \end{lem}
 \begin{proof}
- The first statement follows from deformation theory: the projection $\hat\PtoM\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\hat C}}(\Omega_{\hat C},\OO_{\hat C})=0$.
+ The first statement follows from deformation theory: the projection $\hat\rho\colon\hP\to\hM$ is unobstructed of relative dimension $0$ and $\hM$ is a smooth Artin stack of dimension $0$, since both nodal and cuspidal singularities are l.c.i., so obstructions to their deformations are contained in $\operatorname{Ext}^2_{\OO_{\widehat{C}}}(\Omega_{\widehat{C}},\OO_{\widehat{C}})=0$.
 
@@
  The lower row in the above diagram is induced by the Euler sequence of $\PP^4$.
-The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\mathcal L)$ over $\hP$.
+The middle column comes from identifying the space of stable maps as an open substack of the cone of sections (see above) of $\rm{Vb}(\bigoplus_0^4\hL)$ over $\hP$.
 The existence of such a commutative diagram is \cite[Lemma 2.8]{CLpfields}.
-
- Finally the fact that  $\mathbb T_{\hrM/\hP}\to \mathbb E_{\hrM/\hP}:=\R^\bullet\hat\pi_{\hrM,*}(\bigoplus_0^4 \mathcal L_{\hrM})$ gives the standard virtual class for the moduli space of maps follows from functoriality of virtual pullbacks \cite{Manolache-pullback}.
-\end{proof}
-
-Next consider the moduli space of $1$-stable maps with $p$-fields $\widehat{\pazocal P}$.
+ The final claim follows from functoriality of virtual pullbacks \cite{Manolache-pullback}.
+\end{proof}
+
 \begin{lem}
- There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal P_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}\oplus\mathcal P_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}))\] for the triangle:
- \bcd
- \widehat{\pazocal P}\ar[rr,"\hat\PtoM"]\ar[dr] & & \hrM\ar[dl] \\
+ There is a compatible triple of dual perfect obstruction theories \[(\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\widehat{\mathcal P}_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}}),\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}))\] for the triangle:
+ \bcd
+ \widehat{\pazocal P}\ar[rr,"\hat\rho"]\ar[dr] & & \hrM\ar[dl] \\
  & \hP &
@@
 \end{lem}
-\noindent This follows from the general theory of moduli of sections recalled above.
-
-\smallskip
-
-Notice that the virtual rank of $\mathbb E_{\widehat{\pazocal P}/\hP}:=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\mathcal L_{\widehat{\pazocal P}}^{\oplus 5}\oplus\mathcal P_{\widehat{\pazocal P}})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
+
+Notice that the virtual rank of $\mathbb E_{\widehat{\pazocal P}/\hP}:=\R^\bullet\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}})$ is $0$, hence it endows the moduli space of $1$-stable maps with $p$-fields with a cycle class of dimension $0$.
 However $\widehat{\pazocal P}$ is not proper.
-In the next section we describe Chang-Li's cosection (depending on the choice of $\w\in\k[x_0,\ldots,x_4]_5$) of the obstruction bundle, and show that the corresponding localised cycle is supported on the proper subtack $\Mone{1}{X}{d}$ where $X=V(\w)$ is the quintic threefold, that is the degeneracy locus of the cosection.
+In the next section we describe Chang-Li's cosection (depending on the choice of $\w\in\k[x_0,\ldots,x_4]_5$) of the obstruction bundle, and show that the corresponding localised cycle is supported on the proper subtack $\Mone{1}{X}{d},$ where $X=V(\w)$ is the quintic threefold, that is the degeneracy locus of the cosection.
 
@@
 In facts such a cycle is supported on a way smaller closed substack, namely $\Mone{1}{X}{d}$; this follows from the
-\subsection{Cosection localisation}
+\subsection{Cosection localisation and virtual pullback}\label{sec:cosection}
 Recall Kiem-Li's machinery of cosection localised virtual classes \cite[Theorem 1.1]{KLcosection}:
 
-\begin{teo*}[Localization by cosection]\label{thm:KLlocalisation}
-Let $\pazocal M$ be a Deligne-Mumford stack endowed with a perfect
-obstruction theory. Suppose the obstruction sheaf $\rm{Ob}_\pazocal M$ admits a
-surjective homomorphism $\sigma:\rm{Ob}_\pazocal M|_U  \to \OO_U$
-over an open $U\subseteq \pazocal M$.
-Let $\pazocal{M}(\sigma)=\pazocal{M}\setminus U$.
-Then $(\pazocal{M},\sigma)$ has a localized virtual cycle
-$$[\pazocal{M}]^{\rm{virt}}_{\rm{loc}}\in A_* \pazocal{M}(\sigma).$$
+\begin{teo*}[Localisation by cosection]\label{thm:KLlocalisation}
+Let $Y\to S$ be a morphism of DM type between algebraic stacks, with $Y$ Deligne-Mumford and $S$ smooth, endowed with a perfect
+obstruction theory. Suppose the obstruction sheaf $\rm{Ob}_Y$ admits a
+surjective homomorphism $\sigma:\rm{Ob}_{Y|_U } \to \OO_U$
+over an open $U\subseteq Y$.
+
+Let $\iota\colon Y(\sigma):=Y\setminus U\hookrightarrow Y$,
+then $(Y,\sigma)$ has a localised virtual cycle:
+$$[Y]^{\rm{vir}}_{\rm{loc}}\in A_* Y(\sigma).$$
 This cycle enjoys the usual properties of the virtual cycles; it relates to
-the usual virtual cycle $[\pazocal{M}]^{\rm{virt}}$ via 
-$[\pazocal{M}]^{\rm{virt}} = \iota_*[\pazocal{M}]^{\rm{virt}}_{\rm{loc}} \in A_*  \pazocal{M}$, where
-$\iota: \pazocal{M}(\sigma)\to \pazocal{M}$ is the inclusion.
+the usual virtual cycle $[Y]^{\rm{vir}}$ via 
+$[Y]^{\rm{vir}} = \iota_*[Y]^{\rm{vir}}_{\rm{loc}} \in A_*Y  .$
 \end{teo*}
+We now review a slight generalisation of this, that combines it with Manolache's virtual pullback construction \cite{Manolache-pullback}; this can also be found in \cite[\S~5]{CLpfields}.
+
+Let $Y\to S$ be as in the hypotheses of the theorem, or more generally such that there is a triple of compatible obstruction theories for a triangle $Y\to S\to T$ with $T$ smooth.
+Assume for simplicity that the obstruction theory $\mathbb E_{Y/S}$ is a vector bundle $E$  admitting a cosection:
+\[E\xrightarrow{\sigma}\OO_Y\]
+surjective on an open $U\subseteq Y$; denote by $Y(\sigma)$ the complement $Y\setminus U.$ Recall the following notation from \cite{KLcosection}:
+\[G=\operatorname{Ker}\left(E\rvert_U\to\OO_Y\rvert_U\right),\qquad E(\sigma)=E\rvert_{Y(\sigma)}\cup G.\]
+ Kiem and Li define a localised Gysin map:
+ \[s^!_{\sigma,\rm{loc}}\colon A_*(E(\sigma))\to A_*(Y(\sigma)),\]
+ which we explain in what follows.
+ Let $[B]\in Z_*(E(\sigma))$ be a cycle represented by a closed integral substack. If $B\subset  E\rvert_{Y(\sigma)}$ then
+  they use the standard Gysin morphism: \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma)).\]
+ Suppose instead that $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then we may choose a variety with a \emph{regularising morphism} $\widetilde{Y}\xrightarrow{\nu} Y$ such that:
+ \begin{itemize}\label{cond:deflocal}
+ \item $\nu$ is proper and $\nu(\widetilde{Y})\cap U\neq\emptyset$;
+ \item the pullback along $\nu$ of the cosection $\nu^*\sigma=:\tilde{\sigma}$ extends to a surjective morphism
+ \[\nu^*E\xrightarrow{\tilde{\sigma}}\OO_{\widetilde{Y}}(D)\to 0\]
+ for a Cartier divisor $D\subseteq \widetilde{Y}.$
+ \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb N.$
+ \end{itemize}
+ We denote by  $\nu(\sigma)\colon D\to Y(\sigma)$ the restriction of $\nu$ to the divisor, and by $\tilde{\nu}\colon\widetilde{G}\to E(\sigma)$ the restriction of the natural map $\nu^*E\to E.$
+ The localised Gysin pullback is then defined as:
+ \[s^!_{\sigma,\rm{loc}}[B]:=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
+ In \cite[\S~2]{KLcosection} they prove that: such $(\widetilde{Y},\nu,\widetilde B)$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent of the above choices; the construction preserves rational equivalences and thus defines the desired morphism on Chow groups.
+ \begin{remark}
+ If we consider $[Y]$ as a cycle in $E(\sigma)$, thought of as the zero section of $E$, notice that a natural choice for $\widetilde{Y}$ is $\operatorname{Bl}_{Y(\sigma)}Y.$
+ \end{remark}
+  Kiem and Li then proceed to extend the cosection-localised Gysin pullback to vector bundle stacks $h^1/h^0(\mathbb E)$ (this is relatively easy in the presence of a global resolution, which is the case in the situation at hand); they show that the intrinsic normal cone $\mathfrak C_{Y/S}$ is contained in the closed substack $h^1/h^0(\mathbb{E})(\sigma),$ at least when the cosection of the relative obstruction bundle lifts to a cosection of the absolute obstruction bundle \cite[Corollary~4.5]{KLcosection}.
+\begin{dfn}
+Consider a cartesian diagram of stacks:
+\bcd
+Y'\ar[r,"\varphi'"]\ar[d,"\rho'"]\ar[dr,phantom,"\Box"] & Y\ar[d,"\rho"]\\
+S'\ar[r,"\varphi"] & S
+\ecd
+with $\rho$ as above. Assume furthermore that we have a cosection 
+\[\rm{Ob}_{Y/S}\to \OO_Y\]
+that lifts to a cosection of the absolute obstruction sheaf $\rm{Ob}_Y$.
+Then we can define a localised virtual pullback operation: \[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}\colon A_*(S')\to A_{*-\operatorname{rk}(\mathbb E)}(Y'(\sigma'))\] 
+where $\mathbb E_{Y'/S'}=(\varphi')^*\mathbb E_{Y/S},\;\sigma'=(\varphi')^*(\sigma)$ and $Y'(\sigma')=Y(\sigma)\times_{Y} Y'$.
+\end{dfn}
+Replace $S'$ by a primitive cycle in it, i.e.
+assume that $S'$ is irreducible and reduced.
+Recall that pulling back $\mathbb E_{Y/S}$ along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory.
+Furthermore we can pullback the cosection:
+\[\rm{Ob}_{Y'/S'}\cong \varphi^* \rm{Ob}_{Y/S}\xrightarrow{\sigma'}\OO_{Y'}.\]
+ The degeneracy locus of $\sigma'$ is $Y'(\sigma'),$ which in turn implies that:
+\[h^1/h^0(\mathbb E_{Y'/S'})(\sigma')=(\varphi')^*h^1/h^0(\mathbb E_{Y/S})(\sigma).\]
+%Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
+%\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
+By \cite[Corollary 4.5]{KLcosection} and from the cartesian diagram above,
+\[\mathfrak{C}_{Y'/S'}\subseteq (\varphi')^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
+thus we can define the localised virtual pullback of $[S']$ to be:
+\[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}[S']=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}].\]
+%compare also with \cite[Theorem~5.2]{KLcosection}
+
+\subsection{A cosection for $p$-fields}
 
 We are going to construct the cosection paralleling \cite[\S\S3.2-3.4]{CLpfields}. There is a morphism of vector bundles on $\hP$ induced by iterated tensoring of line bundles:
-\[ h_1\colon\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus\widehat{\mathcal P}_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(z,p)=p\w(z_0,\ldots,z_4)\]
+\[ h_1\colon\rm{Vb}(\hL_{\hP}^{\oplus 5}\oplus\widehat{\mathcal P}_{\hP})\to \rm{Vb}(\omega_{\hat\pi_{\hP}}),\quad h_1(x,p)=p\w(x_0,\ldots,x_4)\]
 By differentiating it and pulling it back along the universal evaluation
@@
  \sigma_1\colon\rm{Ob}_{\widehat{\pazocal P}/\hP}=\R^1\hat\pi_{\widehat{\pazocal P},*}(\hL_{\widehat{\pazocal P}}^{\oplus 5}\oplus\widehat{\mathcal P}_{\widehat{\pazocal P}})\to \R^1\hat\pi_{\widehat{\pazocal P},*}(\omega_{\hat\pi_{\widehat{\pazocal P}}})\simeq \OO_{\widehat{\pazocal P}} \\
- \sigma_{1|(u,\psi)}(x,p)=p\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)x_i
+ \sigma_{1|(u,\psi)}(\mathring{x},\mathring{p})=\mathring{p}\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)\mathring{x}_i
 \end{split}
@@
 The degeneracy locus of this cosection is $\Mone{1}{X}{d}$: by Serre duality if $\w(u)\neq 0$ then we can find a $p$ such that the cosection does not vanish; similarly we can do if $\psi\sum_{i=0}^4\partial_i\w(u)\neq 0$.
-But $\w(u)=0$ and $\partial_i\w(u)=0$ never happen simultaneously by smoothness of $X$, so it has to be $\psi=0$.
-
-Moreover Chang and Li prove that $\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\widehat{\pazocal P}}\to\OO_{\widehat{\pazocal P}}$ with the same degeneracy locus.
-This is a technical expedient to show that the relative intrinsic normal cone is contained in the closed substack of the obstruction bundle determined by the cosection.
+But $\w(u)=0$ and $\partial_i\w(u)=0$ never happen simultaneously by smoothness of $X$, so it has to be $\w(u)=\psi=0$.
+
+Moreover Chang and Li prove that $\sigma_1$ lifts to a cosection of the absolute obstruction bundle $\rm{Ob}_{\widehat{\pazocal P}}\to\OO_{\widehat{\pazocal P}};$ it has the same degeneracy locus because $\rm{Ob}_{\widehat{\pazocal P}/\hP}\to \rm{Ob}_{\widehat{\pazocal P}}$ is surjective.
+This is a sufficient condition for the relative intrinsic normal cone to be contained in the closed substack of the obstruction bundle determined by the cosection, see \S~\ref{sec:cosecvirpull}.
 
@@
 We want to show that it gives the same numerical invariants as the cuspidal Gromov-Witten theory of $X$, up to a sign:
-\begin{thm}
+\begin{thm}\label{thm:p-fields-quintic}
  \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}\]%=:GW_1^{\rm{cusp}}(X,d)\]
@@
 
-\subsection{Sketch of the proof}
+\subsection{From $p$-fields to the quintic threefold}
 This is achieved in two steps: we first compare the invariants of $\Mone{1}{\PP^4}{d}^p$ with the ones coming from $\Mone{1}{N_{X/\PP^4}}{d}^p$, where $N_{X/\PP^4}$ is the normal bundle of the quintic in $\PP^4.$
@@
 
-\subsubsection*{Step~1}
+\subsubsection*{Deformation to the normal cone}
 This is attained in \cite[\S\S4-5]{CLpfields} by a family version of the $p$-fields construction applied to the deformation to the normal cone of $X\subseteq \PP^4$; let us denote the latter by $V\to\Aaff^1_t$, so that $V_{t\neq 0}=\PP^4$ and $V_0=N_{X/\PP^4}.$
@@
 If $C(V)$ denotes the affine cone over $V$, then its tangent bundle is determined by the following exact sequences:
- \begin{equation*}
-  \begin{split}
-   0\to T_{C(V)/\Aaff^1_t}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}}\OO_{C(V)}\to 0 \\
-   0\to T_{C(V)}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}-y\mathring{t}}\OO_{C(V)}\to 0
-  \end{split}
- \end{equation*}
+ \begin{align}
+  0\to T_{C(V)/\Aaff^1_t}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}}\OO_{C(V)}\to 0 \label{eq:reltangentcone}\\
+    0\to T_{C(V)}\to\OO^{\oplus 5}_{C(V)}\oplus\OO_{C(V)}\oplus\OO_{C(V)}\xrightarrow{\sum_i\partial_i\w(x)\mathring{x_i}-t\mathring{y}-y\mathring{t}}\OO_{C(V)}\to 0\label{eq:tangentcone}
+  \end{align}
 \end{lem}
@@
  \[\phi_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}\colon\mathbb T_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}\to\mathbb E_{\widehat{\pazocal V}/\hP\times\Aaff^1_t}:=\R^\bullet\hat\pi_{\widehat{\pazocal V}}(f_{\widehat{\pazocal V}}^*\mathcal H\oplus\widehat{\mathcal P}_{\widehat{\pazocal V}})\]
- where $f_{\widehat{\pazocal V}}\colon \hC_{\widehat{\pazocal V}}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by the exact sequence:
+ where $f_{\widehat{\pazocal V}}\colon \hC_{\widehat{\pazocal V}}\to V$ is the universal map and $\mathcal H$ is the vector bundle on $V$ defined by the exact sequence, see \eqref{eq:reltangentcone}:
  \[0\to\mathcal H\to\pr_{\PP^4}^*\left(\OO_{\PP^4}(1)^{\oplus 5}\oplus \OO_{\PP^4}(5)\right)\xrightarrow{\sum_i\partial_i\w(x)\mathring{x}_i-t\mathring{y}} \pr_{\PP^4}^*\OO_{\PP^4}(5)\to 0.\]
@@
  \[
- \widehat{\pazocal V}_c=\left\{\begin{array}{lr} \widehat{\pazocal P} & c\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & c=0 \end{array}\right.
-\]
-gives the standard obstruction theory of $\widehat{\pazocal V}_c\to\hP$.
+ \widehat{\pazocal V}_t=\left\{\begin{array}{lr} \widehat{\pazocal P} & t\neq 0 \\ \Mone{1}{N_{X/\PP^4}}{d}^p & t=0 \end{array}\right.
+\]
+gives the standard obstruction theory of $\widehat{\pazocal V}_t\to\hP$.
 \end{lem}
@@
 \]
-where $\mathcal K$ is determined by the following exact sequence on $V$:
+where $\mathcal K$ is determined by the following exact sequence on $V$, see \eqref{eq:tangentcone}:
 \[
@@
 \[ \R^1\hat\pi_{\widehat{\pazocal V},*}\OO_{\hC_{\widehat{\pazocal V}}}[-2]\to\mathbb E_{\widehat{\pazocal V}/\hP}\xrightarrow{\nu}\mathbb E'_{\widehat{\pazocal V}/\hP}\xrightarrow{[1]}\]
-Furthermore the lifted obstruction theory is compatible with the standard one for the fibers.
+Furthermore $\phi_{\widehat{\pazocal V}/\hP}$ is compatible with the standard obstruction theory for the fibers:
 \begin{lem}
-For every $c\in\k$ we have a commutative diagram:\marginpar{the lower one is not exact}
+For every $t\in\mathbb A^1_\k$ we have a commutative diagram:
 \bcd
 \hat{\pi}_{\widehat{\pazocal V}_c *}\OO_{\hC_{\widehat{\pazocal V}_c}}[-1]\ar[r] & \mathbb E_{\widehat{\pazocal V}_c/\hP} \ar[r] &\mathbb E_{\widehat{\pazocal V}/\hP}\rvert_{\widehat{\pazocal V}_c}\\
-\mathbb{T}^{\geq 1}_{\widehat{\pazocal V}_c/\widehat{\pazocal V}}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\widehat{\pazocal V}_c/\hP}\ar[u]\ar[r] & \mathbb{T}^{\geq 1}_{\widehat{\pazocal V}/\hP}\rvert_{\widehat{\pazocal V}_c} \ar[u]
+\mathbb{T}^{\leq 1}_{\widehat{\pazocal V}_c/\widehat{\pazocal V}}\ar[u]\ar[r] & \mathbb{T}^{\leq 1}_{\widehat{\pazocal V}_c/\hP}\ar[u]\ar[r] & \mathbb{T}^{\leq 1}_{\widehat{\pazocal V}/\hP}\rvert_{\widehat{\pazocal V}_c} \ar[u]
 \ecd
@@
 For the proof see \cite[\S~4.6]{CL}.
-
-%Since we are working with cosection localised cycles, this is not yet enough to conclude.
- A family version of the cosection is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
+Notice that the lower row is not a distinguished triangle, yet Chang and Li prove in \cite[A.4]{CLpfields} that this weaker (truncated) notion of compatibility is enough to prove functoriality.
+
+Since we are working with cosection localised cycles, we need a family version of the cosection. This is induced by differentiating the following vector bundle morphism on $\hP\times\Aaff^1_t$:
 \[
@@
 The cosection takes then the following form:
-\[\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}\]
+\begin{align*}
+\rm{Ob}_{\widehat{\pazocal V}/\hP\times\mathbb A^1}\subseteq \R^1\hat{\pi}_*(\hL_{\widehat{\pazocal V}}^{\oplus 5}\oplus\hL_{\widehat{\pazocal V}}^{\otimes}\oplus\widehat{\mathcal{P}}_{\widehat{\pazocal V}})\to \R^1\hat{\pi}_*\omega_{\hat{\pi}}\\
+\bar\sigma_{1|(u,v,\psi)}(\mathring{x},\mathring{y},\mathring{p})=\psi\mathring{y}+v\mathring{p}
+\end{align*}
 It is showed in \cite[\S4.7]{CLpfields} that $\bar\sigma_1$ lifts to a cosection $\bar\sigma\colon \rm{Ob}_{\widehat{\pazocal V}}\to \OO_{\widehat{\pazocal V}}$ and that the degeneracy locus of $\bar\sigma$ is
@@
 
-Recall that the sections $(x,y)$ are required to satisfy $\w(x)-ty=0$.
+Recall that the sections $(u,v)$ are required to satisfy $\w(u)-tv=0$.
 So $\bar\sigma_1$ coincides up to a non-zero scalar with the above defined cosection $\sigma_1$ for $\widehat{\pazocal P}$ when $t\neq 0$.
@@
 where we have denoted by $\widehat{\pazocal Q}:=\Mone{1}{X}{d}$.
-\subsubsection*{Step~2}
-We are left with proving that $\deg[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to sign with $\deg[\Mone{1}{X}{d}]^{\rm{vir}}$.
+\subsubsection*{Functoriality of cosection-localised pullback}
+We are left with proving that $\deg[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}$ coincides up to a sign with $\deg[\Mone{1}{X}{d}]^{\rm{vir}}$.
 In the rest of the section we use the following notation: $\widehat{\pazocal N}:=\Mone{1}{N_{X/\PP^4}}{d}^p$, and $\hat v\colon\widehat{\pazocal N}\to\widehat{\pazocal Q}$. 
-We now find a perfect obstruction theory for $\hat v\colon\widehat{\pazocal N}\to\widehat{\pazocal Q}$ compatible with the ones of $\widehat{\pazocal N}\to\hP$ and $\widehat{\pazocal Q}\to\hP$, and then use a cosection-localised version of Manolache's virtual pullback construction~\cite{Manolache-pullback}.
-
-Indeed Chang and Li proved that there is a perfect obstruction theory 
+%We now find a perfect obstruction theory for $\hat v\colon\widehat{\pazocal N}\to\widehat{\pazocal Q}$ compatible with the ones of $\widehat{\pazocal N}\to\hP$ and $\widehat{\pazocal Q}\to\hP$, and then use a cosection-localised version of Manolache's virtual pullback construction~\cite{Manolache-pullback}.
+
+First, Chang and Li prove that there is a perfect obstruction theory 
 \[\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}}:=\R^{\bullet}\hat\pi_{\widehat{\pazocal N},*}(\hL^{\otimes 5}_{\widehat{\pazocal N}}\oplus \widehat{\mathcal P}_{\widehat{\pazocal N}})\]
  compatible with $\mathbb E_{\widehat{\pazocal N}/\hP}$ and $\hat v^*\mathbb E_{\widehat{\pazocal Q}/\hP}$, so that $\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}}$ inherits a cosection $\sigma_0'$ with degeneracy locus $D(\sigma_0')=\widehat{\pazocal Q}$.
-Then in \cite[Lemma 5.5]{CLpfields} they show by using the techniques of \cite{KKP} that $\mathfrak C_{\widehat{\pazocal N}/\widehat{\pazocal Q}}$ is supported inside
-\[
- h^1/h^0(\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}})_{\sigma_0'}:=\operatorname{Ker}(\sigma_0')\cup  h^1/h^0(\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}})\rvert_{D(\sigma_0')}
-\]
-so that they may combine the techniques of virtual pullback \cite{Manolache-pullback} and localisation by cosection \cite{KLcosection} to define:
+So they have a localised virtual pullback:
 \[
@@
 \]
-sending $[\widehat{\pazocal Q}]^{\rm{vir}}$ to $[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\bar\sigma_0}}.$
-
-To conclude it is now enough to compute the degree of $\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}.$
-Since we are only interested in what happens to $A_0(\widehat{\pazocal Q})$, we just need to compute $\deg(\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}[\zeta])$ for a closed point $\zeta$.
+which they then prove to satisfy functoriality using the techniques of \cite{KKP}, so:
+\[\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}[\widehat{\pazocal Q}]^{\rm{vir}}=[\Mone{1}{N_{X/\PP^4}}{d}^p]^{\rm{vir}}_{\rm{\sigma'_0}}.\]
+To conclude it is  enough to compute the degree of $\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}$
+on $A_0(\widehat{\pazocal Q})$; we just need to compute $\deg(\hat v^!_{\mathbb E_{\widehat{\pazocal N}/\widehat{\pazocal Q}},\rm{loc}}[\zeta])$ for a closed point $\zeta$.
 This is done in \cite[Theorem 5.7]{CLpfields} and the same considerations work in our case.
@@
 
-\section{The comparison morphism}
-%In this section we start investigating the Gromov- Witten type invariant obtained from Viscardi compactification studying the case $m=1$: the source curve is at worst cuspidal.
-We will see how in this case we can give a comparison with the GW-invariant and explain why the same technique does not work for higher $m$.
-%The first thing we do is the following:
-%we introduce a moduli space of stably-weighted, prestable, at worst cuspidal, marked curves.
-We show that there is a birational morphism from a correspondingly decorated moduli space of prestable nodal curves.
-Taking the fiber product with Viscardi's moduli space of stable cuspidal maps, we show that the resulting space includes in the usual Kontsevich's moduli space, precisely avoiding the component with elliptic tails $D_{\{d\},\{n\}}(X,d)$.
-
-%Why should such a morphism on decorated prestable curves exist? 
-%Consider an elliptic tail $C$; a one-dimensional family $\mathcal C$  with central fiber $\mathcal C_0\cong C$ will either be locally constant or smoothen the node.
-In the first case we can associate to this the locally constant family of cusps obtained by forgetting the elliptic tail and contracting a length-two infinitesimal neighborhood of the node in the rational component; in the second case, we claim that the line bundle $\mathcal O_\mathcal C(3q)$ gives a morphism to a smoothing of the cuspidal $\PP^1$.
-This heuristics (i.e.
-being able to substitute an elliptic tail with a cusp over points or DVR schemes) motivates us to believe we can define a morphism from suitably defined moduli spaces of nodal genus one curves to cuspidal curves (cfr.
-\cite[Lemma 4.2]{SMY2}).
-In fact we shall extend \cite[Corollary 4.5]{SMY2} to an appropriate setup of moduli stacks of weighted prestable curves.
-Assume $d>0$ throughout the following.
-In this section we shall:
-\begin{itemize}
- \item argue in two different ways that there is a natural fashion to associate a weighted $1$-stable (i.e.
-at worst cuspidal) curve to a weighted-stable (nodal) curve of genus $1$, replacing elliptic tails of weight $0$ by cusps, which results in a morphism:
- \[\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)\]
-extending the identity on the locus of smooth elliptic curves;
- \item introduce the fiber product:
- \[\Z:= \mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)\]
- and show that it is a closed substack of $\oM_1(\PP^4,d)$, isomorphic to it outside the boundary divisor with a contracted elliptic tail;
- \item introduce the fiber product:
- \[\Zp:=\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\times_{\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1)} \oM^{(1)}_{1,n}(\PP^4,d)^p \]
- and endow it with an obstruction theory and a cosection thereof, which are pulled back from $\oM^{(1)}_{1,n}(\PP^4,d)^p$.
-Unfortunately we will not be able to compare them directly with $\oM_1(\PP^4,d)^p$; nonetheless in the next sections we will manage to approach the localised virtual class of $\Zp$ directly by adapting Chang and Li's techniques \cite{CL}.
-\end{itemize}
-%in two different ways that there exists a morphism at the level of weighted prestable curves $\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}\to\mathfrak M_{1,n}^{\operatorname{wt},\text{st}}(1);$ introduce the spaces
-%\[\Z:= \mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M_{1,n}(\PP^4,d)(1),\qquad \Zp:=\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}\times{\mathfrak M_{1,n}^{\operatorname{wt}=d,\text{st}}(1)} \pazocal M^p_{1,n}(\PP^4,d)(1) \]
-%and  and see their relation, respectively, with the moduli space of stable maps, stable maps with fields; use the morphism at the level of prestable curves to induce obstruction theories on $\Z$ and $\Zp.$
-
-%Note that the only type of nodal curves that we are getting rid of are the ones with an elliptic tail of weight zero.
+\section{The weighted $1$-stabilisation morphism}\label{sec:comparison}
+
+The main result of this section is the following.
 
@@
 Abusing notation we will still write $\cC$ and $\hC$ for their pullbacks to the product $\MM\times\hM$ along the two projections.
-The proof of the theorem follows from two Lemmas:
 
 \begin{lem}\label{lemma:def_X}
- There is a locally closed substack $\X\subseteq\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ representing morphisms $C\to \widehat{C}$ that contract elliptic tails of weight $0$ to cusps and are weight-preserving isomorphisms everywhere else.
-\end{lem}
-
-\begin{lem}\label{lamma:projection_iso}
- The first projection $\pr_1\colon \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)\to\MM$ restricted to $\X$ is an isomorphism with $\MM$.
-\end{lem}
-
-\begin{proof}\ref{lemma:def_X}
+ There is a locally closed substack $\X\subseteq\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ representing morphisms that contract genus $1$ tails of weight $0$ to cusps, and are weight-preserving isomorphisms everywhere else.
+\end{lem}
+
+\begin{proof}
 Recall that $\operatorname{Mor}_{\MM\times\hM}(\cC,\hC)$ is an algebraic stack; in fact the map to $\MM\times\hM$ is representable by algebraic spaces \cite{OlssonHOM}.
@@
   for the Picard stacks of $\pi$ and $\hat \pi$ respectively, with universal line bundles $\L$ and $\hL$.
-The projections $\PtoM$ and $\hat \PtoM$ are defined by taking the multi-degree of a line bundle.
 We can now look at the algebraic stack $\operatorname{Mor}_{\mathfrak{P}\times\hP}(\cC,\hC)$ with universal morphism
@@
 $E$ is either an elliptic tail or an elliptic bridge.
-There are basically two possibilities:
+There are two possibilities left:
 \begin{enumerate}
@@
 
- \begin{proof}\ref{lamma:projection_iso}
+\begin{lem}\label{lamma:projection_iso}
+ The first projection $\pr_1\colon \operatorname{Mor}_{\MM\times\hM}(\cC,\hC)\to\MM$ restricted to $\X$ is an isomorphism with $\MM$.
+\end{lem}
+
+ \begin{proof}
  This result will follow from an application of Zariski's Main Theorem for algebraic spaces.
@@
 \bcd C\ar[r,"\phi"]\ar[d,"\psi"] & \widehat{C}\ar[d,"\hat\psi"] \\ C\ar[r,"\phi"] & \widehat{C} \ecd
- Now $\hat\psi$ is determined by $\psi$ due to how $\phi$ behaves (contracting elliptic tails and being an isomorphism everywhere else).
+ Now $\hat\psi$ is determined by $\psi:$ for any $p\in\widehat{C}$, either $\phi$ is an isomorphism in a neighbourhood of its preimage and thus around that point $\hat{\psi}=\phi\circ\psi\circ\phi^{-1},$ or $\phi^{-1}(p)$ is a genus 1 tail, so $\psi$ must preserve it.
 
@@
 \ecd
- Then $\cC_\dvr$ is the pushout of a family of rational curves $\mathcal R_\dvr$ and a family of genus one curves $\mathcal Z_\dvr$:
+ Then $\cC_\dvr$ is the pushout of a family of rational curves $\mathcal R_\dvr$ and a family of genus 1 curves $\mathcal E_\dvr$:
 %The map $S\to\partial \mathfrak M_{1,n}$ lifts to the normalisation of the boundary, i.e.
@@
 \dvr\ar[d]\ar[r] & \mathcal R_\dvr \ar[d] \\
-\mathcal Z_\dvr\ar[r] & \cC_\dvr
+\mathcal E_\dvr\ar[r] & \cC_\dvr
 \end{tikzcd}
 \end{equation}
-Recall that the cuspidal curve $\hC_K$ can be characterised as the pushout of the following diagram:
+Recall that the cuspidal curve $\hC_K$ can be described as the pushout of the following diagram:
 \bcd
@@
 \ecd
-The morphism $\phi_\dvr\colon\cC_\dvr\to\hC_\dvr$ extending $\phi_\eta$ is then defined by exploiting the description of $\cC_\dvr$ as a pushout \eqref{eq:pushout}, and the morphisms $\id\colon\mathcal R_\dvr\to \mathcal R_\dvr$ and $\pr_{\mathcal Z_\dvr}\colon\mathcal Z_\dvr\to \dvr$ to the upper right and bottom left corners of the last diagram respectively.
+The morphism $\phi_\dvr\colon\cC_\dvr\to\hC_\dvr$ extending $\phi_\eta$ is then defined by exploiting the description of $\cC_\dvr$ as a pushout \eqref{eq:pushout}, and the morphisms $\id\colon\mathcal R_\dvr\to \mathcal R_\dvr$ and $\pr_{\mathcal E_\dvr}\colon\mathcal E_\dvr\to \dvr$ to the upper right and bottom left corners of the last diagram respectively.
 \item If $\cC_\dvr$ does smooth the elliptic tail, then $\phi_\eta$ is an isomorphism.
@@
 Then we may pick a smooth section for each rational component of $\cC_0$ and extend them to sections of $\cC_\dvr\to \dvr$ by Grothendieck's existence theorem; let us denote by $\Sigma$ the Cartier divisor that is the sum of all such sections.
-Let $Z$ be the elliptic tail in the central fiber; then we claim that $\omega_{\cC_\dvr/\dvr}(Z)\otimes\mathcal O_{\cC_\dvr}(3\Sigma)$ is $\pi_\dvr$ semi-ample, ample on the generic fiber, and gives the contraction of the elliptic tail to the cusp in the central fiber.
+Let $Z$ be the elliptic tail in the central fiber; then we claim that $\omega_{\cC_\dvr/\dvr}(Z)\otimes\mathcal O_{\cC_\dvr}(2\Sigma)$ is $\pi_\dvr$ semi-ample, ample on the generic fiber, and gives the contraction of the elliptic tail to the cusp in the central fiber.
 We shall not prove the claim here, since this is the core of the second approach.
@@
 
-We shall construct the contraction over $\MM_1^{\rm{div}}$ first, and then show that it descends to $\MM_1^{\rm{wt}}$.
-
-Let $\pazocal E$ be the locus inside the universal curve spanned by elliptic tails of weight $0$; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$, which we shall freely pullback and keep denoting by $\pazocal E$.
-We shall also denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$ (and its various pullbacks), which is a Cartier divisor as well.
+We shall construct the contraction over $\MM_1^{\rm{div}}$ first, and then show that it descends to $\MM_1^{\rm{wt}}$. The weighted stability condition is implicit in the notation.
+
+Let $\pazocal E$ be the locus inside the universal curve spanned by elliptic tails of weight $0$; this is a Cartier divisor in the universal curve over $\MM^{\rm{wt}}_1$; we will abuse notation and denote by $\pazocal E$ all its pullbacks.
+Moreover we denote by $\mathfrak D^1$ its image in $\MM^{\rm{wt}}_1$, which is a Cartier divisor as well.
 
@@
 \begin{equation}\label{eq:linebundlecontraction}
-\mathcal N:=\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D),
+\mathcal N:=\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(2\pazocal D),
 \end{equation} where $\pazocal D$ is the universal Cartier divisor over $\MM_1^{\rm{div}}$.
@@
 \begin{prop}\label{1-stabilization-div}
-In the following diagram $\hC$ is a family of weighted $1$-stable curves and $\phi$ is a regular morphism:
-
- \bcd
- (\cC,\pazocal D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hC=\underline{\operatorname{Proj}}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n}),\phi(\pazocal D))\ar[ld,"\hat\pi"] \\
+Let $\hC=\underline{\operatorname{Proj}}_{\MM_1^{\rm{div}}}(\bigoplus_{n\geq 0}\pi_*\mathcal N^{\otimes n})$. Then $\hC$ is a family of weighted $1$-stable curves and $\phi$ is a regular morphism:
+
+ \bcd
+ (\cC,\pazocal D)\ar[rr,"\phi"]\ar[dr,"\pi"] & & (\hC,\phi(\pazocal D))\ar[ld,"\hat\pi" above left] \\
  & \MM_1^{\rm{div}} &
@@
 We need to prove that $\mathcal N$ is $\pi$-semi-ample (regularity of $\phi$) and that $\pi_*\mathcal N$ is locally free (flatness of $\hat\pi$).
-Both these facts are clear generically, but less so on points of $\pazocal E$ and $\mathfrak D^1$.
-We shall check this by exploiting the next lemma, which is a nice technical gadget taken from \cite{RSPW}: the $\Proj$ construction we are interested in commutes with base-change to generically chosen curves inside $\MM_1^{\rm{div}}$, allowing us to work with a smoothing of the elliptic tail over a DVR scheme $\dvr$.
-
+Both these facts are clearly true generically, but less so on points of $\pazocal E$ and $\mathfrak D^1$.
+We shall check this by exploiting the next lemma, which is a nice technical gadget taken from \cite{RSPW}.
 \begin{lem}[pullback with a boundary]\label{DVR}
 Let $\pi\colon\cC\to S$ be a proper family of curves over a smooth basis, and let $\mathcal N$ be a line bundle on $\cC$ such that $\R^1\pi_*\mathcal N$ is a line bundle supported on a Cartier divisor $\mathfrak D\subseteq S$.
-Then for every spectrum of a DVR $\dvr$ with closed point $0$ and generic point $\eta$, and for every morphism $f\colon \dvr\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
+Then for every DVR scheme $\dvr$ with closed point $0$ and generic point $\eta$, and for every morphism $f\colon \dvr\to S$ such that $f(0)\in\mathfrak D$ and $f(\eta)\in S\setminus\mathfrak D$ we have
 \[f^*\pi_*\mathcal N\cong \pi_{\dvr,*}f_\cC^*\mathcal N.\]
@@
 \[\pi^*\pi_*\mathcal N^{\otimes n}\to \mathcal N^{\otimes n}\]
-is surjective for $n\gg 0$ (in fact $n=1$ suffices).
+is surjective for $n\gg 0$.
 \end{lem}
@@
 On $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1$ we see that $\R^1\pi_*\mathcal N=0$, so $\pi_*\mathcal N$ satisfies Cohomology and Base Change and its rank is determined by Riemann-Roch.
-Given a point $x$ on the boundary $\mathfrak{D}^1$, we can pick a DVR scheme $\dvr$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank at $x$ by looking at $\pi_*f^*\mathcal N$ over $\dvr.$ Now $f^*\mathcal N$ is flat over $\dvr$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free (constant rank).
+Given a point $x$ on the boundary $\mathfrak{D}^1$, we can pick a DVR scheme $\dvr$ whose closed point maps to $x$ and whose generic point maps to $\MM_1^{\rm{div}}\setminus \mathfrak{D}^1.$ Then we are in the hypotheses of Lemma~\ref{DVR} and we can check the rank at $x$ by looking at $\pi_*f^*\mathcal N$ over $\dvr.$ Now $f^*\mathcal N$ is flat over $\dvr$, so $\pi_*f^*\mathcal N$ is as well, which implies torsion-free and thus constant rank.
 \end{proof}
@@
  \bcd
- (\cC_S,\pazocal D_S)\ar[rr,"\phi_S"]\ar[dr,"\pi_S"] & & (\hC_S=\underline{\operatorname{Proj}}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n}),\phi(\pazocal D_S))\ar[ld,"\hat\pi_S"] \\
+ (\cC_S,\pazocal D_S)\ar[rr,"\phi_S"]\ar[dr,"\pi_S"] & & (\hC_S,\phi(\pazocal D_S))\ar[ld,"\hat\pi_S" above left] \\
  & S &
  \ecd
-where $\phi_S$ is a proper and birational morphism since $\mathcal N$ is $\pi_S$-semi-ample and $\hat{\pi}_S$ is flat since $\pi_{S,*}\mathcal N$ is locally free. 
-To verify that this defines a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hat{\cC}_S$ has reduced fibers and only nodes and cusps as singularities.
+where $\hC_S=\underline{\operatorname{Proj}}_{S}(\bigoplus_{n\geq 0}\pi_{S,*}\mathcal N^{\otimes n})$, $\phi_S$ is a proper and birational morphism since $\mathcal N$ is $\pi_S$-semi-ample and $\hat{\pi}_S$ is flat since $\pi_{S,*}\mathcal N$ is locally free.
+To verify that this defines a morphism $S\to \MM_1^{\rm{div}}(1)$ we have to argue that $\hC_S$ has reduced fibers and only nodes and cusps as singularities.
 
@@
 
-Finally to conclude that this defines a morphism 
-\[\MM_1^{\rm{div}}\to \MM_1^{\rm{div}}(1)\]
-it is enough to verify that there is an isomorphism
- $\rm{pr}_1^*\hat \cC_S\cong\rm{pr}_2^*\hat \cC_S$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
-
- This follows from the fact that $\pr_i^*\hat \cC_S$ are obtained from applying the Proj construction to 
- $\rm{pr}_i^*\pi_{S,*}\mathcal{N}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal N$, by flatness of $S'\to S$. Thus it is enough to show that 
- \[\rm{pr}_1^*\mathcal N\cong \rm{pr}_2^*\mathcal N.\]
+Finally to conclude that this defines a morphism $\MM_1^{\rm{div}}\to \MM_1^{\rm{div}}(1)$ it is enough to verify that there is an isomorphism
+ $\rm{pr}_1^*\hC_S\cong\rm{pr}_2^*\hC_S$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{div}}} S\rightrightarrows S$.%and that $\rm{pr}_{ij}\colon S\times_{\MM_1^{\rm{div}}} S\times_{\MM_1^{\rm{div}}} S\to  S\times_{\MM_1^{\rm{div}}} S $ satisfy the cocycle condition.
+
+ This follows from the fact that $\pr_i^*\hC_S$ are obtained from applying the Proj construction to 
+ $\rm{pr}_i^*\pi_{S,*}\mathcal{N}\cong\pi_ {S',*} \rm{pr}_i^*\mathcal N$, by flatness of $S'\to S$. Thus it is enough to show that $\rm{pr}_1^*\mathcal N\cong \rm{pr}_2^*\mathcal N$.
   But $\mathcal N$ is the pullback of a line bundle on $\MM_1^{\rm{div}}$, thus the desired isomorphism follows from the commutativity of the diagram
@@
 \begin{prop}
-The $1$-stabilisation just defined for curves with a divisor induces an analogue morphism on weighted curves:
+The $1$-stabilisation for curves with a divisor induces an analogue morphism on weighted curves:
 \bcd
@@
 \begin{proof}
-{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose smooth sections $s_i$ of the universal curve in a way that their sum as a relative Cartier divisor $\pazocal D$ has degree compatible with the weight function, so in particular it makes $\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
-If $S\to \MM_1^{\rm{wt}}$ is a smooth atlas, this observation allows us to define a lifting $S\to \MM_1^{\rm{div}}$, and thus a morphism $\xi\colon S\to  \MM_1^{\rm{wt}}(1)$ through the construction of Proposition \ref{1-stabilization-div}.
-
-In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{\rm{wt}}(1)$ we need to verify that  $\rm{pr}_1^*(\xi)\cong\rm{pr}_2^*(\xi)$ and the cocycle condition is satisfied, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
+{\'E}tale locally on $\MM_1^{\rm{wt}}$ we can choose smooth sections $s_i$ of the universal curve so that the Cartier divisor $\pazocal D=\sum s_i$ has degree compatible with the weight function, so in particular it makes $\mathcal N=\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(2\pazocal D)$ trivial on the elliptic tails and $\pi$-ample elsewhere.
+For a smooth atlas $S\to \MM_1^{\rm{wt}}$, this observation allows us to define a lifting $S\to \MM_1^{\rm{div}}$, and thus a morphism $\xi\colon S\to  \MM_1^{\rm{wt}}(1)$ through the construction of Proposition \ref{1-stabilization-div}.
+
+In order to show that this descends to a morphism $\MM_1^{\rm{wt}}\rightarrow \MM_1^{\rm{wt}}(1)$ we need to verify that there exists $\rm{pr}_1^*(\xi)\cong\rm{pr}_2^*(\xi)$ satisfying the cocycle condition, where $\rm{pr}_i\colon S'= S\times_{\MM_1^{\rm{wt}}} S\rightrightarrows S$.
 
 This boils down to checking that for two different choices of a lifting $\pazocal D_1,\pazocal D_2\colon S\to\MM_1^{\rm{div}}$ there exists a unique isomorphism 
-\[\hC_1=\underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D_1))^{\otimes n}\right)\cong \underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\omega_{\pi}(\pazocal E)\otimes\mathcal O_{\cC}(3\pazocal D_2))^{\otimes n}\right)=\hC_2.
+\[\hC_1=\underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\mathcal N_1))^{\otimes n}\right)\cong \underline{\operatorname{Proj}}_S\left(\bigoplus_{n\geq 0}\pi_*(\mathcal N_2))^{\otimes n}\right)=\hC_2.
 \]
@@
 \end{proof} 
-
-\subsection{Fiber products and induced obstruction theories}
+\begin{remark}
+The $m$-stabilisation for $m\ge 2$ does not extend to a regular morphism; the following is an example with stable curves:
+\begin{figure}[h]
+\centering
+\begin{tikzpicture}
+\draw (-.1,0) circle (.4cm);
+\draw (.5,.55) circle (.4cm);
+\draw[fill=black] (.3,.55) circle[radius=1.5pt];
+\draw[fill=black] (.7,.55) circle[radius=1.5pt];
+%\node [above right] at (.8,.7) {$d_1$};
+\draw (.5,-.55) circle (.4cm);
+\draw[fill=black] (.3,-.55) circle[radius=1.5pt];
+\draw[fill=black] (.7,-.55) circle[radius=1.5pt];
+%\node [above right] at (.8,-.45) {$d_2$};
+\draw (-.8,-.9) ellipse (.5cm and 1cm);
+\draw (-.85,-.2) .. controls (-.65,-.4) and (-.65,-1.4) .. (-.85,-1.6);
+\draw (-.75,-.4) .. controls (-1,-.4) and (-1,-1.4) .. (-.75,-1.4);
+\draw (-.05,-1.7) circle (.4cm);
+\draw[fill=black] (.15,-1.7) circle[radius=1.5pt];
+\draw[fill=black] (-.25,-1.7) circle[radius=1.5pt];
+%\node [above right] at (.25,-1.8) {$d_3$};
+
+\draw[->] (2.6,-.7) -- (3.8,-.3);
+\draw[->] (2.6,-1.2) -- (3.8,-1.6);
+
+\draw[gray] (5,-.3)-- (7.3,-.3);
+\draw[fill=black] (7,-.3) circle[radius=1.5pt];
+\draw[fill=black] (6.6,-.3) circle[radius=1.5pt];
+%\node [right] at (7,-.2) {$d_3$};
+\draw (5,1) .. controls (6,-.7) and (6.1,-.7) .. (7,1);
+\draw[gray] (6.5,.7)-- (8.5,.7);
+\draw[fill=black] (7.8,.7) circle[radius=1.5pt];
+\draw[fill=black] (8.2,.7) circle[radius=1.5pt];
+%\node [right] at (8.5,.8) {$d_1$};
+\draw[gray] (6.2,.2)-- (8.2,.2);
+\draw[fill=black] (7.5,.2) circle[radius=1.5pt];
+\draw[fill=black] (7.9,.2) circle[radius=1.5pt];
+%\node [right] at (8.2,.3) {$d_2$};
+
+\draw[gray] (5,-2.5)-- (7.3,-2.5);
+\draw[fill=black] (7,-2.5) circle[radius=1.5pt];
+\draw[fill=black] (6.6,-2.5) circle[radius=1.5pt];
+%\node [right] at (7,-2.4) {$d_3$};
+\draw[gray] (6,-1.5)-- (6,-3.8);
+\draw[fill=black] (6,-3.5) circle[radius=1.5pt];
+\draw[fill=black] (6,-3.1) circle[radius=1.5pt];
+%\node [right] at (6.2,-1.5) {$d_2$};
+\draw[gray] (5,-1.5)-- (7.3,-3.8);
+\draw[fill=black] (7,-3.5) circle[radius=1.5pt];
+\draw[fill=black] (6.6,-3.1) circle[radius=1.5pt];
+%\node [right] at (7,-3.4) {$d_1$};
+\end{tikzpicture}
+\caption{An example of different plausible $3$-stabilisations.}
+\end{figure}
+
+The indeterminacy has been resolved by \cite{RSPW}.
+\end{remark}
+\subsection{Auxiliary spaces and induced obstruction theories}
 In this last part of the section we exploit the $1$-stabilisation morphism to introduce some auxiliary spaces with a virtual class that are going to be useful in comparing cuspidal with reduced invariants of the quintic threefold.
@@
 \ecd
-where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisation (i.e. contraction of elliptic tails of weight $0$); arrows over $\id_S$ are commutative diagrams:
+where $f$ is a $1$-stable map and $\phi$ is the weighted $1$-stabilisation; arrows over $\id_S$ are commutative diagrams:
 \bcd
@@
 
-\begin{lem}
+\begin{lem}\label{lem:inclusion}
 The morphism $i\colon\Z\hookrightarrow\oM_1(\PP^4,d)$ is a closed immersion. In particular $\Z$ is a proper DM stack.
@@
 
-Observe that $f$ is constant on the fibers of $\phi_\dvr$, so it factors topologically through $\hC.$
+Observe that $f$ is constant on the fibers of $\phi_\dvr$, so it factors topologically through $\hC_{\dvr}.$
 We can conclude as in \cite{RSPW} or appeal to \cite[Lemma~1.15]{debarre} using $\phi_*\OO_{\cC_\dvr}\cong\OO_{\hC_\dvr}$. To see this consider the exact sequence:
@@
 
- A description of the irreducible components of $\Z$ can be easily obtained from the inclusion $i$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$-many rational tails of positive degree.
-
-Notice that the above lemma means that each and every component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$.
-Indeed given any stable map there is at most one factorisation through the weighted $1$-stabilisation of the curve: objects of $\oM_1(\PP^4,d)\setminus D^1$ are $1$-stable already; objects of $D^1\cap \oM_1(\PP^4,d)^\text{main}$ do factor through the cusp thanks to Vakil's criterion, which implies the node joining the elliptic tail to the rational tail of positive degree is a ramification point of the map; and objects of $D^1\cap D^k$ ($k\geq 2$) do factor through a map which is constant on the cusp.\marginpar{insert figure of a typical element of $D^1\cap D^2$.} On the other hand, objects of $D^{1,\circ}=D^1\setminus(\oM_1(\PP^4,d)^\text{main}\cup\bigcup_{k\geq 2}D^k)$ do not admit any factorisation, so $\Z$ has no corresponding component.
-
+ A description of the irreducible components of $\Z$ can be easily obtained from the inclusion $i$: there is a main component $\Z^\text{main}$ which is the closure of the locus of maps from a smooth elliptic curve, and for every $k\geq 2$ a boundary component $D^k\Z$, whose general point represents a contracted elliptic curve with $k$ many rational tails of positive degree.
+\begin{remark}
+Each component of $\Z$ is isomorphic to the corresponding one in $\oM_1(\PP^4,d)$. 
+Indeed given any stable map there is at most one factorisation through the weighted $1$-stabilisation of the curve and more in details: objects of $\oM_1(\PP^4,d)\setminus D^1$ are $1$-stable already; objects of $D^1\cap \oM_1(\PP^4,d)^\text{main}$ factor through the cusp thanks to the smoothability criterion, which implies the node is a ramification point of the map; and objects of $D^1\cap D^k$ ($k\geq 2$) factor through a map which is constant on the cusp.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\draw (0,0) circle (.5cm);
+\draw[fill=gray!50] (.7,.7) circle (.5cm);
+\draw[fill=gray!50] (.7,-.7) circle (.5cm);
+\draw (-1,0) ellipse (.5cm and 1cm);
+\draw (-1.05,.7) .. controls (-.85,.5) and (-.85,-.5) .. (-1.05,-.7);
+\draw (-.95,.5) .. controls (-1.2,.5) and (-1.2,-.5) .. (-.95,-.5);
+
+\draw[->] (1.5,0) -- (2.5,0);
+\draw (2.9,0) .. controls (3.2,0) and (3.1,.5) .. (3.5,.5);
+\draw (3.5,0) ++(90:.5cm) arc (90:-90:.5cm);
+\draw (2.9,0) .. controls (3.2,0) and (3.1,-.5) .. (3.5,-.5);
+\draw[fill=gray!50] (4.2,.7) circle (.5cm);
+\draw[fill=gray!50] (4.2,-.7) circle (.5cm);
+\end{tikzpicture}
+\caption{A typical element of $D^1\cap D^2$.}
+\end{figure}
+
+On the other hand, objects of $D^{1,\circ}=D^1\setminus(\oM_1(\PP^4,d)^\text{main}\cup\bigcup_{k\geq 2}D^k)$ do not admit any factorisation, so $\Z$ has no corresponding component.
+\end{remark}
 We introduce two more spaces: let $\XP$ and $\Z^p$ be the algebraic stacks defined by the following cartesian diagram:
@@
 \ecd
-
-The obstruction theory $\R^\bullet\hat{\pi}_*(\hL^{\oplus 5}\oplus\widehat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by localised virtual pullback of $[\XP]$.
-%In Section \ref{section:main_proof} we shall analyse this cycle adapting the arguments in \cite{CL}.
 
@@
 \begin{comment}
-Given a line bundle $\mathcal L$ on $C$ and a section $s_0\in\Gamma(C,\mathcal L)$  there is exactly one line bundle $\hat{\mathcal L}$ on the $1$-stabilisation of $C$ and one section $\hat s_0\in\Gamma(\hat C,\hat{\mathcal L})$ that pull back to $(\mathcal L,s_0)$.
-Let us denote with $p$ the node separating the elliptic tail and the $\PP^1$, which we think as pointed normalisation $\nu\colon(\PP^1,p)\to \hat C$ of the cusp.
+Given a line bundle $\mathcal L$ on $C$ and a section $s_0\in\Gamma(C,\mathcal L)$  there is exactly one line bundle $\hat{\mathcal L}$ on the $1$-stabilisation of $C$ and one section $\hat s_0\in\Gamma(\widehat{C},\hat{\mathcal L})$ that pull back to $(\mathcal L,s_0)$.
+Let us denote with $p$ the node separating the elliptic tail and the $\PP^1$, which we think as pointed normalisation $\nu\colon(\PP^1,p)\to \widehat{C}$ of the cusp.
 There are just two cases to be consider: $s_0$ does not vanish on the elliptic curve; the section is identically $0$ on $E$.
 
-In the first case, $\nu(s_0\rvert_{\PP^1})$ is a smooth divisor $\hat{D}_0$ in $\hat$ and the line bundle $\OO_{\hat{C}}(\hat{D}_0)$ together with the defining section equation $\hat{s}_0$ of the smooth sub-scheme  $\nu(s_0\rvert_{\PP^1})$ pull-back to $\mathcal L$ and $s_0.$
+In the first case, $\nu(s_0\rvert_{\PP^1})$ is a smooth divisor $\hat{D}_0$ in $\hat$ and the line bundle $\OO_{\widehat{C}}(\hat{D}_0)$ together with the defining section equation $\hat{s}_0$ of the smooth sub-scheme  $\nu(s_0\rvert_{\PP^1})$ pull-back to $\mathcal L$ and $s_0.$
 
@@
 \begin{lem}\marginpar{CHECK ME}
-Let $\nu\colon(\PP^1,p)\to \hat C$ be the pointed normalisation of the cusp.
-Then $0\neq s\in\Gamma(\PP^1,\OO_{\PP^1}(d))$ with $s(p)=0$  determines a unique line bundle $\hat{\mathcal L}$ on $\hat C$ to which $s$ descends  only if $s'(p)=0$.
+Let $\nu\colon(\PP^1,p)\to \widehat{C}$ be the pointed normalisation of the cusp.
+Then $0\neq s\in\Gamma(\PP^1,\OO_{\PP^1}(d))$ with $s(p)=0$  determines a unique line bundle $\hat{\mathcal L}$ on $\widehat{C}$ to which $s$ descends  only if $s'(p)=0$.
 \end{lem}
@@
 
-\subsection{Cosection-localised virtual pullback}
-In this section we slightly generalise the notion of virtual pullback \cite{Manolache-pullback} to localised cycles and we show that this operation commutes with proper pushforward. 
-We start by recalling the construction of \cite{KLcosection} for the benefit of the non-expert reader.
-
-Let $Y\to S$ be a morphism of algebraic stacks of DM type and let $E$ be a vector bundle over $Y$ admitting a cosection
-\[E\xrightarrow{\sigma}\OO_Y\]
-surjective on an open $U\subseteq Y$; denote by $Y(\sigma)$ the complement $Y\setminus U.$ Recall the following notation from \cite{KLcosection}:
-\[G=\operatorname{Ker}\left(E\rvert_U\to\OO_Y\rvert_U\right),\qquad E(\sigma)=E\rvert_{Y(\sigma)}\cup G.\]
- Kiem and Li define a localized Gysin map:
- \[s^!_{\sigma,\rm{loc}}\colon A_*(E(\sigma))\to A_*(Y(\sigma)).\]
- Let $[B]\in Z_*(E(\sigma))$ be a cycle represented by a closed integral substack. If $B\subset  E\rvert_{Y(\sigma)}$ then
-  they just consider the standard Gysin morphism: \[s^!_{\sigma,\rm{loc}}[B]:=s^!_{E\rvert_{Y(\sigma)}}[B]\in A_*(Y(\sigma)).\]
- Suppose now that $B$ is not contained in $E\rvert_{Y(\sigma)}.$ Then we may choose a variety $X\xrightarrow{\nu} Y$ such that:
- \begin{itemize}\label{cond:deflocal}
- \item $\nu$ is proper and $\nu(X)\cap U\neq\emptyset$;
- \item the pullback along $\nu$ of the cosection $\nu^*\sigma=:\tilde{\sigma}$ extends to a surjective morphism
- \[\nu^*E\xrightarrow{\tilde{\sigma}}\OO_X(D)\to 0\]
- for a Cartier divisor $D\subseteq X.$ The restriction of $\nu$ to the divisor gives a proper morphism $\nu(\sigma)\colon D\to Y(\sigma);$
- \item there is a closed integral $\widetilde{B}\subset\widetilde{G}=\operatorname{Ker}(\tilde{\sigma})$ such that $\tilde{\nu}_*[\widetilde{B}]=k[B]$ for some $k\in\mathbb N.$
- \end{itemize}
- The localised Gysin pullback is then defined as:
- \[s^!_{\sigma,\rm{loc}}[B]:=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y(\sigma)).\]
- In \cite[\S~2]{KLcosection} they prove that: such $(X,\nu,\widetilde B)$ always exist; the cycle $s^!_{\sigma,\rm{loc}}[B]$ is independent of the above choices; the construction preserves rational equivalences and thus defines the desired morphism on Chow groups.
- \begin{remark}
- If we consider $[Y]$ as a cycle in $E(\sigma)$, thought of as the zero section of $E$, notice that a natural choice for $X$ is $\operatorname{Bl}_{Y(\sigma)}Y.$
- \end{remark}
-  Kiem and Li then proceed to extend the cosection-localised Gysin pullback to vector bundle stacks $h^1/h^0(\mathbb E)$ (this is relatively easy in the presence of a global resolution, which is the case in the situation at hand); they show that the intrinsic normal cone $\mathfrak C_{Y/S}$ is contained in the closed substack $h^1/h^0(\mathbb{E})(\sigma),$ at least when the cosection of the relative obstruction bundle lifts to a cosection of the absolute obstruction bundle \cite[Corollary~4.5]{KLcosection}.
-\begin{defprop}
-Consider a cartesian diagram of stacks:
-\bcd
-Y'\ar[r,"\varphi'"]\ar[d,"\rho'"]\ar[dr,phantom,"\Box"] & Y\ar[d,"\rho"]\\
-S'\ar[r,"\varphi"] & S
-\ecd
-such that $\rho$ is a morphism of DM type admitting a perfect obstruction theory $\mathbb E_{Y/S}.$ Assume furthermore that we have a cosection 
-\[\OO b_{Y/S}\to \OO_Y\]
-that lifts to a cosection of the absolute obstruction sheaf $\OO b_Y$.
-Then we can define a localised virtual pullback operation: \[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}\colon A_*(S')\to A_{*-\operatorname{rk}(\mathbb E)}(Y'(\sigma'))\] where $\sigma'=(\varphi')^*(\sigma)$ and $Y'(\sigma')=Y(\sigma)\times_{Y} Y'$.
-\end{defprop}
-Replace $S'$ by a primitive cycle in it, i.e.
-assume that $S'$ is irreducible and reduced.
-Recall that pulling back $\mathbb E_{Y/S}$ along $\varphi'$ endows $\rho'$ with a relative perfect obstruction theory $\mathbb E_{Y'/S'}:=(\varphi')^*\mathbb E_{Y/S}.$ Furthermore notice that we can pullback the cosection:
-\[\OO b_{Y'/S'}\cong \varphi^* \OO b_{Y/S}\xrightarrow{\sigma'}\OO_{Y'}.\]
-Notice that since $\sigma$ lifts to the absolute obstruction sheaf, $\sigma'$ does as well. The degeneracy locus of $\sigma'$ is $Y'(\sigma')=Y(\sigma)\times_{Y} Y',$ which in turns implies that:
-\[h^1/h^0(\mathbb E_{Y'/S'})(\sigma')=(\varphi')^*h^1/h^0(\mathbb E_{Y/S})(\sigma).\]
-%Recall that, following the notation in \cite{KLcosection}, if $U\subseteq Y$ is the open where the cosection is surjective, we denoted
-%\[\mathbb E_{Y/S}(\sigma)=\mathbb E_{Y/S}\rvert_{Y(\sigma)}\cup\operatorname{Ker}\left(\mathbb E_{Y/S}\rvert_U \to \OO_Y\rvert_U\right).\]
-By \cite[Corollary 4.5]{KLcosection} and by the cartesian diagram above,
-\[\mathfrak{C}_{Y'/S'}\subseteq (\varphi')^* \mathfrak{C}_{Y/S}\subseteq \mathbb E_{Y'/S'}(\sigma')\]
-thus we can define the localised virtual pullback of $[S']$ to be:
-\[(\rho')^!_{\mathbb E_{Y'/S'},\sigma'}[S']=s^!_{\sigma',\rm{loc}}[\mathfrak{C}_{Y'/S'}].\]
-%compare also with \cite[Theorem~5.2]{KLcosection}
-
-The above construction applies to $\Z^p$.
-Indeed consider on $\Z^p$ the perfect obstruction theory: \[\mathbb E_{\Z^p/\XP}:=\alpha^*\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)\] and the induced cosection
-$\alpha^*\sigma\colon \OO b_{\Z^p/\XP}\to \Z^p$
-with degeneracy locus:
-\[\pazocal D(\alpha^*\sigma)=\Mone{1}{X}{d}\times_{\Mone{1}{\PP^4}{d}^p} \Z^p.\]
-Then we have that
-\begin{align*}
-\mathfrak C_{\Z^p/\XP}& \subseteq \alpha^*\mathfrak C_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic_1}{(1)}}\\
-& \subseteq \alpha^* h^1/h^0\left(\mathbb E_{\Mone{1}{\PP^4}{d}^p/\mathfrak{Pic}_1{(1)}}\right)(\sigma)\\
-&\cong h^1/h^0\left(\mathbb E_{\Z^p/\XP}\right)(\alpha^*\sigma)
-\end{align*}
-and we can thus define $[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].$
+\subsection{A cosection-localised class on $\Zp$}\label{sec:cosecvirpull}
+
+The perfect obstruction theory $\R^\bullet\hat{\pi}_*(\hL^{\oplus 5}\oplus\widehat{\mathcal P})$ for the morphism $\overline{\mathcal M}_1^{(1)}(\PP^4,d)^p\to\mathfrak{Pic}_1{(1)}$ together with its cosection induce a localised virtual class on $\Z^p$ by localised virtual pullback, see \S~\ref{sec:cosection}:
+\[[\Z^p]^{\rm{vir}}_{\alpha^*\sigma,\rm{loc}}:=\gamma^!_{\mathbb E_{\Z^p/\XP},\alpha^*\sigma}[\XP].\]
+
+In order to show that this gives the same invariants as the space of $1$-stable maps with $p$-fields, we need to prove that localised virtual pullback commutes with proper pushforward.
+
 \begin{lem}\label{lem:comutativity}
-With the same setup and notation as in the definition of localised virtual pullback, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$.
-For every cycle $[B']\in A_*(S')$,
-\[\phi'_*\circ(\rho')^!_{\mathbb E_{Y'/S'}}[B']=(\rho)^!_{\mathbb E_{Y/S}}\circ\phi_*[B]\in A_*(Y(\sigma)).\]
+With the same setup and notation as in \S~\ref{sec:cosection}, suppose furthermore that $\varphi$ is proper and $\varphi'(Y')\cap U\neq\emptyset$. For every cycle $[B']\in A_*(S')$,
+\[\varphi'_*\circ(\rho')^!_{\mathbb E_{Y'/S'}}[B']=(\rho)^!_{\mathbb E_{Y/S}}\circ\varphi_*[B]\in A_*(Y(\sigma)).\]
 
@@
 \ecd
-Only the left-most square is not classical. Hence we are left with showing that for every cycle $[B']\in A_*(h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma'))$ we have:
+Only the right-most square is not classical. Hence we are left with showing that for every cycle $[B']\in A_*(h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma'))$ we have:
 \begin{equation}\label{eq:commcos}\varphi'_*( s^!_{\sigma',\rm{loc}}[B'])=s^!_{\sigma,\rm{loc}}\left(\varphi^{\mathbb{E}}_*[B']\right)\,\in\, A_*(Y(\sigma)),
@@
 
-Assume then that $B'$ is a prime cycle in $h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')$ not contained in $h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$.
-Then, according to the construction recalled at the beginning of this section,
+Assume then that $B'$ is a prime cycle in $h^1/h^0(\mathbb{E}_{Y'/S'})(\sigma')$ not contained in $h^1/h^0(\mathbb{E}_{Y'/S'})\rvert_{Y'(\sigma')}$. Then recall that: 
  \[s^!_{\sigma',\rm{loc}}[B']:=\frac{1}{k} \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\,\in\,A_*(Y'(\sigma')),\]
- where $\nu'\colon X\to Y'$, $(\nu')^*(\sigma')$ and $\widetilde B$ satisfy the conditions~\eqref{cond:deflocal}. Notice that if we consider the composition
- $\nu\colon X\xrightarrow{\nu'} Y'\xrightarrow{\varphi'} Y$ and the pull-back $\nu^*(\sigma)$, the first two conditions in \eqref{cond:deflocal} are satisfied. How about
- \[\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B')=:B?\]
- Suppose first that $B'\to B$ is generically finite of degree $h$; then $\widetilde{B}\to B$ satisfies the last condition in \eqref{cond:deflocal} and has degree $hk$, so:
+ where $\nu'\colon \widetilde{Y}\to Y'$, $(\nu')^*(\sigma')$ and $\widetilde B$ satisfy the conditions of a regularising morphism, see \S~\ref{cond:deflocal}.
+Notice that if we consider the composition
+ $\nu\colon \widetilde{Y}\xrightarrow{\nu'} Y'\xrightarrow{\varphi'} Y$ and the pull-back $\nu^*(\sigma)$, the first two of those conditions are always satisfied. How about
+ $\widetilde{B}\to B'\to \varphi^{\mathbb{E}}(B')=:B?$
+ Suppose first that $B'\to B$ is generically finite of degree $h$; then $\widetilde{B}\to B$ is  generically finite of degree $hk$, so:
  \begin{align*}
- \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= \frac{1}{k}\varphi'_*\ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
+ \varphi'_*( s^!_{\sigma',\rm{loc}}[B'])&= \frac{1}{k}\varphi'_*\circ \nu'(\sigma')_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
  &=\frac{1}{k} \nu(\sigma)_*\left([D]\cdot s^!_{\widetilde{G}}[\widetilde{B}]\right)\\
@@
 
-\begin{cor}
+\begin{cor}\label{cor:Zp-vs-pfields}
 $\deg[\Z^p]^{\rm{vir}}_{\rm{loc}}=\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}$
@@
 \ecd
-We may in fact assume that $\phi_{\eta}$ is an isomorphism, and then it is enough to take the semistable model of $\hC.$
+We may in fact assume that $\phi_{\eta}$ is an isomorphism, and then it is enough to take the weighted stable model of $\hC.$
 \end{proof}
@@
 We are going to need a description of the normal cone $\mathfrak C_{\Z^p/\XP}$ in order to perform a splitting.
-
-Since $\Z^p$ simply is a line bundle over the boundary of $\Z$, we may instead find equations for the latter.
-
-Recall that $\Z$ can be embedded as an open inside $C(\hat{\pi}_*\mathcal L^{\oplus 5})$ over $\XP$.
-We are going to find an embedding of $C(\hat{\pi}_*\mathcal L^{\oplus 5})$ in a smooth ambient space over $\XP$, that will be a vector bundle obtained by suitably twisting $\mathcal L$.
-
-Following \cite{HL}, we work locally on $\Z$: start with a point $\xi=[(C\xrightarrow{\phi}\hat C\xrightarrow{f}\PP^4]\in\Z$ and choose coordinates on $\PP^4$ such that $f^{-1}\{x_0=0\}$ is a simple smooth divisor $D=\sum_{i=1}^d\delta_i$ on $\hat C$.
-This continues to be true on a neighbourhood $U$.
-
- Locally the morphism $\Z\to\XP$ can be written as $\xi\mapsto[C\to\hat C,\OO_{\hat C}(D)]$, which admits a local lifting $U\to\MM_1^{(1),\rm{div}}$ and in fact hits the smooth locus of the latter.
-
-  Notice though that the projection $\MM_1^{(1),\rm{div}}\to \XP$ (or to $\Pic_1^{(1)}$ for what it is worth) is \emph{not} smooth.
-In fact, when the line bundle is trivial on the minimal elliptic subcurve $E$, it may be deformed to a degree $0$, non-effective line bundle on such a subcurve, so that sections of $\OO_{\hat C}(D)$ which are constant and non-zero on $E$ are obstructed.
-
-There is a way around this: in a neighbourhood $V\subseteq \XP$ of $[C\to\hat C,\OO_{\hat C}(D)]$ we can write the universal line bundle $\mathcal L_V$ as $\OO_{\hC_V}(\pazocal D + p-p_0)$.
-Indeed we can pick a local section $p_0$ through the minimal genus $1$ subcurve, so that $\mathcal L_V(p_0)$ becomes effective.
-We should then think of $p$ as a local coordinate on $\XP$ relative to $\X$.
-
-Locally on $V$ we can pick another smooth section $\A$ of the minimal genus $1$ subcurve not intersecting $p_0$, neither the support of $\pazocal D+p$.
+Since $\Z^p$ is a line bundle over the boundary of $\Z$, we find instead equations for the latter.
+
+Recall that $\Z$ can be embedded as an open inside $C(\hat{\pi}_*\hL^{\oplus 5})$ over $\XP$.
+We are going to find an embedding of $C(\hat{\pi}_*\hL^{\oplus 5})$ in a smooth ambient space over $\XP$, that will be a vector bundle obtained by suitably twisting $\hL$.
+
+Following \cite{HL}, we work locally on $\Z$: start with a point $\xi=[(C\xrightarrow{\phi}\widehat{C}\xrightarrow{f}\PP^4]\in\Z$ and choose coordinates on $\PP^4$ such that $f^{-1}\{x_0=0\}$ is a simple smooth divisor $D=\sum_{i=1}^d\delta_i$ on $\widehat{C}$.
+This continues to be true on a neighbourhood $\pazocal U$ of $\xi$.
+
+ Locally the morphism $\Z\to\XP$ can be written as $\xi\mapsto[C\to\widehat{C},\OO_{\widehat{C}}(D)]$, which admits a local lifting $\pazocal U\to\X^{\rm{div}}:=\MM_1^{\rm{div}}(1)\times_{\hM}\X$, and in fact hits the smooth locus of the latter.
+
+ \begin{remark}
+  The projection $\X^{\rm{div}}\to \XP$ 
+  %(or to $\Pic_1^{(1)}$ for what it is worth) 
+  is \emph{not} smooth.
+In fact, when the line bundle is trivial on the minimal elliptic subcurve $E$, it may be deformed to a degree $0$, non-effective line bundle on such a subcurve, so that sections of $\OO_{\widehat{C}}(D)$ which are constant and non-zero on $E$ are obstructed.
+
+There is a way around this: in a neighbourhood $\pazocal V\subseteq \XP$ of $[C\to\widehat{C},\OO_{\widehat{C}}(D)]$ we can write the universal line bundle $\hL_{\pazocal V}$ as $\OO_{\hC_{\pazocal V}}(\pazocal D + p-p_0)$.
+Indeed we can pick a local section $p_0$ through the core, so that $\hL_{\pazocal V}(p_0)$ becomes effective.
+We should think of $p$ as a local coordinate on $\XP$ relative to $\X$.
+\end{remark}
+
+Locally on $\pazocal V$ we can pick another smooth section $\A$ of the core not intersecting $p_0$, neither the support of $\pazocal D+p$.
 
 \begin{lem}
-$C(\hat\pi_*\mathcal L)$ is the kernel of the vector bundle map:
+$C(\hat\pi_*\hL_{\pazocal V})$ is the kernel of the vector bundle map:
 \[ \hat\pi_*\OO_{\hC}(\A+\pazocal D+p-p_0)\xrightarrow{\varphi}\hat\pi_*\OO_{\A}(\A)\]
-Up to shrinking $V$ we may write:
-\[\hat\pi_*\OO_{\hC}(\A+\pazocal D+p-p_0)\cong\bigoplus_{i=1}^d\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i+p-p_0)\oplus\hat\pi_*\OO_{\hC}(\A+p-p_0)\]
+Up to shrinking $\pazocal V$ we may write:
+\[\hat\pi_*\OO_{\hC}(\A+\pazocal D+p-p_0)\cong\bigoplus_{i=1}^d\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i-p_0)\oplus\hat\pi_*\OO_{\hC}(\A+p-p_0)\]
 \end{lem}
 Compare with \cite[Lemma 4.10]{HL}.
-Denote by \[\varphi_i\colon\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i+p-p_0)\to\hat\pi_*\OO_{\A}(\A)\] (and similarly $\varphi_p$) the composite of the inclusion with $\varphi$.
-
-Let us introduce some more notation: around a point $[\hat C]\in\MM_1^{(1),\rm{wt}}$, for every node $q$ of $\hat C$ there is a coordinate $\zeta_q$ whose vanishing locus is the divisor where such a node is \emph{not} smoothed.
-These functions can be pulled back to $V$.
-Denote by \[\zeta_{[\delta_i,a]}=\prod\zeta_q\]
-where the product runs over all the nodes separating $\delta_i$ from the minimal genus $1$ curve.
+Denote by \[\varphi_i\colon\hat\pi_*\OO_{\hC}(\A+\pazocal \delta_i-p_0)\to\hat\pi_*\OO_{\A}(\A)\] (and similarly $\varphi_p$) the composite of the inclusion with $\varphi$.
+
+Let us introduce some more notation: around a point $[\widehat{C}]\in\MM_1^{\rm{wt}}(1)$, for every node $q$ of $\widehat{C}$ there is a coordinate $\zeta_q$ whose vanishing locus is the divisor where such a node is \emph{not} smoothed.
+These functions can be pulled back to $\pazocal V$.
+Denote by \[\zeta_{[\delta_i,\pazocal A]}=\prod\zeta_q\]
+where the product runs over all the nodes separating $\delta_i$ from the core.
 
 \begin{lem}
-We may find an explicit local expression for $\varphi_i$ and $\varphi_p$ after trivialising the relevant line bundles:
+There are trivialisations for the line bundles $\pi_*\OO_{\hC}(\A+\pazocal \delta_i-p_0),\,\hat\pi_*\OO_{\hC}(\A+p-p_0),\, \pi_*\OO_{\A}(\A) $ such that locally we have the following explicit expression for $\varphi_i$ and $\varphi_p$:
 \[\varphi_i=\zeta_{[\delta_i,a]}, \quad \varphi_p=(p-p_0)\]
@@
 \begin{remark}
-The vanishing locus of $(p-p_0)$ on the boundary means that the line bundle restricts to the trivial one on the minimal genus $1$ subcurve. The meaning of it is not clear outside the boundary.
+The vanishing locus of $(p-p_0)$ on the boundary means that the line bundle restricts to the trivial one on the core.
 \end{remark}
@@
 \begin{lem}\label{lem:equations}
-A local chart $U$ for $\Z$ can be embedded as an open inside:
-\[ (F_0=\ldots=F_4=0)\subseteq \rm{Vb}(\hat{\pi}_*\mathcal L^{\oplus 5}) \]
+A local chart $\pazocal U$ for $\Z$ can be embedded as an open inside:
+\[ (F_0=\ldots=F_4=0)\subseteq \rm{Vb}(\hat{\pi}_*\hL_{\pazocal V}(\A)^{\oplus 5}) \]
 where
-\[ F_j=\sum_{i=1}^d \zeta_{[\delta_i,a]}w_i^j+(p-p_0)w_{d+1}^j \]
-and $w_i^j$ are coordinates on the fiber of the $j$-th copy of $\rm{Vb}(\hat{\pi}_*\mathcal L)$ over $\XP$.
+\[ F_j=\sum_{i=1}^d \zeta_{[\delta_i,\pazocal A]}w_i^j+(p-p_0)w_{d+1}^j \]
+and $w_i^j$ are coordinates on the fiber of the $j$-th copy of $\rm{Vb}(\hat{\pi}_*\hL_{\pazocal V}(\A))$ over $\pazocal V$.
 \end{lem}
@@
 \subsection{Hu-Li blow-up and desingularisation}
-We perform a modular blow-up of $\MM_1^{1,\rm{wt}}$: we successively blow up $\hat\Theta_k, \;k\geq 2$  defined as the closure of the loci where the minimal elliptic subcurve $E$ has weight $0$ and $\lvert\overline{C\setminus E}\cap E\rvert=k.$
-
-Notice that after the $k$-th blow-up, the strict transform of $\Theta_{k+1}$ is smooth, so the final result  $\widetilde{\MM}_1^{1,\rm{wt}}$ is smooth as well.
+We perform a modular blow-up of $\MM_1^{\rm{wt}}(1)$: we successively blow up $\widehat{\Theta}_k, \;k\geq 2,$  defined as the closure of the loci where the minimal elliptic subcurve $E$ has weight $0$ and $\left\lvert\overline{C\setminus E}\cap E\right\rvert=k.$
+
+Notice that after the $k$-th blow-up, the strict transform of $\widehat{\Theta}_{k+1}$ is smooth, so the final result  $\widetilde{\MM}_1^{\rm{wt}}(1)$ is smooth as well.
 
@@
 The fiber product 
-\[\widetilde{\MM}_1^{1,\rm{wt}}\times_{\MM_1^{1,\rm{wt}}}\MM_1^{\rm{wt}}\]
-recovers the Hu-Li blow-up $\widetilde{\MM}_1^{\rm{wt}}.$ The key observation is that $\Theta_1$ is already a Cartier divisor and the pullback of $\hat\Theta_k$ is precisely $\Theta_k$.
-\marginpar{you can use the universal property of the blow up to show there are maps in both directions. Check the statement about the $\Theta_k$}
+\[\widetilde{\MM}_1^{\rm{wt}}(1)\times_{\MM_1^{\rm{wt}}(1)}\MM_1^{\rm{wt}}\]
+recovers the Hu-Li blow-up $\widetilde{\MM}_1^{\rm{wt}}.$ The key observation is that $\Theta_1$ is already a Cartier divisor and the inverse image of $\widehat{\Theta}_k$ is precisely $\Theta_k$; 
+using the universal property of the blow-up, it can be shown that there are maps in both directions, and they are inverse to one another. 
 \end{remark}
@@
 \[\tilde\zeta\tilde w+(p-p_0)w_{d+1}=0\]
-where $\tilde\zeta$ is one of the newly created boundary divisors $\widetilde{\Theta_k}$ from $\widetilde{\MM}_1^{\rm{wt}}$ (i.e.
-one of the exceptional divisors produced by the blow-up process), and $\tilde w$ is a suitably defined coordinate on the fiber of $\rm{Vb}(\hat{\pi}_*\mathcal L)\times_{\XP}\widetilde{\XP}$.
+where $\tilde\zeta$ is one of the newly created boundary divisors $\widetilde{\Theta}_k$ from $\widetilde{\MM}_1^{\rm{wt}}$ (i.e.
+one of the exceptional divisors produced by the blow-up process), and $\tilde w$ is a suitably defined coordinate on the fiber of $\rm{Vb}(\hat{\pi}_*\hL(\A))\times_{\XP}\widetilde{\XP}$.
 \end{remark}
@@
 \tM_1(\PP^4,d)\ar[d] & \widetilde{\Z} \ar[l,hook,swap,"i"]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \tM_1^{(1)}(\PP^4,d) \ar[d] \\
-\widetilde{\mathfrak{Pic}}_1\ar[d] &\widetilde{\XP}\ar[l]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \widetilde{\mathfrak{Pic}}_1 ^{(1)}\ar[d]\\
-\widetilde{\MM}^{\rm{wt}}_1 & \widetilde{\X}\ar[l,swap,"\sim"]\ar[r] & \widetilde{\MM}_1^{(1),\rm{wt}}
-\ecd
-
-\begin{comment}
-where this time an object of $\Z^p$ over $S$ is given by
-\bcd
-\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[rr,"f"]\ar[dl,"\hat\pi"] & & \PP^4 & \text{and} & \xi\in\Gamma(\hat\cC,f^*\OO_\PP(-5)\otimes\omega_{\hat\cC/S}) \\
-& S & & & & &
-\ecd
-(I think to satisfy the stack condition $\xi$ should be really thought of as a section of $\hat\pi_*(f^*\OO_\PP(-5)\otimes\omega_{\hat\cC/S})$.)
-
-For the existence of $j$ we are claiming that, pulling back along $\phi$, $\xi$ induces a section of $\pi_*((f\circ\phi)^*\OO_\PP(-5)\otimes\omega_{\cC/S})$.
-We may work on an atlas for $\Z^p$, which we shall (maybe abusing notation slightly) denote by $S$, as the base scheme in the above diagram; let us also denote by $\hat{\mathcal L}=f^*\OO(1)$ and $\L=\phi^*\hL$.
-
-First we claim that the adjunction map $\OO_{\hat\cC}\to\phi_*\OO_\cC$ is an isomorphism: it is injective by dominance of $\phi$; to check the cokernel is trivial it is enough to do so after restricting to each and every irreducible component of $\Z^p$.
-Then $\hat\cC$ is normal\marginpar{NO, $\hat\cC_{|D^k}$ has multiple components} (so is the base\footnote{on VZ here}; R1 follows from the fact that singularities are isolated in the fiber, S2 \footnote{OK when fibers are Cartier i.e.
-over a DVR; actually take a look at Thm 23.9 in Matsumura's Commutative Ring Theory, fibers are CM in the situation at hand } follows from reducedness of the fibers) and we conclude by Zariski's main theorem (geometric fibers of $\phi$ are either points or elliptic curves, in either case connected).
-
-The equality $\phi^*\omega_{\hat\cC/S}=\omega_{\cC/S}(\mathcal E)$, where $\mathcal E$ is the locus spanned by elliptic tails, can be checked on $\X$ and then pulled back.
-Notice that $\mathcal E$ is a Cartier divisor; $\phi$ is generically an isomorphism, so $\phi^*\omega_{\hat\cC/S}$ and $\omega_{\cC/S}$ may differ only on the locus where $\phi$ is not an isomorphism.
-The statement may now be proved by an intersection-theoretic argument by reducing to smoothings over the spectrum of a DVR, see\cite[Lemma 2.13]{SMY1}.
-
-It is clear now that $\omega_{\cC/S}\otimes\L^{\otimes -5}\hookrightarrow \phi^*(\omega_{\hat\cC/S}\otimes\hL^{\otimes-5})$.
-Pushing down along $\pi=\hat\pi\circ\phi$, we get a map $\pi_*(\omega_{\cC/S}\otimes\L^{\otimes -5})\hookrightarrow \hat\pi_*(\omega_{\hat\cC/S}\otimes\hL^{\otimes-5})$ (using the projection formula and $\phi_*\OO_\cC=\OO_{\hat\cC}$).
-These are both $0$ on $\Z^{\text{main},\circ}=\Z^\text{main}\setminus(\bigcup_{k\geq2} D^k\Z)$; on the other hand they are both line bundles on $D^k\Z$...
-\marginpar{Fix me}
-
-\begin{lem}
-There is a close embedding $j\colon \Z^p\hookrightarrow \oM_1(\PP^4,d)^p$.
-\end{lem}
-
-Notice that the $p$-field is forced to vanish on $\Z^{\text{main},\circ}$, so $(\Z^p)^{\text{main},\circ}\simeq\Z^{\text{main},\circ}$ is the zero-section of the cone $\Z^p\to\Z$ (even though $\oM_1(\PP^4,d)^p\to \oM_1(\PP^4,d)$ is non-trivial on $\oM_1(\PP^4,d)^\text{main}\cap D^1$).
-
-Finally it will be useful to introduce
-\bcd
-\XP\ar[r]\ar[d]\ar[dr,phantom,"\Box"] & \mathfrak{Pic}_1^{(1)}\ar[d] \\
-\X\ar[r] & \MM_1^{(1)}
-\ecd
-so that objects of $\XP(S)$ are
-\bcd
-\cC\ar[rr,"\phi"]\ar[dr,"\pi"] & & \hat\cC\ar[dl,"\hat\pi"] & \text{and} & \hL\in\Pic_{\hat \cC/S}(S) \\
-& S & & &
-\ecd
-Notice that the map $\XP\to\mathfrak{Pic}$ that associates to an object as above $(\cC\to S,\phi^*\hL)$ is highly non-trivial on the locus of elliptic tails/cusps, since
-\begin{itemize}
-\item line bundles of the same degree on the cusp are identified (there is a $\mathbb G_a$ wealth of them), and
-\item only line bundles that restrict to effective line bundles on the elliptic tail are in the image of this morphism.
-\end{itemize}
-\end{comment}
-We conclude this brief section remarking that the blow up procedure does not affect the invariants:
-\begin{lem}
+\widetilde{\mathfrak{Pic}}_1\ar[d] &\widetilde{\XP}\ar[l]\ar[r]\ar[d]\ar[rd,phantom,"\Box"] & \widetilde{\mathfrak{Pic}}_1 (1)\ar[d]\\
+\widetilde{\MM}^{\rm{wt}}_1 & \widetilde{\X}\ar[l,swap,"\sim"]\ar[r] & \widetilde{\MM}_1^{\rm{wt}}(1)
+\ecd
+
+Notice that the components of $\tZp$ are in bijection with those of $\Zp$, however all the boundary ones have the same dimension $5d+4$, and their intersection with main is a divisor in the latter.
+
+We conclude this brief section remarking that the blow-up procedure does not affect the invariants:
+\begin{lem}\label{lem:tilding}
 We have the identity:
-\[\deg\virloc{\tZp}=\deg\virloc{\Zp}\]
+\[\deg\virloc{\tZp}=\deg\virloc{\Zp}.\]
 \end{lem}
@@
 \section{Splitting the cone and proof of the Main Theorem}\label{section:main_proof}
-We are finally in a position to study the cone $\mathfrak{C}_{\tZp/\tXP}.$ This is essentially going to be a word-by-word repetition of the arguments in \cite{CLpfields}.
+We are finally able to study the cone $\mathfrak{C}_{\tZp/\tXP}.$ This is going to be a word-by-word repetition of the arguments in \cite{CLpfields}.
 \begin{lem}\label{lem:open_cones}
-Let $\tilde{\rho}\colon \tZp\to\tXP$ be the natural map and $\mathbb {E}_{\tZp/\tXP}=\R\hat\pi_*(\mathcal L^{\oplus 5}\oplus\widehat{\mathcal P})$  the relative perfect obstruction theory for $\tilde{\rho},$ then $\mathfrak{C}_{\tZp/\tXP}$ has the following properties:
+The map $\tilde{\rho}\colon \tZp\to\tXP$ has a relative perfect obstruction theory $\mathbb {E}_{\tZp/\tXP}=\R^{\bullet}\hat\pi_*(\hL^{\oplus 5}\oplus\widehat{\mathcal P})$.
+The intrinsic normal cone $\mathfrak{C}_{\tZp/\tXP}$ has the following properties:
 \begin{enumerate}
-\item Its restriction to  $\tZ^{p,\circ}= \tZ^{p,\rm{main}}\setminus \bigcup_{k\geq 2}D^k \tZp$ can be described as the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}$
-\item Its restriction to $\tZ^{p,gst,\circ}=\tZp - \tZ^{p,\rm{main}}$  is a rank $2$ subbundle stack of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,gst,\circ}}$
+\item Its restriction to the open $\tZ^{p,\circ}= \tZ^{p,\rm{main}}\setminus \bigcup_{k\geq 2}D^k \tZp$ can be described as the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}$
+\item Its restriction to the open $\tZ^{p,\rm{gst},\circ}=\tZp - \tZ^{p,\rm{main}}$  is a rank $2$ subbundle stack of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{gst},\circ}}$
 \end{enumerate}
@@
 \begin{enumerate}
-\item Observe that $\tZ^{p,\circ}\cong \tZ^{\circ}$ because here $H^0(\hat C, L^{\otimes -5}\otimes \omega_{\hat C})=0$.
-Moreover $\tZ^{\circ}$ is unobstructed on its image, which is an open of $\tXP$, because $\R^1\hat{\pi}_*\mathcal L=0$.
-So the normal cone is $[\tZ^{p,\circ}/\hat{\pi}_*\mathcal L^{\oplus 5}]$, which is the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}=[0\oplus \R^1\hat{\pi}_*\widehat{\mathcal P}/\hat{\pi}_*\mathcal L^{\oplus 5}\oplus 0]$.
-\item We know that $\tZ^{p,gst,\circ}$ is a line bundle over $\tZ^{gst,\circ}$.
-From the equations \ref{rmk:eqn} we see that the latter is smooth over its image $\pazocal W$ in $\tXP$, which is the codimension $2$ locus where the minimal genus $1$ subcurve has weight $0$ and the line bundle is trivial on it.
-Recall that every smooth morphism $A\to B$ factors as $A\xrightarrow{\acute{e}t} B\times \Aaff^n\xrightarrow{\pr_1} B$.
+\item Observe that $\tZ^{p,\circ}\cong \tZ^{\circ}$ because here $H^0(\widehat{C}, \widehat{L}^{\otimes -5}\otimes \omega_{\widehat{C}})=0$.
+Moreover $\tZ^{\circ}$ is unobstructed on its image, which is an open of $\tXP$, because $\R^1\hat{\pi}_*\hL=0$.
+So the normal cone is $[\tZ^{p,\circ}/\hat{\pi}_*\hL^{\oplus 5}]$, which is the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\circ}}=[0\oplus \R^1\hat{\pi}_*\widehat{\mathcal P}/\hat{\pi}_*\hL^{\oplus 5}\oplus 0]$.
+
+\item We know that $\tZ^{p,\rm{gst},\circ}$ is a line bundle over $\tZ^{\rm{gst},\circ}$.
+From the equations \ref{rmk:eqn} we see that the latter is smooth over its image $\pazocal W$ in $\tXP$, which is the codimension $2$ locus where the core has weight $0$ and the line bundle is trivial on it.
+Recall that every smooth morphism $A\to B$ of relative dimension $n$ factors as $A\xrightarrow{\acute{e}t} B\times \Aaff^n\xrightarrow{\pr_1} B$.
 So we have
 \bcd
-\tZ^{p,gst,\circ} \ar[r,"\acute{e}t"] & \pazocal W\times\Aaff^{5d+5}\ar[r,hook]\ar[d,"q"] & \tXP\times \Aaff^{5d+5}\ar[d] \\
+\tZ^{p,\rm{gst},\circ} \ar[r,"\acute{e}t"] & \pazocal W\times\Aaff^{5d+6}\ar[r,hook]\ar[d,"q"] & \tXP\times \Aaff^{5d+6}\ar[d] \\
 & \pazocal W \ar[r,hook] & \tXP
@@
 where the bottom horizontal arrow is a codimension $2$ regular embedding. Thus 
-\[\mathfrak{C}_{\tZp/\tXP}\rvert_{\tZ^{gst,\circ}}\cong \left[ q^* C_{\pazocal W/\tXP}/ \hat{\pi}_*\mathcal L^{\oplus 5}\right]\]
-is a rank 2 subbundle stack of  $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,gst,\circ}}.$
+\[\mathfrak{C}_{\tZp/\tXP}\rvert_{\tZ^{p,\rm{gst},\circ}}\cong \left[ q^* C_{\pazocal W/\tXP}/ \hat{\pi}_*\hL^{\oplus 5}\oplus\hat{\pi}_*\widehat{\mathcal P}\right]\]
+is a rank 2 subbundle stack of  $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{gst},\circ}}.$
 \end{enumerate}
 \end{proof}
-
- Notice that the image of $\tZ^{\circ}$ in $\tM_1(\PP^4)$ contains $\tM_1(\PP^4)^{main}\cap \tilde{D}^1.$
-
-Recall the definition of the \emph{closure of the zero section of a vector bundle stack}: let $B$ be an integral algebraic stack and let $[F_0\xrightarrow{d} F_1]$ be a complex of locally free sheaves on $B$.
-The zero section is $0_{\mathbf F}\colon [F_0/F_0]\to\mathbf F=[F_1/F_0]$ (notice that it is not in general a closed embedding); the closure of the zero section is then defined as:
-\[ \overline{0}_{\mathbf F}=[\operatorname{cl}(dF_0)/F_0] \]
-$\overline{0}_{\mathbf F}$ is an integral stack.
+Notice that the image of $\tZ^{\circ}$ in $\tM_1(\PP^4)$ contains $\tM_1(\PP^4)^{\rm{main}}\cap \widetilde{D}^1.$
+
+\subsection{Contribution of the main component}
+Recall the definition of the \emph{closure of the zero section of a vector bundle stack}: let $B$ be an integral algebraic stack and let $\mathbb F=[F_0\xrightarrow{d} F_1]$ be a complex of locally free sheaves on $B$.
+The zero section is $0_{\mathbb F}\colon [F_0/F_0]\to h^1/h^0(\mathbb F)=[F_1/F_0]$, which is in general not a closed embedding; its closure is defined as:
+\[ \overline{0}_{\mathbb F}=[\operatorname{cl}(dF_0)/F_0] \]
+$\overline{0}_{\mathbb F}$ is an integral stack.
 
 \begin{ex}
-When $h^0(F_\bullet)=0$, the closure of the zero section looks like $B$ with some stacky structure on the vanishing locus of $d$.
-Consider for example $B=\PP^1$ and $F_\bullet=[\OO_{\PP^1}\xrightarrow{x}\OO_{\PP^1}(1)]$.
-Then the action of $e\in F_0$ on $F_1$ is by $f\mapsto f+xe$.
+When $h^0(\mathbb F)=0$, the closure of the zero section looks like $B$ with some further stacky structure on the vanishing locus of $d$.
+Consider for example $B=\PP^1$ and $\mathbb F=[\OO_{\PP^1}\xrightarrow{x}\OO_{\PP^1}(1)]$.
+Then the action of $e\in F_0$ on $F_1$ is given by $f\mapsto f+xe$.
 Clearly $\operatorname{cl}(dF_0)$ is the whole line bundle $F_1$; the $F_0$-action is transitive on the fibers over $\{x\neq 0\}$ and trivial on the $\{x=0\}$-fiber.
-Hence $\overline{0}_{\mathbf F}$ is isomorphic to $\PP^1\setminus\{x=0\}$ with a gerbe $[\Aaff^1/\mathbb G_{\rm a}]$ replacing the point $\{x=0\}$.
+Hence $\overline{0}_{\mathbb F}$ is isomorphic to $\PP^1\setminus\{x=0\}$ with a gerbe $[\Aaff^1/\mathbb G_{\rm a}]$ replacing the point $\{x=0\}$.
 \end{ex}
 
-We may now split the cone $\mathfrak{C}_{\tZp/\tXP}$ in the following manner: we denote by $\mathfrak C^{\rm{main}}$ the closure of the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{main}}}$, which is an irreducible cone supported on the main component; all the rest is supported on the boundary components, possibly on their intersection with the main one, and we are going to pack all the components supported on $D^k\tZp$ together and label them $\mathfrak C^k$ accordingly, so in the end we obtain a splitting:
+We may now split the cone $\mathfrak{C}_{\tZp/\tXP}$ in the following manner: we denote by $\mathfrak C^{\rm{main}}$ the closure of the zero section of $h^1/h^0(\mathbb {E}_{\tZp/\tXP})\rvert_{\tZ^{p,\rm{main}}}$, which is an irreducible cone supported on the main component.
+All the rest is supported on the boundary components, possibly on their intersection with the main one, and we are going to pack all the components supported on $D^k\tZp$ together and label them $\mathfrak C^k$ accordingly, so in the end we obtain a splitting:
 \[
@@
 
-In order to prove the first we proceed as in \cite[\S5]{CLpfields}: notice that the obstruction theory $\mathbb E$ splits as $\mathbb E_1\oplus\mathbb E_2$ where $\mathbb E_1=\R\hat\pi_*(\mathcal L^{\oplus 5})$ and $\mathbb E_2=\R\hat\pi_*(\widehat{\mathcal P})$.
-When we restrict ourselves to $\tZ^{p,\rm{main}}$ we see that $\mathbb E_1$ is the closure of its own zero section; it follows that:
+In order to prove the first claim we proceed as in \cite[\S5]{CLpfields}; let us start by noticing that the obstruction theory $\mathbb E:=\mathbb E_{\tZp/\tXP}$ splits as $\mathbb E_1\oplus\mathbb E_2$ where $\mathbb E_1=\R^{\bullet}\hat\pi_*(\hL^{\oplus 5})$ and $\mathbb E_2=\R^{\bullet}\hat\pi_*(\widehat{\mathcal P})$.
+When we restrict to $\tZ^{p,\rm{main}}$ we see that $h^1/h^0(\mathbb E_1)$ is the closure of its own zero section; it follows that:
 \[
- \mathfrak C^{\rm{main}}=\overline{0}_{\mathbb E\rvert_{\tZ^{p,\rm{main}}}}=\mathbb E_1\rvert_{\tZ^{p,\rm{main}}}\oplus \overline{0}_{\mathbb E_2\rvert_{\tZ^{p,\rm{main}}}}
-\]
-Then by excess intersection:
+ \mathfrak C^{\rm{main}}=\overline{0}_{\mathbb E\rvert_{\tZ^{p,\rm{main}}}}=h^1/h^0(\mathbb E_1)\rvert_{\tZ^{p,\rm{main}}}\oplus \overline{0}_{\mathbb E_2\rvert_{\tZ^{p,\rm{main}}}}
+\]
+Then by standard intersection theory (pullback the right-hand side by $\hat\pi_{\mathbb E}^*=\hat\pi_{\mathbb E_1}^*\circ\hat\pi_{\mathbb E_2}^*$):
 \[
@@
 Let $\mathbb E=[E_0\to E_1]$ be a complex of locally free sheaves on an integral Deligne-Mumford stack $B$ such that
-$H^1(\mathbb E)$ is a torsion sheaf on $B$ and the image sheaf of $E_0\to E_1$ is locally free.
-Let $U\subseteq B$ be the complement of the support of $H^1(\mathbb E)$, and let $\mathbf{B}\subseteq h^1/h^0(\mathbb E^\vee[-1])$
-be the closure of the zero section  of the vector bundle $h^1/h^0(\mathbb E^\vee[-1]|_U)= H^0(\mathbb E|_U)^\vee$. Then
-$$0^![\mathbf{B}]=e(H^0(\mathbb E)^\vee)\in A_*(B).
+$h^1(\mathbb E)$ is a torsion sheaf on $B$ and the image sheaf of $E_0\to E_1$ is locally free.
+Let $U\subseteq B$ be the complement of the support of $h^1(\mathbb E)$, and let $\mathbf{B}\subseteq h^1/h^0(\mathbb E^\vee[-1])$
+be the closure of the zero section  of the vector bundle $h^1/h^0(\mathbb E^\vee[-1]|_U)= h^0(\mathbb E|_U)^\vee$. Then
+$$0^![\mathbf{B}]=e(h^0(\mathbb E)^\vee)\in A_*(B).
 $$
@@
 
-We apply this lemma to $\mathbb E=\R\hat{\pi}_*\mathcal L^{\otimes 5}$.
-Notice that it satisfies the hypotheses by virtue of the equations in Remark \ref{rmk:eqn}: indeed the question may be addressed locally; looking at the resolution of $\mathbb E$:
+We apply this lemma to $\R^{\bullet}\hat{\pi}_*\hL^{\otimes 5}=\mathbb E_2^\vee$ on $\tZ^{p,\rm{main}}$.
+Notice that it satisfies the hypotheses by virtue of the equations in Remark \ref{rmk:eqn}: indeed the question may be addressed locally; looking at the resolution of $\mathbb E_2^\vee$:
 \[
- \hat\pi_*\mathcal L^{\otimes 5}(\A)\to \hat\pi_*\mathcal L^{\otimes 5}(\A)\rvert_{\A}
-\]
-we deduce from the equation that the image sheaf of this map is $\pi_*\mathcal L^{\otimes 5}(\A)\rvert_{\A}\otimes\OO_{\tZ^{p,\rm{main}}}(-\Delta)$, where $\Delta$ denotes the boundary of the main component $\Delta=\tZ^{p,\rm{main}}\cap\left(\bigcup_{k\geq 2}D^k\tZp\right)$.
-Then $\hat\pi_*\mathcal L^{\otimes 5}$ is a vector bundle.
-
-\begin{lem}
+ \hat\pi_*\hL^{\otimes 5}(\A)\to \hat\pi_*\hL^{\otimes 5}(\A)\rvert_{\A}
+\]
+we deduce from the equation that the image of this map is $\pi_*\hL^{\otimes 5}(\A)\rvert_{\A}\otimes\OO_{\tZ^{p,\rm{main}}}(-\Xi)$, where $\Xi$ denotes the Cartier divisor $\Xi=\tZ^{p,\rm{main}}\cap\left(\bigcup_{k\geq 2}D^k\tZp\right)$.
+Then $\hat\pi_*\hL^{\otimes 5}$ is a vector bundle, being the kernel of a vector bundle map.
+
+\begin{lem}\label{lem:main-compo}
  If we let $i$ be the inclusion of $\tZ$ in $\tM_1(\PP^4,d)$, then:
  \[
-  i_*(c_{\rm{top}}(\hat{\pi}_*\hat{\mathcal L}^{\otimes 5})\cap[\tZ^{p,\rm{main}}])=c_{\rm{top}}({\pi}_*\mathcal L^{\otimes 5})\cap[\tM_1(\PP^4,d)^{p,\rm{main}}]
+  i_*(c_{\rm{top}}(\hat{\pi}_*\hL^{\otimes 5})\cap[\tZ^{p,\rm{main}}])=c_{\rm{top}}({\pi}_*\mathcal L^{\otimes 5})\cap[\tM_1(\PP^4,d)^{p,\rm{main}}]
  \]
@@
 \begin{proof}
- Obviously $i_*[\tZ^{p,\rm{main}}]=[\tM_1(\PP^4,d)^{p,\rm{main}}]$. On the other hand notice that on $\tZ^{p,\rm{main}}$ we have:
+ Recall that the projection $(-)^p\to (-)$ is an isomorphism on main, so it makes sense to write $i_*[\tZ^{p,\rm{main}}]=[\tM_1(\PP^4,d)^{p,\rm{main}}]$, which follows from Lemma~\ref{lem:inclusion}.
+On the other hand notice that on $\tZ^{p,\rm{main}}$ we have:
  \[
-  \pi_*\mathcal L=\hat{\pi}_*\phi_*\phi^*\hat{\mathcal L}=\hat{\pi}_*\hat{\mathcal L}
- \]
-by projection formula and since $\phi_*\OO_{\cC_{\tZ^{p,\rm{main}}}}=\OO_{\hC_{\tZ^{p,\rm{main}}}}$. The result follows then from the projection formula for Chern classes.
-\end{proof}
-
-We are left with showing that the rest of the $\mathfrak C^k$'s do not contribute to the invariants.
+  \pi_*\mathcal L=\hat{\pi}_*\phi_*\phi^*\hL=\hat{\pi}_*\hL
+ \]
+by projection formula and since $\phi_*\OO_{\cC_{\tZ^{p,\rm{main}}}}=\OO_{\hC_{\tZ^{p,\rm{main}}}}$ by Zariski connectedness theorem. The result follows from the projection formula for Chern classes.
+\end{proof}
+
+We are left with showing that the rest of the $\mathfrak C^k$ do not contribute to the invariants.
 This is essentially a dimensional computation.
-The arguments of \cite[\SS6-8]{CLpfields} may be directly applied; we shall outline them for the benefit of the reader.
+The arguments of \cite[\S\S6-8]{CLpfields} may be adapted; we shall outline them for the benefit of the reader.
 We introduce the notation $\tZ^{p,\rm{gst}}:=\bigcup_{k\geq 2} D^k\tZp$ for the union of the boundary components, and $\mathfrak C^{\rm{gst}}=\bigcup_{k\geq 2}\mathfrak C^k$.
 
-\subsection*{Step I: reduction to the case of a cone inside a vector bundle and homogeneity}
+\subsection*{Step I: reduction to the case of a cone inside a vector bundle}
+
 This section deals with removing the technicalities of working with a cone stack inside a vector bundle stack.
 
-The key point is that $\mathbb E\rvert_{\tZ^{p,\rm{gst}}}$ has locally free $h^0$ \emph{and} $h^1$, as can be seen from the equations.
-Then, when we pick a resolution by locally free sheaves $\mathbb E=[F_0\xrightarrow{d} F_1]$, the image sheaf $d(F_0)$, which is the kernel of $F_1\to h^1(\mathbb E\rvert_{\tZ^{p,\rm{gst}}})$, is really a sub-vector bundle of $F_1$.
-Then the projections:
+The key point is that $\mathbb E:=\mathbb E\rvert_{\tZ^{p,\rm{gst}}}$ has locally free $h^0$ \emph{and} $h^1$: the equations in Remark \ref{rmk:eqn} are automatically satisfied on the boundary, without imposing any condition on the fiber coordinates.
+
+When we fix a resolution by locally free sheaves $\mathbb E=[F_0\xrightarrow{d} F_1]$, the image sheaf $d(F_0)$, which is the kernel of $F_1\to h^1(\mathbb E)$, is a subbundle of $F_1$.
+Consider the projections:
 \[
- \beta\colon F_1\to h^1/h^0(\mathbb E) \quad \text{and} \quad \beta'\colon F_1\to \tilde{V}:=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5}\oplus\widehat{\mathcal P})
-\]
-are both flat.
-The cone stack $\mathfrak C^{\rm{gst}}$ can be descended to a cone $C^{\rm{gst}}$ by means of taking the quotient of $\beta^{-1}\mathfrak C^{\rm{gst}}$ by the free action of $d(F_0)$; $C^{\rm{gst}}$ should then be thought of as the coarse moduli of $\mathfrak C^{\rm{gst}}$.
-Recall that the cosection $\sigma$ is induced by a cosection $\sigma_1$ of $\tilde V$ (see Eq.
-\eqref{eqn:cosection}).
-\marginpar{rewrite what they are}It follows from the commutativity of localised Gysin pullback with flat pullback that:
+ \beta\colon F_1\to h^1/h^0(\mathbb E) \quad \text{and} \quad \beta'\colon F_1\to \tilde{V}:=\R^1\hat{\pi}_*(\hL^{\oplus 5}\oplus\widehat{\mathcal P});
+\]
+the second is also flat since $d(F_0)$ is a vector bundle.
+The cone stack $\mathfrak C^{\rm{gst}}$ can be descended to a cone $C^{\rm{gst}}\subseteq \tilde{V}$ by taking the quotient of $\beta^{-1}\mathfrak C^{\rm{gst}}$ by the free action of $d(F_0)$; $C^{\rm{gst}}$ should then be thought of as the coarse moduli of $\mathfrak C^{\rm{gst}}$.
+Recall that we started with a cosection $\sigma_1$ of $V$ (see Eq.
+\eqref{eqn:cosection}) and pulled it back to all relevant spaces.
+It follows from the commutativity of localised Gysin pullback with flat pullback that:
 \[
- 0^!_{h^1/h^0(\mathbb E),\sigma}(\mathfrak C^{\rm{gst}})= 0^!_{\tilde V,\sigma_1}(C^{\rm{gst}})
+ s^!_{h^1/h^0(\mathbb E),\tilde\sigma_1}[\mathfrak C^{\rm{gst}}]= s^!_{\tilde V,\tilde\sigma_1}[C^{\rm{gst}}]
 \]
@@
 
-They then introduce the notion of \emph{homogeneity} for substacks of $\tilde V$: write 
-\[\tilde V=\tilde V_1\oplus\tilde V_2\;\;\text{ with} \;\;\tilde V_1=\R^1\hat{\pi}_*(\hat{\mathcal L}^{\oplus 5})\;\; \text{and}\;\; \tilde V_2=\R^1\hat{\pi}_*(\widehat{\mathcal P}),\]
+\subsection*{Step II: from cosection localised to standard Gysin map}
+Recall that the construction of a localised virtual class refines the standard one, namely:
+\[\iota_*\virloc{Y}=\vir{Y},\]
+where $\iota\colon Y(\sigma)\hookrightarrow Y$ is the degeneray locus of the cosection.
+In particular, when $Y$ itself is a proper Deligne-Mumford stack, the degree of the localised virtual class can be computed after pushing it forward to $Y$.
+
+Then to compute $s^!_{\tilde V,\tilde\sigma_1}[C^{\rm{gst}}]$ we are going to compactify $\tZ^{p,\rm{gst}},$ extend the cone, the vector bundle and the cosection to it, and then make use of the fact we just recalled.
+
+Since $\tZ^{p,\rm{gst}}\cong\operatorname{Vb}_{\tZ^{\rm{gst}}}\left(\hat{\pi}_*\widehat{\mathcal P}\right)$, we take its standard copactification:
+\[\bar{\gamma}\colon \overline{\Z}^{p,\rm{gst}}:=\PP\left(\hat{\pi}_*\widehat{\mathcal P}\oplus \OO_{\tZ^{\rm{gst}}}\right)\to \tZ^{\rm{gst}}.\]
+We want to pullback the cosection:
+\[\sigma_{1|(u,\psi)}(\mathring{x},\mathring{p})=\mathring{p}\w(u)+\psi\sum_{i=0}^4\partial_i\w(u)\mathring{x}_i;\]
+noticing that in the compactification the $p$-field $\psi$ can go to infinity, we define the vector bundles on $\oZp$:
+\[\tilde{V}^{\rm{cpt}}_1=\bar{\gamma}^*V_1(-D_{\infty}),\qquad \tilde{V}^{\rm{cpt}}_2=\bar{\gamma}^*V_2.\]
+We are now able to extend the cosection and get:
+\[\bar{\sigma}\colon \tilde{V}^{\rm{cpt}}=\tilde{V}^{\rm{cpt}}_1\oplus \tilde{V}^{\rm{cpt}}_2\to\OO_{\oZp}. \]
+
+ The compatibility of $\tilde\sigma$ with $\bar\sigma$, and the fact that $\oZp$ is proper, together with the observation at the beginning of this section, explain the following:
+ \begin{prop}
+ Let $\iota_{!}\colon Z_*(\tilde{V}(\widetilde{\sigma}))\to Z_*(\tilde{V}^{\rm{cpt}})$ be defined by 
+ $\iota_{!}[C]=[\overline{C}].$ And $i\colon D(\widetilde{\sigma})\to \tZ^{\rm{gst}}$ the inclusion. Then
+ \[\bar{\gamma}_*\circ s^{!}_{\tilde{V}^{\rm{cpt}}}\circ\iota_{!}=i_*\circ s^{!}_{\tilde\sigma,\rm{loc}}\colon  Z_*(\tilde{V}(\widetilde{\sigma}))\to A_*(\tilde{Z}^{\rm{gst}}).\]
+ \end{prop}
+ See \cite[Proposition~6.4]{CL} for full details.
+
+ Furthermore, from functoriality of Gysin pullbacks and the deformation to the normal cone it follows that:
+ \[s^!_{\tilde V^{\rm{cpt}}}[\overline C]=s^!_{\tilde V_2^{\rm{cpt}}}\circ s^!_{\tilde V_1^{\rm{cpt}}}[N_{\overline C\cap 0\oplus\tilde V_2^{\rm{cpt}}}\overline C].\]
+
+ \subsection*{Step III: homogeneous cones}
+Chang an Li introduce the notion of \emph{homogeneity} for substacks of $\tilde V$ on $\tZ^{p,\rm{gst}}$: write 
+\[\tilde V=\tilde V_1\oplus\tilde V_2\;\;\text{ with} \;\;\tilde V_1=\R^1\hat{\pi}_*(\hL^{\oplus 5})\;\; \text{and}\;\; \tilde V_2=\R^1\hat{\pi}_*(\widehat{\mathcal P}),\]
  and $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ the projection.
 Since $\tZ^{p,\rm{gst}}$ is the total space of a line bundle over $\tZ^{\rm{gst}}$, it comes with a natural $\Gm$-action on the fibers of $\gamma$.
-Moreover, since
+Moreover, since the highest pushforwards satisfy cohomology and base-change:
  \[\tilde V_i=\gamma^*V_i\]
- \marginpar{say few words, that is not the definition of $\tilde V_i$ but a property (Lemma 6.1)}
- for the corresponding vector bundles $V_i$ on $\tZ^{\rm{gst}}$, the total space of $\tilde V_i$ can be endowed with a $\Gm$-action that makes the projection to $\tZ^{p,\rm{gst}}$ equivariant.
-A closed substack of $\tilde V$ is $0$-homogeneous if it is the pullback of a closed substack of $V$ along $\gamma$.
-In facts the $\tilde V_i$'s can be endowed with different $\Gm$ actions that make the projection to $\tZ^{p,\rm{gst}}$ equivariant by twisting with two characters of $\Gm$, one for each $\tilde V_i$; this defines the concept of $(l_1,l_2)$-homogeneous substacks of $\tilde V$.
+ for the corresponding vector bundles $V_i$ on $\tZ^{\rm{gst}}$, so the total space of $\tilde V_i$ can be endowed with a $\Gm$-action that makes the projection to $\tZ^{p,\rm{gst}}$ equivariant.
+We say that a closed substack of $\tilde V$ is $0$-homogeneous if it is the pullback of a closed substack of $V$ along $\gamma$.
+In fact there are different $\Gm$-actions on $\tilde V$ that make the projection to $\tZ^{p,\rm{gst}}$ equivariant: namely, we can twist the trivial action on the fibers by two characters of $\Gm$, one for each $\tilde V_i$.
+Then we say that a substack of $\tilde V$ is $(l_1,l_2)$-homogeneous if it is invariant with respect to such an action.
 Here is how we are going to use the homogeneity:
@@
 \begin{lem}
- Let $\tilde C\subseteq \tilde V$ be an $(l_1,l_2)$-homogeneous sub\emph{cone} of $\tilde V$; then the cone $\tilde C\cap(0\oplus\tilde V_2)$ is pulled back from a cone in $V_2$.
+ Let $C\subseteq \tilde V$ be an $(l_1,l_2)$-homogeneous sub\emph{cone} of $\tilde V$; then the cone $\overline{C}\cap(0\oplus\tilde V_2^{\rm{cpt}})$ is pulled back from a cone in $V_2$ on $\tZ^{\rm{gst}}$.
 \end{lem}
 \begin{proof}
- Locally we may pick coordinates $t$ on the fibers of $\gamma$, $x_1,\ldots,x_5$ on the fibers of $\tilde V_1$, and $y_1,\ldots,y_{5d+5}$ on the fibers of $\tilde V_2$, such that the ideal of $\tilde C$ is generated by homogeneous polynomials $p_j$ in $t^{-l_1}x_i$ and $t^{-l_2}y_i$.
-The ideal of $\tilde C\cap(0\oplus\tilde V_2)$ is then given by $\langle x_1,\ldots, x_5,p_j(0,t^{-l_2}y)\rangle_j$, where $p_j(0,t^{-l_2}y)$ results from setting $x_i=0$ in $p_j$; notice now that $\tilde C$ being a cone, it is invariant by scalar multiplication on the fibers of $\tilde V$, so we may as well say that $\tilde C\cap(0\oplus\tilde V_2)$ is cut by the ideal $\langle x_1,\ldots, x_5,p_j(0,y)\rangle_j$.
-This makes it clear that $\tilde C\cap(0\oplus\tilde V_2)$ is pulled back from $(0\oplus V_2)$ on $\tZ^{\rm{gst}}$.
-\end{proof}
-
-Finally Chang and Li point out that the coarse moduli cone $C^{\rm{gst}}$ is $(0,1)$-homogeneous \cite[Proposition 6.7]{CLpfields}: recalling the interpretation of $\Mone{1}{\PP^4}{d}^p$ as an open inside the cone of sections of $\mathcal V=\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ over $\hC_{\mathfrak{Pic}_1^{(1)}}$, the desired $\Gm$-action on the fibers of $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ is induced by endowing $\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ with the $\Gm$-action that is trivial on the fibers of every copy of $\rm{Vb}(\mathcal L)$, and has character $1$ on those of $\rm{Vb}(\widehat{\mathcal P})$, with an underlying trivial action on $\mathfrak{Pic}_1^{(1)}$.
+ Locally we may pick coordinates $t$ on the fibers of $\gamma$, $x_1,\ldots,x_5$ on the fibers of $\tilde V_1^{\rm{cpt}}$, and $y_1,\ldots,y_{5d+5}$ on the fibers of $\tilde V_2^{\rm{cpt}}$, such that the ideal of $\overline{C}$ is generated by separately homogeneous polynomials $p_j$ in $t^{-l_1}x_i$ and $t^{-l_2}y_i$.
+The ideal of $\overline{C}\cap(0\oplus\tilde V_2^{\rm{cpt}})$ is then given by $\langle x_1,\ldots, x_5,p_j(0,t^{-l_2}y)\rangle_j$, where $p_j(0,t^{-l_2}y)$ results from setting $x_i=0$ in $p_j$.
+Notice now that $\overline{C}$ being a cone, it is invariant by scalar multiplication on the fibers of $\tilde V^{\rm{cpt}}$, so we may as well say that $\overline{C}\cap(0\oplus\tilde V_2^{\rm{cpt}})$ is cut by the ideal $\langle x_1,\ldots, x_5,p_j(0,y)\rangle_j$.
+This makes it clear that $\overline{C}\cap(0\oplus\tilde V_2^{\rm{cpt}})$ is pulled back from $(0\oplus V_2)$ on $\tZ^{\rm{gst}}$.
+\end{proof}
+
+Finally Chang and Li point out that the coarse moduli cone $C^{\rm{gst}}$ is $(0,1)$-homogeneous \cite[Proposition 6.7]{CLpfields}.
+%recalling the interpretation of $\Mone{1}{\PP^4}{d}^p$ as an open inside the cone of sections of $\mathcal V=\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ over $\hC_{\mathfrak{Pic}_1^{(1)}}$, the desired $\Gm$-action on the fibers of $\gamma\colon \tZ^{p,\rm{gst}}\to\tZ^{\rm{gst}}$ is induced by endowing $\rm{Vb}(\mathcal L^{\oplus 5}\oplus \widehat{\mathcal P})$ with the $\Gm$-action that is trivial on the fibers of every copy of $\rm{Vb}(\mathcal L)$, and has character $1$ on those of $\rm{Vb}(\widehat{\mathcal P})$, with an underlying trivial action on $\mathfrak{Pic}_1^{(1)}$.
 This influences the obstruction theory  $\R^\bullet\hat\pi_*\left(\mathfrak e^* T_{\mathcal V/\hC_{\mathfrak{Pic}_1^{(1)}}}\right)$ of $\Mone{1}{\PP^4}{d}^p$ in the obvious way, and consequently $\mathbb E$ on $\tZp$.
 
-\begin{comment}{
-We may notice that $(\Z^p)^{\text{main},\circ}\to\XP$ is smooth onto its image, which is an open substack; furthermore on this open the relative tangent is represented by $\hat\pi_*\hL^{\oplus 5}$, and $\R^1\hat\pi_*\hL^{\oplus 5}=\hat\pi_*(\hat\omega\otimes\hL^{\otimes -5})=0$.
-Let $E^\bullet=\R^\bullet\hat\pi_*(\hL^{\oplus 5}\oplus \hat\omega\otimes\hL^{\otimes -5})$ denote the dual perfect obstruction theory of $\Z^p\to \XP$.
-Then the intrinsic normal cone of $\Z^p\to \XP$ splits into:
-\begin{itemize}
-\item the closure of the zero section of $h^1/h^0(E^\bullet)_{|\text{main},\circ}$, which we shall name $\mathfrak C^{\text{main}}$;
-\item other components supported on the boundary, which we should accordingly name $\mathfrak C^k$ ($k\geq 2$).
-\end{itemize}}
-\end{comment}
-\subsection*{Step II: from cosection localized to standard Gysin map}
-Recall that when we are working on a proper DM stack $\pazocal M$ endowed with a perfect obstruction theory and admitting a cosection $\sigma$, then the cosection localized Gysin map can be reduced to the ordinary Gysin map, i.e.
-\[\iota_*\circ 0^{!}_{E,\sigma}=0_E^{!}\circ \tilde{\iota}\;\;\;\text{where}\;\;\iota\colon D(\sigma)\hookrightarrow\pazocal M,\;\;\tilde{\iota}\colon E(\sigma)\hookrightarrow E\]
-and $E$ is the vector bundle containing the cone.
-
-Then to compute $0^!_{\tilde V,\sigma_1}(C^{\rm{gst}})$ we plan to compactify $\tZ^{p,\rm{gst}},$ extend the cone, the vector bundle and the section over it and then make use of the fact we just recalled.
-
-Since $\tZ^{p,\rm{gst}}\cong\operatorname{Tot}_{\tZ^{\rm{gst}}}\left(\R^1\hat{\pi}_*\widehat{\mathcal P}\right)$ we compactify considering
-\[\overline{\gamma}\colon \overline{\tZ^{p,\rm{gst}}}:=\PP\left(\R^1\hat{\pi}_*\widehat{\mathcal P}\oplus \OO_{\tZ^{\rm{gst}}}\right)\to \tZ^{\rm{gst}}\]
-and extend $\tilde{V}_1,\tilde{V}_2$ via:
-\[\tilde{V}^{\rm{cpt}}_1=\overline{\gamma}V_1(-D_{\infty}),\qquad \tilde{V}^{\rm{cpt}}_2=\overline{\gamma}V_2.\]
-Finally, let us extend the cosection as well. From the cosection $\sigma$ defined by \ref{eqn:cosection} we clearly get a cosection on $\Z^p$ by pull-back and again a 
-\[\widetilde{\sigma}\colon \pazocal Ob_{\tZp}\to\OO_{\tZp} \]
- on the blow-up. Let us denote by $\widetilde{\sigma}_{\rm{gst}}$ its restriction to $\tZ^{\rm{gst}}.$
- Writing down what $\widetilde{\sigma}_{\rm{gst}}$ looks like on points\cite[Lemma~6.2]{CL}, we see that it extend to a homomorphism of vector bundles:
- \[\overline{\sigma}\colon\tilde{V}^{\rm{cpt}}=\tilde{V}^{\rm{cpt}}_1\oplus \tilde{V}^{\rm{cpt}}_2\to \overline{\tZ^{p,\rm{gst}}}.\]
- \begin{prop}
- Let $\iota_{!}\colon Z_*(\tilde{V}(\widetilde{\sigma}_{\rm{gst}}))\to Z_*(\tilde{V}^{\rm{cpt}})$ be defined by 
- $\iota_{!}[C]=[\overline{C}].$ And $i\colon D(\widetilde{\sigma}_{\rm{gst}})\to \tilde{Z}_{\rm{gst}}$ the inclusion. Then
- \[\overline{\gamma}_*\circ 0^{!}_{\tilde{V}^{\rm{cpt}}}\circ\iota_{!}=i\circ 0^{!}_{\widetilde{\sigma}_{\rm{gst}},\rm{loc}}\colon  Z_*(\tilde{V}(\widetilde{\sigma}_{\rm{gst}}))\to A_*(\tilde{Z}_{\rm{gst}}).\]
- \end{prop}
- This follows essentially from the property of cosection localized cycles recalled at the beginning of the section; see \cite[Proposition~6.4]{CL} for full details.
- \subsection*{Step III: reduction of the support of the cone}
+\subsection*{Step IV: reduction of the support of the cone}
 We now explain a key technical lemma which will enable us to show that $C^{\rm{gst}}$ pushes forward to zero under a suitably defined morphism.
-It is basically reducing the support of $C^{\rm{gst}}\cap 0\oplus\tilde V_2$ to a manageable substack of $\tilde V_2$, that is the union of the zero-section (i.e.
-$\tZp$) and a sub-line bundle of $\tilde V_2$ supported on $\tilde \Delta=\tZ^{p,\rm{main}}\cap\tZ^{p,\rm{gst}}$.
-Even better, using the homogeneity we can show that such a line bundle comes from $\Delta=\tZ^{\rm{main}}\cap\tZ^{\rm{gst}}$.
-This is \cite[Proposition 7.1]{CLpfields}.
+It is basically reducing the support of $\overline{C^{\rm{gst}}}\cap 0\oplus\tilde{V}_2^{\rm{cpt}}$ to a manageable substack of $\tilde{V}_2^{\rm{cpt}}$, that is the union of the zero-section (i.e.
+$\oZp$) and a line subbundle of $\tilde{V}_2^{\rm{cpt}}$ supported on $\widetilde{\Xi}=\tZ^{p,\rm{main}}\cap\tZ^{p,\rm{gst}}$.
+Even better, using the homogeneity we can show that such a line bundle comes from $\Xi=\tZ^{\rm{main}}\cap\tZ^{\rm{gst}}$.
+We give a sketch of the proof, see \cite[Proposition 7.1]{CLpfields} for more details.
 \begin{lem}
- There is a sub-line bundle $F$ of $V_2\rvert_\Delta$ such that:
+ There is a line subbundle $F$ of $V_2\rvert_\Xi$ such that:
  \[
-  C^{\rm{gst}}\cap 0\oplus\tilde V_2\subseteq 0_{\tilde V_2}\cup \tilde F:= \tZ^{p,\rm{gst}}\cup \gamma^* F
- \]
-\end{lem}
-First they use the fact that there is a triple of compatible obstruction theories for the triangle:
-\bcd
-\tZp \ar[rr]\ar[dr,"\gamma"] & & \tZ \ar[dl] \\
-& \XP &
-\ecd
-such that their restrictions to $\tZ^{p,\rm{gst}}$ have locally free $h^0$ and $h^1$. To the effect that by taking $h^1$ of the dual obstruction theories we obtain a commutative diagram:
+  \overline{C^{\rm{gst}}}\cap 0\oplus\tilde{V}_2^{\rm{cpt}}\subseteq 0_{\tilde{V}_2^{\rm{cpt}}}\cup \tilde F:= \oZp\cup \bar\gamma^* F
+ \]
+\end{lem}
+It is enough to show this before taking the closure. First they use the fact that there is a triple of compatible obstruction theories for the triangle:
+\bcd
+\tZp \ar[rr,"\gamma"]\ar[dr] & & \tZ \ar[dl] \\
+& \widetilde{\XP} &
+\ecd
+such that their restrictions to $\tZ^{p,\rm{gst}}$ have locally free $h^0$ and $h^1$. By taking $h^1$ of the dual obstruction theories we obtain a commutative diagram:
 \bcd
 h^1(\mathbb L_{\tZp/\tZ}^\vee\rvert_{\tZ^{p,\rm{gst}}}) \ar[r]\ar[d] & h^1(\mathbb L_{\tZp/\XP}^\vee\rvert_{\tZ^{p,\rm{gst}}})\ar[r]\ar[d] &h^1(\gamma^*\mathbb L_{\tZ/\XP}^\vee\rvert_{\tZ^{p,\rm{gst}}})\ar[d] \\
-\tilde V_2\ar[r,"i_2"] & \tilde V_1\oplus\tilde V_2 \ar[r,"\pr_1"] & \tilde V_1
+\tilde{V}_2\ar[r,"i_2"] & \tilde{V}_1\oplus\tilde{V}_2 \ar[r,"\pr_1"] & \tilde{V}_1
 \ecd
 The vertical arrows are injective by the definition of an obstruction theory, and the bottom triangle is exact.
-Notice that $0\oplus\tilde V_2$ is precisely the kernel of $\pr_1$.
-It follows that, in order to understand the support of $C^{\rm{gst}}\cap 0\oplus\tilde V_2$, it is enough to study that of $N$, where $N$ is the coarse moduli cone of $\mathfrak C_{\tZp/\tZ}$, living in the upper left corner of the above diagram.
+Notice that $0\oplus\tilde{V}_2$ is precisely the kernel of $\pr_1$.
+It follows that, in order to understand the support of $C^{\rm{gst}}\cap 0\oplus\tilde{V}_2$, it is enough to study that of $N$, where $N$ is the coarse moduli cone of $\mathfrak C_{\tZp/\tZ}$, living in the upper left corner of the above diagram.
 
 This is an easier task, since we know that $\tZp/\tZ$ is a line bundle on $\tZ^{\rm{gst}}$ and an isomorphism on $\tZ^{\rm{main},\circ}$.
-Hence we can always find a local chart $S\to \tZ$ such that the following diagram holds:
-\bcd
-\tZp\ar[d] & T\ar[l]\ar[ld,phantom,"\Box"]\ar[d]\ar[r,hook,"V(\zeta t)"] & S\times\Aaff^1_t\ar[ld] \\
+Hence we can always find a local chart $S\to \tZ$ and a diagram as follows:
+\bcd
+\tZp\ar[d] & T\ar[l]\ar[ld,phantom,"\Box"]\ar[d]\ar[r,hook,"V(\tilde\zeta t)"] & S\times\Aaff^1_t\ar[ld] \\
 \tZ & S\ar[l,"\acute{e}t"] &
 \ecd
-where $\zeta$ is a local equation for the boundary.
-Then $\tau^{\geq-1}\mathbb L_{\tZp/\tZ}\rvert_T=[I/I^2\xrightarrow{\delta}\Omega_{\Aaff^1_S/S}]$; $I$ is generated by $\zeta t$, whose image under $\delta$ is $\zeta \rm{d}t$, which restricts to $0$ on $\tZ^{p,\rm{gst}}\times_{\tZp}T=\{\zeta=0\}$.
-So the action is trivial, and in fact the restriction of the coarse moduli cone is precisely $\Spec_{T^{\rm{gst}}}\operatorname{Sym}^{\bullet} I/I^2$, which is a line bundle supported on $\tilde \Delta\times_{\tZp}T$ and trivial otherwise.
-By gluing different charts we get the line bundle $\tilde F$ on $\tilde \Delta$.
-
-The last part of the statement, namely that $\tilde F$ descends to a line bundle $F$ on $\Delta$ is proved by homogeneity: the normal cone of $\tZp/\tZ$ is homogeneous with respect to the $\Gm$-action with character $1$ on the fibers of $\tilde V_2\to \tZ^{p,\rm{gst}}$, but being a cone it is $0$-homogeneous as well (see the above discussion of homogeneity), so it is $\gamma^*F$ for some line bundle $F$ on $\Delta\subseteq \tZ$.
-
-\subsection*{Step IV: pushing forward to zero} Recall from the previous sections that we need to show that the degree of the following class is $0$:
+where $\tilde\zeta$ is a local equation for the boundary.
+Then $\tau^{\geq-1}\mathbb L_{\tZp/\tZ}\rvert_T=[I/I^2\xrightarrow{\delta}\Omega_{\Aaff^1_S/S}]$; $I$ is generated by $\tilde\zeta t$, whose image under $\delta$ is $\tilde\zeta \rm{d}t$, which restricts to $0$ on $\tZ^{p,\rm{gst}}\times_{\tZp}T=\{\tilde\zeta=0\}$.
+So the action is trivial, and the coarse moduli cone is precisely $\Spec_{T^{\rm{gst}}}\operatorname{Sym}^{\bullet} I/I^2$, which is a line bundle supported on $\widetilde{\Xi}\times_{\tZp}T$ and trivial otherwise.
+By gluing different charts we get the line bundle $\tilde F$ on $\widetilde{\Xi}$.
+
+The last part of the statement, namely that $\tilde F$ descends to a line bundle $F$ on $\Xi$ is proved by homogeneity: the normal cone of $\tZp/\tZ$ is homogeneous with respect to the $\Gm$-action with character $1$ on the fibers of $\tilde{V}_2\to \tZ^{p,\rm{gst}}$, but being a cone it is $0$-homogeneous as well (see the above discussion of homogeneity), so it is $\bar\gamma^*F$ for some line bundle $F$ on $\Xi\subseteq \tZ$.
+
+\subsection*{Step V: the boundary pushes forward to zero} Recall that we need to show that the degree of the following class is $0$:
 \[
- 0_{\overline{V}}^![\overline C^{\rm{gst}}]=0_{\overline V_2}^!(0_{\overline{V}_1}^![\overline C^{\rm{gst}}])=0_{\overline V_2}^!([N_{\overline C^{\rm{gst}}\cap (0\oplus \overline V_2)}\overline C^{\rm{gst}}])
-\]
-\bcd
-? \ar[r]\ar[d] & X\ar[d] & \\
-\overline C^{\rm{gst}}\cap (0\oplus \overline V_2) \ar[r]\ar[d] & V_2\ar[r]\ar[d] & X\ar[d] \\
-\overline C^{\rm{gst}} \ar[r] & \overline V\ar[r] & \overline V_1
-\ecd
-We know from the previous section that the cycle in the last bracket can be split into two parts, one (call it $N_1$) supported on a sub-line bundle of $\overline V_2$ on $\tilde\Delta$, the other one (call it $N_2$) supported on the zero section of $\overline V_2$.
-
-\begin{lem}
- Both $N_1$ and $N_2$ are $5d+1$-dimensional cycles, and $\deg(0_{\overline V_2}^![N_i])=0$ for $i=1,2$.
+ s_{\tilde{V}^{\rm{cpt}}}^![\overline {C^{\rm{gst}}}]=s_{\tilde{V}_2^{\rm{cpt}}}^!\circ s_{\tilde{V}_1^{\rm{cpt}}}^![N_{\overline {C^{\rm{gst}}}\cap (0\oplus {\tilde{V}_2^{\rm{cpt}}})}\overline {C^{\rm{gst}}}]
+\]
+
+It follows from the previous section that $s_{\tilde{V}_1^{\rm{cpt}}}^![N_{\overline {C^{\rm{gst}}}\cap (0\oplus {\tilde{V}_2^{\rm{cpt}}})}\overline {C^{\rm{gst}}}]$ can be represented by the sum of two cycles, one (call it $N_1$) supported on a line subbundle of $\tilde{V}_2^{\rm{cpt}}$ on $\widetilde\Xi$, the other one (call it $N_2$) supported on the zero section of $\tilde{V}_2^{\rm{cpt}}$.
+
+\begin{lem}\label{lem:boundary}
+ Both $N_1$ and $N_2$ are $5d+1$-dimensional cycles, and for $i=1,2$: \[\deg(s_{\tilde{V}_2^{\rm{cpt}}}^![N_i])=0.\]
 \end{lem}
@@
 The coarse moduli cone has then dimension $5d+6$, as can be argued from Lemma \ref{lem:open_cones}.
-$\overline V_1\rvert_{\tZ^{p,\rm{gst}}}$ has rank $5$, so $0_{\overline{V_1}}^![\overline C^{\rm{gst}}]$ is represented by a cycle of dimension $5d+1$.
+$\tilde{V}_1^{\rm{cpt}}\rvert_{\oZp}$ has rank $5$, so $s_{\tilde{V}_1^{\rm{cpt}}}^![\overline {C^{\rm{gst}}}]$ is represented by a cycle of dimension $5d+1$.
 We shall exploit the commutativity of Gysin pullback with proper pushforward.
 
-For $N_1$ we conclude easily from the above facts, since $\deg(0_{\overline V_2}^![N_1])=\deg(0_{V_2}^!\gamma_*[N_1])$, but $\gamma_*[N_1]\in A_{5d+1}(F)$ must be trivial, since $F$ has dimension $5d$, being a line bundle on $\Delta$ which is a divisor in $\Z^{\rm{main}}$.
-
-On the other hand $N_2\subseteq \overline{V}_2$ admits a further splitting into $N_{2,\mu}\subseteq \overline V_{2,\mu}$ according to the number $k$ of rational tails of the generic element of the boundary component on which they are supported and a partition of the degree $\mu\vdash d$ in $k$ many parts.
+For $N_1$ we conclude easily from the above facts, since $\deg(s_{\tilde{V}_2^{\rm{cpt}}}^![N_1])=\deg(s_{V_2}^!\bar{\gamma}_*[N_1])$, but $\bar{\gamma}_*[N_1]\in A_{5d+1}(F)$ must be trivial, since $F$ has dimension $5d$, being a line bundle on $\Xi$ which is a divisor in $\Z^{\rm{main}}$.
+
+On the other hand $N_2\subseteq \tilde{V}_2^{\rm{cpt}}$ admits a further splitting into $N_{2,\mu}\subseteq \tilde{V}_{2,\mu}^{\rm{cpt}}$ according to the component $D^{\mu}\oZp$ on which they are supported, with $\mu\vdash d$ in $k$ parts.
 There exists a comparison morphism:
-\[\beta_{\mu}\colon D^\mu\tZp\to D^\mu\Z=D^\mu\oM_1(\PP^4,d)\to \pazocal W_{\mu}\]
-where $\pazocal W_{\mu}\subseteq\prod_{i=1}^k \M{0}{1}{\PP^4}{d_i}$ is defined by requiring that the maps do attain the same value at the markings.
-$\beta_{\mu}$ is obtained by forgetting the $p$-field,  the Vakil-Zinger blow-up and the $k$-pointed elliptic curve contracted by the map to $\PP^4$.
-This has the nice property that $\overline V_2$ is the pullback along $\beta_{\mu}$ of a vector bundle on $\pazocal W_{\mu}$.
-Namely the universal curve over each factor can be glued to the other ones along the given sections, producing a genus $0$ non-Gorenstein (unless $k=2$) singularity to which the universal maps to $\PP^4$ descend by the property of pushouts:
+\[\beta_{\mu}\colon D^\mu\oZp\to D^\mu\Z=D^\mu\oM_1(\PP^4,d)\to \pazocal W_{\mu}\]
+where $\pazocal W_{\mu}:=\prod_{i=1}^k \M{0}{1}{\PP^4}{d_i}\times_{(\PP^r)^k}\PP^r$.
+The map $\beta_{\mu}$ is given by forgetting the $p$-field,  the Vakil-Zinger blow-up and the $k$-pointed elliptic curve contracted by the map to $\PP^4$.
+This has the nice property that $\tilde{V}_2^{\rm{cpt}}$ is the pullback along $\beta_{\mu}$ of a vector bundle on $\pazocal W_{\mu}$.
+First construct a connected curve $\overline \cC_\mu$ by gluing the universal curve over each factor along the given sections, producing a genus $0$ non-Gorenstein (unless $k=2$) singularity to which the universal maps to $\PP^4$ descend by the property of pushouts:
 \bcd
@@
 \ecd
-The sheaf $V_\mu:=\bar\pi_*\bar f^*\OO_{\PP^4}(5)$ is indeed a vector bundle of rank $5d+1$ on $\pazocal W_\mu$, as can be checked by Riemann-Roch and the normalisation sequence (the topological type of the curve is constant near the singularity), and $\overline V_{2,\mu}=\beta_{\mu}^* V_\mu$.
+Notice now that the sheaf $V_\mu:=\bar\pi_*\bar f^*\OO_{\PP^4}(5)$ is a vector bundle of rank $5d+1$ on $\pazocal W_\mu$, as can be checked by Riemann-Roch and the normalisation sequence, and $\tilde{V}_{2,\mu}^{\rm{cpt}}=\beta_{\mu}^*(V_\mu^\vee)$.
 Finally the actual dimension of $\pazocal W_\mu$ is $5d+4-2k <5d+1$ for $k\geq 2$ by Kleiman-Bertini theorem, so $\beta_{\mu,*}[N_{2,\mu}]=0$.
+
+\end{proof}
+\begin{proof}(\emph{Main Theorem})
+For the benefit of the reader we summarise here the key results which allow us to conclude:
+\begin{itemize}
+\item $p$-fields give the same invariants as the quintic up to a sign, see Theorem \ref{thm:p-fields-quintic}: \[\deg[\Mone{1}{\PP^4}{d}^p]^{\rm{vir}}_{\rm{loc}}= (-1)^{5d}\deg[\Mone{1}{X}{d}]^{\rm{vir}}.\]
+\item $\Zp$ and $\Mone{1}{\PP^4}{d}^p$ are virtually birational, see Corollary \ref{cor:Zp-vs-pfields}:
+\[\deg\virloc{\Zp}=\deg\virloc{\Mone{1}{\PP^4}{d}^p}.\]
+\item The desingularisation $\tZp\to \Zp$ does not alter the invariants, see Lemma \ref{lem:tilding} \[\deg\virloc{\tZp}=\deg\virloc{\Zp}.\]
+\item The main component of $\tZp$ contributes with the reduced invariants up to a sign, while the boundary is numerically irrelevant, see Lemmas \ref{lem:main-compo} and \ref{lem:boundary}:
+\[\deg\virloc{\tZp}=(-1)^{5d}\deg\left(c_{\rm{top}}(\tilde\pi_*\tilde f^*\OO_{\PP^4}(5)\cap[\widetilde{\pazocal M}_1(\PP^4,d)^{\rm{main}}]\right).\]
+\end{itemize}
 
@@
 
+\bigskip\bigskip
+
+\noindent Luca Battistella\\
+Department of Mathematics, Imperial College London \\
+\texttt{l.battistella14@imperial.ac.uk}\\
+
+\noindent Francesca Carocci \\
+Department of Mathematics, Imperial College London \\
+\texttt{f.carocci14@imperial.ac.uk}\\
+
+\noindent Cristina Manolache \\
+Department of Mathematics, Imperial College London \\
+\texttt{c.manolache@imperial.ac.uk}
+
 \end{document}
